### 2017-01-19 docs/language_constraint.tex
Working version

%
% File acl2017.tex
%
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2017}
\usepackage{times}
\usepackage{latexsym}

\usepackage{url}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{???}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
In this paper we show that writing tasks that impose constraints on the writer result in the author adopting a  different writing style compared to tasks that do not.
As a case study, we experiment with a recently published machine reading task: the story cloze task \cite{Mostafazadeh:2016}. 
In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
We show that a linear classifier, which applies only simple style features, such as sentence length and PoS counts, obtains state-of-the-art results on the task,
substantially higher than sophisticated sequence-to-sequence models.
Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the constraint put on the authors. 
Our results indicate that such constraints dramatically affect the way people write. 
They also suggest that careful attention to the instructions given to the authors needs to taken when designing new NLP tasks.

  \end{abstract}

% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2017}
\bibliography{acl2017}
\bibliographystyle{acl_natbib}

\end{document}

### 2017-01-19 docs/language_constraint.tex
Introduction V1

@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
+\newcommand{\secref}[1]{Section~\ref{ssec:#1}}
+\newcommand{\isection}[2]{\section{#1}\label{ssec:#2}}
+\newcommand{\isectionb}[1]{\section{#1}\label{ssec:#1}}
 
@@
 In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
-We show that a linear classifier, which applies only simple style features, such as sentence length and PoS counts, obtains state-of-the-art results on the task,
-substantially higher than sophisticated sequence-to-sequence models.
+We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, obtains state-of-the-art results on the task,
+substantially higher than sophisticated deep learning models.
 Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the constraint put on the authors. 
@@
   \end{abstract}
+\section{Introduction}
+Writing style is defined as the choice of words, spelling, grammar and punctuation made by the author.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
+It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, native language \cite{Koppel:2005}, or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010} and whether it is sarcastic \cite{Tsur:2010}.
+In this paper we study to what extent is writing style affected by more intricate factors, such as the type of constraints put on the author.
+
+As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
+This task was created by having authors write five-sentence self-contained stories.
+Following, a subset of the the stories was given to another group of authors, who were shown only the first four sentences of each story, 
+and were asked to write two one-sentence endings for it: a {\it correct} ending, and a {\it wrong} ending.
+The goal of the task is to determine which of the endings is the correct one.
+
+Interestingly, although originally intended to be a machine reading task, the compliation of this task raises several research questions which seem to differ from the original intent of the designers.
+First, do authors use different style when asked to write a {\it correct} sentence, compared to a {\it wrong} sentence?
+Second, do authors use different style when writing the ending as part of a five sentence story, compared to reading four sentences, and then writing a standalone (correct) ending?
+
+We show that the answer to both of these questions is positive. 
+We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and PoS counts. 
+We show that on a balanced dataset (random guess is 50\%) our classifier can distinguish between {\it correct} and {\it wrong} sentences in 64.5\% of the cases. 
+Importantly, the classifier is trained {\bf only} on the last sentences, and does not consider the four input sentences.
+It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
+Furthermore, when trained to distinguish between original endings and new endings, the classifier obtains 70.9\% accuracy.
+
+In order to estimate the quality of our results, we turn back to the story cloze task.
+We show that using our classifier, we are able to obtain 71.6\% accuracy on the task, a 12\% improvement compared to the published state-of-the-art results \cite{Speer:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}).
+At the time of submission, the leading results is 71.1\%, which is much closer to our results, although still inferior.
+No details about the methods used to generate this result are available.}
+
+We present an ablation study which shows that the style differences are realized in syntactic features (such as the over/under use of coordination words like ``and'' and ``but'').
+Furthermore, we also show that sentiment plays an important role in the writing style differences.
+For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" by the latter.
+
+Our results suggest that writing style is affected by the state of mind the writer is at.
+Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it correct}. 
+Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.
+These differences can be distinguished to a large extent by simple machine learning tools.
+
+The results presented here also provide valuable lessons for designing new NLP tasks.
+Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
+addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
+%We show that these details are actually very significant.
+
+Finally, we show that our stylistic features can benefit from combining with a machine-reading model, for which this task was designed.
+We train an neural language model on the original five sentence training corpus, and then compute the language probability of each of the candidates answers. 
+We add the numbers as features in our linear classifier, and get an additional 4\% improvement (75.6\%).
+
+the reminder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
+We present our model, our experiments and our results at sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results}, respectively.
+Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
+We conclude at \secref{Conclusion}.
+
+\isection{The Cloze Story Task}{ROC_Story}
+
+\isectionb{Model}
+
+\isectionb{Experiments}
+
+\isectionb{Results}
+
+\isection{Ablation Study}{Ablation}
+
+\isectionb{Discussion}
+
+\isection{Related Work}{Related}
+
+\begin{itemize}
+\item Different style application (as in introduction). Also include deception works (Yejin has 1-2 papers on it). 
+\item Machine reading papers? 
+\end{itemize}
+
+\isectionb{Conclusion}
 
@@
 %\bibliography{acl2017}
+
+\newpage
 \bibliography{acl2017}

### 2017-01-19 ROC_SVM.py

@@ -27,8 +27,9 @@ def read_features(ifile, n_feats):
             for f in fs:
                 [f,v] = f.split(":")
             
-                # print f,v
-                local_fs[int(f)] = float(v)
+                f = int(f)
+                
+                local_fs[f] = float(v)
         
 #            local_fs_sparse = csr_matrix(local_fs)
 #            print line,d[0],local_fs,local_fs_sparse.toarray()

### 2017-01-19 gen_pattern_features.PL

@@ -8,17 +8,23 @@ my %CW_TAGS = ("N" => undef, "V" => undef, "J" => undef, "R" => undef);
 sub main(@) {
 	my $min_thr = 5;
 	my $max_patt_len = 5;
-	my $if = shift;
-	my $patt_file = shift;
-	my $of = shift or die "Usage: $0 <if> <patt file> <of> <min_thr = $min_thr> <max patt length = $max_patt_len\n";
+	my $if;
+	my $patt_file;
+	my $of;
+	my $use_len;
+	my $char_ngrams=5;
 	
-	if (@_) {
-		$min_thr = shift;
-		if (@_) {
-			$max_patt_len = shift;
-		}
-	}
-		
+	MyUtils::usage({
+		"if=s" => \$if,
+		"patt_file=s" 					=> \$patt_file,
+		"of=s"							=> \$of,
+		"max_patt_len=i" 				=> \$max_patt_len,
+		"min_thr=i"						=> \$min_thr,
+		"char_ngrams=i"					=> \$char_ngrams,
+		"len+"							=> \$use_len,
+	}, ["if=s","of=s","patt_file=s"]);
+	
+	$max_patt_len--;
 	my %saved;
 
 	if (-e $patt_file) {
@@ -42,7 +48,7 @@ sub main(@) {
 	
 			my @w = split(" ", $text);
 
-			my $patts = get_patts(\@w, $max_patt_len);
+			my $patts = get_patts(\@w, $max_patt_len, $char_ngrams);
 
 			foreach my $patt (keys %$patts) {
 				$patts{$patt} += $patts->{$patt};
@@ -62,8 +68,12 @@ sub main(@) {
 		$ofh->close();
 	}
 
-	my $n_feats = scalar(keys %saved)+1;
+	my $n_feats = scalar(keys %saved)+defined($use_len);
 	print $n_feats." found\n";
+	
+	unless ($n_feats) {
+		return 1;
+	}
 
 	
 	my $ifh = openRFile($if);
@@ -76,7 +86,7 @@ sub main(@) {
 		
 		my @w = split(" ", $text);
 
-		my $patts = get_patts(\@w, $max_patt_len);
+		my $patts = get_patts(\@w, $max_patt_len, $char_ngrams);
 		
 		my %ts;
 		
@@ -86,7 +96,9 @@ sub main(@) {
 			}
 		}
 		
[…]

### 2017-01-19 train_SVM.py

@@ -1,36 +1,32 @@
 #!/usr/bin/env python
 
 import sys
-sys.path.insert(0, '/Users/roysch/aristo/entailment/scripts/')
 import ROC_SVM
 from scipy.sparse import *
 from scipy import *
 from sklearn import svm
 import pickle
+from optparse import OptionParser,OptionValueError
 
 def main():
-    C=0.025
-    penalty='l2'
     loss='squared_hinge'
     dual=True
-    do_rank = 0
-    argc=len(sys.argv)
-    if (argc < 4):
-        print "Usage:",sys.argv[0],"<if> <n features> <of> <C="+str(C)+"> <penalty="+penalty+"><do rank>"
-        return -1
-    elif (argc > 4):
-        C=float(sys.argv[4])
-        if (argc > 5):
-            penalty=sys.argv[5]
-            if (argc > 6):
-                do_rank = bool(sys.argv[6])
-            
-    n_feats = int(sys.argv[2])
+
+    options = usage()
+
+    ifile = options.ifile
+    n_feats = options.n_feats
+    C = float(options.C)
+    do_rank = bool(options.do_rank)
+    n_feats = int(options.n_feats)
+    model_of = options.model_of
+    penalty=options.penalty
+    
     if (penalty == 'l1'):
 #        loss='hinge'
         dual=False
 
-    [features, labels] = ROC_SVM.read_features(sys.argv[1], n_feats)
+    [features, labels] = ROC_SVM.read_features(ifile, n_feats)
     
     if (do_rank):
         [features,labels] = ROC_SVM.gen_ranking(features, labels)
@@ -38,8 +34,10 @@ def main():
     print "Done. Now feating"
     
     clf = svm.LinearSVC(C=C,penalty=penalty,loss=loss,dual=dual)
+
     clf.fit(features, labels)
-    pickle.dump(clf, open(sys.argv[3], 'wb'))
+    pickle.dump(clf, open(model_of, 'wb'))
+    # print clf.coef_[0][0]
     
     print "Done. Now testing"
     
@@ -48,6 +46,44 @@ def main():
     n_correct = 0
     
     ROC_SVM.evaluate(test,labels)
+
+
+
+def usage():
+    C=0.025
+    penalty='l2'
+    loss='squared_hinge'
+    dual=True
+    do_rank = 0
+   
+    parser = OptionParser()
+    give_tag=0
+    n_training_samples = -1
+
+    parser.add_option("-i", dest="ifile",
[…]

### 2017-01-22 docs/language_constraint.tex
first pass at ROC stories and language model sections

@@
 \usepackage{latexsym}
-
+\usepackage{xcolor}
 \usepackage{url}
@@
 \newcommand{\isectionb}[1]{\section{#1}\label{ssec:#1}}
+
+\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
 
@@
 \end{abstract}
+
 \section{Introduction}
@@
 
-Interestingly, although originally intended to be a machine reading task, the compliation of this task raises several research questions which seem to differ from the original intent of the designers.
+Interestingly, although originally intended to be a machine reading task, the compilation of this task raises several research questions which seem to differ from the original intent of the designers.
 First, do authors use different style when asked to write a {\it correct} sentence, compared to a {\it wrong} sentence?
-Second, do authors use different style when writing the ending as part of a five sentence story, compared to reading four sentences, and then writing a standalone (correct) ending?
+Second, do authors use different style when writing the ending as part of their own five sentence story, compared to reading four sentences, and then writing a standalone (correct) ending?
 
@@
 
-Our results suggest that writing style is affected by the state of mind the writer is at.
+Our results suggest that writing style is affected by the the writer's state of mind.
 Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it correct}. 
@@
 \isection{The Cloze Story Task}{ROC_Story}
+Developed as an effort to simplify the representation and learning of commonsense knowledge, the \textit{Cloze Story Task} \cite{Mostafazadeh:2016} has become the Shared Task for the LSDSem workshop.
+% this is a terrible sentence.
+The task provides two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
+
+\paragraph{ROC Stories}
+consist of $98,163$ five-sentence commonsense stories, collected on AMT.
+Workers were instructed to write a coherent story where something happens, and with a clear beginning and end.
+To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
+\paragraph{Story Cloze} test sets were created on AMT, using a subset of ROC Stories.
+Presented with the first four sentences of a story, workers were asked to write a ``right'' and a ``wrong'' ending.
+The ending had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
+
+The resulting stories were then individually rated for coherence and meaningfulness by AMT workers.
+Only stories with a coherent and meaningful ``right'' ending and a neutral ``wrong'' ending were selected for the test, yielding $3,744$ test stories.
+\ms{Hope the ``neutral'' thing makes sense, I didn't know how else to explain 4.2.2 of the Story cloze paper.}
 
@@
 
+\subsection{Neural Language Model}
+\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
+
+We trained a simple RNN Language model \cite{mikolov2010recurrent} using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
+We used the ROC Stories for training, setting aside $10\%$ for validation of the language model.
+We replaced all words occuring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=21,582$.
+Only during training, we applied a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories.
+Using AdamOptimizer \cite{kingma2014adam} and a learning rate of $\eta=.001$, we trained with backpropagation on cross-entropy.
+% minibatches of $50$ stories.
+% h=512, dropout rate of 60%, V=21582, 10% validation set
+
+To construct features for the Story Cloze task, we scored each of the two endings using our neural language model.
+We computed the probability of each ending given the first four sentences $p_\theta(ending|story)$, as well as the probability of the endings out of context $p_\theta(ending)$.
+We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.
 \isectionb{Experiments}
@@
 \item Machine reading papers? 
+\item \ms{Pennebaker's work on function words?}
 \end{itemize}

### 2017-01-22 docs/shared_task_paper.tex
added an outline for the shared task paper

\documentclass[11pt]{article}
\usepackage{eacl2017}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

% \eaclfinalcopy % Uncomment this line for the final submission
%\def\eaclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Story Cloze task -- UW System}

\author{Roy Schwartz\\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And	
  Maarten Sap \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
Taking part in the LSDSem `17 shared task, we describe our system.

\end{abstract}

\section{Intro}

\section{System Overview}

\section{Features}

\section{Results}

\section{Discussion \& Conclusion}

\bibliography{acl2017}
\bibliographystyle{eacl2017}

\end{document}

### 2017-01-23 docs/language_constraint.tex
Roy's comments on ROC stories and RNN model

@@
 \usepackage{xcolor}
+\usepackage[normalem]{ulem}
 \usepackage{url}
@@
 \newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
+\newcommand{\roy}[1]{\footnote{\color{red}{\textbf{Roy: #1}}}}
+\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
+\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
 
@@
 
-\isection{The Cloze Story Task}{ROC_Story}
-Developed as an effort to simplify the representation and learning of commonsense knowledge, the \textit{Cloze Story Task} \cite{Mostafazadeh:2016} has become the Shared Task for the LSDSem workshop.
-% this is a terrible sentence.
+\isection{The Cloze Story Task}{ROC_Story}\roy{We should start with a general paragraph reminding the reader of the problem and why we are using this corpus.}
+Developed as an effort to simplify\roy{``simplify'' is not the right term here.
+{\it Facilitate} maybe?
+}  the representation and learning of commonsense knowledge, the \textit{Cloze Story Task} \cite{Mostafazadeh:2016} has become the Shared Task for the LSDSem workshop.\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task.
+This is a rather minor detail and has very little relevance to our story.
+Think about what we want to reader who has very little time or energy to know.
+Specifically, I would start with few very general details and motivation (as you did), but then directly move to mention the interesting design decisions they took, 
+which actually raise  very different type of research questions, which we tackle in this paper.
+Then you can move to describe it more formally, as you do below (you can mention the shared task there if you want, not sure it's even necessary).} % this is a terrible sentence.
 The task provides two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
@@
 \paragraph{ROC Stories}
-consist of $98,163$ five-sentence commonsense stories, collected on AMT.
+consist of $98,163$ five-sentence commonsense stories, collected on AMT\roy{I would use ``Amazon Mechanical Turk (AMT)'' here, and AMT from now on}.
 Workers were instructed to write a coherent story where something happens, and with a clear beginning and end.
@@
 Presented with the first four sentences of a story, workers were asked to write a ``right'' and a ``wrong'' ending.
-The ending had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
+\royb{The ending}{Both endings} had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
 
@@
 Only stories with a coherent and meaningful ``right'' ending and a neutral ``wrong'' ending were selected for the test, yielding $3,744$ test stories.
-\ms{Hope the ``neutral'' thing makes sense, I didn't know how else to explain 4.2.2 of the Story cloze paper.}
+\ms{Hope the ``neutral'' thing makes sense, I didn't know how else to explain 4.2.2 of the Story cloze paper.}\roy{Reading 4.2.2, it seems that they were not targeting badly phrased ``wrong'' sentences, but just the stories as a whole, and validated that all ``right'' stories were valid and all ``wrong'' stories were invalid (unless this is how you read the -1 option in their description, which is not addressed anywhere else in the text).
+If I am correct, I would write this and explicitly mention that no validation was performed on the ending level.}
+
+\roy{The following might belong in the related work section, but probably more relevant here: I would add a section about performance on this task, stating that the authors tried quite a few baselines and showed that all pretty much fail on the task, and other than that there was just one paper that got slightly better results.
+This is a place to make two more arguments: 
+(a) the low results obtained by the various baseline methods, as well as the low number of works (only one) that improved results on this task, compared to other similar tasks published in recent years (SQUAD, SNLI, CNN/Daily Mail., etc.), indicate that this is task is relatively hard, even for machine reading systems that has made a huge progress in recent years.
+(b) To the best of our knowledge, this is the first work to consider the style differences between the two endings, rather than the setup suggested by the author. \\
+Btw, this could be a good place to mention the shared task.}
 
@@
 \subsection{Neural Language Model}
-\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
+\ms{Below is a messy dump of all the hyper parameters...
+Didn't know how many details were needed}\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good.
+What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
+(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
+Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
+which resemble the tools the authors had in mind when they designed the task).}
 
@@
 We computed the probability of each ending given the first four sentences $p_\theta(ending|story)$, as well as the probability of the endings out of context $p_\theta(ending)$.
-We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.
+We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:
+(a) performance of the model as a standalone (both how we evaluated it and how much it got).
+(b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.
+(c) results of the combination (75.1\%).\\
+These numbers might best fit in a small table.}
 \isectionb{Experiments}

### 2017-01-24 docs/language_constraint.tex
tweaks
Introduction V2; Sections 3-5 V1

@@
 \usepackage{url}
+\usepackage{pgfplots}
+\usepackage{tikz}
+
+% Define bar chart colors
+%
+\definecolor{bblue}{HTML}{4F81BD}
+\definecolor{rred}{HTML}{C0504D}
+\definecolor{ggreen}{HTML}{9BBB59}
+\definecolor{ppurple}{HTML}{9F4C7C}
 
@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
+
+% Writing macros
 \newcommand{\secref}[1]{Section~\ref{ssec:#1}}
+\newcommand{\figref}[1]{Figure~\ref{#1}}
+\newcommand{\tabref}[1]{Table~\ref{#1}}
 \newcommand{\isection}[2]{\section{#1}\label{ssec:#2}}
 \newcommand{\isectionb}[1]{\section{#1}\label{ssec:#1}}
+\newcommand{\com}[1]{}
 
+% Editing macros
 \newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
@@
 \newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
+\renewcommand{\ms}[1]{}
+\renewcommand{\roy}[1]{}
+\renewcommand{\royb}[1]{}
+\renewcommand{\royc}[1]{}
 
@@
 \section{Introduction}
-Writing style is defined as the choice of words, spelling, grammar and punctuation made by the author.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
-It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, native language \cite{Koppel:2005}, or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010} and whether it is sarcastic \cite{Tsur:2010}.
+Writing style is defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
+It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, native language \cite{Koppel:2005}, or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010} and its level of sarcasm \cite{Tsur:2010}.
 In this paper we study to what extent is writing style affected by more intricate factors, such as the type of constraints put on the author.
@@
 As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
-This task was created by having authors write five-sentence self-contained stories.
-Following, a subset of the the stories was given to another group of authors, who were shown only the first four sentences of each story, 
+In this task, authors were asked to write five-sentence self-contained stories.
+Following, the stories were given to another group of authors, who were shown only the first four sentences of each story, 
 and were asked to write two one-sentence endings for it: a {\it correct} ending, and a {\it wrong} ending.
 The goal of the task is to determine which of the endings is the correct one.
+\tabref{ROC-example} shows an example of an original story, a {\it correct} story and a {\it wrong} story.
+
+\begin{table}[!t]
+\small
+\begin{tabular}{|p{.95cm}|p{6cm}|} \hline
+{\bf Type} & {\bf Example} \\ \hline
+{\it Original} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
+{\it Correct} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{green}{She felt buyer's remorse after the purchase.}} \\ \hline
+{\it Wrong} story & I Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	Kathy hated buying shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
+\end{tabular}
+\caption{\label{ROC-example}}
+Examples of stories from the story cloze task. The first row shows an original story written by one author. 
+The second and third row show two endings of the same story: a {\it correct} ending and a {\it wrong} one.
+%\end{center}
+\end{table}
 
@@
 First, do authors use different style when asked to write a {\it correct} sentence, compared to a {\it wrong} sentence?
-Second, do authors use different style when writing the ending as part of their own five sentence story, compared to reading four sentences, and then writing a standalone (correct) ending?
+Second, do authors use different style when writing the ending as part of their own five sentence story, compared to reading four sentences, and then writing a standalone ({\it correct}) ending?
 
-We show that the answer to both of these questions is positive. 
+Our experiments indicate that the answer to both questions is positive. 
 We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and PoS counts. 
-We show that on a balanced dataset (random guess is 50\%) our classifier can distinguish between {\it correct} and {\it wrong} sentences in 64.5\% of the cases. 
+First, we show that on a balanced dataset (random guess is 50\%) our classifier distinguishes between {\it correct} and {\it wrong} sentences in 64.5\% of the cases. 
 Importantly, the classifier is trained {\bf only} on the last sentences, and does not consider the four input sentences.
-It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
-Furthermore, when trained to distinguish between original endings and new endings, the classifier obtains 70.9\% accuracy.
+%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
+Second, when trained to distinguish between original endings and new ({\it correct}) endings, the classifier obtains 70.9\% accuracy.
 
 In order to estimate the quality of our results, we turn back to the story cloze task.
-We show that using our classifier, we are able to obtain 71.6\% accuracy on the task, a 12\% improvement compared to the published state-of-the-art results \cite{Speer:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}).
+Using our classifier, we are able to obtain 71.5\% accuracy on the task, a 11.6\% improvement compared to the published state-of-the-art results \cite{Salle:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}).
 At the time of submission, the leading results is 71.1\%, which is much closer to our results, although still inferior.
 No details about the methods used to generate this result are available.}
+An ablation study shows that the style differences are realized in syntactic features (such as the over/under use of coordination words like ``and'' and ``but''),
+but that sentiment also plays an important role in the writing style differences.
+For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.
 
-We present an ablation study which shows that the style differences are realized in syntactic features (such as the over/under use of coordination words like ``and'' and ``but'').
-Furthermore, we also show that sentiment plays an important role in the writing style differences.
-For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" by the latter.
+\com{Our results suggest that writing style is affected by the the writer's state of mind.
+Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it correct}. 
+Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.}
 
-Our results suggest that writing style is affected by the the writer's state of mind.
-Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it correct}. 
-Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.
-These differences can be distinguished to a large extent by simple machine learning tools.
-
-The results presented here also provide valuable lessons for designing new NLP tasks.
-Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
-addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
+Our results may have a wide impact on a range of fields. 
+First, they have the potential to shed light on cognitive processes that take place in the brain during writing.
+Second, our results might have a more practical value in an era when fake news are becoming prominent,
+as they suggest that these might have different style compared to real news.
+Third, the results presented here also provide valuable lessons for designing new NLP tasks,
+both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
+%Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
+%addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
 %We show that these details are actually very significant.
 
-Finally, we show that our stylistic features can benefit from combining with a machine-reading model, for which this task was designed.
-We train an neural language model on the original five sentence training corpus, and then compute the language probability of each of the candidates answers. 
-We add the numbers as features in our linear classifier, and get an additional 4\% improvement (75.6\%).
+Finally, one interesting question that remains open is whether state-of-the-art machine reading tools, for which this task was designed, 
+capture in fact the same stylistic features as our linear classifier. 
+We show that this is not the case. 
+We train a neural language model on the original five sentence training corpus, and then compute the language probability of each of the candidates answers. 
+We add the numbers as features in our linear classifier, and get an additional 3.6\% improvement (75.1\%).
 
 the reminder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
-We present our model, our experiments and our results at sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results}, respectively.
+We present our model and our experiments at sections \ref{ssec:Model} and \ref{ssec:Experiments} respectively.
 Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
@@
 
-\subsection{Neural Language Model}
+The goal of this paper is to determine to what extent does constraining authors in their writing assignments lead to them adopting different writing styles. 
+In order to answer these questions, we use simple, classic NLP tools, which have been shown to be very effective for recognizing style (see \secref{Related}).
+We describe our model below.
+
+We train a linear SVM classifier to distinguish between different endings. 
+Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
+We use the following style features.
+
+\begin{itemize}
+\item{Length} The number of words in the sentence.
+\item{Word n-grams} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
+Specifically, we replace content words with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
+\item{Character n-grams} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
+We used character 5-grams.
+\end{itemize}
+
+\isectionb{Experiments}
+We design two experiments to answer our research questions. 
+The first is an attempt to distinguish between {\it correct} and {\it wrong} endings.
+The second attempts to distinguish between original endings and new {\it correct} endings.
+We describe both experiments below.
+
+\paragraph{Experiment 1: Correct/Wrong Endings.}
+The goal of this experiment is to measure to what extent  style features capture differences between {\it correct} and {\it wrong} endings.
+As the cloze story task doesn't have a training corpus for the {\it correct} and {\it wrong} endings, we use the development set as our training set. 
+We split it (90/10) into our training and development set. We keep the story cloze test set as is.
+The final size of our training/development/test sizes are 3366/374/3742, respectively.
+
+We take  {\it correct} endings as positive samples and {\it wrong} endings as our negative examples. 
+By ignoring the coupling between {\it correct}/{\it wrong} pairs, we are able make a more general claim about the style used when writing each of the tasks.
+
+We add a special START symbol at the beginning of each sentence. 
+For computing our features, we keep n-gram (character or word) features that occur at least five times in the training set.\footnote{Virtually all sentences end with a period, so no need for an END token}
+For the PoS features, we tag each sentence with the Spacy PoS tagger.\footnote{\url{spacy.io/}}
+We use  sklearn's LinearSVC SVM implementation\footnote{\url{scikit-learn.org/stable/modules/generated/sklearn.svm.LinearSVC.html}} 
+with L2 loss. We grid search the regularization parameter on our development set.
+
+\paragraph{Experiment 2: Original/New Endings.}
+
+Here the goal is to measure whether writing the ending as part of a story imposes different style compared to writing a ({\it correct}) ending to an existing story.
+We use the endings of the original ROC stories as our {\it original} training samples and {\it correct} endings from the ROC stories development set as {\it new} training samples.
+As there are far more {\it original} samples than {\it new} ones, we randomly select $N$ {\it original} samples, where $N$ is the number of {\it new} samples,
+such that we have balanced labels in our training, validation and test sets.
+We apply the same experimental decisions as in Experiment 1, and repeat this process 5 times while reporting the average.
+
+\paragraph{Results.}
+\figref{results} shows our results.
+Results show that for Experiment 1, our model obtains results well above a random baseline -- 64.5\% classification accuracy. 
+For Experiment 2, we get even higher results -- 70.9\%. 
+These numbers indicate that these different writing tasks clearly impose a different writing style on authors.
+
+As a complementary experiment, we measured whether these style differences are additive. 
+That is, whether the style differences between {\it correct} endings and {\it wrong} ones are different from the differences between {\it correct} and {\it original} endings.
+We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
+Our hypothesis is that differences would be even clearer. 
+Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 78\%.
+
+\begin{figure}
+\begin{tikzpicture}
+\small
+    \begin{axis}[
+        width  = 0.45*\textwidth,
+        height = 4cm,
+      %  major x tick style = transparent,
+        ybar=2*\pgflinewidth,
+       % bar width=14pt,
+        ymajorgrids = true,
+        ylabel = {Classification Performance},
+        symbolic x coords={{\it Correct/Wrong}, {\it Original/New}, {\it Original/Wrong}},
+        xtick = data,
+        scaled y ticks = false,
+        %enlarge x limits=0.25,
+        ymin=0.4,
+        legend cell align=left,
+        legend style={
+                at={(1,1.05)},
+                anchor=south east,
+                column sep=1ex
+        }
+    ]
+        \addplot[style={bblue,fill=bblue,mark=none}]
+            coordinates {({\it Correct/Wrong}, 0.5) ({\it Original/New}, 0.5) ({\it Original/Wrong},.5)};
+
+        \addplot[style={rred,fill=rred,mark=none}]
+            coordinates {({\it Correct/Wrong}, 0.645) ({\it Original/New}, 0.709) ({\it Original/Wrong},0.78)};
+
+        \legend{Random Baseline, Our Model}
+    \end{axis}
+\end{tikzpicture}
+\caption{\label{results} Results of  experiments 1 and 2 (left two charts). 
+Rightmost experiment shows a control experiment which classifies {\it original} endings vs \textit{\textbf{wrong}} endings. }
+\end{figure}
+
+\paragraph{Story Cloze.}
+Results of Experiment 1 indicate that {\it correct} and {\it wrong} endings are characterized by different styles.
+In order to estimate the quality of our classification results, we tackle the story cloze task using our classifier.
+This classification task is much more constrained than Experiment 1, as here the task is given two endings, which one is {\it correct} and which is {\it wrong}.
+In order to solve the task, we use the output of our trained classifier. 
+For each pair of endings $e_1,e_2$, if both endings have different classification labels, we keep these labels. 
+If they share the same label, we use the classifier confidence level as a deciding factor: the label of the one with the lower confidence is reversed.
+
+\tabref{cloze_results} shows our results on the story cloze test set. Our classifier obtains 71.5\% accuracy, which is 11.6\% better than the published state-of-the-art result on the task.
+Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even look at the first four sentences of the story in question.
+These numbers indicate that the styles between {\it correct} and {\it wrong} are indeed very different.
+
+Other than the published works that tackled this task, a few  recent works published their results in the LSDSem shared task website.\footnote{\url{https://competitions.codalab.org/competitions/15333}}
+As to the time of submission, our results are still state-of-the-art (though by a much smaller margin). No other information other than the name of the group and their results is available.
+
+\begin{table}[!t]
+\begin{center}
+\small
+\begin{tabular}{|c|c|} \hline
+{\bf Model} & {\bf Results} \\ \hline
+{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ \hline
+{ LexVec} \cite{Salle:2016} & 0.599 \\ \hline
+{RNN}		& 0.677 \\ \hline
+{\bf Our Model} & {\bf 0.715} \\ \hline
+{\bf Combined (Our model, RNN)} & {\bf 0.751} \\ \hline\hline
+{ tbmihaylov (shared task)} & 0.711\\ \hline
+{ Niko (shared task)}	& 0.7\\ \hline\hline
+Human judgment & 1 \\ \hline
+\end{tabular}
+\end{center}
+\caption{\label{cloze_results}}
+Results on the test set of the cloze story task. 
+Upper part are published results (Lexvec results are taken from \cite{Speer:2016}).
+Bottom part are taken from the cloze task shared task webpage.
+\end{table}
+
+\isection{Ablation Study}{Ablation}
+
+\paragraph{Most Discriminative Feature Types.}
+A natural question that follows this study is which features are most helpful in making predictions about writing style. 
+To answer this question, we re-ran Experiment 1 with different sub-groups of features. 
+\tabref{subgroups} shows our results. Results clearly show that  character n-grams are the most effective style predictors, reaching within less than 2\% of the full model.
+These findings are in line with previous works that used character n-grams along with other types of features to predict writing  style \cite{Schwartz:2013}.
+
+\begin{table}[!t]
+\begin{center}
+\small
+\begin{tabular}{|c|c|} \hline
+{\bf Feature Type} & {\bf Result}\\ \hline
+Word n-grams & 0.646 \\ \hline
+Char n-grams & 0.699 \\ \hline
+Word n-grams, length, char n-grams (Full Model) & 0.715 \\ \hline
+
+\end{tabular}
+\end{center}
+\caption{\label{subgroups}}
+Results on Experiment 1 with different types of features.
+\end{table}
+
+\paragraph{Most Salient Features.}
+In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
+This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.715).  
+\tabref{features} shows the 5 features with the highest positive and negative weights in the hyperplane. 
+These correspond to the 5 most salient features for {\it correct} and {\it wrong} endings, respectively.
+
+The table shows a few interesting trends. 
+First, some syntactic features play become salient when authors are asked to write {\it wrong} vs. {\it correct} endings.
+For instance, {\it correct} endings are more likely to the coordinator ``but'', while {\it wrong} ones would prefer to use ``and''.
+
+More interestingly, {\it correct} endings are likely to use positive words (e.g., `` bett'', which in all cases stands for `` bett{\bf er}''), while  {\it wrong} endings would use negative words (e.g., `` hate'').
+The idea that  sentiment would play a role in this task was suggested in the original story cloze paper, where two sentiment-based baselines were evaluated. 
+However, these baselines measured the relative sentiment between the ending and the previous sentences, and did not test whether there is a general tendency of the {\it wrong} endings to have a negative sentiment, and the {\it correct} one to have a positive sentiment.
+Indeed, the performance of both these baselines was roughly chance-level.
+
+\begin{table}[!t]
+\begin{center}
+\small
+\begin{tabular}{|c|c|} \hline
+{\bf Positive} & {\bf Negative}\\ \hline
+` time' & `ed of'\\ \hline
+` bett' & `and d'\\ \hline
+`found' & `threw'\\ \hline
+`but' & `ever '\\ \hline
+`ally ' & ` hate'\\ \hline
+
+\end{tabular}
+\end{center}
+\caption{\label{features}}
+The top 5 most discriminative features for predicting {\it correct} (Positive)  and {\it wrong} (Negative) endings.\end{table}
+
+\paragraph{Neural Language Model.}
 \ms{Below is a messy dump of all the hyper parameters...
@@
 These numbers might best fit in a small table.}
-\isectionb{Experiments}
-
-\isectionb{Results}
-
-\isection{Ablation Study}{Ablation}
 

### 2017-01-24 docs/language_constraint.tex
addressing some revision

--- 2017-01-23 docs/language_constraint.tex
@@
 \isection{The Cloze Story Task}{ROC_Story}\roy{We should start with a general paragraph reminding the reader of the problem and why we are using this corpus.}
-Developed as an effort to simplify\roy{``simplify'' is not the right term here.
-{\it Facilitate} maybe?
-}  the representation and learning of commonsense knowledge, the \textit{Cloze Story Task} \cite{Mostafazadeh:2016} has become the Shared Task for the LSDSem workshop.\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task.
+Writing tasks are plentiful on Amazon Mechanical Turk (AMT) \ms{cite various examples?}.
+As a testbed for our analyses, we chose the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, during which workers were asked to write intuitive and counter-intuitive endings to short stories.
+This task is particularly interesting in that the two endings were written by the same author, for the same story, allowing for careful comparison.
+
+The Story Cloze task was developed as an effort to facilitate representation and learning of commonsense knowledge.\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task.
 This is a rather minor detail and has very little relevance to our story.
@@
 Presented with the first four sentences of a story, workers were asked to write a ``right'' and a ``wrong'' ending.
-\royb{The ending}{Both endings} had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
+Both endings had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
 
@@
 
-To construct features for the Story Cloze task, we scored each of the two endings using our neural language model.
+% Eval
+On its own, our neural language model performs moderately on the Story Cloze test.
+As hinted at by the creators of this task, simple language models aren't enough to do well.
+In fact, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55\%$ accuracy.
+When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68\%$.
+This doesn't beat reported SOTA, which is why we included these features into our stylistic driven model.
+
+% To construct features for the Story Cloze task, we scored each of the two endings using our neural language model.
 We computed the probability of each ending given the first four sentences $p_\theta(ending|story)$, as well as the probability of the endings out of context $p_\theta(ending)$.
-We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:
-(a) performance of the model as a standalone (both how we evaluated it and how much it got).
-(b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.
-(c) results of the combination (75.1\%).\\
-These numbers might best fit in a small table.}
+We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.
+%\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:(a) performance of the model as a standalone (both how we evaluated it and how much it got).
+(b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.(c) results of the combination (75.1\%).\\These numbers might best fit in a small table.}
 \isectionb{Experiments}
@@
 \item Machine reading papers? 
-\item \ms{Pennebaker's work on function words?}
+\item \ms{Pennebaker's work on function words? they link function words to psychological aspects}
 \end{itemize}

### 2017-01-24 docs/language_constraint.tex

--- 2017-01-24 docs/language_constraint.tex
@@
 {\it Correct} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{green}{She felt buyer's remorse after the purchase.}} \\ \hline
-{\it Wrong} story & I Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	Kathy hated buying shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
+{\it Wrong} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
 \end{tabular}
@@
 
-\isection{The Cloze Story Task}{ROC_Story}\roy{We should start with a general paragraph reminding the reader of the problem and why we are using this corpus.}
-Developed as an effort to simplify\roy{``simplify'' is not the right term here.
-{\it Facilitate} maybe?
-}  the representation and learning of commonsense knowledge, the \textit{Cloze Story Task} \cite{Mostafazadeh:2016} has become the Shared Task for the LSDSem workshop.\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task.
+\isection{The Cloze Story Task}{ROC_Story}
+Writing tasks are plentiful on Amazon Mechanical Turk (AMT) \ms{cite various examples?}.
+As a testbed for our analyses, we chose the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, during which workers were asked to write intuitive and counter-intuitive endings to short stories.
+This task is particularly interesting in that the two endings were written by the same author, for the same story, allowing for careful comparison.
+
+Originally, the task was developed as an effort to facilitate representation and learning of commonsense knowledge.
+For that purpose, the creators crowdsourced the creation of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
+%\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task.
 This is a rather minor detail and has very little relevance to our story.
 Think about what we want to reader who has very little time or energy to know.
-Specifically, I would start with few very general details and motivation (as you did), but then directly move to mention the interesting design decisions they took, 
-which actually raise  very different type of research questions, which we tackle in this paper.
+Specifically, I would start with few very general details and motivation (as you did), but then directly move to mention the interesting design decisions they took, which actually raise  very different type of research questions, which we tackle in this paper.
 Then you can move to describe it more formally, as you do below (you can mention the shared task there if you want, not sure it's even necessary).} % this is a terrible sentence.
-The task provides two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
 
 \paragraph{ROC Stories}
-consist of $98,163$ five-sentence commonsense stories, collected on AMT\roy{I would use ``Amazon Mechanical Turk (AMT)'' here, and AMT from now on}.
+consist of $98,163$ five-sentence commonsense stories, collected on AMT.
 Workers were instructed to write a coherent story where something happens, and with a clear beginning and end.
@@
 Presented with the first four sentences of a story, workers were asked to write a ``right'' and a ``wrong'' ending.
-\royb{The ending}{Both endings} had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
+Both endings had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
 
-The resulting stories were then individually rated for coherence and meaningfulness by AMT workers.
-Only stories with a coherent and meaningful ``right'' ending and a neutral ``wrong'' ending were selected for the test, yielding $3,744$ test stories.
-\ms{Hope the ``neutral'' thing makes sense, I didn't know how else to explain 4.2.2 of the Story cloze paper.}\roy{Reading 4.2.2, it seems that they were not targeting badly phrased ``wrong'' sentences, but just the stories as a whole, and validated that all ``right'' stories were valid and all ``wrong'' stories were invalid (unless this is how you read the -1 option in their description, which is not addressed anywhere else in the text).
+The resulting stories, matched with each ending, were then individually rated for coherence and meaningfulness by AMT workers.
+Only stories rated as simultaneaously coherent with ``right'' ending and neutral with a ``wrong'' ending were selected for the test, yielding $3,744$ test stories.
+It is worth noting that workers rated the stories as a whole, not the endings; no selection was done on the endings alone.
+%\ms{Hope the ``neutral'' thing makes sense, I didn't know how else to explain 4.2.2 of the Story cloze paper.}\roy{Reading 4.2.2, it seems that they were not targeting badly phrased ``wrong'' sentences, but just the stories as a whole, and validated that all ``right'' stories were valid and all ``wrong'' stories were invalid (unless this is how you read the -1 option in their description, which is not addressed anywhere else in the text).
 If I am correct, I would write this and explicitly mention that no validation was performed on the ending level.}
 
-\roy{The following might belong in the related work section, but probably more relevant here: I would add a section about performance on this task, stating that the authors tried quite a few baselines and showed that all pretty much fail on the task, and other than that there was just one paper that got slightly better results.
-This is a place to make two more arguments: 
-(a) the low results obtained by the various baseline methods, as well as the low number of works (only one) that improved results on this task, compared to other similar tasks published in recent years (SQUAD, SNLI, CNN/Daily Mail., etc.), indicate that this is task is relatively hard, even for machine reading systems that has made a huge progress in recent years.
-(b) To the best of our knowledge, this is the first work to consider the style differences between the two endings, rather than the setup suggested by the author. \\
-Btw, this could be a good place to mention the shared task.}
+\paragraph{Benchmarks}
+~\ms{Like you said, maybe this belongs in related work, but for now I'll put it here}
+The creators of the dataset implemented various benchmarks, using surface level features as well as narrative informed ones.
+Compared to similar tasks \cite{CNN, SQUAD, SNLI}, the baselines perform relatively poorly, indicating that the task is a relatively hard one.
+%\roy{The following might belong in the related work section, but probably more relevant here: I would add a section about performance on this task, stating that the authors tried quite a few baselines and showed that all pretty much fail on the task, and other than that there was just one paper that got slightly better results.
+This is a place to make two more arguments:  (a) the low results obtained by the various baseline methods, as well as the low number of works (only one) that improved results on this task, compared to other similar tasks published in recent years (SQUAD, SNLI, CNN/Daily Mail., etc.), indicate that this is task is relatively hard, even for machine reading systems that has made a huge progress in recent years.
+(b) To the best of our knowledge, this is the first work to consider the style differences between the two endings, rather than the setup suggested by the author.
+\\ Btw, this could be a good place to mention the shared task.}
 
@@
 \begin{itemize}
-\item{Length} The number of words in the sentence.
-\item{Word n-grams} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
+\item\textit{\textbf{Length~}} The number of words in the sentence.
+\item\textit{\textbf{Word n-grams~}} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
 Specifically, we replace content words with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
-\item{Character n-grams} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
+\item\textit{\textbf{Character n-grams~}} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
 We used character 5-grams.
@@
 { LexVec} \cite{Salle:2016} & 0.599 \\ \hline
-{RNN}		& 0.677 \\ \hline
+{RNN}		& 0.681 \\ \hline
 {\bf Our Model} & {\bf 0.715} \\ \hline
@@
 \paragraph{Neural Language Model.}
-\ms{Below is a messy dump of all the hyper parameters...
-Didn't know how many details were needed}\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good.
+~\ms{This needs to be placed somewhere else LOL}
+~\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
+\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good.
 What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
@@
 
-We trained a simple RNN Language model \cite{mikolov2010recurrent} using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
+To leverage the genre of these short stories, we train a recurrent language model (RLM) \cite{mikolov2010recurrent}, which are used to achieve state-of-the-art performance on various tasks (e.g.
+machine translation).
+Training this RLM on the ROC stories, we harness the unsupervised, single-ended stories, which boosts performance on the Story Cloze task.
+
+We trained an RLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
 We used the ROC Stories for training, setting aside $10\%$ for validation of the language model.
@@
 
-To construct features for the Story Cloze task, we scored each of the two endings using our neural language model.
+% Eval
+On its own, our neural language model performs moderately on the Story Cloze test.
+As hinted at by the creators of this task, simple language models aren't enough to do well.
+In fact, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55\%$ accuracy.
+When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68\%$.
+This doesn't beat reported SOTA, which is why we included these features into our stylistic driven model.
+
+% To construct features for the Story Cloze task, we scored each of the two endings using our neural language model.
 We computed the probability of each ending given the first four sentences $p_\theta(ending|story)$, as well as the probability of the endings out of context $p_\theta(ending)$.
-We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:
-(a) performance of the model as a standalone (both how we evaluated it and how much it got).
-(b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.
-(c) results of the combination (75.1\%).\\
-These numbers might best fit in a small table.}
+We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.
+%\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:(a) performance of the model as a standalone (both how we evaluated it and how much it got).
+(b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.(c) results of the combination (75.1\%).\\These numbers might best fit in a small table.}
 

### 2017-01-24 docs/language_constraint.tex
Roy's V2 comments on ROC stories and RNN model

@@
 \usepackage{tikz}
+
+\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
 
@@
 \newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
-\renewcommand{\ms}[1]{}
-\renewcommand{\roy}[1]{}
-\renewcommand{\royb}[1]{}
-\renewcommand{\royc}[1]{}
+
+%\renewcommand{\ms}[1]{}
+%\renewcommand{\roy}[1]{}
+%\renewcommand{\royb}[1]{}
+%\renewcommand{\royc}[1]{}
 
@@
 \begin{table}[!t]
-\small
-\begin{tabular}{|p{.95cm}|p{6cm}|} \hline
+%\small
+\begin{tabular}{|p{1.3cm}|p{5.6cm}|} \hline
 {\bf Type} & {\bf Example} \\ \hline
 {\it Original} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
-{\it Correct} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{green}{She felt buyer's remorse after the purchase.}} \\ \hline
+{\it Correct} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
 {\it Wrong} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
@@
 \isection{The Cloze Story Task}{ROC_Story}
-Writing tasks are plentiful on Amazon Mechanical Turk (AMT) \ms{cite various examples?}.
-As a testbed for our analyses, we chose the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, during which workers were asked to write intuitive and counter-intuitive endings to short stories.
-This task is particularly interesting in that the two endings were written by the same author, for the same story, allowing for careful comparison.
+\roy{High level on first paragraph: much better, but still not enough connection to our story. You need to be explicit as to why we chose this task. 
+Our work is currently not mentioned at all}
+Writing tasks are plentiful on Amazon Mechanical Turk (AMT) \ms{cite various examples?}\roy{I would not start with AMT, as it is not important to our discussion.
+Think of the message that a first sentence in a paragraph gives: this is the topic/main focus of this paragraph.
+AMT is only a technical detail that should be mentioned later}.
+As a testbed for our analyses, we \royb{chose}{focus on} the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, during which\roy{not sure ``during which'' is right here.
+consider rephrasing} workers were asked to write intuitive and counter-intuitive endings to short stories.
+This task is particularly interesting in that the two endings were written by the same author, for the same story, allowing for careful comparison.\roy{This is indeed particularly interesting {\bf for us}, but currently this is out of context.
+I would say that this task has a few interesting properties that we exploit.}
 
 Originally, the task was developed as an effort to facilitate representation and learning of commonsense knowledge.
-For that purpose, the creators crowdsourced the creation of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
+For that purpose, the creators crowdsourced the creation\roy{Don't use ``creators \dots creation''.
+Regardless, {\it creators} is not the right word here} of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
 %\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task.
@@
 \paragraph{ROC Stories}
-consist of $98,163$ five-sentence commonsense stories, collected on AMT.
-Workers were instructed to write a coherent story where something happens, and with a clear beginning and end.
+consist of $98,163$\roy{Minor, but still: writing the number inside dollar signs adds a white space in the pdf.
+This is a bit annoying, and also potentially confusing, as in the next case you use it below (3,744 something)}  five-sentence commonsense stories, collected on AMT.
+Workers were instructed to write a coherent story where something happens, and with\roy{``and with'' doesn't sound right here.
+rephrase} a clear beginning and end.
 To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
-\paragraph{Story Cloze} test sets were created on AMT, using a subset of ROC Stories.
+\paragraph{Story Cloze}\roy{say something general first before diving into details} test sets were created on AMT, using a subset of ROC Stories.
 Presented with the first four sentences of a story, workers were asked to write a ``right'' and a ``wrong'' ending.
-Both endings had to complete the story using a character in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
+Both endings had to complete the story using \royb{a character}{one of the characters} in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
 
@@
 If I am correct, I would write this and explicitly mention that no validation was performed on the ending level.}
+\roy{Other things to talk about (not necessarily in that order): 
+1.
+no training corpus for the task.
+That is, the training set (a) does not contain negative example (just positive), and (b) was not generated in the same way as the positive test samples.
+Here you need to explicitly say that we show that we show that the training and test sets use very different styles.
+2. Maybe talk about the shared task, as well as their RepEval paper, which suggested this task as a vector-space evaluation measure?
+3.
+Say that the authors did an extensive work in order to  assure that the positive and negative samples are not easily distinguishable: for each pair, both endings were written by the same author (you addressed this earlier, but this seems like a better location), they tried an extensive set of baselines, showing all don't surpass a random baseline by much.
+Maybe now you can briefly mention the benchmarks, saying that several baselines were presented in the papers.
+All benchmarks attempted to learn the connection between the previous paragraph and the ending, and all performed near chance level..
+However, no baseline looked at the endings independently.
+Then you can add the benchmark text below, and conclude that this indicates that this task is well designed and hard and the one hand, but might also point to potential disagreements between the train and the test data, which we highlight in this paper.}
 
@@
 \begin{center}
-\small
+%\small
 \begin{tabular}{|c|c|} \hline
@@
 {\bf Combined (Our model, RNN)} & {\bf 0.751} \\ \hline\hline
-{ tbmihaylov (shared task)} & 0.711\\ \hline
 { Niko (shared task)}	& 0.7\\ \hline\hline
+{ tbmihaylov (shared task)} & 0.711\\ \hline\hline
 Human judgment & 1 \\ \hline
@@
 Char n-grams & 0.699 \\ \hline
-Word n-grams, length, char n-grams (Full Model) & 0.715 \\ \hline
+Full Model & 0.715 \\ \hline
 
@@
 
+\[add\ control\ experiments\]
+
 \paragraph{Neural Language Model.}
@@
 ~\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
-\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good.
+%\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good.
 What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
-(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
-Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
-which resemble the tools the authors had in mind when they designed the task).}
+%(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
+%Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
+%which resemble the tools the authors had in mind when they designed the task).}
 
-To leverage the genre of these short stories, we train a recurrent language model (RLM) \cite{mikolov2010recurrent}, which are used to achieve state-of-the-art performance on various tasks (e.g.
-machine translation).
-Training this RLM on the ROC stories, we harness the unsupervised, single-ended stories, which boosts performance on the Story Cloze task.
+To leverage the genre of these short stories,\roy{Not sure this is the best introductory sentence, but you can leave it to me if you can't find anything better} we train a recurrent language model (RLM) \cite{mikolov2010recurrent},\roy{don't start with the details, but with the high level.
+We wanted wether our model can be combined with state-of-the-art text comprehension models, for which this task was designed.
+{\bf Specifically}, we train an RLM \dots}  which are used to achieve state-of-the-art performance on various tasks (e.g.
+machine translation)\roy{citation required}.
+Training this RLM on the ROC stories, we harness the unsupervised, single-ended stories\roy{I would frame it differently.
+Unlike the model suggested in this paper, which only considers the endings, this model harnesses the training set as intended by the authors, which is composed of unsupervised, single-ended stories}, which boosts performance on the Story Cloze task.\roy{In what sense does it boost performance?
+we get STOA results without it...}
 
@@
 We used the ROC Stories for training, setting aside $10\%$ for validation of the language model.
-We replaced all words occuring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=21,582$.
+We replaced all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=21,582$.
 Only during training, we applied a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories.
@@
 In fact, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55\%$ accuracy.
-When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68\%$.
-This doesn't beat reported SOTA, which is why we included these features into our stylistic driven model.
+When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68\%$.\roy{(see \tabref{cloze_results}).
+also, its 68.1, isn't it?
+(just to be consistent with the table)} This doesn't beat reported SOTA\roy{SOTA is not a standard abbreviation.
+Use state-of-the-art}, which is why we included these features into our stylistic driven model.\roy{no, this is not why we include these as features (at least not in this paper:).
+It's because we want to see whether the different approaches are complementary.}\roy{Now you need to discuss our results and what they mean.
+You can point to \tabref{cloze_results}}
 

### 2017-01-26 docs/language_constraint.tex

@@
 
-the reminder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
+The remainder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
 We present our model and our experiments at sections \ref{ssec:Model} and \ref{ssec:Experiments} respectively.
@@
 \isection{The Cloze Story Task}{ROC_Story}
-\roy{High level on first paragraph: much better, but still not enough connection to our story. You need to be explicit as to why we chose this task. 
-Our work is currently not mentioned at all}
-Writing tasks are plentiful on Amazon Mechanical Turk (AMT) \ms{cite various examples?}\roy{I would not start with AMT, as it is not important to our discussion.
-Think of the message that a first sentence in a paragraph gives: this is the topic/main focus of this paragraph.
-AMT is only a technical detail that should be mentioned later}.
-As a testbed for our analyses, we \royb{chose}{focus on} the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, during which\roy{not sure ``during which'' is right here.
-consider rephrasing} workers were asked to write intuitive and counter-intuitive endings to short stories.
-This task is particularly interesting in that the two endings were written by the same author, for the same story, allowing for careful comparison.\roy{This is indeed particularly interesting {\bf for us}, but currently this is out of context.
-I would say that this task has a few interesting properties that we exploit.}
+%\roy{High level on first paragraph: much better, but still not enough connection to our story. You need to be explicit as to why we chose this task. Our work is currently not mentioned at all}
+To understand how constrained writing affects writing style, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}.
+We exploit various interesting properties of the associated dataset and achieve state-of-the-art performance on the task.
 
 Originally, the task was developed as an effort to facilitate representation and learning of commonsense knowledge.
-For that purpose, the creators crowdsourced the creation\roy{Don't use ``creators \dots creation''.
-Regardless, {\it creators} is not the right word here} of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
-%\roy{Not sure that this sentence is so terrible, but I would not put the focus on the shared task.
-This is a rather minor detail and has very little relevance to our story.
-Think about what we want to reader who has very little time or energy to know.
-Specifically, I would start with few very general details and motivation (as you did), but then directly move to mention the interesting design decisions they took, which actually raise  very different type of research questions, which we tackle in this paper.
-Then you can move to describe it more formally, as you do below (you can mention the shared task there if you want, not sure it's even necessary).} % this is a terrible sentence.
+For that purpose, \citet{Mostafazadeh:2016} crowdsourced the collection of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
 
 \paragraph{ROC Stories}
-consist of $98,163$\roy{Minor, but still: writing the number inside dollar signs adds a white space in the pdf.
-This is a bit annoying, and also potentially confusing, as in the next case you use it below (3,744 something)}  five-sentence commonsense stories, collected on AMT.
-Workers were instructed to write a coherent story where something happens, and with\roy{``and with'' doesn't sound right here.
-rephrase} a clear beginning and end.
-To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
-\paragraph{Story Cloze}\roy{say something general first before diving into details} test sets were created on AMT, using a subset of ROC Stories.
-Presented with the first four sentences of a story, workers were asked to write a ``right'' and a ``wrong'' ending.
-Both endings had to complete the story using \royb{a character}{one of the characters} in it, and when read out of context, had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
+consist of $98,163$ % \roy{Minor, but still: writing the number inside dollar signs adds a white space in the pdf.
+This is a bit annoying, and also potentially confusing, as in the next case you use it below (3,744 something)}
+five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).
+Workers were instructed to write a coherent story where something happens, and with%\roy{``and with'' doesn't sound right here.
+rephrase}
+a clear beginning and end. To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
+\paragraph{Story Cloze}%\roy{say something general first before diving into details} 
+test sets consist of $3,744$ short stories, each with one ``right'' and one ``wrong'' ending, also collected on AMT.
+Presented with the first four sentences of a ROC story, workers were asked to write a ``right'' and a ``wrong'' ending.
+Both endings had to complete the story using one of the characters in it, and when read out of context, the ending had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
 
 The resulting stories, matched with each ending, were then individually rated for coherence and meaningfulness by AMT workers.
-Only stories rated as simultaneaously coherent with ``right'' ending and neutral with a ``wrong'' ending were selected for the test, yielding $3,744$ test stories.
+Only stories rated as simultaneaously coherent with a ``right'' ending and neutral with a ``wrong'' ending were selected for the test.
 It is worth noting that workers rated the stories as a whole, not the endings; no selection was done on the endings alone.
-%\ms{Hope the ``neutral'' thing makes sense, I didn't know how else to explain 4.2.2 of the Story cloze paper.}\roy{Reading 4.2.2, it seems that they were not targeting badly phrased ``wrong'' sentences, but just the stories as a whole, and validated that all ``right'' stories were valid and all ``wrong'' stories were invalid (unless this is how you read the -1 option in their description, which is not addressed anywhere else in the text).
-If I am correct, I would write this and explicitly mention that no validation was performed on the ending level.}
-\roy{Other things to talk about (not necessarily in that order): 
-1.
+
+\paragraph{Design.}
+In this task, training (ROC Stories) and test (Story Cloze) data were created differently.
+%The task was designed such that the ROC stories would be used as training data and the Story Cloze stories as validation and test sets, i.e. the training and test data were created differently. 
+The ROC Stories were written by one author, and only have one ``right'' ending, whereas the Story Cloze stories have two endings, neither or which were written by the author of the rest of the story.
+Furthermore, \citet{Mostafazadeh:2016} made sure the Story Cloze endings would be hard to distinguish automatically, as each pair of endings was written by the same author.
+We show that, as a result of these design choices, the style of the ROC stories is rather different from the Story Cloze stories.
+
+\paragraph{Benchmarks.} While the Story Cloze test is now the LSDSem `17 Shared Task and was proposed as a testbed for vector-space evaluation \cite{mostafazadeh2016story}, reported performance isn't far from a random baseline.
+\citet{Mostafazadeh:2016} implemented various benchmarks trained on the ROC Stories, using surface level features as well as narrative-informed ones.
+Compared to similar tasks \cite{hermann2015teaching,rajpurkar2016squad,bowman2015large}, the benchmarks perform relatively poorly, indicating that high performance is hard to achieve.
+To the best of our knowledge, no training has been done on pairs of endings.
+
+%\roy{Other things to talk about (not necessarily in that order): 
+%1.
 no training corpus for the task.
@@
 Here you need to explicitly say that we show that we show that the training and test sets use very different styles.
-2. Maybe talk about the shared task, as well as their RepEval paper, which suggested this task as a vector-space evaluation measure?
-3.
+%2. Maybe talk about the shared task, as well as their RepEval paper, which suggested this task as a vector-space evaluation measure?
+%3.
 Say that the authors did an extensive work in order to  assure that the positive and negative samples are not easily distinguishable: for each pair, both endings were written by the same author (you addressed this earlier, but this seems like a better location), they tried an extensive set of baselines, showing all don't surpass a random baseline by much.
@@
 However, no baseline looked at the endings independently.
-Then you can add the benchmark text below, and conclude that this indicates that this task is well designed and hard and the one hand, but might also point to potential disagreements between the train and the test data, which we highlight in this paper.}
-
-\paragraph{Benchmarks}
-~\ms{Like you said, maybe this belongs in related work, but for now I'll put it here}
-The creators of the dataset implemented various benchmarks, using surface level features as well as narrative informed ones.
-Compared to similar tasks \cite{CNN, SQUAD, SNLI}, the baselines perform relatively poorly, indicating that the task is a relatively hard one.
-%\roy{The following might belong in the related work section, but probably more relevant here: I would add a section about performance on this task, stating that the authors tried quite a few baselines and showed that all pretty much fail on the task, and other than that there was just one paper that got slightly better results.
-This is a place to make two more arguments:  (a) the low results obtained by the various baseline methods, as well as the low number of works (only one) that improved results on this task, compared to other similar tasks published in recent years (SQUAD, SNLI, CNN/Daily Mail., etc.), indicate that this is task is relatively hard, even for machine reading systems that has made a huge progress in recent years.
-(b) To the best of our knowledge, this is the first work to consider the style differences between the two endings, rather than the setup suggested by the author.
-\\ Btw, this could be a good place to mention the shared task.}
+%Then you can add the benchmark text below, and conclude that this indicates that this task is well designed and hard and the one hand, but might also point to potential disagreements between the train and the test data, which we highlight in this paper.}
 
@@
 \paragraph{Neural Language Model.}
-~\ms{This needs to be placed somewhere else LOL}
-~\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
+%~\ms{This needs to be placed somewhere else LOL}
+%~\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
 %\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good.
@@
 
-To leverage the genre of these short stories,\roy{Not sure this is the best introductory sentence, but you can leave it to me if you can't find anything better} we train a recurrent language model (RLM) \cite{mikolov2010recurrent},\roy{don't start with the details, but with the high level.
+We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed.
+Specifically, we train a recurrent language model (RLM) \cite{mikolov2010recurrent}.
+% , which have been shown to help
+Unlike the model in this paper, which only considers the story endings, this language model harnesses the ROC Stories training set as intended by the authors, which consists of unsupervised, single-ending stories.
+Adding in the features from the language model further boosts our performance on the Story Cloze task.
+
+% To leverage the genre of these short stories,\roy{Not sure this is the best introductory sentence, but you can leave it to me if you can't find anything better} we train a recurrent language model (RLM) \cite{mikolov2010recurrent},\roy{don't start with the details, but with the high level.
 We wanted wether our model can be combined with state-of-the-art text comprehension models, for which this task was designed.
@@
 machine translation)\roy{citation required}.
-Training this RLM on the ROC stories, we harness the unsupervised, single-ended stories\roy{I would frame it differently.
+%Training this RLM on the ROC stories, we harness the unsupervised, single-ended stories\roy{I would frame it differently.
 Unlike the model suggested in this paper, which only considers the endings, this model harnesses the training set as intended by the authors, which is composed of unsupervised, single-ended stories}, which boosts performance on the Story Cloze task.\roy{In what sense does it boost performance?
@@
 As hinted at by the creators of this task, simple language models aren't enough to do well.
-In fact, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55\%$ accuracy.
-When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68\%$.\roy{(see \tabref{cloze_results}).
-also, its 68.1, isn't it?
-(just to be consistent with the table)} This doesn't beat reported SOTA\roy{SOTA is not a standard abbreviation.
-Use state-of-the-art}, which is why we included these features into our stylistic driven model.\roy{no, this is not why we include these as features (at least not in this paper:).
-It's because we want to see whether the different approaches are complementary.}\roy{Now you need to discuss our results and what they mean.
-You can point to \tabref{cloze_results}}
+In fact, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55.0\%$ accuracy.
+When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68.1\%$ (see \tabref{cloze_results}).
+
+We notice that these features boosts perfromance by $3.6\%$, indicating that harnessing the unsupervised data from the ROC Stories complements using stylistic differences in the two endings in the Story Cloze stories.
+% \roy{Now you need to discuss our results and what they mean. You can point to \tabref{cloze_results}}
+
+% \roy{no, this is not why we include these as features (at least not in this paper:). It's because we want to see whether the different approaches are complementary.}
 

### 2017-01-27 docs/language_constraint.tex
First complete draft

@@
 \usepackage{url}
+\usepackage{caption}
+\usepackage{subcaption}
 \usepackage{pgfplots}
@@
 % Editing macros
+\newcommand{\my}[1]{\footnote{\color{red}{\textbf{#1}}}}
+
 \newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
@@
 
-\title{???}
+\title{The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task}
 
@@
 People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
-In this paper we show that writing tasks that impose constraints on the writer result in the author adopting a  different writing style compared to tasks that do not.
-As a case study, we experiment with a recently published machine reading task: the story cloze task \cite{Mostafazadeh:2016}. 
+In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
+As a case study, we experiment with a recently published machine reading task: the {\it Story Cloze task} \cite{Mostafazadeh:2016}. 
 In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
@@
 substantially higher than sophisticated deep learning models.
-Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the constraint put on the authors. 
-Our results indicate that such constraints dramatically affect the way people write. 
-They also suggest that careful attention to the instructions given to the authors needs to taken when designing new NLP tasks.
+Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors. 
+Our results indicate that different tasks dramatically affect the way people write. 
+They also provide important lessons for designing new NLP tasks.
 
@@
 Writing style is defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
-It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, native language \cite{Koppel:2005}, or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010} and its level of sarcasm \cite{Tsur:2010}.
-In this paper we study to what extent is writing style affected by more intricate factors, such as the type of constraints put on the author.
-
-As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
-In this task, authors were asked to write five-sentence self-contained stories.
-Following, the stories were given to another group of authors, who were shown only the first four sentences of each story, 
-and were asked to write two one-sentence endings for it: a {\it correct} ending, and a {\it wrong} ending.
-The goal of the task is to determine which of the endings is the correct one.
-\tabref{ROC-example} shows an example of an original story, a {\it correct} story and a {\it wrong} story.
+It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003} or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010}, its level of sarcasm \cite{Tsur:2010} and whether it's deceptive \cite{Feng:2012}.
+In this paper we study to what extent is writing style affected by more intricate factors, such as the nature of the writing task.
 
@@
 {\bf Type} & {\bf Example} \\ \hline
-{\it Original} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
-{\it Correct} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
-{\it Wrong} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
+{\color{blue}{\it Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
+{\color{forestgreen}{\it Correct}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
+{\color{red}{\it Wrong}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
 \end{tabular}
 \caption{\label{ROC-example}}
-Examples of stories from the story cloze task. The first row shows an original story written by one author. 
+Examples of stories from the story cloze task. The first row shows an {\it original} story written by one author. 
 The second and third row show two endings of the same story: a {\it correct} ending and a {\it wrong} one.
@@
 \end{table}
+
+As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
+In this task, authors were asked to write five-sentence self-contained stories (henceforth {\it original} stories).
+Following, the stories were given to other authors, who were shown only the first four sentences of each story, 
+and were asked to write two one-sentence endings: a {\it correct} ending, and a {\it wrong} ending.
+The goal of the task is to determine which of the endings is the correct one.
+\tabref{ROC-example} shows an example of an {\it original} story, a {\it correct} story and a {\it wrong} story.
 
@@
 Our experiments indicate that the answer to both questions is positive. 
-We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and PoS counts. 
-First, we show that on a balanced dataset (random guess is 50\%) our classifier distinguishes between {\it correct} and {\it wrong} sentences in 64.5\% of the cases. 
-Importantly, the classifier is trained {\bf only} on the last sentences, and does not consider the four input sentences.
+We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
+First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between {\it correct} and {\it wrong} endings in 64.5\% of the cases. 
 %It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
-Second, when trained to distinguish between original endings and new ({\it correct}) endings, the classifier obtains 70.9\% accuracy.
+Second, when trained to distinguish between {\it original} endings and new ({\it correct}) endings, the classifier obtains 68.5\% accuracy. 
+Importantly, in both experiments, the classifier uses {\bf only} the last sentence of each of the stories, and does not consider the first four sentences.
 
-In order to estimate the quality of our results, we turn back to the story cloze task.
-Using our classifier, we are able to obtain 71.5\% accuracy on the task, a 11.6\% improvement compared to the published state-of-the-art results \cite{Salle:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}).
-At the time of submission, the leading results is 71.1\%, which is much closer to our results, although still inferior.
-No details about the methods used to generate this result are available.}
-An ablation study shows that the style differences are realized in syntactic features (such as the over/under use of coordination words like ``and'' and ``but''),
-but that sentiment also plays an important role in the writing style differences.
-For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.
+In order to further estimate the quality of our results, we turn back to the story cloze task.
+Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% improvement compared to the published state-of-the-art results \cite{Salle:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}).
+At the time of submission, the leading results was 71.1\%, which is  closer to our results, although still inferior.
+No details about the validity of this result or the methods used to generate it are available.}
+When analyzing the results of our classifier, we see that sentiment plays a significant role in its success,
+which suggests that constraining authors to ``wrong'' sentences results in negative text.
+
+We show that the style differences captured by our model can be combined with a state-of-the-art machine reading tool, for which this task was designed, in order to get increased performance on the story cloze task.
+We train a neural language model on the {\it original} five sentence training corpus, and then compute the language probability of each of the candidate endings. 
+We add the resulting probabilities as features in our linear classifier, and get an additional 2.8\% improvement -- 75.2\% -- which is 15.3\% better than the best published result.
+%For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.
 
@@
 First, they have the potential to shed light on cognitive processes that take place in the brain during writing.
-Second, our results might have a more practical value in an era when fake news are becoming prominent,
-as they suggest that these might have different style compared to real news.
-Third, the results presented here also provide valuable lessons for designing new NLP tasks,
+%Second, our results might have a more practical value in an era when fake news are becoming prominent,
+%as they suggest that these might have different style compared to real news.
+Second, the results presented here also provide valuable lessons for designing new NLP tasks,
 both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
@@
 
-Finally, one interesting question that remains open is whether state-of-the-art machine reading tools, for which this task was designed, 
-capture in fact the same stylistic features as our linear classifier. 
-We show that this is not the case. 
-We train a neural language model on the original five sentence training corpus, and then compute the language probability of each of the candidates answers. 
-We add the numbers as features in our linear classifier, and get an additional 3.6\% improvement (75.1\%).
-
 The remainder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
-We present our model and our experiments at sections \ref{ssec:Model} and \ref{ssec:Experiments} respectively.
+We present our model, our experiments and our resutls in sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
 Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
@@
 \isection{The Cloze Story Task}{ROC_Story}
-%\roy{High level on first paragraph: much better, but still not enough connection to our story. You need to be explicit as to why we chose this task. Our work is currently not mentioned at all}
-To understand how constrained writing affects writing style, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}.
-We exploit various interesting properties of the associated dataset and achieve state-of-the-art performance on the task.
+In this paper, we seek to understand how different writing tasks affect writing style.
+To do so, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}. 
+While this task was developed to facilitate representation and learning of commonsense knowledge,
+it introduces a few interesting properties which makes it ideal for our purpose. 
+We describe the task below.
 
-Originally, the task was developed as an effort to facilitate representation and learning of commonsense knowledge.
-For that purpose, \citet{Mostafazadeh:2016} crowdsourced the collection of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
+%For that purpose, \citet{Mostafazadeh:2016} crowdsourced the collection of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
 
-\paragraph{ROC Stories}
-consist of $98,163$ % \roy{Minor, but still: writing the number inside dollar signs adds a white space in the pdf.
-This is a bit annoying, and also potentially confusing, as in the next case you use it below (3,744 something)}
-five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).
-Workers were instructed to write a coherent story where something happens, and with%\roy{``and with'' doesn't sound right here.
-rephrase}
-a clear beginning and end. To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories.
-\paragraph{Story Cloze}%\roy{say something general first before diving into details} 
-test sets consist of $3,744$ short stories, each with one ``right'' and one ``wrong'' ending, also collected on AMT.
-Presented with the first four sentences of a ROC story, workers were asked to write a ``right'' and a ``wrong'' ending.
-Both endings had to complete the story using one of the characters in it, and when read out of context, the ending had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
+\paragraph{ROC Stories.}
 
-The resulting stories, matched with each ending, were then individually rated for coherence and meaningfulness by AMT workers.
-Only stories rated as simultaneaously coherent with a ``right'' ending and neutral with a ``wrong'' ending were selected for the test.
-It is worth noting that workers rated the stories as a whole, not the endings; no selection was done on the endings alone.
+The ROC Story Corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
+Workers were instructed to write a coherent story, which has a clear beginning and end. 
+To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
+which resulted in a wide range of different topics.
 
-\paragraph{Design.}
-In this task, training (ROC Stories) and test (Story Cloze) data were created differently.
-%The task was designed such that the ROC stories would be used as training data and the Story Cloze stories as validation and test sets, i.e. the training and test data were created differently. 
-The ROC Stories were written by one author, and only have one ``right'' ending, whereas the Story Cloze stories have two endings, neither or which were written by the author of the rest of the story.
-Furthermore, \citet{Mostafazadeh:2016} made sure the Story Cloze endings would be hard to distinguish automatically, as each pair of endings was written by the same author.
-We show that, as a result of these design choices, the style of the ROC stories is rather different from the Story Cloze stories.
+\paragraph{Story Cloze Task.}
+After compiling the story corpus, the {\it Story Cloze Task} -- a task based on the corpus -- was introduced.
+A subset of the stories was selected, and the first four sentences of each story were presented to AMT workers.
+Workers were asked to write a {\it correct} and a {\it wrong} ending to each story prefix. 
+Both endings had to complete the story using one of the characters in it.
+Importantly,  when read out of context, the ending had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
 
-\paragraph{Benchmarks.} While the Story Cloze test is now the LSDSem `17 Shared Task and was proposed as a testbed for vector-space evaluation \cite{mostafazadeh2016story}, reported performance isn't far from a random baseline.
-\citet{Mostafazadeh:2016} implemented various benchmarks trained on the ROC Stories, using surface level features as well as narrative-informed ones.
-Compared to similar tasks \cite{hermann2015teaching,rajpurkar2016squad,bowman2015large}, the benchmarks perform relatively poorly, indicating that high performance is hard to achieve.
-To the best of our knowledge, no training has been done on pairs of endings.
+The resulting stories, both {\it correct} and {\it wrong}, were then individually rated for coherence and meaningfulness. 
+Only stories rated as simultaneously coherent with a {\it correct} ending and neutral with a {\it wrong} ending were selected for the task. 
+It is worth noting that workers rated the stories as a whole, not only the endings.
+
+Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it Story Cloze Task}. 
+The task is simple -- given a pair of stories that differ only in their endings, the system is required to determine which ending is {\it correct} and which is {\it wrong}.
+The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it correct} and {\it wrong} endings are found.
+The task was suggested as an extensive evaluation framework:
+as a machine reading task, as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
+
+\paragraph{State-of-the-Art Performance.}
+Interestingly, at the time of submission, 10 months after the paper was first published, the published benchmark on this task is still below 60\% \cite{Salle:2016}.\footnote{The LSDSem`17 shared task website does report higher results (71.1\%), which are still unpublished.}
+This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and SNLI \cite{bowman2015large}, for which results improved dramatically over a similar period of time.
+This suggest that this task is challenging and that high performance is hard to achieve.
+
+\paragraph{Different Writing Tasks in the Story Cloze Task.}
+\citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this task. 
+First, each pair of endings was written by the same author, which ensured that author style differences could not be used to solve the task. 
+Furthermore, the authors implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
+These results indicate that real understanding of text is required in order to solve the task.
+
+Despite these efforts, several key aspects were not controlled for. 
+First, the training set for the task (ROC Stories corpus) is not really a training set, as it contains only positive ({\it correct}) samples, and not negative ({\it wrong}) ones. 
+On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it correct} samples, which serve as the positive samples in the development and test sets.
+While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
+and then asking her to generate a fifth {\it correct} ending. 
+This raises the question of whether these different writing setups impose different writing styles. 
+We show that this is indeed the case.
+
+Second, although the {\it correct} and {\it wrong} sentences were generated by the same author, 
+the tasks for generating them were quite different: in one case, the author was asked to write a {\it correct} ending, which would create a coherent five-sentence story along with the other four sentences.
+In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story.
+In this work, we show that these differences are significant and impose different writing styles on authors.
+
+\paragraph{Initial Analysis.}
+We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it correct} endings and {\it wrong} endings (both from the story cloze task development set).
+Our analysis  reveals several style differences between the different groups. 
+First, {\it original} endings are on average much longer (11 words per sentence) than {\it correct} endings (8.75 words), which are in turn also longer (though not as much)  than {\it wrong} ones (8.47 words).
+Second, \figref{roc_pos_distribution} shows the distribution of five frequent PoS tags in all three groups. 
+The figure shows that both {\it original} and {\it correct} endings use pronouns more frequently than {\it wrong} endings,
+which in turn prefer proper nouns, especially compared to {\it original} endings.
+
+Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
+The figure shows that {\it original} endings prefer to use coordinations (``and'') more than  {\it correct} endings, and substantially more than {\it wrong} ones.
+Furthermore, {\it original} and {\it correct} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates'').
+Next we show that these style differences are not anecdotic, but can be used to distinguish between the different groups of text.
+
+\com{\begin{table*}[!t]
+\begin{center}
+%\small
+\begin{tabular}{|p{2.5cm}|p{4cm}|p{4cm}|p{4cm}|} \hline
+ & {\bf Original}& {\bf Correct} & {\bf Wrong}\\ \hline
+Sentence Length (\#words) & 11.02 & 8.75 & 8.47\\ \hline
+Most Frequent PoS tags (\%)  & NN:15.3\%, VBD:13.4\%, PRP:10.1, DT:9.1\%, IN:8.7\% & VBD:15.8\%, NN:15.7\%, DT:9.7\%, PRP:8.8\%, NNP:8.3\%  & NN:16.3\%, VBD:15.1\%,  NNP:9.5\%, DT:9.4, IN:7.9\%\\ \hline
+Most Frequent Words  (\%) & the:4.5\%, to:3.3\%, and:2.7\%, was:2.6\%, a:2.2\% & the:4.8\%, to:3.9\%, was:3.5\%, a:2.5\%, and:2.1\%   & the:5\%, to:4\%, was:3\%, a:2\%, I:1.6\%\\ \hline
+\end{tabular}
+\end{center}
+\caption{\label{roc_pos_distribution} 
+\end{table*}
+}}
+
+\begin{figure*}[t!]
+\begin{subfigure}{.5\textwidth}
+\begin{tikzpicture}
+\small
+    \begin{axis}[
+        width  = 0.4*\textwidth,
+        height = 4cm,
+      %  major x tick style = transparent,
+        ybar=\pgflinewidth,
+        x=2.5cm,
+       bar width=5pt,
+        ymajorgrids = true,
+        ylabel = {Frequency in Corpus (\%)},
+        symbolic x coords={{\it Original}, {\it Correct}, {\it Wrong}},
+        xtick = data,
+        scaled y ticks = false,
+        %enlarge x limits=0.25,
+        ymin=3,
+        legend cell align=left,
+        legend style={
+        		legend columns=-1,
+                at={(1,1.05)},
+                anchor=south east,
+                column sep=1ex
+        }
+    ]
+        \addplot[style={bblue,fill=bblue,mark=none}]
+            coordinates {({\it Original}, 15.3) ({\it Correct}, 15.7) ({\it Wrong}, 16.3)};
+
+        \addplot[style={rred,fill=rred,mark=none}]
+            coordinates {({\it Original}, 13.4) ({\it Correct}, 15.8) ({\it Wrong}, 15.1)};
+
+        \addplot[style={ggreen,fill=ggreen,mark=none}]
+            coordinates {({\it Original}, 10.1) ({\it Correct}, 9.7) ({\it Wrong}, 7.4)};
+
+        \addplot[style={brown,fill=brown,mark=none}]
+            coordinates {({\it Original}, 9.1) ({\it Correct}, 9.7) ({\it Wrong}, 9.4)};
+
+        \addplot[style={gray,fill=gray,mark=none}]
+            coordinates {({\it Original}, 4.7) ({\it Correct}, 8.3) ({\it Wrong}, 9.5)};
+
+        \legend{NN, VBD, PRP, DT, NNP}
+    \end{axis}
+\end{tikzpicture}
+\caption{\label{roc_pos_distribution}PoS tags}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+\begin{tikzpicture}
+\small
+    \begin{axis}[
+        width  = 0.4*\textwidth,
+        height = 4cm,
+      %  major x tick style = transparent,
+        ybar=\pgflinewidth,
+        x=2.5cm,
+       bar width=5pt,
+        ymajorgrids = true,
+%        ylabel = {Frequency in Corpus (\%)},
+        symbolic x coords={{\it Original}, {\it Correct}, {\it Wrong}},
+        xtick = data,
+        scaled y ticks = false,
+        %enlarge x limits=0.25,
+        ymin=0,
+        legend cell align=left,
+        legend style={
+        		legend columns=-1,
+                at={(1,1.05)},
+                anchor=south east,
+                column sep=1ex
+        }
+    ]
+        \addplot[style={bblue,fill=bblue,mark=none}]
+            coordinates {({\it Original}, 3.4) ({\it Correct}, 3.9) ({\it Wrong}, 4)};
+
+        \addplot[style={rred,fill=rred,mark=none}]
+            coordinates {({\it Original}, 2.8) ({\it Correct}, 2) ({\it Wrong}, 1.5)};
+
+        \addplot[style={ggreen,fill=ggreen,mark=none}]
+            coordinates {({\it Original}, 1.1) ({\it Correct}, 1.4) ({\it Wrong}, 1.6)};
+
+        \addplot[style={brown,fill=brown,mark=none}]
+            coordinates {({\it Original}, 0) ({\it Correct}, 0) ({\it Wrong}, 0.7)};
+
+        \addplot[style={gray,fill=gray,mark=none}]
+            coordinates {({\it Original}, 0.1) ({\it Correct}, 0.2) ({\it Wrong}, 0)};
+
+        \legend{to, and, I, hates, better}
+    \end{axis}
+\end{tikzpicture}
+\caption{\label{roc_word_distribution}Words}
+\end{subfigure}
+\caption{The distribution of five frequent PoS tags (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})  across different endings: {\it Original} -- endings of stories from the ROC story corpus (the story cloze training set).
+{\it Correct} -- correct endings, {\it Wrong} -- wrong endings (both from story cloze task).}
+
+\end{figure*}
 
@@
 
-We train a linear SVM classifier to distinguish between different endings. 
+We train a linear logistic regression (aka Maximum Entropy) classifier to distinguish between different endings. 
 Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
@@
 \begin{itemize}
-\item\textit{\textbf{Length~}} The number of words in the sentence.
-\item\textit{\textbf{Word n-grams~}} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
-Specifically, we replace content words with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
-\item\textit{\textbf{Character n-grams~}} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
-We used character 5-grams.
+\item\textit{\textbf{Length}.} The number of words in the sentence.
+\item\textit{\textbf{Word n-grams.}} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
+Specifically, we replace content words, which are often low frequency, with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
+\item\textit{\textbf{Character n-grams.}} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
+We use character 4-grams.
 \end{itemize}
@@
 The first is an attempt to distinguish between {\it correct} and {\it wrong} endings.
-The second attempts to distinguish between original endings and new {\it correct} endings.
+The second attempts to distinguish between {\it original} endings and new ({\it correct}) endings.
 We describe both experiments below.
@@
 The goal of this experiment is to measure to what extent  style features capture differences between {\it correct} and {\it wrong} endings.
-As the cloze story task doesn't have a training corpus for the {\it correct} and {\it wrong} endings, we use the development set as our training set. 
+As the cloze story task doesn't have a training corpus for the {\it correct} and {\it wrong} endings (see \secref{ROC_Story}), we use the development set as our training set. 
 We split it (90/10) into our training and development set. We keep the story cloze test set as is.
-The final size of our training/development/test sizes are 3366/374/3742, respectively.
+The final size of our training/development/test sizes are 3,366/374/3,742 endings, respectively.
 
-We take  {\it correct} endings as positive samples and {\it wrong} endings as our negative examples. 
-By ignoring the coupling between {\it correct}/{\it wrong} pairs, we are able make a more general claim about the style used when writing each of the tasks.
-
-We add a special START symbol at the beginning of each sentence. 
-For computing our features, we keep n-gram (character or word) features that occur at least five times in the training set.\footnote{Virtually all sentences end with a period, so no need for an END token}
-For the PoS features, we tag each sentence with the Spacy PoS tagger.\footnote{\url{spacy.io/}}
-We use  sklearn's LinearSVC SVM implementation\footnote{\url{scikit-learn.org/stable/modules/generated/sklearn.svm.LinearSVC.html}} 
-with L2 loss. We grid search the regularization parameter on our development set.
+It is worth nothing that our classification task is slightly different from the {\it story cloze Task}. 
+Instead of classifying pairs of endings, one which is {\it correct} and another which is {\it wrong}, we take the set of  {\it correct} endings as positive samples and the set of {\it wrong} endings as our negative examples.
+By ignoring the coupling between {\it correct} and {\it wrong} pairs, we are able make a more general claim about the style used when writing each of the tasks.
 
@@
 Here the goal is to measure whether writing the ending as part of a story imposes different style compared to writing a ({\it correct}) ending to an existing story.
-We use the endings of the original ROC stories as our {\it original} training samples and {\it correct} endings from the ROC stories development set as {\it new} training samples.
+We use the endings of the ROC stories as our {\it original} training samples and {\it correct} endings from the story cloze task  development and test sets as {\it new} training samples.
 As there are far more {\it original} samples than {\it new} ones, we randomly select $N$ {\it original} samples, where $N$ is the number of {\it new} samples,
-such that we have balanced labels in our training, validation and test sets.
-We apply the same experimental decisions as in Experiment 1, and repeat this process 5 times while reporting the average.
+such that we have balanced labels in our training, validation and test sets (sizes are the same as in Experiment 1).
+We randomly sample 5 training sets and report the average classification result.
 
-\paragraph{Results.}
+\paragraph{Experimental Setup.}
+In both experiments, we add a START symbol at the beginning of each sentence.\footnote{Virtually all sentences end with a period or an exclamation mark, so we do not add an END token} 
+For computing our features, we keep n-gram (character or word) features that occur at least five times in the training set.
+All feature values are normalized to [0-1].
+For the PoS features, we tag all endings with the Spacy PoS tagger.\footnote{\url{spacy.io/}}
+We use  python's sklearn logistic regression implementation with L2 loss. 
+We grid search the regularization parameter on our development set.
+
+\isectionb{Results}
 \figref{results} shows our results.
 Results show that for Experiment 1, our model obtains results well above a random baseline -- 64.5\% classification accuracy. 
-For Experiment 2, we get even higher results -- 70.9\%. 
-These numbers indicate that these different writing tasks clearly impose a different writing style on authors.
+For Experiment 2, we get even higher results -- 68.5\%. 
+These numbers indicate that these different writing tasks clearly impose different writing styles on authors.
 
@@
 Our hypothesis is that differences would be even clearer. 
-Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 78\%.
+Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.
 
@@
         \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it Correct/Wrong}, 0.645) ({\it Original/New}, 0.709) ({\it Original/Wrong},0.78)};
+            coordinates {({\it Correct/Wrong}, 0.645) ({\it Original/New}, 0.685) ({\it Original/Wrong},0.756)};
 
@@
 \caption{\label{results} Results of  experiments 1 and 2 (left two charts). 
-Rightmost experiment shows a control experiment which classifies {\it original} endings vs \textit{\textbf{wrong}} endings. }
+Rightmost graph shows a control experiment which classifies {\it original} endings vs \textit{\textbf{wrong}} endings. }
 \end{figure}
 
-\paragraph{Story Cloze.}
-Results of Experiment 1 indicate that {\it correct} and {\it wrong} endings are characterized by different styles.
-In order to estimate the quality of our classification results, we tackle the story cloze task using our classifier.
-This classification task is much more constrained than Experiment 1, as here the task is given two endings, which one is {\it correct} and which is {\it wrong}.
+\paragraph{Story Cloze Task.}
+The results of Experiment 1 indicate that {\it correct} and {\it wrong} endings are characterized by different styles.
+In order to further estimate the quality of our classification results, we tackle the story cloze task using our classifier.
+This classification task is more constrained than Experiment 1, as here the task is given two endings, which one is {\it correct} and which is {\it wrong}.
 In order to solve the task, we use the output of our trained classifier. 
-For each pair of endings $e_1,e_2$, if both endings have different classification labels, we keep these labels. 
-If they share the same label, we use the classifier confidence level as a deciding factor: the label of the one with the lower confidence is reversed.
+For each pair of endings in our test set, if the classifier assigns different labels to them, we keep these labels. 
+If they share the same label, then one of them must be wrong, so we use the classifier confidence level as a deciding factor: the label of the one with the lower confidence is reversed.
 
-\tabref{cloze_results} shows our results on the story cloze test set. Our classifier obtains 71.5\% accuracy, which is 11.6\% better than the published state-of-the-art result on the task.
+\tabref{cloze_results} shows our results on the story cloze test set. Our classifier obtains 72.4\% accuracy, which is 12.5\% higher than the published state-of-the-art result on the task.
 Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even look at the first four sentences of the story in question.
-These numbers indicate that the styles between {\it correct} and {\it wrong} are indeed very different.
+These numbers indicate that the styles of {\it correct} and {\it wrong} endings are indeed very different.
 
 Other than the published works that tackled this task, a few  recent works published their results in the LSDSem shared task website.\footnote{\url{https://competitions.codalab.org/competitions/15333}}
-As to the time of submission, our results are still state-of-the-art (though by a much smaller margin). No other information other than the name of the group and their results is available.
+As to the time of submission, our results are still state-of-the-art (though by a  smaller margin). 
+No other information other than the name of the groups and their results is available.
 
@@
 {DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ \hline
-{ LexVec} \cite{Salle:2016} & 0.599 \\ \hline
-{RNN}		& 0.681 \\ \hline
-{\bf Our Model} & {\bf 0.715} \\ \hline
-{\bf Combined (Our model, RNN)} & {\bf 0.751} \\ \hline\hline
-{ Niko (shared task)}	& 0.7\\ \hline\hline
+{ LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
+{ Niko (shared task)}	& 0.7\\ \hline
 { tbmihaylov (shared task)} & 0.711\\ \hline\hline
+{RNN}		& 0.677 \\ \hline
+{\bf Our Model} & {\bf 0.724} \\ \hline
+{\bf Combined (Our model, RNN)} & {\bf 0.752} \\ \hline\hline
 Human judgment & 1 \\ \hline
@@
 Results on the test set of the cloze story task. 
-Upper part are published results (Lexvec results are taken from \cite{Speer:2016}).
-Bottom part are taken from the cloze task shared task webpage.
+Upper part are published results.
+LexVec results are taken from \cite{Speer:2016}.
+Results in the middle part are taken from the LSDSem 2017 shared task webpage.
+Bottom part is our results.
+RNN is our implementation of an RNN.
 \end{table}
+
+\paragraph{Combination with an RLM.}
+We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed. 
+Specifically, we experiment with a recurrent language model (RLM, \citet{mikolov2010recurrent}). % on the ROC story corpus training data,
+%and use it to compute the probability of both {\it correct} and {\it wrong} endings in the story cloze test set.
+Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the story cloze task designers, and harnesses the ROC Stories training set, which consists of single-ending stories.
+We show that adding the language model features  further boosts our performance on the story cloze task.
+
+We train the RLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
+We use the ROC Stories for training, setting aside $10\%$ for validation of the language model. 
+We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=$21,582.
+Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
+Using AdamOptimizer \cite{kingma2014adam} and a learning rate of $\eta=.001$, we train with backpropagation on cross-entropy. % minibatches of $50$ stories.
+% h=512, dropout rate of 60%, V=21582, 10% validation set
+
+% Eval
+On its own, our neural language model performs moderately on the story cloze test. 
+This is not surprising, as \citet{Mostafazadeh:2016} hinted  that simple language models do not perform well on the task. 
+Indeed, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55\%$ accuracy. 
+However, when using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, performance jumps to $67.7\%$ (see \tabref{cloze_results}).\footnote{Further analysis of this large performance gain is out of the scope of this paper.}
+
+We combine our linear model with the RLM by adding three features to our classifier: $p_\theta(ending|story),p_\theta(ending)$ and $\frac{p_\theta(ending|story)}{p_\theta(ending)}$. 
+We retrain our linear  model with the new feature set, and notice a performance   boost  of $2.8\%$ -- up to 75.2\%, which is 15.3\% better than current published state-of-the-art, and 4.1\% better than best unpublished result.
+These results indicate that while style features can be used to obtain high accuracy on the task, adding context and training on a large dataset can improve performance even more.
 
@@
 To answer this question, we re-ran Experiment 1 with different sub-groups of features. 
-\tabref{subgroups} shows our results. Results clearly show that  character n-grams are the most effective style predictors, reaching within less than 2\% of the full model.
+\tabref{subgroups} shows our results.
+Results clearly show that  character n-grams are the most effective style predictors, reaching within  0.6\% of the full model, but that word n-grams also capture much of the signal, yielding 61.2\%.
 These findings are in line with previous works that used character n-grams along with other types of features to predict writing  style \cite{Schwartz:2013}.
@@
 {\bf Feature Type} & {\bf Result}\\ \hline
-Word n-grams & 0.646 \\ \hline
-Char n-grams & 0.699 \\ \hline
-Full Model & 0.715 \\ \hline
+Word n-grams & 61.2\% \\ \hline
+Char n-grams & 63.9\% \\ \hline
+Full Model & 64.5\% \\ \hline
 
@@
 
-\paragraph{Most Salient Features.}
-In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
-This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.715).  
-\tabref{features} shows the 5 features with the highest positive and negative weights in the hyperplane. 
+\paragraph{Most Salient Features -- Experiment 1.}
+%In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
+%This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.724).  
+\tabref{exp1_features} shows the five features with the highest positive and negative weights in the logistic regression classifier hyperplane for Experiment 1. 
 These correspond to the 5 most salient features for {\it correct} and {\it wrong} endings, respectively.
@@
 The table shows a few interesting trends. 
-First, some syntactic features play become salient when authors are asked to write {\it wrong} vs. {\it correct} endings.
-For instance, {\it correct} endings are more likely to the coordinator ``but'', while {\it wrong} ones would prefer to use ``and''.
+First, it seems that authors tend to design their sentences differently when writing {\it correct}  vs. {\it wrong} endings.
+For instance, {\it correct} endings are more likely start with an adverb (e.g., ``then'', ``so'', ``eventually''), while {\it wrong} ones would prefer to start with a proper noun.
+Similarly, {\it wrong} endings have a preference to end the sentence with a common noun.
 
-More interestingly, {\it correct} endings are likely to use positive words (e.g., `` bett'', which in all cases stands for `` bett{\bf er}''), while  {\it wrong} endings would use negative words (e.g., `` hate'').
-The idea that  sentiment would play a role in this task was suggested in the original story cloze paper, where two sentiment-based baselines were evaluated. 
-However, these baselines measured the relative sentiment between the ending and the previous sentences, and did not test whether there is a general tendency of the {\it wrong} endings to have a negative sentiment, and the {\it correct} one to have a positive sentiment.
-Indeed, the performance of both these baselines was roughly chance-level.
+More interestingly, the different writing tasks seem to impose a specific sentiment on the writer. 
+Three of the top four most salient features for detecting {\it wrong} endings are variants of the verb ``hate''.
+This indicates that when authors are asked to write {\it wrong} text, they tend to use negative language.
+
+An alternative explanation to this hypothesis might be that the first four sentences of the stories in the ROC story corpus tend to be positive, and thus in order to make an ending {\it wrong}, authors adopted a negative approach.
+A similar idea was suggested in the original story cloze paper, where two sentiment-based baselines were evaluated. 
+These baselines measured the relative sentiment between the ending and the previous sentences.
+The performance of both these baselines was roughly chance-level, which seems to suggest that this is not the case.
 
@@
 \begin{tabular}{|c|c|} \hline
-{\bf Positive} & {\bf Negative}\\ \hline
-` time' & `ed of'\\ \hline
-` bett' & `and d'\\ \hline
-`found' & `threw'\\ \hline
-`but' & `ever '\\ \hline
-`ally ' & ` hate'\\ \hline
+\textit{\textbf{Correct}} & \textit{\textbf{Wrong}}\\ \hline
+`ally' & ` hate'\\ \hline
+`VBD the' & ` hat'\\ \hline
+`START RB' & `START NNP'\\ \hline
+`ved ' & `ated'\\ \hline
+` tim' & `NN .'\\ \hline
 
@@
 \end{center}
-\caption{\label{features}}
-The top 5 most discriminative features for predicting {\it correct} (Positive)  and {\it wrong} (Negative) endings.\end{table}
+\caption{\label{exp1_features}}
+The top 5 most discriminative features for predicting {\it correct} and {\it wrong} endings.\end{table}
 
-\[add\ control\ experiments\]
+\paragraph{Most Salient Features -- Experiment 2.}
+%In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
+%This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.724).  
+\tabref{exp2_features} shows the same analysis for Experiment 2.
+Interestingly, here the most salient features are quite different. 
+As noticed on \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
+Another clear style difference is the use of punctuation: {\it original} endings often end with exclamation marks, while {\it new} endings end almost exclusively with periods. 
+Finally, syntactic difference appear to play an important role in stylistic differences between the two tasks. 
+Specifically, {\it original} endings contain more common nouns (NN), adverbs (RB) and gerunds (VBG), while {\it new} endings seem to contain more past tense verbs (VBD), especially as the second word in the sentence.
 
-\paragraph{Neural Language Model.}
-%~\ms{This needs to be placed somewhere else LOL}
-%~\ms{Below is a messy dump of all the hyper parameters... Didn't know how many details were needed}
-%\roy{The level of description seems fine (we might remove some of them if space is an issue, but for now it's good.
-What I'm missing here are (a) an introductory 1-2  sentences to what are we doing here (I realize that it is not 100\% clear from the intro what is the role of these experiments other than showing that we have STOA results, so this can come later\\
-%(b) A one-sentence description of your model. Currently, there is no clear separation between the model (RNN using LSTM) and the technical details. 
-%Some general description of the model, and specifically the motivation behind (nothing fancy, just saying that we applied state-of-the-art LM tools, 
-%which resemble the tools the authors had in mind when they designed the task).}
+\begin{table}[!t]
+\begin{center}
+%\small
+\begin{tabular}{|c|c|} \hline
+\textit{\textbf{Original}} & \textit{\textbf{New}}\\ \hline
+{\it length} & `.'\\ \hline
+`!' & `START NNP'\\ \hline
+`NN' & `START NNP VBD'\\ \hline
+`RB' & `START I VBD'\\ \hline
+`VBG' & `NNS .'\\ \hline
 
-We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed.
-Specifically, we train a recurrent language model (RLM) \cite{mikolov2010recurrent}.
-% , which have been shown to help
-Unlike the model in this paper, which only considers the story endings, this language model harnesses the ROC Stories training set as intended by the authors, which consists of unsupervised, single-ending stories.
-Adding in the features from the language model further boosts our performance on the Story Cloze task.
-
-% To leverage the genre of these short stories,\roy{Not sure this is the best introductory sentence, but you can leave it to me if you can't find anything better} we train a recurrent language model (RLM) \cite{mikolov2010recurrent},\roy{don't start with the details, but with the high level.
-We wanted wether our model can be combined with state-of-the-art text comprehension models, for which this task was designed.
-{\bf Specifically}, we train an RLM \dots}  which are used to achieve state-of-the-art performance on various tasks (e.g.
-machine translation)\roy{citation required}.
-%Training this RLM on the ROC stories, we harness the unsupervised, single-ended stories\roy{I would frame it differently.
-Unlike the model suggested in this paper, which only considers the endings, this model harnesses the training set as intended by the authors, which is composed of unsupervised, single-ended stories}, which boosts performance on the Story Cloze task.\roy{In what sense does it boost performance?
-we get STOA results without it...}
-
-We trained an RLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
-We used the ROC Stories for training, setting aside $10\%$ for validation of the language model.
-We replaced all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=21,582$.
-Only during training, we applied a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories.
-Using AdamOptimizer \cite{kingma2014adam} and a learning rate of $\eta=.001$, we trained with backpropagation on cross-entropy.
-% minibatches of $50$ stories.
-% h=512, dropout rate of 60%, V=21582, 10% validation set
-
-% Eval
-On its own, our neural language model performs moderately on the Story Cloze test.
-As hinted at by the creators of this task, simple language models aren't enough to do well.
-In fact, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55.0\%$ accuracy.
-When using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, we obtain $68.1\%$ (see \tabref{cloze_results}).
-
-We notice that these features boosts perfromance by $3.6\%$, indicating that harnessing the unsupervised data from the ROC Stories complements using stylistic differences in the two endings in the Story Cloze stories.
-% \roy{Now you need to discuss our results and what they mean. You can point to \tabref{cloze_results}}
-
-% \roy{no, this is not why we include these as features (at least not in this paper:). It's because we want to see whether the different approaches are complementary.}
-
-% To construct features for the Story Cloze task, we scored each of the two endings using our neural language model.
-We computed the probability of each ending given the first four sentences $p_\theta(ending|story)$, as well as the probability of the endings out of context $p_\theta(ending)$.
-We also included the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ into our classifier.
-%\roy{This will probably change once we have the rest of the paper, but generally a few things that are missing:(a) performance of the model as a standalone (both how we evaluated it and how much it got).
-(b) modifying this paragraph to indicate that in order to combine between the style features presented in this paper and this model, we did the above.(c) results of the combination (75.1\%).\\These numbers might best fit in a small table.}
+\end{tabular}
+\end{center}
+\caption{\label{exp2_features}}
+The top 5 most discriminative features for predicting {\it original} and {\it new} ({\it correct}) endings.\end{table}
 
@@
 
+In this paper we have shown that different writing tasks affect writing style. 
+Our results indicate that when authors are asked to write the last sentence of a five sentence story, they will use different style to write a {\it correct} ending compared to a {\it wrong} ending.
+We have also shown that writing the ending as part of a five sentence story is very different than reading four sentences and then writing the fifth.
+
+Our findings hint that the nature of the writing task imposes a different mental state on the author, which is expressed in ways which are often implicit, but can be unfolded using simple automatic tools.
+This is in line with previous cognitive findings. 
+For instance, previous studies have shown that when answering questions, people  tend to adopt the writing style of the question \cite{Ireland:2010}.
+
+Other studies have shown that writing tasks can even have a long term effect.
+A range of works have shown that writing emotional texts and benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
+Some of these works showed that these changes are also accompanied by changes in writing style \cite{Campbell:2003}. 
+The results of the current study can shed more light on the processes that people undergo when presented with different writing tasks.
+
+This paper also reveals several important lessons for the future design of NLP tasks. 
+First, it stresses the need to carefully control for even seemingly minor details. 
+Second, it emphasizes the importance of running baseline models.
+While recent advances in NLP  suggest that many classic NLP methods are out-of-date, 
+this is not necessarily the case, especially for small datasets.
+This is particularly important in order to ensure that  new technological improvements are capturing a qualitatively different signal.
+Luckily, the substantial improvement we get when combining our model with the RNN language model (\secref{Experiments}) suggests that despite the high results obtained by the simple, classic model, the more recent RNN approach captures a different aspect of the task.
+
 \isection{Related Work}{Related}
 
-\begin{itemize}
-\item Different style application (as in introduction). Also include deception works (Yejin has 1-2 papers on it). 
-\item Machine reading papers? 
-\item \ms{Pennebaker's work on function words? they link function words to psychological aspects}
-\end{itemize}
+\paragraph{Writing Style.}
+Writing style has been an active topic of research for decades now. 
+The models used to effectively solve  such tasks are often linear classifiers with style features such as character and word n-grams \cite{Stamatatos:2009,Koppel:2009}.
+Previous works have shown that different authors can be grouped by their writing style, according to factors such as age \cite{Pennebaker:2003,Argamon:2003,Schler:2006,Rosenthal:2011}, gender \cite{Argamon:2003,Schler:2006} and native language \cite{Koppel:2005}.
+At the extreme case, each individual author adopts a unique writing style \cite{pennebaker1999linguistic,Schwartz:2013}. 
+Interestingly, previous work have shown that individual style can be affected from coarse-grained factors such as those just described, but also from other less apparent factors such as mental state, or even living in a high elevation location \cite{schwartz2013personality}.
+
+Unlike the works just described which compare the writing style between different authors, some works have shown that the same author can adopt different style used when writing positive vs.
+negative text \cite{Davidov:2010} and when writing sarcastic text \cite{Tsur:2010}.
+In this work, we have shown that the same author can adopt a different style when facing different writing tasks.
+
+The line of works that most resembles our work is the detection of deceptive text. 
+Several works used stylometric features to  predict deception 
+\cite{Newman:2003,hancock2007lying,ott2011finding,Feng:2012}.
+Some works even showed that writing style applied when lying is different across genders \cite{Perez:2014a,Perez:2014b}.
+In this work, we have shown that an even more subtle writing task -- writing {\it correct} and {\it wrong} story endings -- imposes different styles on the author.
+
+\paragraph{Machine Reading.}
+The cloze story task, which is the focus of this paper, is part of a wide set of machine reading works published in the last couple of years.
+These include datasets like bAbI \cite{Weston:2015}, SNLI \cite{bowman2015large}, CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and LAMBADA \cite{Paperno:2016}.
+
+While these works have presented valuable resources for the NLP community (as well as for the deep learning community), 
+it is often the case that these datasets suffer from methodological problems, such as inherent ambiguity caused by applying automatic tools when generating the datasets \cite{Chen:2016}. 
+In this paper we have pointed to other methodological problems in  machine reading tasks, namely the different writing tasks used to generated the data, which largely affect the writing style of the positive and negative samples, as well as creates a discrepancy between the training and the test data.
 
 \isectionb{Conclusion}
+
+The research question that guided this work is to what extent do different writing tasks impose different writing styles on authors.
+We experimented with the story cloze task, which introduces two interesting setups for our purposes:
+a setup where the same author writes both a {\it correct} and a {\it wrong} ending to a story, 
+and one which compares an ending written as part of a story to a standalone ending added to a story written by someone else.
+In both cases, a simple linear model reveals that different styles are imposed.
+The different styles allow our style detection model to reach state-of-the-art results on the story cloze task, more than 12\% improvement compared to the best published result.
+
+The findings presented in this paper have  cognitive implications, as they motivate further research on the exact effect that different writing tasks have on humans.
+They also provide valuable lessons as to the design of future NLP datasets.
+Future work will include testing whether other similar writing tasks, such as fake news, also impose their own unique and identifiable style on their authors.
 

### 2017-01-27 gen_pattern_features.PL

@@ -12,7 +12,7 @@ sub main(@) {
 	my $patt_file;
 	my $of;
 	my $use_len;
-	my $char_ngrams=5;
+	my $char_ngrams=4;
 	
 	MyUtils::usage({
 		"if=s" => \$if,
@@ -27,13 +27,17 @@ sub main(@) {
 	$max_patt_len--;
 	my %saved;
 
+	my $max_len = 0;
+	
 	if (-e $patt_file) {
 		my $ifh = openRFile($patt_file);
 		
+		$max_len = $ifh->getline();
+		chomp($max_len);
 		while (my $line = $ifh->getline()) {
 			chomp($line);
-			my ($patt, $n) = split("	", $line);
-			$saved{$patt} = $n;
+			my ($patt, $n, $sum, $max) = split("	", $line);
+			$saved{$patt} = [$n, $max];
 		}
 		
 		$ifh->close();
@@ -41,29 +45,44 @@ sub main(@) {
 		my %patts;
 		my $ifh = openRFile($if);
 
+		my $is_first = 1;
 		while (my $line = $ifh->getline()) {
 			chomp($line);
 	
 			my ($label, $text) = split("\t", $line);
 	
 			my @w = split(" ", $text);
+			
+			if (defined $use_len and @w > $max_len) {
+				$max_len = @w;
+			}
 
 			my $patts = get_patts(\@w, $max_patt_len, $char_ngrams);
 
 			foreach my $patt (keys %$patts) {
-				$patts{$patt} += $patts->{$patt};
+				unless (exists $patts{$patt}) {
+					$patts{$patt} = [$patts->{$patt}, $patts->{$patt}];
+				} else {
+					$patts{$patt}->[0] += $patts->{$patt};
+					if ($patts{$patt}->[1] < $patts->{$patt}) {
+						$patts{$patt}->[1] = $patts->{$patt}
+					}
+				}
 			}
+			$is_first = 0;
 		}
 		$ifh->close();
 		
 		my $i = 0;
-		my @sk = sort {$patts{$b} <=> $patts{$a}} keys %patts;
+		my @sk = sort {$patts{$b}->[0] <=> $patts{$a}->[0]} keys %patts;
 
 		my $ofh = openWFile($patt_file);
+		
+		$ofh->print($max_len."\n");
 		foreach my $k (@sk) {
[…]

### 2017-01-27 train_SVM.py

@@ -4,7 +4,7 @@ import sys
 import ROC_SVM
 from scipy.sparse import *
 from scipy import *
-from sklearn import svm
+from sklearn import svm,linear_model
 import pickle
 from optparse import OptionParser,OptionValueError
 
@@ -18,13 +18,14 @@ def main():
     n_feats = options.n_feats
     C = float(options.C)
     do_rank = bool(options.do_rank)
+    do_logistic_regression = bool(options.do_logistic_regression)
     n_feats = int(options.n_feats)
     model_of = options.model_of
     penalty=options.penalty
     
     if (penalty == 'l1'):
-#        loss='hinge'
         dual=False
+        loss='hinge'
 
     [features, labels] = ROC_SVM.read_features(ifile, n_feats)
     
@@ -33,7 +34,11 @@ def main():
     
     print "Done. Now feating"
     
-    clf = svm.LinearSVC(C=C,penalty=penalty,loss=loss,dual=dual)
+    if (do_logistic_regression):
+        dual=False
+        clf = linear_model.LogisticRegression(C=C,penalty=penalty,dual=dual)
+    else:
+        clf = svm.LinearSVC(C=C,penalty=penalty,loss=loss,dual=dual)
 
     clf.fit(features, labels)
     pickle.dump(clf, open(model_of, 'wb'))
@@ -55,6 +60,7 @@ def usage():
     loss='squared_hinge'
     dual=True
     do_rank = 0
+    do_logistic_regression = 0
    
     parser = OptionParser()
     give_tag=0
@@ -76,6 +82,8 @@ def usage():
                             default=penalty)
     parser.add_option("-r", dest="do_rank", default=False, action="store_true",
                             help="Use ranking")
+    parser.add_option("-l", dest="do_logistic_regression", default=False, action="store_true",
+                            help="Use logistic regression and not SVM")
                     
     
     (options, args) = parser.parse_args()

### 2017-01-28 docs/language_constraint.tex
compressed abstract
compressed abstract

@@
 \begin{abstract}
-People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
-In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
-As a case study, we experiment with a recently published machine reading task: the {\it Story Cloze task} \cite{Mostafazadeh:2016}. 
-In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
-We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, obtains state-of-the-art results on the task,
-substantially higher than sophisticated deep learning models.
-Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors. 
+People's writing style %is affected by many factors, including topics, sentiment, and individual personality. 
+depends on both personal factors such as demographic background and situational factors such as the purpose of writing.
+%In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
+In this paper, we show that authors adopt different writing style even when engaged with similar tasks if their purpose differs.
+%As a case study, we experiment with a recently published machine reading task: 
+We present a case study based on 
+the {\it story cloze task} \cite{Mostafazadeh:2016}, %.
+%In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
+where people were asked to write two contrastive sentences as story ending: one plausible and one implausible for a given story context. 
+%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
+We show that a simple linear classifier with stylistic features obtains 
+state-of-the-art results on the task,
+substantially higher than sophisticated deep learning models,
+even without looking at the story context. 
+%Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors. 
 Our results indicate that different tasks dramatically affect the way people write. 

### 2017-01-29 docs/language_constraint.tex

@@
 \newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
+\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
 
@@
 \begin{abstract}
-People's writing style %is affected by many factors, including topics, sentiment, and individual personality. 
-depends on both personal factors such as demographic background and situational factors such as the purpose of writing.
+%People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
+People's writing style depends not just on the authors' personal traits but also on the intent and the cognitive states of the authors. 
 %In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
-In this paper, we show that authors adopt different writing style even when engaged with similar tasks if their purpose differs.
+In this paper, we show how similar writing tasks involving different cognitive processes can lead to measurable differences in people's writing style. % of the same authors.  
 %As a case study, we experiment with a recently published machine reading task: 
@@
 %In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
-where people were asked to write two contrastive sentences as story ending: one plausible and one implausible for a given story context. 
+where annotators were assigned with similar writing tasks with different constraints: (1) writing an entire story on their own vs.
+adding only a story ending for a given story context and (2) writing a story ending that makes the overall story coherent vs.
+incoherent.
 %We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
-We show that a simple linear classifier with stylistic features obtains 
-state-of-the-art results on the task,
+We show that a simple linear classifier informed with stylistic features obtains 
+state-of-the-art results on the story cloze challenge,
 substantially higher than sophisticated deep learning models,
@@
 %Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors. 
-Our results indicate that different tasks dramatically affect the way people write. 
+Our results demonstrate that different task framings can dramatically affect the way people write. 
 They also provide important lessons for designing new NLP tasks.
@@
 \section{Introduction}
-Writing style is defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
-It is often affected by inter-writer factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003} or mere personality \cite{Stamatatos:2009}, but also by other parameters such as the sentiment of the text \cite{Davidov:2010}, its level of sarcasm \cite{Tsur:2010} and whether it's deceptive \cite{Feng:2012}.
-In this paper we study to what extent is writing style affected by more intricate factors, such as the nature of the writing task.
+Writing style is 
+%defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
+expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
+%It is often affected by inter-writer 
+It is influenced by both 
+personal 
+factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003} 
+%or mere 
+and 
+personality \cite{Stamatatos:2009}, 
+%but also by other parameters 
+and the cognitive states of the authors such as 
+%such as the sentiment of the text \cite{Davidov:2010}, its level of sarcasm \cite{Tsur:2010} and whether it's deceptive \cite{Feng:2012}.
+sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
+In this paper, we study 
+%to what extent is 
+the extent to which people's 
+writing style is affected by intricate factors, such as 
+the nature of the writing task that would involve different cognitive processes.
 
@@
 %\small
-\begin{tabular}{|p{1.3cm}|p{5.6cm}|} \hline
+\begin{tabular}{|p{1.6cm}|p{5.3cm}|} \hline
 {\bf Type} & {\bf Example} \\ \hline
 {\color{blue}{\it Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
-{\color{forestgreen}{\it Correct}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
-{\color{red}{\it Wrong}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
+{\color{forestgreen}{\it Coherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
+{\color{red}{\it Incoherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
 \end{tabular}
-\caption{\label{ROC-example}}
+\caption{\label{ROC-example}
 Examples of stories from the story cloze task. The first row shows an {\it original} story written by one author. 
-The second and third row show two endings of the same story: a {\it correct} ending and a {\it wrong} one.
+The second and third row show revised stories with two contrastive endings:
+ %of the same story: 
+ a {\it right} ending and a {\it wrong} one.
+}
 %\end{center}
@@
 
-As a testbed, we experiment with the story cloze task \cite{Mostafazadeh:2016}. 
-In this task, authors were asked to write five-sentence self-contained stories (henceforth {\it original} stories).
-Following, the stories were given to other authors, who were shown only the first four sentences of each story, 
-and were asked to write two one-sentence endings: a {\it correct} ending, and a {\it wrong} ending.
-The goal of the task is to determine which of the endings is the correct one.
-\tabref{ROC-example} shows an example of an {\it original} story, a {\it correct} story and a {\it wrong} story.
+%As a testbed, we experiment with
+As a case study, we present experiments   based on 
+the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
+In this task, crowdsourced authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
+%Following, 
+Then, 
+%the stories were given to other authors, 
+each original story was given to a different author, 
+who was shown only the first four sentences as a story context, 
+and asked to write contrastive story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
+%The goal of the task is to determine which of the endings is the correct one.
+Framed as a story cloze task, the goal of this dataset was to serve as a commonsense challenge. 
+\tabref{ROC-example} shows an example of an {\it original} story, a {\it coherent} story and an {\it incoherent} story.
 
-Interestingly, although originally intended to be a machine reading task, the compilation of this task raises several research questions which seem to differ from the original intent of the designers.
-First, do authors use different style when asked to write a {\it correct} sentence, compared to a {\it wrong} sentence?
-Second, do authors use different style when writing the ending as part of their own five sentence story, compared to reading four sentences, and then writing a standalone ({\it correct}) ending?
+While originally designed to be 
+%a machine reading task, 
+a commonsense story understanding challenge, 
+%the compilation of this task 
+the annotation process  
+%raises several research questions
+triggers interesting questions 
+%which seem to differ from the original intent of the designers.
+that may go beyond the original intent of the designers.
+First, do 
+%authors use different
+people maintain the same writing 
+style when asked to write  
+%a {\it right} ending, compared to a {\it wrong} ending?
+both coherent and incoherent story endings? Second, do people  
+%use different style when composing the final sentence as part of their own five sentence story, compared to reading four sentences, and then writing a standalone ({\it right}) ending?
+maintain the same writing style when writing the entire story on their own compared to 
+writing only the final sentence for a given story context written by someone else?
 
-Our experiments indicate that the answer to both questions is positive. 
-We train a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
-First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between {\it correct} and {\it wrong} endings in 64.5\% of the cases. 
+%Our analysis indicates that the answer to both questions is positive. 
+Our analysis indicates that different framings of similar writing tasks 
+can lead to measurable differences in people's writing style.
+%We experiment with a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
+%First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between the {\it right} and {\it wrong} endings in 64.5\% of the cases. 
+Using a simple classifier informed with stylistic features, we show that our classifier can distinguish the {\it right} and {\it wrong} endings with 64.5\% accuracy, even without looking at the story context, where chance performance is 50\%.
 %It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
-Second, when trained to distinguish between {\it original} endings and new ({\it correct}) endings, the classifier obtains 68.5\% accuracy. 
-Importantly, in both experiments, the classifier uses {\bf only} the last sentence of each of the stories, and does not consider the first four sentences.
+%Second, when trained to distinguish between the {\it original} endings and the new ({\it right}) endings, the classifier obtains 68.5\% accuracy. 
+Further, our classifier can also distinguish between the {\it original} endings and the new ({\it right}) endings with 68.5\% accuracy, again without looking at the story context.
 
-In order to further estimate the quality of our results, we turn back to the story cloze task.
-Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% improvement compared to the published state-of-the-art results \cite{Salle:2016}.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}).
-At the time of submission, the leading results was 71.1\%, which is  closer to our results, although still inferior.
-No details about the validity of this result or the methods used to generate it are available.}
-When analyzing the results of our classifier, we see that sentiment plays a significant role in its success,
-which suggests that constraining authors to ``wrong'' sentences results in negative text.
+%Importantly, in both experiments, the classifier uses {\bf only} the 
+%last sentence of each of the stories, and does not consider the first four sentences.
+%final sentence without the story context.
 
-We show that the style differences captured by our model can be combined with a state-of-the-art machine reading tool, for which this task was designed, in order to get increased performance on the story cloze task.
-We train a neural language model on the {\it original} five sentence training corpus, and then compute the language probability of each of the candidate endings. 
-We add the resulting probabilities as features in our linear classifier, and get an additional 2.8\% improvement -- 75.2\% -- which is 15.3\% better than the best published result.
+In order to further estimate the quality of our results, we 
+%turn back to the story cloze task.
+also directly tackle the story cloze challenge. 
+Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase 
+%compared to the published state-of-the-art results 
+over previously reported state-of-the-art 
+\cite{Salle:2016}.
+%When analyzing the results of our classifier, we see that sentiment plays a significant role in its success, which suggests that constraining authors to ``wrong'' sentences results in negative text.
+Our analysis reveals that sentiment plays a significant role, such that authors writing the wrong endings often engage negative sentiment.
+
+Finally, we show that the style differences captured by our model can be combined with 
+%a state-of-the-art machine reading tool, for which this task was designed, in order to obtain increased performance on the story cloze task.  
+neural language models to make a better use of the story context. 
+%We train a neural language model on the {\it original} five sentence training corpus, and then compute the language probability of each of the candidate endings. 
+%We add the resulting probabilities as features in our linear classifier, and get 
+Our final model that combines context with stylistic features achieves 
+an additional 2.8\% gain -- 75.2\% -- which is 15.3\% better than the best published result.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}).
+At the time of submission, the leading results was 71.1\%,
+%, which is  closer to our results, although still inferior.
+%No details about the validity of this result or the methods used to generate it are available.
+but no details are available for their results. 
+}
 %For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.
@@
 \com{Our results suggest that writing style is affected by the the writer's state of mind.
-Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it correct}. 
+Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it right}. 
 Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.}
 
-Our results may have a wide impact on a range of fields. 
-First, they have the potential to shed light on cognitive processes that take place in the brain during writing.
+%Our results may have a wide impact on a range of fields. 
+The contributions of our study are threefold. 
+First, findings from our study can potentially shed light on 
+%cognitive processes that take place in the brain during writing.
+how different cognitive overloads influence the style of language people use in writing. 
 %Second, our results might have a more practical value in an era when fake news are becoming prominent,
 %as they suggest that these might have different style compared to real news.
-Second, the results presented here also provide valuable lessons for designing new NLP tasks,
+Second, our results provide valuable lessons for designing new NLP tasks,
 both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
@@
 %We show that these details are actually very significant. 
+Third, we establish a new state-of-the-art result on the commonsense story cloze challenge.
 
-The remainder of this paper is organized as follows. In \secref{ROC_Story} we introduce the cloze story task.
-We present our model, our experiments and our resutls in sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
-Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, while \secref{Related}  surveys related work. 
+The remainder of this paper is organized as follows. In \secref{ROC_Story} we describe the story cloze task.
+We then present our model, experiments and results in sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
+Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, followed by related work in  \secref{Related}. 
 We conclude at \secref{Conclusion}.
@@
 To do so, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}. 
-While this task was developed to facilitate representation and learning of commonsense knowledge,
-it introduces a few interesting properties which makes it ideal for our purpose. 
+While this task was developed to facilitate representation and learning of commonsense story understanding,
+it introduces a few interesting properties which make it ideal for our study. 
 We describe the task below.
@@
 The ROC Story Corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
-Workers were instructed to write a coherent story, which has a clear beginning and end. 
+Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
 To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
@@
 After compiling the story corpus, the {\it Story Cloze Task} -- a task based on the corpus -- was introduced.
-A subset of the stories was selected, and the first four sentences of each story were presented to AMT workers.
-Workers were asked to write a {\it correct} and a {\it wrong} ending to each story prefix. 
-Both endings had to complete the story using one of the characters in it.
-Importantly,  when read out of context, the ending had to be ``realistic and sensible'' \cite{Mostafazadeh:2016}.
+A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
+Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}.
+Both endings are required to complete the story using one of the characters in the story context. 
+Additionally,  the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
 
-The resulting stories, both {\it correct} and {\it wrong}, were then individually rated for coherence and meaningfulness. 
-Only stories rated as simultaneously coherent with a {\it correct} ending and neutral with a {\it wrong} ending were selected for the task. 
+The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness. 
+Only stories rated as simultaneously coherent with a {\it right} ending and neutral with a {\it wrong} ending were selected for the task. 
 It is worth noting that workers rated the stories as a whole, not only the endings.
@@
 Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it Story Cloze Task}. 
-The task is simple -- given a pair of stories that differ only in their endings, the system is required to determine which ending is {\it correct} and which is {\it wrong}.
-The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it correct} and {\it wrong} endings are found.
+The task is simple -- given a pair of stories that differ only in their endings, the system is required to determine which ending is {\it right} and which is {\it wrong}. 
+%The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
+The official training data contains only the original stories (without alternative endings), while development and test data consist only of the revised stories with alternative endings (for a different set of original stories that are included in the training set).
 The task was suggested as an extensive evaluation framework:
-as a machine reading task, as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
+%as a machine reading task, 
+as a commonsense story understanding task, 
+as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
 
@@
 This suggest that this task is challenging and that high performance is hard to achieve.
+\yc{SQuAD was officially published in Nov 2016.
+by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper.
+Given that, the statement of this paragraph seems a bit of overkill...?}
 
@@
 Despite these efforts, several key aspects were not controlled for. 
-First, the training set for the task (ROC Stories corpus) is not really a training set, as it contains only positive ({\it correct}) samples, and not negative ({\it wrong}) ones. 
-On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it correct} samples, which serve as the positive samples in the development and test sets.
+First, the training set for the task (ROC Stories corpus) is not really a training set, as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
+\yc{As far as I understand, this was intentional --- they didn't want people to pick up on random superfluous cues that can inevidently get into the data creation process, exactly the kind that our work picks up.
+Given that, stating this can be viewed as misunderstanding, I'm afraid.}
+
+On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} samples, which serve as the positive samples in the development and test sets.
 While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
-and then asking her to generate a fifth {\it correct} ending. 
+and then asking her to generate a fifth {\it right} ending. 
 This raises the question of whether these different writing setups impose different writing styles. 
@@
 
-Second, although the {\it correct} and {\it wrong} sentences were generated by the same author, 
-the tasks for generating them were quite different: in one case, the author was asked to write a {\it correct} ending, which would create a coherent five-sentence story along with the other four sentences.
+Second, although the {\it right} and {\it wrong} sentences were generated by the same author, 
+the tasks for generating them were quite different: in one case, the author was asked to write a {\it right} ending, which would create a coherent five-sentence story along with the other four sentences.
 In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story.
@@
 \paragraph{Initial Analysis.}
-We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it correct} endings and {\it wrong} endings (both from the story cloze task development set).
-Our analysis  reveals several style differences between the different groups. 
-First, {\it original} endings are on average much longer (11 words per sentence) than {\it correct} endings (8.75 words), which are in turn also longer (though not as much)  than {\it wrong} ones (8.47 words).
-Second, \figref{roc_pos_distribution} shows the distribution of five frequent PoS tags in all three groups. 
-The figure shows that both {\it original} and {\it correct} endings use pronouns more frequently than {\it wrong} endings,
+We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
+Our analysis  reveals several style differences between different groups. 
+First, {\it original} endings are on average much longer (11 words per sentence) than {\it right} endings (8.75 words), which are in turn also longer (though not as much)  than {\it wrong} ones (8.47 words).
+\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
+Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
+The figure shows that both {\it original} and {\it right} endings use pronouns more frequently than {\it wrong} endings,
 which in turn prefer proper nouns, especially compared to {\it original} endings.
+\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}
 
 Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
-The figure shows that {\it original} endings prefer to use coordinations (``and'') more than  {\it correct} endings, and substantially more than {\it wrong} ones.
-Furthermore, {\it original} and {\it correct} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates'').
+The figure shows that {\it original} endings prefer to use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
+Furthermore, {\it original} and {\it right} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates''). 
+\yc{Again, any cogsci literature on this?}
 Next we show that these style differences are not anecdotic, but can be used to distinguish between the different groups of text.
@@
         ylabel = {Frequency in Corpus (\%)},
-        symbolic x coords={{\it Original}, {\it Correct}, {\it Wrong}},
+        symbolic x coords={{\it Original}, {\it right}, {\it Wrong}},
         xtick = data,
@@
         \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it Original}, 15.3) ({\it Correct}, 15.7) ({\it Wrong}, 16.3)};
+            coordinates {({\it Original}, 15.3) ({\it right}, 15.7) ({\it Wrong}, 16.3)};
 
         \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it Original}, 13.4) ({\it Correct}, 15.8) ({\it Wrong}, 15.1)};
+            coordinates {({\it Original}, 13.4) ({\it right}, 15.8) ({\it Wrong}, 15.1)};
 
         \addplot[style={ggreen,fill=ggreen,mark=none}]
-            coordinates {({\it Original}, 10.1) ({\it Correct}, 9.7) ({\it Wrong}, 7.4)};
+            coordinates {({\it Original}, 10.1) ({\it right}, 9.7) ({\it Wrong}, 7.4)};
 
         \addplot[style={brown,fill=brown,mark=none}]
-            coordinates {({\it Original}, 9.1) ({\it Correct}, 9.7) ({\it Wrong}, 9.4)};
+            coordinates {({\it Original}, 9.1) ({\it right}, 9.7) ({\it Wrong}, 9.4)};
 
         \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it Original}, 4.7) ({\it Correct}, 8.3) ({\it Wrong}, 9.5)};
+            coordinates {({\it Original}, 4.7) ({\it right}, 8.3) ({\it Wrong}, 9.5)};
 
@@
 %        ylabel = {Frequency in Corpus (\%)},
-        symbolic x coords={{\it Original}, {\it Correct}, {\it Wrong}},
+        symbolic x coords={{\it Original}, {\it right}, {\it Wrong}},
         xtick = data,
@@
         \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it Original}, 3.4) ({\it Correct}, 3.9) ({\it Wrong}, 4)};
+            coordinates {({\it Original}, 3.4) ({\it right}, 3.9) ({\it Wrong}, 4)};
 
         \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it Original}, 2.8) ({\it Correct}, 2) ({\it Wrong}, 1.5)};
+            coordinates {({\it Original}, 2.8) ({\it right}, 2) ({\it Wrong}, 1.5)};
 
         \addplot[style={ggreen,fill=ggreen,mark=none}]
-            coordinates {({\it Original}, 1.1) ({\it Correct}, 1.4) ({\it Wrong}, 1.6)};
+            coordinates {({\it Original}, 1.1) ({\it right}, 1.4) ({\it Wrong}, 1.6)};
 
         \addplot[style={brown,fill=brown,mark=none}]
-            coordinates {({\it Original}, 0) ({\it Correct}, 0) ({\it Wrong}, 0.7)};
+            coordinates {({\it Original}, 0) ({\it right}, 0) ({\it Wrong}, 0.7)};
 
         \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it Original}, 0.1) ({\it Correct}, 0.2) ({\it Wrong}, 0)};
+            coordinates {({\it Original}, 0.1) ({\it right}, 0.2) ({\it Wrong}, 0)};
 
@@
 \end{subfigure}
-\caption{The distribution of five frequent PoS tags (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})  across different endings: {\it Original} -- endings of stories from the ROC story corpus (the story cloze training set).
-{\it Correct} -- correct endings, {\it Wrong} -- wrong endings (both from story cloze task).}
+\caption{The distribution of five frequent POS tags (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})  across different endings: {\it Original} -- endings of stories from the ROC story corpus (the story cloze training set).
+{\it right} -- correct endings, {\it Wrong} -- wrong endings (both from story cloze task).}
 
@@
 
-The goal of this paper is to determine to what extent does constraining authors in their writing assignments lead to them adopting different writing styles. 
+The goal of this paper is to determine the extent to which 
+%does constraining authors in their writing assignments lead to them adopting different writing styles. 
+different writing constraints lead the authors to adopt different writing styles. 
 In order to answer these questions, we use simple, classic NLP tools, which have been shown to be very effective for recognizing style (see \secref{Related}).
@@
 We design two experiments to answer our research questions. 
-The first is an attempt to distinguish between {\it correct} and {\it wrong} endings.
-The second attempts to distinguish between {\it original} endings and new ({\it correct}) endings.
+The first is an attempt to distinguish between the {\it right} and {\it wrong} endings.
+The second attempts to distinguish between the {\it original} endings and new ({\it right}) endings.
 We describe both experiments below.
@@
 \paragraph{Experiment 1: Correct/Wrong Endings.}
-The goal of this experiment is to measure to what extent  style features capture differences between {\it correct} and {\it wrong} endings.
-As the cloze story task doesn't have a training corpus for the {\it correct} and {\it wrong} endings (see \secref{ROC_Story}), we use the development set as our training set. 
+The goal of this experiment is to measure to what extent  style features capture differences between the {\it right} and {\it wrong} endings.
+As the cloze story task doesn't have a training corpus for the {\it right} and {\it wrong} endings (see \secref{ROC_Story}), we use the development set as our training set. 
 We split it (90/10) into our training and development set. We keep the story cloze test set as is.
@@
 
-It is worth nothing that our classification task is slightly different from the {\it story cloze Task}. 
-Instead of classifying pairs of endings, one which is {\it correct} and another which is {\it wrong}, we take the set of  {\it correct} endings as positive samples and the set of {\it wrong} endings as our negative examples.
-By ignoring the coupling between {\it correct} and {\it wrong} pairs, we are able make a more general claim about the style used when writing each of the tasks.
+It is worth nothing that our classification task is slightly different from the { story cloze task}. 
+Instead of classifying pairs of endings, one which is {\it right} and another which is {\it wrong}, we take the set of  {\it right} endings as positive samples and the set of {\it wrong} endings as our negative examples.
+By ignoring the coupling between {\it right} and {\it wrong} pairs, we are able make a more general claim about the style used when writing each of the tasks.
 
@@
 
-Here the goal is to measure whether writing the ending as part of a story imposes different style compared to writing a ({\it correct}) ending to an existing story.
-We use the endings of the ROC stories as our {\it original} training samples and {\it correct} endings from the story cloze task  development and test sets as {\it new} training samples.
+Here the goal is to measure whether writing the ending as part of a story imposes different style compared to writing a ({\it right}) ending to an existing story.
+We use the endings of the ROC stories as our {\it original} training samples and {\it right} endings from the story cloze task  development and test sets as {\it new} training samples.
 As there are far more {\it original} samples than {\it new} ones, we randomly select $N$ {\it original} samples, where $N$ is the number of {\it new} samples,
@@
 All feature values are normalized to [0-1].
-For the PoS features, we tag all endings with the Spacy PoS tagger.\footnote{\url{spacy.io/}}
+For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
 We use  python's sklearn logistic regression implementation with L2 loss. 
@@
 As a complementary experiment, we measured whether these style differences are additive. 
-That is, whether the style differences between {\it correct} endings and {\it wrong} ones are different from the differences between {\it correct} and {\it original} endings.
+That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
 We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
@@
 \paragraph{Story Cloze Task.}
-The results of Experiment 1 indicate that {\it correct} and {\it wrong} endings are characterized by different styles.
+The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
 In order to further estimate the quality of our classification results, we tackle the story cloze task using our classifier.
-This classification task is more constrained than Experiment 1, as here the task is given two endings, which one is {\it correct} and which is {\it wrong}.
+This classification task is more constrained than Experiment 1, as here the task is given two endings, which one is {\it right} and which is {\it wrong}.
 In order to solve the task, we use the output of our trained classifier. 
@@
 Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even look at the first four sentences of the story in question.
-These numbers indicate that the styles of {\it correct} and {\it wrong} endings are indeed very different.
+These numbers indicate that the styles of {\it right} and {\it wrong} endings are indeed very different.
 
 Other than the published works that tackled this task, a few  recent works published their results in the LSDSem shared task website.\footnote{\url{https://competitions.codalab.org/competitions/15333}}
-As to the time of submission, our results are still state-of-the-art (though by a  smaller margin). 
+At the time of submission, our results are still state-of-the-art (though by a  smaller margin). 
 No other information other than the name of the groups and their results is available.
@@
 \end{center}
-\caption{\label{cloze_results}}
+\caption{\label{cloze_results}
 Results on the test set of the cloze story task. 
@@
 RNN is our implementation of an RNN.
+}
 \end{table}
@@
 Specifically, we experiment with a recurrent language model (RLM, \citet{mikolov2010recurrent}). % on the ROC story corpus training data,
-%and use it to compute the probability of both {\it correct} and {\it wrong} endings in the story cloze test set.
+%and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
 Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the story cloze task designers, and harnesses the ROC Stories training set, which consists of single-ending stories.
@@
 We combine our linear model with the RLM by adding three features to our classifier: $p_\theta(ending|story),p_\theta(ending)$ and $\frac{p_\theta(ending|story)}{p_\theta(ending)}$. 
-We retrain our linear  model with the new feature set, and notice a performance   boost  of $2.8\%$ -- up to 75.2\%, which is 15.3\% better than current published state-of-the-art, and 4.1\% better than best unpublished result.
+We retrain our linear  model with the new feature set, and gain a performance   boost  of $2.8\%$ -- up to 75.2\%, which is 15.3\% better than the published state-of-the-art, and 4.1\% better than the best unpublished result.
 These results indicate that while style features can be used to obtain high accuracy on the task, adding context and training on a large dataset can improve performance even more.
@@
 \end{center}
-\caption{\label{subgroups}}
+\caption{\label{subgroups}
 Results on Experiment 1 with different types of features.
+}
 \end{table}
@@
 \tabref{exp1_features} shows the five features with the highest positive and negative weights in the logistic regression classifier hyperplane for Experiment 1. 
-These correspond to the 5 most salient features for {\it correct} and {\it wrong} endings, respectively.
+These correspond to the 5 most salient features for {\it right} (coherent) and {\it wrong} (incoherent) endings, respectively.
 
 The table shows a few interesting trends. 
-First, it seems that authors tend to design their sentences differently when writing {\it correct}  vs. {\it wrong} endings.
-For instance, {\it correct} endings are more likely start with an adverb (e.g., ``then'', ``so'', ``eventually''), while {\it wrong} ones would prefer to start with a proper noun.
-Similarly, {\it wrong} endings have a preference to end the sentence with a common noun.
+First, authors tend to structure their sentences differently when writing {coherent}  vs. {incoherent} endings.
+For instance, {coherent} endings are more likely to start with an adverb (e.g., ``then'', ``so'', ``eventually''), while {incoherent} ones tend to start with a proper noun.
+In addition, we find that {incoherent} endings are more likely to finish the sentence with a common noun.
 
@@
 The performance of both these baselines was roughly chance-level, which seems to suggest that this is not the case.
+\yc{Is it really because there's no statistical tendency in the original stories to have happy endings, as opposed to the alternative possibility --- the sentiment classifier used by Monstafazadeh 2016 didn't quite nail down the optimal feature encodings?}
 
@@
 \caption{\label{exp1_features}}
-The top 5 most discriminative features for predicting {\it correct} and {\it wrong} endings.\end{table}
+The top 5 most discriminative features for predicting {\it right} and {\it wrong} endings.\end{table}
 
@@
 \caption{\label{exp2_features}}
-The top 5 most discriminative features for predicting {\it original} and {\it new} ({\it correct}) endings.\end{table}
+The top 5 most discriminative features for predicting {\it original} and {\it new} ({\it right}) endings.\end{table}
 
@@
 In this paper we have shown that different writing tasks affect writing style. 
-Our results indicate that when authors are asked to write the last sentence of a five sentence story, they will use different style to write a {\it correct} ending compared to a {\it wrong} ending.
+Our results indicate that when authors are asked to write the last sentence of a five sentence story, they will use different style to write a {\it right} ending compared to a {\it wrong} ending.
 We have also shown that writing the ending as part of a five sentence story is very different than reading four sentences and then writing the fifth.
@@
 Some works even showed that writing style applied when lying is different across genders \cite{Perez:2014a,Perez:2014b}.
-In this work, we have shown that an even more subtle writing task -- writing {\it correct} and {\it wrong} story endings -- imposes different styles on the author.
+In this work, we have shown that an even more subtle writing task -- writing {\it coherent} and {\it incoherent} story endings -- imposes different styles on the author.
 
@@
 it is often the case that these datasets suffer from methodological problems, such as inherent ambiguity caused by applying automatic tools when generating the datasets \cite{Chen:2016}. 
-In this paper we have pointed to other methodological problems in  machine reading tasks, namely the different writing tasks used to generated the data, which largely affect the writing style of the positive and negative samples, as well as creates a discrepancy between the training and the test data.
+In this paper we have pointed to other methodological problems in  machine reading tasks, namely the different writing tasks used to generated the data, which largely affect the writing style of the positive and negative samples, as well as create a discrepancy between the training and the test data.
 
@@
 
-The research question that guided this work is to what extent do different writing tasks impose different writing styles on authors.
-We experimented with the story cloze task, which introduces two interesting setups for our purposes:
-a setup where the same author writes both a {\it correct} and a {\it wrong} ending to a story, 
-and one which compares an ending written as part of a story to a standalone ending added to a story written by someone else.
-In both cases, a simple linear model reveals that different styles are imposed.
-The different styles allow our style detection model to reach state-of-the-art results on the story cloze task, more than 12\% improvement compared to the best published result.
+The research question that guided this work is the extent to which different writing tasks result in different writing styles.
+We experimented with the story cloze task, which introduces two interesting comparison points: %setups for our purposes:
+%a setup where the same author writes both a {\it right} and an {\it wrong} ending to a story, 
+%and one which compares an ending written as part of a story to a standalone ending added to a story written by someone else.
+ the difference between people writing a story on their own and people continuing someone else's story 
+ and the difference between the same author writing a coherent and an incoherent story ending.
+In both cases, a simple linear model reveals measurable differences in people's writing styles, %that different styles are imposed.
+%The different styles allow our style detection 
+which in turn allows our final 
+model to reach state-of-the-art results on the story cloze task, more than 12\% improvement compared to the best published result.
 
 The findings presented in this paper have  cognitive implications, as they motivate further research on the exact effect that different writing tasks have on humans.
-They also provide valuable lessons as to the design of future NLP datasets.
+They also provide valuable lessons for designing new NLP datasets.
 Future work will include testing whether other similar writing tasks, such as fake news, also impose their own unique and identifiable style on their authors.

### 2017-01-29 docs/shared_task_paper.tex
outlined some of the shared task stuff
more shared task editing, not quite done!

@@
 \usepackage{url}
-\usepackage{latexsym}
+\usepackage{latexsym,xcolor}
 
@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
+% Editing macros
+\newcommand{\my}[1]{\footnote{\color{red}{\textbf{#1}}}}
+
+\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
+\newcommand{\roy}[1]{\footnote{\color{red}{\textbf{Roy: #1}}}}
+\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
+\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
+\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
 
@@
 
-\section{Intro}
+\section{Introduction}
+% Describe the overall landscape of the problem
+%  - Commonsense knowledge
+%  - Script Learning
+%  -
 
-\section{System Overview}
+Learning of commonsense knowledge is one of AI's biggest challenges, since it is not usually found in knowledge bases.
+Coming up with the right types of data to analyze has been hard, and models are also not working well.
 
-\section{Features}
+One particular type of commonsense knowledge that has gotten attention is story understanding \cite{??}.
+Stories have narratives that require understanding of how events typically flow and of what events are coherent after others.
+Related to understanding event sequences is script learning, which focuses on stereotypical chains of events.
 
-\section{Results}
+% Mention the specific purpose of the shared task (i.e. from the website)
+The 2017 LSD Sem Shared Task provide a testbed to further commonsense story understanding: the \textit{Story Cloze} task \cite{Mostafazadeh:2016}.
+It was specifically designed for the purpose of facilitating the learning of commonsense knowledge.
+The task consist of finding the \textit{corrent} ending to four sentence short stories, out of two possible endings.
+With the two-ending stories, Mostafazadeh, et al. ~(2016)\nocite{Mostafazadeh:2016} also released nearly $100$k five-sentence short stories, to facilitate learning of commonsense narratives.
 
-\section{Discussion \& Conclusion}
+% Last paragraph should be a quick description of our system.
+In this paper, we describe the system submission from the University of Washington NLP group (UW NLP).
+We implement a simple classifier that uses surface features as well as language model features. Using the Shared Task test set, we achieve $75.1\%$ accuracy.
+
+\section{System Description}
+%% Explain that we have two sets of features, style and language.
+%% Maybe mention here that we're doing training on validation set ?
+In our system, we implement a simple linear classifier to choose between the \textit{correct} and \textit{incorrect} endings.
+% \section{Features}
+Specifically, we use two types of features (described in below), designed to capture different dimensions of the problem.
+We use \textit{stylistic} features to capture differences in writing between ``coherent'' endings and ``incoherent'' ones.
+We opt for \textit{language model} features to leverage corpus level word distributions, specifically longer term sequence probabilities.
+
+\ms{Some info about training, etc.}
+
+\subsection{Stylistic Features}
+%% take stuff from the paper
+In our classification task, we add the following features to capture style differences between the two endings:
+\begin{itemize}
+\item\textit{\textbf{Length}.} The number of words in the sentence.
+\item\textit{\textbf{Word n-grams.}} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
+Specifically, we replace content words, which are often low frequency, with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
+\item\textit{\textbf{Character n-grams.}} Character n-grams are useful features in author style \cite{Stamatatos:2009} or language identification \cite{lui2011cross}.
+We use character 4-grams.
+\end{itemize}
+
+\subsection{Language Model Features}
+%% take the RLM paragraph from the paper
+In addition to stylistic features, we experiment with state-of-the-art text comprehension models, specifically a recurrent language model (RLM, Mikolov, et al. (2010)\nocite{mikolov2010recurrent}).
+We train the RLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
+We use the ROC Stories for training, setting aside $10\%$ for validation of the language model. 
+We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=$21,582.
+Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
+Using AdamOptimizer \cite{kingma2014adam} and a learning rate of $\eta=.001$, we train with backpropagation on cross-entropy. % minibatches of $50$ stories.
+\section{Results \& Discussion}
+% Show results
+
+% ablation study? Table 2 from the paper sort of?
+
+\section{Conclusion}
+
+% Our system makes use of knowledge brought to us by the constrained writing literature (?)
+% talk about how we use state-of-the-art language modelling tools.
+% We achieve $75.1\%$ which is ranked XXth in the ongoing codalab competition.
 

### 2017-01-30 docs/language_constraint.tex
Noah's V1 comments

@@
 \newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
+\newcommand{\nascomment}[1]{{\color{blue}\textsc{[#1 --nas]}}}
 
@@
 %People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
-People's writing style depends not just on the authors' personal traits but also on the intent and the cognitive states of the authors. 
+% People's writing style depends not just on the authors' personal
+% traits but also on the intent and the cognitive states of the
+% authors. 
+A writer's style depends not just on personal traits but also on her
+intent and cognitive state.
 %In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
-In this paper, we show how similar writing tasks involving different cognitive processes can lead to measurable differences in people's writing style. % of the same authors.  
+In this paper, we show how writing tasks involving different cognitive processes can lead to measurable differences in writing style. % of the same authors.  
 %As a case study, we experiment with a recently published machine reading task: 
@@
 %In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
-where annotators were assigned with similar writing tasks with different constraints: (1) writing an entire story on their own vs.
-adding only a story ending for a given story context and (2) writing a story ending that makes the overall story coherent vs.
-incoherent.
+where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story on their own vs.~adding only a story ending for a given story context and (2) writing a story ending that makes the overall story coherent or incoherent.
 %We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
@@
 Our results demonstrate that different task framings can dramatically affect the way people write. 
-They also provide important lessons for designing new NLP tasks.
+They also provide important lessons for designing new NLP
+tasks. \nascomment{drop this sentence if we only have a paragraph
+  about this at the end, as we currently do}
 
 \end{abstract}
+
+\nascomment{resolve:  story cloze or cloze story?  we go back and
+  forth.  use the standard one and capitalize it consistently.}
 
@@
 personal 
-factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003} 
+factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, 
 %or mere 
@@
 %to what extent is 
-the extent to which people's 
-writing style is affected by intricate factors, such as 
-the nature of the writing task that would involve different cognitive processes.
+the extent to which 
+writing style is affected by 
+the nature of the writing task she was asked to perform, since
+different tasks likely engage different cognitive processes.
+%that would involve different cognitive processes.
 
@@
  a {\it right} ending and a {\it wrong} one.
+\nascomment{I like the colors a lot.  Instead of all the italicizing,
+  let's consider just color-coding these three terms.  It's less distracting.}
 }
@@
 %The goal of the task is to determine which of the endings is the correct one.
-Framed as a story cloze task, the goal of this dataset was to serve as a commonsense challenge. 
-\tabref{ROC-example} shows an example of an {\it original} story, a {\it coherent} story and an {\it incoherent} story.
+Framed as a story cloze task, the goal of this dataset was to serve as
+a commonsense challenge for NLP and AI research. 
+\tabref{ROC-example} shows an example of an {\it original} story, a {\it coherent} story, and an {\it incoherent} story.
 
@@
 %a machine reading task, 
-a commonsense story understanding challenge, 
+a story understanding challenge, 
 %the compilation of this task 
@@
 %compared to the published state-of-the-art results 
-over previously reported state-of-the-art 
+over the previously reported state of the art 
 \cite{Salle:2016}.
 %When analyzing the results of our classifier, we see that sentiment plays a significant role in its success, which suggests that constraining authors to ``wrong'' sentences results in negative text.
-Our analysis reveals that sentiment plays a significant role, such that authors writing the wrong endings often engage negative sentiment.
+Our analysis reveals that \nascomment{feels like a leap here, maybe
+  change wording a bit -- will come back to this.  note after reading
+  all the way to the end:  need to be careful about conclusions drawn
+  from weights alone } sentiment plays a significant role, such that authors writing the wrong endings often engage negative sentiment.
 
@@
 Our final model that combines context with stylistic features achieves
-an additional 2.8\% gain -- 75.2\% -- which is 15.3\% better than the best published result.\footnote{Recently, a shared task for the story cloze task has been published (\url{https://competitions.codalab.org/competitions/15333}).
-At the time of submission, the leading results was 71.1\%,
-%, which is  closer to our results, although still inferior.
-%No details about the validity of this result or the methods used to generate it are available.
-but no details are available for their results. 
+75.2\%---an additional 2.8\% gain, 15.3\% better than the best
+published result.\footnote{
+%Recently, a shared task for the story cloze
+%  task has been conducted (\url{https://competitions.codalab.org/competitions/15333}). At the time of submission, the leading results was 71.1\%,
+%%, which is  closer to our results, although still inferior.
+%%No details about the validity of this result or the methods used to generate it are available.
+%but no details are available for their results. 
+I commented out this footnote, because we mention this later.  We
+should only mention it once and not in the intro.
 }
@@
 %cognitive processes that take place in the brain during writing.
-how different cognitive overloads influence the style of language people use in writing. 
+how different kinds of cognitive load influence the style of written language. 
 %Second, our results might have a more practical value in an era when fake news are becoming prominent,
@@
 The remainder of this paper is organized as follows. In \secref{ROC_Story} we describe the story cloze task.
-We then present our model, experiments and results in sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
-Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an ablation study and a discussion, followed by related work in  \secref{Related}. 
-We conclude at \secref{Conclusion}.
+We then present our model, experiments and results in Sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
+Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an
+ablation study and a discussion, followed by related work and conclusions.
 
@@
 \paragraph{Story Cloze Task.}
-After compiling the story corpus, the {\it Story Cloze Task} -- a task based on the corpus -- was introduced.
+After compiling the story corpus, the {\it Story Cloze Task}---a task based on the corpus---was introduced.
 A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
@@
 
-The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness. 
+The resulting stories, both {\it right} and {\it wrong}, were then
+individually rated for coherence and meaningfulness \nascomment{by
+  additional AMT workers? or someone else?}. 
 Only stories rated as simultaneously coherent with a {\it right} ending and neutral with a {\it wrong} ending were selected for the task. 
@@
 Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it Story Cloze Task}. 
-The task is simple -- given a pair of stories that differ only in their endings, the system is required to determine which ending is {\it right} and which is {\it wrong}. 
+The task is simple:  given a pair of stories that differ only in their endings, the system decides which ending is {\it right} and which is {\it wrong}. 
 %The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
@@
 
-\paragraph{State-of-the-Art Performance.}
-Interestingly, at the time of submission, 10 months after the paper was first published, the published benchmark on this task is still below 60\% \cite{Salle:2016}.\footnote{The LSDSem`17 shared task website does report higher results (71.1\%), which are still unpublished.}
+\paragraph{State-of-the-art performance.}
+Interestingly, at the time of this submission, 10 months after the
+paper was first published, the published benchmark on this task is
+still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
+  task website (\url{https://competitions.codalab.org/competitions/15333}) does report higher results (71.1\%), which are still
+  unpublished along with the underlying methodology.}
 This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and SNLI \cite{bowman2015large}, for which results improved dramatically over a similar period of time.
-This suggest that this task is challenging and that high performance is hard to achieve.
-\yc{SQuAD was officially published in Nov 2016.
-by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper.
-Given that, the statement of this paragraph seems a bit of overkill...?}
+This suggests that this task is challenging and that high performance is hard to achieve.
+\yc{SQuAD was officially published in Nov 2016. by the time the
+  official EMNLP talk was presented, the leaderboard performance
+  (still unpublished) was  30\% beyond the best results in the
+  paper. Given that, the statement of this paragraph seems a bit of
+  overkill...?} \nascomment{it sounds like Yejin is saying that on
+  squad, there was an even faster acceleration?  or that we should
+  change ``similar period of time'' to ``similar or shorter period of time''?}
 
-\paragraph{Different Writing Tasks in the Story Cloze Task.}
-\citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this task. 
+\paragraph{Different writing tasks in the Story Cloze Task.}
+\citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
 First, each pair of endings was written by the same author, which ensured that author style differences could not be used to solve the task. 
@@
 Despite these efforts, several key aspects were not controlled for. 
-First, the training set for the task (ROC Stories corpus) is not really a training set, as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
-\yc{As far as I understand, this was intentional --- they didn't want people to pick up on random superfluous cues that can inevidently get into the data creation process, exactly the kind that our work picks up.
-Given that, stating this can be viewed as misunderstanding, I'm afraid.}
+First, the training set for the task (ROC Stories corpus) is not a
+training sample in the usual sense,\footnote{I.e., the training
+  instances are drawn from a population similar to the one that future
+  testing instances will be drawn from.}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
+\yc{As far as I understand, this was intentional --- they didn't want
+  people to pick up on random superfluous cues that can inevidently
+  get into the data creation process, exactly the kind that our work
+  picks up. Given that, stating this can be viewed as
+  misunderstanding, I'm afraid.} \nascomment{We should maybe say that
+  they did this intentionally and concede that our approach goes
+  against the intentions of their task design.  But a task that
+  insists that systems avoid using features that might encode one kind
+of information (like style) is absurd.  Alternately, we could reframe
+this not as ``things weren't controlled for'' but instead stick to the
+facts here and just describe what they did without judgment.}
 
@@
 This raises the question of whether these different writing setups impose different writing styles. 
-We show that this is indeed the case.
+% We show that this is indeed the case.
 
@@
 In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story.
-In this work, we show that these differences are significant and impose different writing styles on authors.
+In this work, we show that these differences are significant and
+impose different writing styles on authors. \nascomment{this bit feels
+  a little heavy and reptititive.}
 
@@
 Our analysis  reveals several style differences between different groups. 
-First, {\it original} endings are on average much longer (11 words per sentence) than {\it right} endings (8.75 words), which are in turn also longer (though not as much)  than {\it wrong} ones (8.47 words).
+First, {\it original} endings are on average much longer (11 words per
+sentence) than {\it right} endings (8.75 words), which are in turn
+slightly longer than {\it wrong} ones (8.47 words). 
 \yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
@@
 Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
-The figure shows that {\it original} endings prefer to use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
+The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
 Furthermore, {\it original} and {\it right} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates''). 
-\yc{Again, any cogsci literature on this?}
-Next we show that these style differences are not anecdotic, but can be used to distinguish between the different groups of text.
+\yc{Again, any cogsci literature on this?} \nascomment{feels
+  Pennebaker-ish, that might be a good place to look.}
+Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.
 
@@
 \begin{tabular}{|p{2.5cm}|p{4cm}|p{4cm}|p{4cm}|} \hline
- & {\bf Original}& {\bf Correct} & {\bf Wrong}\\ \hline
+ & {\bf Original}& {\bf Right} & {\bf Wrong}\\ \hline
 Sentence Length (\#words) & 11.02 & 8.75 & 8.47\\ \hline
-Most Frequent PoS tags (\%)  & NN:15.3\%, VBD:13.4\%, PRP:10.1, DT:9.1\%, IN:8.7\% & VBD:15.8\%, NN:15.7\%, DT:9.7\%, PRP:8.8\%, NNP:8.3\%  & NN:16.3\%, VBD:15.1\%,  NNP:9.5\%, DT:9.4, IN:7.9\%\\ \hline
+Most Frequent POS tags (\%)  & NN:15.3\%, VBD:13.4\%, PRP:10.1, DT:9.1\%, IN:8.7\% & VBD:15.8\%, NN:15.7\%, DT:9.7\%, PRP:8.8\%, NNP:8.3\%  & NN:16.3\%, VBD:15.1\%,  NNP:9.5\%, DT:9.4, IN:7.9\%\\ \hline
 Most Frequent Words  (\%) & the:4.5\%, to:3.3\%, and:2.7\%, was:2.6\%, a:2.2\% & the:4.8\%, to:3.9\%, was:3.5\%, a:2.5\%, and:2.1\%   & the:5\%, to:4\%, was:3\%, a:2\%, I:1.6\%\\ \hline
@@
         ylabel = {Frequency in Corpus (\%)},
-        symbolic x coords={{\it Original}, {\it right}, {\it Wrong}},
+        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
         xtick = data,
@@
         \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it Original}, 15.3) ({\it right}, 15.7) ({\it Wrong}, 16.3)};
+            coordinates {({\it original}, 15.3) ({\it right}, 15.7) ({\it wrong}, 16.3)};
 
         \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it Original}, 13.4) ({\it right}, 15.8) ({\it Wrong}, 15.1)};
+            coordinates {({\it original}, 13.4) ({\it right}, 15.8) ({\it wrong}, 15.1)};
 
         \addplot[style={ggreen,fill=ggreen,mark=none}]
-            coordinates {({\it Original}, 10.1) ({\it right}, 9.7) ({\it Wrong}, 7.4)};
+            coordinates {({\it original}, 10.1) ({\it right}, 9.7) ({\it wrong}, 7.4)};
 
         \addplot[style={brown,fill=brown,mark=none}]
-            coordinates {({\it Original}, 9.1) ({\it right}, 9.7) ({\it Wrong}, 9.4)};
+            coordinates {({\it original}, 9.1) ({\it right}, 9.7) ({\it wrong}, 9.4)};
 
         \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it Original}, 4.7) ({\it right}, 8.3) ({\it Wrong}, 9.5)};
+            coordinates {({\it original}, 4.7) ({\it right}, 8.3) ({\it wrong}, 9.5)};
 
@@
 \end{tikzpicture}
-\caption{\label{roc_pos_distribution}PoS tags}
+\caption{\label{roc_pos_distribution}POS tags}
 \end{subfigure}
@@
 %        ylabel = {Frequency in Corpus (\%)},
-        symbolic x coords={{\it Original}, {\it right}, {\it Wrong}},
+        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
         xtick = data,
@@
         \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it Original}, 3.4) ({\it right}, 3.9) ({\it Wrong}, 4)};
+            coordinates {({\it original}, 3.4) ({\it right}, 3.9) ({\it wrong}, 4)};
 
         \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it Original}, 2.8) ({\it right}, 2) ({\it Wrong}, 1.5)};
+            coordinates {({\it original}, 2.8) ({\it right}, 2) ({\it wrong}, 1.5)};
 
         \addplot[style={ggreen,fill=ggreen,mark=none}]
-            coordinates {({\it Original}, 1.1) ({\it right}, 1.4) ({\it Wrong}, 1.6)};
+            coordinates {({\it original}, 1.1) ({\it right}, 1.4) ({\it wrong}, 1.6)};
 
         \addplot[style={brown,fill=brown,mark=none}]
-            coordinates {({\it Original}, 0) ({\it right}, 0) ({\it Wrong}, 0.7)};
+            coordinates {({\it original}, 0) ({\it right}, 0) ({\it wrong}, 0.7)};
 
         \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it Original}, 0.1) ({\it right}, 0.2) ({\it Wrong}, 0)};
+            coordinates {({\it original}, 0.1) ({\it right}, 0.2) ({\it wrong}, 0)};
 
@@
 \end{subfigure}
-\caption{The distribution of five frequent POS tags (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})  across different endings: {\it Original} -- endings of stories from the ROC story corpus (the story cloze training set).
-{\it right} -- correct endings, {\it Wrong} -- wrong endings (both from story cloze task).}
+\caption{The distribution of five frequent POS tags
+  (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})
+  across \emph{original} endings (Story Cloze training set), and
+  \emph{right} and \emph{wrong} endings (from the Story Cloze Task).}
 
@@
 different writing constraints lead the authors to adopt different writing styles. 
-In order to answer these questions, we use simple, classic NLP tools, which have been shown to be very effective for recognizing style (see \secref{Related}).
+In order to answer these questions, we use simple methods that have been shown to be very effective for recognizing style (see \secref{Related}).
 We describe our model below.
 
-We train a linear logistic regression (aka Maximum Entropy) classifier to distinguish between different endings. 
+We train a logistic regressionclassifier to distinguish between different endings. 
 Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
@@
 \item\textit{\textbf{Length}.} The number of words in the sentence.
-\item\textit{\textbf{Word n-grams.}} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
-Specifically, we replace content words, which are often low frequency, with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
-\item\textit{\textbf{Character n-grams.}} Character n-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
+\item\textit{\textbf{Word n-grams.}} We use sequences of 1-5
+  words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
+Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their part-of-speech tags.
+\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
 We use character 4-grams.
@@
 We design two experiments to answer our research questions. 
-The first is an attempt to distinguish between the {\it right} and {\it wrong} endings.
-The second attempts to distinguish between the {\it original} endings and new ({\it right}) endings.
+The first is an attempt to distinguish between {\it right} and {\it wrong} endings,
+the second  between {\it original} endings and new ({\it right}) endings.
 We describe both experiments below.
 
-\paragraph{Experiment 1: Correct/Wrong Endings.}
+\paragraph{Experiment 1: right/wrong endings.}
 The goal of this experiment is to measure to what extent  style features capture differences between the {\it right} and {\it wrong} endings.
-As the cloze story task doesn't have a training corpus for the {\it right} and {\it wrong} endings (see \secref{ROC_Story}), we use the development set as our training set. 
-We split it (90/10) into our training and development set. We keep the story cloze test set as is.
-The final size of our training/development/test sizes are 3,366/374/3,742 endings, respectively.
+As the cloze story task doesn't have a training corpus for the {\it
+  right} and {\it wrong} endings (see \secref{ROC_Story}), we use the
+development set as our training set, holding out 10\% for development
+(3,366 training endings, 374 for development). 
+ We keep the Story Cloze test set as is (3,742 endings).
 
-It is worth nothing that our classification task is slightly different from the { story cloze task}. 
-Instead of classifying pairs of endings, one which is {\it right} and another which is {\it wrong}, we take the set of  {\it right} endings as positive samples and the set of {\it wrong} endings as our negative examples.
-By ignoring the coupling between {\it right} and {\it wrong} pairs, we are able make a more general claim about the style used when writing each of the tasks.
+It is worth nothing that our classification task is slightly different from the story cloze task. 
+Instead of classifying pairs of endings, one which is {\it right} and
+another which is {\it wrong}, our classifier decides about each ending
+individually, whether it is \emph{right} (positive instance) or
+\emph{wrong} (negative instance).
+By ignoring the coupling between {\it right} and {\it wrong} pairs, we
+are able make a more general claim about the style used when writing
+each of the tasks \nascomment{I'm not sure I follow this sentence; can
+we be more clear?}.
 
-\paragraph{Experiment 2: Original/New Endings.}
+\paragraph{Experiment 2: original/new endings.}
 
-Here the goal is to measure whether writing the ending as part of a story imposes different style compared to writing a ({\it right}) ending to an existing story.
-We use the endings of the ROC stories as our {\it original} training samples and {\it right} endings from the story cloze task  development and test sets as {\it new} training samples.
-As there are far more {\it original} samples than {\it new} ones, we randomly select $N$ {\it original} samples, where $N$ is the number of {\it new} samples,
-such that we have balanced labels in our training, validation and test sets (sizes are the same as in Experiment 1).
+Here the goal is to measure whether writing the ending as part of a
+story imposes different style compared to writing a new ({\it right}) ending to an existing story.
+We use the endings of the ROC stories as our {\it original} training
+samples and {\it right} endings from the story cloze task  development
+and test sets \nascomment{if you're using the test examples as
+  training data, what are you using for test? and development?  I would have thought
+  you'd follow the same pattern as above ...} as {\it new} training samples.
+As there are far more {\it original} instances than {\it new}
+instances, we randomly select the same number of \emph{original}
+instances \nascomment{(give the number in parentheses, for train/dev/test)} as we have
+\emph{new} instances, for each of the training, development, and test sets.
 We randomly sample 5 training sets and report the average classification result.
 
-\paragraph{Experimental Setup.}
-In both experiments, we add a START symbol at the beginning of each sentence.\footnote{Virtually all sentences end with a period or an exclamation mark, so we do not add an END token} 
-For computing our features, we keep n-gram (character or word) features that occur at least five times in the training set.
-All feature values are normalized to [0-1].
-For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
-We use  python's sklearn logistic regression implementation with L2 loss. 
-We grid search the regularization parameter on our development set.
+\paragraph{Experimental setup.}
+In both experiments, we add a \textsc{start} symbol at the beginning
+of each sentence.\footnote{Virtually all sentences end with a period
+  or an exclamation mark, so we do not add a \textsc{stop} symbol.}
+For computing our features, we keep $n$-gram (character or word) features that occur at least five times in the training set.
+All feature values are normalized to $[0, 1]$.
+For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{http://spacy.io/}}
+We use  Python's sklearn logistic regression implementation with $L_2$
+regularization, performing grid search on the development test to
+select the hyperparameter.  \nascomment{any other hyperparameters?  if
+  not, say this is the only one.  else explain what they are.}
 
@@
 \figref{results} shows our results.
-Results show that for Experiment 1, our model obtains results well above a random baseline -- 64.5\% classification accuracy. 
-For Experiment 2, we get even higher results -- 68.5\%. 
-These numbers indicate that these different writing tasks clearly impose different writing styles on authors.
+In Experiment 1, our model obtains 64.5\%
+classification accuracy, well above a (50\%-accurate) random baseline.
+For Experiment 2, our model is even stronger, at 68.5\%.
+These results indicate that an author's style is affected in an
+easily-detected way when she is prompted to write (1) a \emph{wrong} story ending vs.~a
+\emph{right} one, or (2) finishing her own short story vs.~someone else's.
+%These numbers indicate that these different writing tasks clearly impose different writing styles on authors.
 
-As a complementary experiment, we measured whether these style differences are additive. 
-That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
-We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
-Our hypothesis is that differences would be even clearer. 
-Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.
+We further measured whether these style effects are additive, by
+classifying \emph{original} vs.~\emph{wrong} endings.  The setup is
+exactly as in Experiment 2, but using \emph{wrong} endings instead of
+\emph{right} ones.  The result is that the effects are somewhat
+additive:  this third classifier achieves 75.2\%.
+% That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
+% We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
+% Our hypothesis is that differences would be even clearer. 
+% Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.
 
@@
 \caption{\label{results} Results of  experiments 1 and 2 (left two charts). 
-Rightmost graph shows a control experiment which classifies {\it original} endings vs \textit{\textbf{wrong}} endings. }
+Rightmost graph shows a control experiment which classifies {\it
+  original} endings vs \textit{\textbf{wrong}}
+endings. \nascomment{this is overkill.  I suggest replacing it with a
+  table that just shows our model, no baseline, and reiterate in the
+  caption that our setup implies a 50\%-accurate random baseline.
+  Also, I like including the third comparison, but I don't
+  see how it's a ``control.'' }}
 \end{figure}
@@
 The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
-In order to further estimate the quality of our classification results, we tackle the story cloze task using our classifier.
-This classification task is more constrained than Experiment 1, as here the task is given two endings, which one is {\it right} and which is {\it wrong}.
-In order to solve the task, we use the output of our trained classifier. 
-For each pair of endings in our test set, if the classifier assigns different labels to them, we keep these labels. 
-If they share the same label, then one of them must be wrong, so we use the classifier confidence level as a deciding factor: the label of the one with the lower confidence is reversed.
+In order to further estimate the quality of our classification results, we tackle the Story Cloze Task using our classifier.
+This classification task is more constrained than Experiment 1, as two
+endings are given and question is which is \emph{right} and which is
+\emph{wrong}.
+We apply the classifier from Experiment 1 as follows:
+if it assigns different labels to the two given endings, we keep
+them.  If not, the label whose posterior probability is lower is reversed.
 
-\tabref{cloze_results} shows our results on the story cloze test set. Our classifier obtains 72.4\% accuracy, which is 12.5\% higher than the published state-of-the-art result on the task.
-Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even look at the first four sentences of the story in question.
-These numbers indicate that the styles of {\it right} and {\it wrong} endings are indeed very different.
+\tabref{cloze_results} shows our results on the Story Cloze test
+set. Our classifier obtains 72.4\% accuracy, 12.5\% higher than the
+published state-of-the-art result on the task \nascomment{cite that here}.
+Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
+These numbers further support the claim that the styles of {\it right} and {\it wrong} endings are indeed very different.
 
-Other than the published works that tackled this task, a few  recent works published their results in the LSDSem shared task website.\footnote{\url{https://competitions.codalab.org/competitions/15333}}
-At the time of submission, our results are still state-of-the-art (though by a  smaller margin). 
-No other information other than the name of the groups and their results is available.
+\nascomment{I suppressed the sentences about the LSDSem shared task;
+  once, in the earlier footnote, is enough.}
+% Other than the published works that tackled this task, a few  recent works published their results in the LSDSem shared task website.\footnote{\url{https://competitions.codalab.org/competitions/15333}}
+% At the time of submission, our results are still state-of-the-art (though by a  smaller margin). 
+% No other information other than the name of the groups and their results is available.
+
+\begin{table}[!t]
+\begin{center}
+%\small
+\begin{tabular}{|l|r|} \hline
+{\bf Model} & {\bf Accuracy} \\ \hline
+{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
+{LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
+{Niko (shared task)}	& 0.700\\ 
+{tbmihaylov (shared task)} & 0.711\\ \hline\hline
+{RNN}		& 0.677 \\ 
+{\bf Ours} & {\bf 0.724} \\ 
+{\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
+Human judgment & 1.000 \\ \hline
+\end{tabular}
+\end{center}
+\caption{\label{cloze_results}
+Results on the test set of the Cloze Story task. 
+The first block are published results, the second block
+as-yet-unpublished results from the LSDSem 2017 leaderboard, the third
+block ours.
+LexVec results are taken from \cite{Speer:2016}.
+RNN is our implementation. \nascomment{I added 0s to ``Niko'' result
+  and ``human''
+  so sig. digits would line up.  if we don't have sig digits for some
+  of them, make the zeros white so the numbers line up.  where did the
+human judgments come from?  those are not mentioned in our text anywhere!}
+}
+\end{table}
+
+\paragraph{Combination with a neural language model.}
+We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed. 
+Specifically, we experiment with a recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
+%and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
+Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the Story Cloze task designers, and harnesses their ROC Stories training set, which consists of single-ending stories.
+We show that the adding our features to this powerful language model
+gives improvements over our classifier as well as the language
+model. \nascomment{reworded.  more important that our features help
+  the language model, than the other way around!}
+
+We train the RNNLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension 512.
+We use the ROC Stories for training, setting aside 10\% for validation of the language model. 
+We replace all words occurring less than 3 times by a special
+out-of-vocabulary character, yielding a vocabulary size of  21,582.
+Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
+Using AdamOptimizer \cite{kingma2014adam} and a learning rate of
+$\eta=.001$, we train to minimize cross-entropy. % minibatches of $50$ stories.
+% h=512, dropout rate of 60%, V=21582, 10% validation set
+
+To apply the language model to the classification problem, we select
+as \emph{right} the ending with the higher value of
+\begin{equation}
+\frac{p_\theta(\textrm{ending} \mid
+  \textrm{story})}{p_\theta(\textrm{ending})} \label{eq:ratio}
+\end{equation}
+The intuition is that a \emph{right} ending should be unsurprising (to
+the model)
+given the four preceding sentences of the story (the numerator), controlling for the
+inherent surprisingness of the words in that ending (the denominator).
+
+\nascomment{please check the paragraph above.  we need to say how we
+  use the LM before we evaluate it!  also, has anyone tried an approach like this
+  before?  even if we aren't exactly replicating another paper, if
+  someone else used RNNs for this task, we should credit them.}
+
+% Eval
+On its own, our neural language model performs moderately well on the Story Cloze test. 
+This is not surprising, as \citet{Mostafazadeh:2016} hinted  that
+simple language models are insufficient.
+Indeed, using our neural language model and selecting endings based on
+$p_\theta(\textrm{ending} \mid \textrm{story})$ (i.e., the numerator of
+Equation~\ref{eq:ratio}), we obtained only 55\% accuracy.   The ratio
+in Equation~\ref{eq:ratio} achieves 67.7\%  (see
+\tabref{cloze_results}).\footnote{Further analysis of this large
+  difference is out of the scope of this paper, but suggests careful
+  study of suitable probabilistic inference methods for such tasks.}
+
+We combine our linear model with the RNNLM by adding three features to
+our classifier: the numerator, denominator, and ratio in
+Equation~\ref{eq:ratio}. % $p_\theta(ending|story),p_\theta(ending)$ and $\frac{p_\theta(ending|story)}{p_\theta(ending)}$.
+We retrain our linear  model with the new feature set, and gain 2.8\%
+absolute, reaching 75.2\% (15.3\% better than the published state of
+the art and 4.1\% better than the best unpublished result).
+These results indicate that context-ignorant style features can be used to obtain high
+accuracy on the task, adding value even when context and a large
+training dataset are used. \nascomment{check reframing here}
+
+\isection{Further Analysis}{Ablation}
+
+\nascomment{these aren't just ablations, so I retitled}
+
+\paragraph{Most discriminative feature types.}
+A natural question that follows this study is which style features are most
+helpful in detecting the underlying task an ending's author was asked
+to perform. 
+To answer this question, we re-ran Experiment 1 with different sub-groups of features. 
+\tabref{subgroups} shows our results.
+Results show that  character $n$-grams are the most effective style predictors, reaching within  0.6\% of the full model, but that word $n$-grams also capture much of the signal, yielding 61.2\%.
+These findings are in line with previous work that used character $n$-grams along with other types of features to predict writing  style \cite{Schwartz:2013}.
 
@@
 \begin{tabular}{|c|c|} \hline
-{\bf Model} & {\bf Results} \\ \hline
-{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ \hline
-{ LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
-{ Niko (shared task)}	& 0.7\\ \hline
-{ tbmihaylov (shared task)} & 0.711\\ \hline\hline
-{RNN}		& 0.677 \\ \hline
-{\bf Our Model} & {\bf 0.724} \\ \hline
-{\bf Combined (Our model, RNN)} & {\bf 0.752} \\ \hline\hline
-Human judgment & 1 \\ \hline
-\end{tabular}
-\end{center}
-\caption{\label{cloze_results}
-Results on the test set of the cloze story task. 
-Upper part are published results.
-LexVec results are taken from \cite{Speer:2016}.
-Results in the middle part are taken from the LSDSem 2017 shared task webpage.
-Bottom part is our results.
-RNN is our implementation of an RNN.
-}
-\end{table}
-
-\paragraph{Combination with an RLM.}
-We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed. 
-Specifically, we experiment with a recurrent language model (RLM, \citet{mikolov2010recurrent}). % on the ROC story corpus training data,
-%and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
-Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the story cloze task designers, and harnesses the ROC Stories training set, which consists of single-ending stories.
-We show that adding the language model features  further boosts our performance on the story cloze task.
-
-We train the RLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
-We use the ROC Stories for training, setting aside $10\%$ for validation of the language model. 
-We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=$21,582.
-Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
-Using AdamOptimizer \cite{kingma2014adam} and a learning rate of $\eta=.001$, we train with backpropagation on cross-entropy. % minibatches of $50$ stories.
-% h=512, dropout rate of 60%, V=21582, 10% validation set
-
-% Eval
-On its own, our neural language model performs moderately on the story cloze test. 
-This is not surprising, as \citet{Mostafazadeh:2016} hinted  that simple language models do not perform well on the task. 
-Indeed, using our neural LM and selecting endings based on $p_\theta(ending|story)$, we obtain only $55\%$ accuracy. 
-However, when using the likelihood ratio $\frac{p_\theta(ending|story)}{p_\theta(ending)}$ to select endings, performance jumps to $67.7\%$ (see \tabref{cloze_results}).\footnote{Further analysis of this large performance gain is out of the scope of this paper.}
-
-We combine our linear model with the RLM by adding three features to our classifier: $p_\theta(ending|story),p_\theta(ending)$ and $\frac{p_\theta(ending|story)}{p_\theta(ending)}$. 
-We retrain our linear  model with the new feature set, and gain a performance   boost  of $2.8\%$ -- up to 75.2\%, which is 15.3\% better than the published state-of-the-art, and 4.1\% better than the best unpublished result.
-These results indicate that while style features can be used to obtain high accuracy on the task, adding context and training on a large dataset can improve performance even more.
-
-\isection{Ablation Study}{Ablation}
-
-\paragraph{Most Discriminative Feature Types.}
-A natural question that follows this study is which features are most helpful in making predictions about writing style. 
-To answer this question, we re-ran Experiment 1 with different sub-groups of features. 
-\tabref{subgroups} shows our results.
-Results clearly show that  character n-grams are the most effective style predictors, reaching within  0.6\% of the full model, but that word n-grams also capture much of the signal, yielding 61.2\%.
-These findings are in line with previous works that used character n-grams along with other types of features to predict writing  style \cite{Schwartz:2013}.
-
-\begin{table}[!t]
-\begin{center}
-%\small
-\begin{tabular}{|c|c|} \hline
-{\bf Feature Type} & {\bf Result}\\ \hline
-Word n-grams & 61.2\% \\ \hline
-Char n-grams & 63.9\% \\ \hline
-Full Model & 64.5\% \\ \hline
+{\bf Feature Type} & {\bf Accuracy}\\ \hline
+Word $n$-grams & 0.612 \\ \hline
+Character $n$-grams & 0.639 \\ \hline
+Full model & 0.645 \\ \hline
 
@@
 \caption{\label{subgroups}
-Results on Experiment 1 with different types of features.
+Results on Experiment 1 with different subsets of features.
 }
@@
 
-\paragraph{Most Salient Features -- Experiment 1.}
+\paragraph{Most salient features---experiment 1.}
 %In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
 %This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.724).  
-\tabref{exp1_features} shows the five features with the highest positive and negative weights in the logistic regression classifier hyperplane for Experiment 1. 
-These correspond to the 5 most salient features for {\it right} (coherent) and {\it wrong} (incoherent) endings, respectively.
+\tabref{exp1_features} shows the five features with the highest positive and negative coefficients in the logistic regression classifier for Experiment 1. 
+These correspond to the 5 most salient features for {\it right}
+(coherent) and {\it wrong} (incoherent) endings,
+respectively. \nascomment{have to be very careful here.  see
+  \href{http://homes.cs.washington.edu/~nasmith/papers/yano+smith+wilkerson.naacl12.pdf}{Yano/Smith/Wilkerson}
+  \S 4.3 where we propose an alternative to inspecting
+  feature coefficients!}
 
@@
 For instance, {coherent} endings are more likely to start with an adverb (e.g., ``then'', ``so'', ``eventually''), while {incoherent} ones tend to start with a proper noun.
-In addition, we find that {incoherent} endings are more likely to finish the sentence with a common noun.
+In addition, we find that {incoherent} endings are more likely to
+finish the sentence with a common noun.  \nascomment{note to self to come back
+  to this after we agree on methodology.}
 
@@
 \begin{tabular}{|c|c|} \hline
-\textit{\textbf{Correct}} & \textit{\textbf{Wrong}}\\ \hline
+\textit{\textbf{Right}} & \textit{\textbf{Wrong}}\\ \hline
 `ally' & ` hate'\\ \hline
@@
 \caption{\label{exp1_features}}
-The top 5 most discriminative features for predicting {\it right} and {\it wrong} endings.\end{table}
+The top 5 most discriminative features for predicting {\it right} vs.~{\it wrong} endings.\end{table}
 
-\paragraph{Most Salient Features -- Experiment 2.}
+\paragraph{Most salient features---experiment 2.}
 %In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
@@
 Interestingly, here the most salient features are quite different. 
-As noticed on \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
+As noted in \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
 Another clear style difference is the use of punctuation: {\it original} endings often end with exclamation marks, while {\it new} endings end almost exclusively with periods. 
@@
 \caption{\label{exp2_features}}
-The top 5 most discriminative features for predicting {\it original} and {\it new} ({\it right}) endings.\end{table}
+The top 5 most discriminative features for predicting {\it original} vs.~{\it new} ({\it right}) endings.\end{table}
 
@@
 
-In this paper we have shown that different writing tasks affect writing style. 
-Our results indicate that when authors are asked to write the last sentence of a five sentence story, they will use different style to write a {\it right} ending compared to a {\it wrong} ending.
-We have also shown that writing the ending as part of a five sentence story is very different than reading four sentences and then writing the fifth.
+In this paper we have shown that giving a writer a different writing
+task affects her writing style in easily detected ways.
+Our results indicate that when authors are asked to write the last
+sentence of a five sentence story, they will use different style to
+write a {\it right} ending compared to a {\it wrong} ending. We have
+also shown that writing the ending as part of one's own five-sentence story is very different than reading four sentences and then writing the fifth.
 
-Our findings hint that the nature of the writing task imposes a different mental state on the author, which is expressed in ways which are often implicit, but can be unfolded using simple automatic tools.
+Our findings hint that the nature of the writing task imposes a
+different mental state on the author, which is expressed in ways which
+are often implicit, but can be observed using extremely simple automatic tools. 
 This is in line with previous cognitive findings. 
 For instance, previous studies have shown that when answering questions, people  tend to adopt the writing style of the question \cite{Ireland:2010}.
+\nascomment{there must be closer examples?}
 
 Other studies have shown that writing tasks can even have a long term effect.
-A range of works have shown that writing emotional texts and benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
-Some of these works showed that these changes are also accompanied by changes in writing style \cite{Campbell:2003}. 
-The results of the current study can shed more light on the processes that people undergo when presented with different writing tasks.
+A range of works have shown that writing emotional texts can benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
+Some of these works showed that these changes \nascomment{what are
+  ``these changes''?} are also accompanied by changes in writing style
+\cite{Campbell:2003}. The current study suggests that even subtle
+changes to a writing prompt can affect these processes.
+%The results of the current study can shed more light on the processes that people undergo when presented with different writing tasks.
 
-This paper also reveals several important lessons for the future design of NLP tasks. 
+This paper also reveals several important lessons for the future
+design of NLP tasks. 
+\nascomment{this paragraph needs extra care.  the authors of the ROC
+  paper did try to control for a lot of things and they did run
+  baselines.  we ought to be generous and reiterate that here.  what,
+  precisely, did they miss?  the lesson isn't just ``run more controls
+  and baselines'' is it?}
 First, it stresses the need to carefully control for even seemingly minor details. 
@@
 While recent advances in NLP  suggest that many classic NLP methods are out-of-date, 
-this is not necessarily the case, especially for small datasets.
+this is not necessarily the case, especially for small
+datasets. \nascomment{ this bit about simple models feels like a red herring}
 This is particularly important in order to ensure that  new technological improvements are capturing a qualitatively different signal.
-Luckily, the substantial improvement we get when combining our model with the RNN language model (\secref{Experiments}) suggests that despite the high results obtained by the simple, classic model, the more recent RNN approach captures a different aspect of the task.
+Luckily, the substantial improvement we get when combining our model
+with the RNN language model (\secref{Experiments}) suggests that
+despite the high results obtained by the simple model, the
+more recent RNN approach captures a different aspect of the
+task. \nascomment{I like ending on this happier note, but let's not
+  call it ``luck'' and let's focus on the task and representations,
+  not the ML methods, which are probably not the heart of the difference}
 
@@
 
-\paragraph{Writing Style.}
-Writing style has been an active topic of research for decades now. 
-The models used to effectively solve  such tasks are often linear classifiers with style features such as character and word n-grams \cite{Stamatatos:2009,Koppel:2009}.
-Previous works have shown that different authors can be grouped by their writing style, according to factors such as age \cite{Pennebaker:2003,Argamon:2003,Schler:2006,Rosenthal:2011}, gender \cite{Argamon:2003,Schler:2006} and native language \cite{Koppel:2005}.
-At the extreme case, each individual author adopts a unique writing style \cite{pennebaker1999linguistic,Schwartz:2013}. 
-Interestingly, previous work have shown that individual style can be affected from coarse-grained factors such as those just described, but also from other less apparent factors such as mental state, or even living in a high elevation location \cite{schwartz2013personality}.
+\paragraph{Writing style.}
+Writing style has been an active topic of research for decades. 
+The models used to characterize style are often linear classifiers with style features such as character and word $n$-grams \cite{Stamatatos:2009,Koppel:2009}.
+Previous work has shown that different authors can be grouped by their
+writing style, according to factors such as age
+\cite{Pennebaker:2003,Argamon:2003,Schler:2006,Rosenthal:2011,nguyen:2011:latech},
+gender \cite{Argamon:2003,Schler:2006,bamman2014gender}, and native language
+\cite{Koppel:2005}.  \nascomment{cite generously here, it costs us nothing}
+At the extreme case, each individual author adopts a unique writing
+style \cite{mosteller1963inference,pennebaker1999linguistic,Schwartz:2013}. 
+Interestingly, previous work has shown that individual style can be affected from coarse-grained factors such as those just described, but also from other less apparent factors such as mental state, or even living in a high-elevation location \cite{schwartz2013personality}.
 
-Unlike the works just described which compare the writing style between different authors, some works have shown that the same author can adopt different style used when writing positive vs.
-negative text \cite{Davidov:2010} and when writing sarcastic text \cite{Tsur:2010}.
-In this work, we have shown that the same author can adopt a different style when facing different writing tasks.
+Unlike the works just described which compare the writing style
+between different authors, some works have shown that the same author
+can adopt a different style used when writing positive vs.~negative
+text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}. In this work, we have shown that the same author can adopt a different style when facing different writing tasks.
 
-The line of works that most resembles our work is the detection of deceptive text. 
-Several works used stylometric features to  predict deception 
+The line of work that most resembles our work is the detection of deceptive text. 
+Several researchers have used stylometric features to  predict deception 
 \cite{Newman:2003,hancock2007lying,ott2011finding,Feng:2012}.
 Some works even showed that writing style applied when lying is different across genders \cite{Perez:2014a,Perez:2014b}.
-In this work, we have shown that an even more subtle writing task -- writing {\it coherent} and {\it incoherent} story endings -- imposes different styles on the author.
+In this work, we have shown that an even more subtle writing task---writing {\it coherent} and {\it incoherent} story endings---imposes different styles on the author.
 
-\paragraph{Machine Reading.}
-The cloze story task, which is the focus of this paper, is part of a wide set of machine reading works published in the last couple of years.
-These include datasets like bAbI \cite{Weston:2015}, SNLI \cite{bowman2015large}, CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and LAMBADA \cite{Paperno:2016}.
+\paragraph{Machine reading.}
+The cloze story task, which is the focus of this paper, is part of a wide set of machine reading works published in the last few years.
+These include datasets like bAbI \cite{Weston:2015}, SNLI \cite{bowman2015large}, CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad}, and LAMBADA \cite{Paperno:2016}.
 
-While these works have presented valuable resources for the NLP community (as well as for the deep learning community), 
-it is often the case that these datasets suffer from methodological problems, such as inherent ambiguity caused by applying automatic tools when generating the datasets \cite{Chen:2016}. 
-In this paper we have pointed to other methodological problems in  machine reading tasks, namely the different writing tasks used to generated the data, which largely affect the writing style of the positive and negative samples, as well as create a discrepancy between the training and the test data.
+While these works have presented valuable resources for researchers, 
+it is often the case that these datasets suffer from methodological
+problems, such as inherent ambiguity caused by applying automatic
+tools \nascomment{this is not clear to me, what does it mean?} when generating the datasets \cite{Chen:2016}. 
+In this paper we have pointed to another methodological challenge in
+designing machine reading tasks, namely that different writing tasks
+used to generated the data affect the writing style of the positive
+and negative samples, confounding the classification problem.
+%, as well as create a discrepancy between the training and the test data.
+\nascomment{dropped the train/test discrepancy here}
 
@@
 The research question that guided this work is the extent to which different writing tasks result in different writing styles.
-We experimented with the story cloze task, which introduces two interesting comparison points: %setups for our purposes:
+We experimented with the Story Cloze task, which introduces two interesting comparison points: %setups for our purposes:
 %a setup where the same author writes both a {\it right} and an {\it wrong} ending to a story, 
 %and one which compares an ending written as part of a story to a standalone ending added to a story written by someone else.
- the difference between people writing a story on their own and people continuing someone else's story 
- and the difference between the same author writing a coherent and an incoherent story ending.
-In both cases, a simple linear model reveals measurable differences in people's writing styles, %that different styles are imposed.
+ the difference between writing a story on one's own and continuing someone else's story,
+ and the difference between writing a coherent and an incoherent story ending.
+In both cases, a simple linear model reveals measurable differences in writing styles, %that different styles are imposed.
 %The different styles allow our style detection 
 which in turn allows our final 
-model to reach state-of-the-art results on the story cloze task, more than 12\% improvement compared to the best published result.
+model to achieve state-of-the-art results on the story cloze task.
 
-The findings presented in this paper have  cognitive implications, as they motivate further research on the exact effect that different writing tasks have on humans.
+The findings presented in this paper have  cognitive implications, as
+they motivate further research on the exact effect that a writing
+prompt has on an author's response.
 They also provide valuable lessons for designing new NLP datasets.
-Future work will include testing whether other similar writing tasks, such as fake news, also impose their own unique and identifiable style on their authors.
+\nascomment{drop the last sentence, it makes this paper seem less
+  complete} Future work will include testing whether other similar writing tasks, such as fake news, also impose their own unique and identifiable style on their authors.
 
@@
 
-\newpage
 \bibliography{acl2017}

### 2017-01-30 docs/shared_task_paper.tex
added a bunch more to the shared task paer

@@
 \maketitle
-\begin{abstract}
-Taking part in the LSDSem `17 shared task, we describe our system.
-
+\begin{abstract} % This is my real quick try at this lol
+As an effort to further commonsense short story understanding, Mostafazadeh, et al.
+~(2016)\nocite{Mostafazadeh:2016} developed the \textit{Story Cloze Task}, now the 2017 LSD Sem shared task.
+This paper describes the University of Washington's submitted system.
+We use stylistic and text comprehension features to determine which of two endings best fits a short story.
+We achieve $75.1\%$ accuracy.
 \end{abstract}
@@
 The 2017 LSD Sem Shared Task provide a testbed to further commonsense story understanding: the \textit{Story Cloze} task \cite{Mostafazadeh:2016}.
-It was specifically designed for the purpose of facilitating the learning of commonsense knowledge.
-The task consist of finding the \textit{corrent} ending to four sentence short stories, out of two possible endings.
-With the two-ending stories, Mostafazadeh, et al. ~(2016)\nocite{Mostafazadeh:2016} also released nearly $100$k five-sentence short stories, to facilitate learning of commonsense narratives.
+Specifically designed for the purpose of facilitating the learning of commonsense knowledge, the task consist of finding the \textit{corrent} ending to four sentence short stories, out of two possible endings.
+With the two-ending stories, Mostafazadeh, et al.
+~(2016)\nocite{Mostafazadeh:2016} also released nearly $100$k five-sentence short stories (ROC Stories), to facilitate learning of commonsense narratives.
 
@@
 
+\section{Task summary}
+% this section helps clarify some of the nomenclature?
+\ms{note: I don't know if we're emphasizing ``story understanding'' too much, given that we're really not doing that?}
+The \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, selected as the 2017 LSD Sem Shared Task, aims to test commonsense story understanding.
+Towards that goal, two waves of short story collection were done.
+\ms{Below is mostly copy-pasted from the paper, with a little of editing to remove our langConstraint angle.}
+\paragraph{ROC Stories.}
+The ROC Story Corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
+Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
+To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
+which resulted in a wide range of different topics.
+\paragraph{Story Cloze Task.}
+After compiling the story corpus, the {\it Story Cloze Task} -- a task based on the corpus -- was introduced.
+A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
+Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}.
+Both endings are required to complete the story using one of the characters in the story context. 
+Additionally,  the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
+
+The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness. 
+Only stories rated as simultaneously coherent with a {\it right} ending and neutral with a {\it wrong} ending were selected for the task.
+
+Based on these new stories, the task becomes: given a pair of stories that differ only in their endings, how well can the system determine which ending is {\it right} and which is {\it wrong}?
+
+Mostafazadeh, et al. ~(2016)\nocite{Mostafazadeh:2016} split the Story Cloze stories into a development and a test set, each containing $1,871$ stories.
+
+\subsection{Data}
+While the ROC Stories provide data to do unsupervised learning of how stories should end, our goal is to be able to determine whether an ending is the \textit{right} one or the \textit{wrong} one.
+To that extent, we use the development set to train a classifier using features of the individual endings.
+We split that development set (90/10) into training and development.
+The final size of our training/development/test sizes are 3,366/374/3,742 endings, respectively.
+
+It is worth nothing that our classification task is a slightly different take on the {\it Story cloze task}. 
+Instead of classifying pairs of endings, one which is {\it right} and another which is {\it wrong}, we take the set of  {\it right} endings as positive samples and the set of {\it wrong} endings as our negative examples.
+
 \section{System Description}
@@
 %% Maybe mention here that we're doing training on validation set ?
-In our system, we implement a simple linear classifier to choose between the \textit{correct} and \textit{incorrect} endings.
-% \section{Features}
-Specifically, we use two types of features (described in below), designed to capture different dimensions of the problem.
+In our system, we implement a simple linear classifier to determine whether and ending is the \textit{correct} one or the \textit{incorrect} one.
+Specifically, we use the logistic regression implementation by Scikit-Learn \cite{sklearn}, regularizing using an L2 loss.
+We grid search the regularization parameter on our development set. 
+\ms{We should maybe add one of two more sentences?}
+
+\subsection{Features}
+We use two types of features (described below), designed to capture different dimensions of the problem.
 We use \textit{stylistic} features to capture differences in writing between ``coherent'' endings and ``incoherent'' ones.
 We opt for \textit{language model} features to leverage corpus level word distributions, specifically longer term sequence probabilities.
-
-\ms{Some info about training, etc.}
-
-\subsection{Stylistic Features}
+Our end system makes use of $XX$ distinct features. \ms{Would be nice to add that number?}
+\paragraph{Stylistic Features}
 %% take stuff from the paper
@@
 \end{itemize}
+For computing our features, we keep n-gram (character or word) features that occur at least five times in the training set.
+All stylistic feature values are normalized to [0-1].
+For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
 
-\subsection{Language Model Features}
+\paragraph{Language Model Features}
 %% take the RLM paragraph from the paper
@@
 We use the ROC Stories for training, setting aside $10\%$ for validation of the language model. 
-We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=$21,582.
+We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=21,582$.
 Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 

### 2017-01-31 docs/language_constraint.tex
Roy V2

@@
 \newcommand{\com}[1]{}
-
+\newcommand{\resolved}[1]{}
 % Editing macros
@@
 \newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
-\newcommand{\roy}[1]{\footnote{\color{red}{\textbf{Roy: #1}}}}
+\newcommand{\roy}[1]{{\color{orange}\textsc{[#1 --rs]}}}
 \newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
@@
 \newcommand{\nascomment}[1]{{\color{blue}\textsc{[#1 --nas]}}}
+\newcommand{\clinic}[1]{{\color{magenta}\textsc{[#1 --CLINIC]}}}
 
 %\renewcommand{\ms}[1]{}
-%\renewcommand{\roy}[1]{}
+\renewcommand{\roy}[1]{}
+%\renewcommand{\nascomment}[1]{}
+%\renewcommand{\yc}[1]{}
 %\renewcommand{\royb}[1]{}
@@
   Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
+  {\tt email@domain} \\
+  }
 
@@
 %In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
-where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story on their own vs.~adding only a story ending for a given story context and (2) writing a story ending that makes the overall story coherent or incoherent.
+where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story on their own vs.~adding only a story ending for a given story context and (2) writing a story ending that makes the overall story coherent or incoherent.\clinic{Many felt these 2 contraints looks like 3 constraints.
+clarify}
 %We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
@@
 state-of-the-art results on the story cloze challenge,
-substantially higher than sophisticated deep learning models,
+substantially higher than  deep learning models,
 even without looking at the story context. 
 %Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors. 
-Our results demonstrate that different task framings can dramatically affect the way people write. 
-They also provide important lessons for designing new NLP
+Our results demonstrate that different task framings can dramatically affect the way people write.\clinic{Similarly to previous comment: which results does this comment address?} 
+\resolved{They also provide important lessons for designing new NLP
 tasks. \nascomment{drop this sentence if we only have a paragraph
-  about this at the end, as we currently do}
+  about this at the end, as we currently do}}
 
 \end{abstract}
-
-\nascomment{resolve:  story cloze or cloze story?  we go back and
-  forth.  use the standard one and capitalize it consistently.}
 
@@
 %or mere 
-and 
-personality \cite{Stamatatos:2009}, 
+and personality \cite{Stamatatos:2009}, 
 %but also by other parameters 
-and the cognitive states of the authors such as 
+as well as the cognitive states\clinic{Avoid using ``cognitive"?} of the authors such as 
 %such as the sentiment of the text \cite{Davidov:2010}, its level of sarcasm \cite{Tsur:2010} and whether it's deceptive \cite{Feng:2012}.
@@
 writing style is affected by 
-the nature of the writing task she was asked to perform, since
-different tasks likely engage different cognitive processes.
+the nature of the writing task the writer was asked to perform, since
+different tasks likely engage different cognitive processes.\clinic{Add citation}
 %that would involve different cognitive processes.
@@
 {\bf Type} & {\bf Example} \\ \hline
-{\color{blue}{\it Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
-{\color{forestgreen}{\it Coherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
-{\color{red}{\it Incoherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
+{\color{blue}{Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
+{\color{forestgreen}{Coherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
+{\color{red}{Incoherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
 \end{tabular}
 \caption{\label{ROC-example}
-Examples of stories from the story cloze task. The first row shows an {\it original} story written by one author. 
+Examples of stories from the story cloze task \cite{Mostafazadeh:2016}. The first row shows an {\color{blue}{Original}} story written by one author. 
 The second and third row show revised stories with two contrastive endings:
  %of the same story: 
- a {\it right} ending and a {\it wrong} one.
-\nascomment{I like the colors a lot.  Instead of all the italicizing,
-  let's consider just color-coding these three terms.  It's less distracting.}
+ a {\color{forestgreen}{Coherent}} ending and a {\color{red}{Incoherent}} one.\clinic{They said it would be great to have three endings to the same story.
+Unfortunately Nasrin et al.
+didn't publish the original endings for the dev/test data.
+We could ask her, but not sure if this is worth it}
+ \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
+let's consider just color-coding these three terms.  It's less distracting.}}
 }
@@
 %use different style when composing the final sentence as part of their own five sentence story, compared to reading four sentences, and then writing a standalone ({\it right}) ending?
-maintain the same writing style when writing the entire story on their own compared to 
+maintain the same writing style\clinic{What is style? (Luke)} when writing the entire story on their own compared to 
 writing only the final sentence for a given story context written by someone else?
@@
 Our analysis indicates that different framings of similar writing tasks 
-can lead to measurable differences in people's writing style.
+can lead to measurable differences in people's writing style.\clinic{This is the main message -- should come earlier}
 %We experiment with a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
@@
 Further, our classifier can also distinguish between the {\it original} endings and the new ({\it right}) endings with 68.5\% accuracy, again without looking at the story context.
+\clinic{Why do we care?
+(Luke)}
 
@@
 over the previously reported state of the art 
-\cite{Salle:2016}.
+\cite{Salle:2016}.\clinic{Too many numbers in these paragraphs}
 %When analyzing the results of our classifier, we see that sentiment plays a significant role in its success, which suggests that constraining authors to ``wrong'' sentences results in negative text.
-Our analysis reveals that \nascomment{feels like a leap here, maybe
+We analyze the results of our classifier, and show that when distinguishing between {\it right} and {\it wrong} endings,  \resolved{\nascomment{feels like a leap here, maybe
   change wording a bit -- will come back to this.  note after reading
   all the way to the end:  need to be careful about conclusions drawn
-  from weights alone } sentiment plays a significant role, such that authors writing the wrong endings often engage negative sentiment.
+  from weights alone }} sentiment plays a significant role: authors writing the wrong endings often engage negative sentiment.\roy{Better wording?
+we keep it depending on whether we keep our methodology}\clinic{more details required?}
 
@@
 75.2\%---an additional 2.8\% gain, 15.3\% better than the best
-published result.\footnote{
+published result.\resolved{\footnote{
 %Recently, a shared task for the story cloze
@@
 should only mention it once and not in the intro.
-}
+}}
 %For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.
@@
 %as they suggest that these might have different style compared to real news.
-Second, our results provide valuable lessons for designing new NLP tasks,
+Second, our results provide valuable insights for designing new NLP tasks,\clinic{unclear}
 both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
@@
 We then present our model, experiments and results in Sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
-Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present an
-ablation study and a discussion, followed by related work and conclusions.
+Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present a further analysis of our results  and a discussion, followed by related work and conclusions.\clinic{Omit this paragraph?}
 
-\isection{The Cloze Story Task}{ROC_Story}
-In this paper, we seek to understand how different writing tasks affect writing style.
-To do so, we focus on the \textit{Story Cloze Task} \cite{Mostafazadeh:2016}. 
+\isection{Background: The Story Cloze Task}{ROC_Story}
+To understand how different writing tasks affect writing style, 
+we focus on the \textit{story cloze task} \cite{Mostafazadeh:2016}. 
 While this task was developed to facilitate representation and learning of commonsense story understanding,
-it introduces a few interesting properties which make it ideal for our study. 
+it introduces a few interesting properties\clinic{which properties?} which make it ideal for our study. 
 We describe the task below.
@@
 \paragraph{Story Cloze Task.}
-After compiling the story corpus, the {\it Story Cloze Task}---a task based on the corpus---was introduced.
+After compiling the story corpus, the {\it story cloze task}---a task based on the corpus---was introduced.
 A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
@@
 
-The resulting stories, both {\it right} and {\it wrong}, were then
-individually rated for coherence and meaningfulness \nascomment{by
-  additional AMT workers? or someone else?}. 
+The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness by additional AMT workers. \resolved{\nascomment{by
+-  additional AMT workers? or someone else?}} 
 Only stories rated as simultaneously coherent with a {\it right} ending and neutral with a {\it wrong} ending were selected for the task. 
@@
 
-Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it Story Cloze Task}. 
+Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it story cloze task}. 
 The task is simple:  given a pair of stories that differ only in their endings, the system decides which ending is {\it right} and which is {\it wrong}. 
@@
 
-\paragraph{State-of-the-art performance.}
+\paragraph{A Hard Task.}\roy{Was ``State-of-the-art results". Luke mentioned that this puts the focus on our results rather than on the nature of the task, as we intended}
 Interestingly, at the time of this submission, 10 months after the
-paper was first published, the published benchmark on this task is
+task was first introduced, the published benchmark on this task is
 still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
@@
   unpublished along with the underlying methodology.}
-This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and SNLI \cite{bowman2015large}, for which results improved dramatically over a similar period of time.
+This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and SNLI \cite{bowman2015large}, for which results improved dramatically over a similar or shorter period of time.
 This suggests that this task is challenging and that high performance is hard to achieve.
-\yc{SQuAD was officially published in Nov 2016. by the time the
-  official EMNLP talk was presented, the leaderboard performance
-  (still unpublished) was  30\% beyond the best results in the
-  paper. Given that, the statement of this paragraph seems a bit of
-  overkill...?} \nascomment{it sounds like Yejin is saying that on
-  squad, there was an even faster acceleration?  or that we should
-  change ``similar period of time'' to ``similar or shorter period of time''?}
+ \resolved{\yc{SQuAD was officially published in Nov 2016.
+by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper.
+Given that, the statement of this paragraph seems a bit of overkill...?} \nascomment{it sounds like Yejin is saying that on squad, there was an even faster acceleration?
+or that we should change ``similar period of time'' to ``similar or shorter period of time''?}}
 
-\paragraph{Different writing tasks in the Story Cloze Task.}
+\paragraph{Different Writing Tasks in the Story Cloze Task.}
 \citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
@@
 
-Despite these efforts, several key aspects were not controlled for. 
+Several key design decisions make this task an interesting testbed for our purpose.\clinic{Which purpose?}
 First, the training set for the task (ROC Stories corpus) is not a
@@
   testing instances will be drawn from.}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
-\yc{As far as I understand, this was intentional --- they didn't want
+ \resolved{\yc{As far as I understand, this was intentional --- they didn't want
   people to pick up on random superfluous cues that can inevidently
@@
 this not as ``things weren't controlled for'' but instead stick to the
-facts here and just describe what they did without judgment.}
+facts here and just describe what they did without judgment.}}
 
@@
 
-Second, although the {\it right} and {\it wrong} sentences were generated by the same author, 
+Finally, although the {\it right} and {\it wrong} sentences were generated by the same author, 
 the tasks for generating them were quite different: in one case, the author was asked to write a {\it right} ending, which would create a coherent five-sentence story along with the other four sentences.
 In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story.
-In this work, we show that these differences are significant and
+ \resolved{In this work, we show that these differences are significant and
 impose different writing styles on authors. \nascomment{this bit feels
-  a little heavy and reptititive.}
+  a little heavy and reptititive.}}
 
-\paragraph{Initial Analysis.}
+\isection{Surface Analysis.}{Surface}
 We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
 Our analysis  reveals several style differences between different groups. 
-First, {\it original} endings are on average much longer (11 words per
+First, {\it original} endings are on average longer (11 words per
 sentence) than {\it right} endings (8.75 words), which are in turn
@@
   (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})
-  across \emph{original} endings (Story Cloze training set), and
-  \emph{right} and \emph{wrong} endings (from the Story Cloze Task).}
+  across \emph{original} endings (story cloze training set), and
+  \emph{right} and \emph{wrong} endings (from the story cloze task).}
 
@@
 
-The goal of this paper is to determine the extent to which 
+One goal of this paper is to determine the extent to which 
 %does constraining authors in their writing assignments lead to them adopting different writing styles. 
@@
 
-We train a logistic regressionclassifier to distinguish between different endings. 
+We train a logistic regression classifier to distinguish between different endings. 
 Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
@@
 The goal of this experiment is to measure to what extent  style features capture differences between the {\it right} and {\it wrong} endings.
-As the cloze story task doesn't have a training corpus for the {\it
+As the story cloze task doesn't have a training corpus for the {\it
   right} and {\it wrong} endings (see \secref{ROC_Story}), we use the
@@
 (3,366 training endings, 374 for development). 
- We keep the Story Cloze test set as is (3,742 endings).
+ We keep the story cloze test set as is (3,742 endings).
 
-It is worth nothing that our classification task is slightly different from the story cloze task. 
+It is worth noting that our classification task is slightly different from the story cloze task. 
 Instead of classifying pairs of endings, one which is {\it right} and
@@
 \emph{wrong} (negative instance).
-By ignoring the coupling between {\it right} and {\it wrong} pairs, we
+By ignoring the coupling between {\it right} and {\it wrong} pairs, 
+we are able to decrease the impact of author-specific style differences,
+and focus on the difference between the styles accompanied with {\it right} and {\it wrong} writing.
+\resolved{we
 are able make a more general claim about the style used when writing
 each of the tasks \nascomment{I'm not sure I follow this sentence; can
-we be more clear?}.
+we be more clear?}.}\roy{Better now?}
 
@@
 story imposes different style compared to writing a new ({\it right}) ending to an existing story.
-We use the endings of the ROC stories as our {\it original} training
-samples and {\it right} endings from the story cloze task  development
-and test sets \nascomment{if you're using the test examples as
+We use the endings of the ROC stories as our {\it original} samples and {\it right} endings from the story cloze task   \resolved{\nascomment{if you're using the test examples as
   training data, what are you using for test? and development?  I would have thought
-  you'd follow the same pattern as above ...} as {\it new} training samples.
+  you'd follow the same pattern as above ... }}as {\it new} samples.
 As there are far more {\it original} instances than {\it new}
 instances, we randomly select the same number of \emph{original}
-instances \nascomment{(give the number in parentheses, for train/dev/test)} as we have
-\emph{new} instances, for each of the training, development, and test sets.
-We randomly sample 5 training sets and report the average classification result.
+instances  \resolved{\nascomment{(give the number in parentheses, for train/dev/test)} }as we have
+\emph{new} instances (3,366 training endings, 374 development endings, and 3,742 test endings).
+We randomly sample 5 {\it original} sets and repeat the classification experiments.
+We report the average classification result.
 
@@
 We use  Python's sklearn logistic regression implementation with $L_2$
-regularization, performing grid search on the development test to
-select the hyperparameter.  \nascomment{any other hyperparameters?  if
-  not, say this is the only one.  else explain what they are.}
+regularization, performing grid search on the development set to
+tune a single hyperparameter -- the regularization parameter.   \resolved{\nascomment{any other hyperparameters?  if
+  not, say this is the only one.  else explain what they are.}}
 
@@
 In Experiment 1, our model obtains 64.5\%
-classification accuracy, well above a (50\%-accurate) random baseline.
+classification accuracy, well above a (50\%-accurate) random baseline.\clinic{How good is this?}
 For Experiment 2, our model is even stronger, at 68.5\%.
@@
 
+ \resolved{
 \begin{figure}
@@
 \end{figure}
+}
+
+\begin{table}[!t]
+\begin{center}
+%\small
+\begin{tabular}{|c|c|} \hline
+{\bf Experiment} & {\bf Accuracy} \\ \hline
+{\it Right/Wrong} & 64.5\% \\ \hline
+{\it Original/Right} & 68.5\% \\ \hline
+{\it Original/Wrong} & 75.6\% \\ \hline
+\end{tabular}
+\end{center}
+\caption{\label{results} Results of  experiments 1 ({\it Right/Wrong}) and 2 ({\it Original/Right}). 
+Bottom row shows an additional experiment which classifies {\it  original} endings vs \textit{\textbf{wrong}} endings.
+In all cases, our setup implies a 50\% random baseline.}
+\end{table}
 
@@
 The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
-In order to further estimate the quality of our classification results, we tackle the Story Cloze Task using our classifier.
+In order to further estimate the quality of our classification results, we tackle the story cloze task using our classifier.
 This classification task is more constrained than Experiment 1, as two
@@
 
-\tabref{cloze_results} shows our results on the Story Cloze test
+\tabref{cloze_results} shows our results on the story cloze test
 set. Our classifier obtains 72.4\% accuracy, 12.5\% higher than the
-published state-of-the-art result on the task \nascomment{cite that here}.
+published state-of-the-art result on the task \cite{Salle:2016} \resolved{\nascomment{cite that here}}.
 Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
@@
 
-\nascomment{I suppressed the sentences about the LSDSem shared task;
-  once, in the earlier footnote, is enough.}
+ \resolved{\nascomment{I suppressed the sentences about the LSDSem shared task;
+  once, in the earlier footnote, is enough.}}
 % Other than the published works that tackled this task, a few  recent works published their results in the LSDSem shared task website.\footnote{\url{https://competitions.codalab.org/competitions/15333}}
@@
 \caption{\label{cloze_results}
-Results on the test set of the Cloze Story task. 
+Results on the test set of the  story cloze task. 
 The first block are published results, the second block
@@
 LexVec results are taken from \cite{Speer:2016}.
-RNN is our implementation. \nascomment{I added 0s to ``Niko'' result
+RNN is our implementation. 
+Human judgement scores are taken from \cite{Mostafazadeh:2016}. \resolved{\nascomment{I added 0s to ``Niko'' result
   and ``human''
@@
 human judgments come from?  those are not mentioned in our text anywhere!}
-}
+}\clinic{Add a symbol for ``uses story context?''}}
 \end{table}
@@
 %and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
-Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the Story Cloze task designers, and harnesses their ROC Stories training set, which consists of single-ending stories.
+Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the story cloze task designers, and harnesses their ROC Stories training set, which consists of single-ending stories.
 We show that the adding our features to this powerful language model
 gives improvements over our classifier as well as the language
-model. \nascomment{reworded.  more important that our features help
-  the language model, than the other way around!}
+model.  \resolved{\nascomment{reworded.  more important that our features help
+  the language model, than the other way around!}}
 
@@
 % Eval
-On its own, our neural language model performs moderately well on the Story Cloze test. 
+On its own, our neural language model performs moderately well on the story cloze test. 
 This is not surprising, as \citet{Mostafazadeh:2016} hinted  that
@@
 accuracy on the task, adding value even when context and a large
-training dataset are used. \nascomment{check reframing here}
+training dataset are used.  \resolved{\nascomment{check reframing here}}
 
@@
 
-\nascomment{these aren't just ablations, so I retitled}
+ \resolved{\nascomment{these aren't just ablations, so I retitled}}
 
@@
 These baselines measured the relative sentiment between the ending and the previous sentences.
-The performance of both these baselines was roughly chance-level, which seems to suggest that this is not the case.
-\yc{Is it really because there's no statistical tendency in the original stories to have happy endings, as opposed to the alternative possibility --- the sentiment classifier used by Monstafazadeh 2016 didn't quite nail down the optimal feature encodings?}
+The performance of both these baselines was roughly chance-level, which seems to suggest that this is not entirely the case.
+\resolved{\yc{Is it really because there's no statistical tendency in the original stories to have happy endings, as opposed to the alternative possibility --- the sentiment classifier used by Monstafazadeh 2016 didn't quite nail down the optimal feature encodings?}} \roy{this is definitely an option, and that's partly why I used hedging (``seems to suggest'').
+Tones it down a bit more.}
 
@@
 In this paper we have shown that giving a writer a different writing
-task affects her writing style in easily detected ways.
+task affects writing style in easily detected ways.
 Our results indicate that when authors are asked to write the last
@@
 A range of works have shown that writing emotional texts can benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
-Some of these works showed that these changes \nascomment{what are
-  ``these changes''?} are also accompanied by changes in writing style
-\cite{Campbell:2003}. The current study suggests that even subtle
-changes to a writing prompt can affect these processes.
+Some of these works showed that these health benefits  \resolved{\nascomment{what are
+  ``these changes''?}} are also accompanied by changes in writing style
+\cite{Campbell:2003}.\clinic{Which kind of changes? related to our by any chance?} The current study suggests that even subtle
+changes to a writing prompt can affect these processes.\clinic{Belongs to introduction?}
 %The results of the current study can shed more light on the processes that people undergo when presented with different writing tasks.
@@
 design of NLP tasks. 
-\nascomment{this paragraph needs extra care.  the authors of the ROC
+The story cloze task was very carefully designed. Many factors, such as the topic diversity, as well as  temporal and causal relation diversity,  were controlled for \cite{Mostafazadeh:2016}. 
+The authors also made sure each pair of endings was written by the same author, partly in order to avoid author specific style effects.
+ Nonetheless, this paper shows that despite these efforts, several significant style differences are found between the training and the test set, as well as between the positive and negative labels.
+
+The findings in this paper suggest that careful attention must be paid to instructions given to authors, especially in unnatural tasks such as writing a {\it wrong} ending. 
+One way to avoid such problems is by using shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
+A different approach is to use naturally occurring text, as used in recent machine reading tasks (see \secref{Related}). 
+However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
+
+Another lesson from this paper relates to baseline methods. 
+The authors of the story cloze task experimented with a wide and diverse set of baselines, including n-gram baselines, word embeddings baselines, sentiment baselines, and narrative chain baselines. 
+Nonetheless, running preliminary tests on the data, such as average length or  POS and word distribution,  could have revealed potentially unwanted phenomena in the data.
+\resolved{\nascomment{this paragraph needs extra care.  the authors of the ROC
   paper did try to control for a lot of things and they did run
@@
 this is not necessarily the case, especially for small
-datasets. \nascomment{ this bit about simple models feels like a red herring}
+datasets. \nascomment{ this bit about simple models feels like a red herring}}
 This is particularly important in order to ensure that  new technological improvements are capturing a qualitatively different signal.
-Luckily, the substantial improvement we get when combining our model
+The substantial improvement we get when combining our model
 with the RNN language model (\secref{Experiments}) suggests that
-despite the high results obtained by the simple model, the
-more recent RNN approach captures a different aspect of the
-task. \nascomment{I like ending on this happier note, but let's not
+despite the high results obtained by the simple model, 
+methods that exploit the wider context  capture a different aspect of the
+task. \resolved{\nascomment{I like ending on this happier note, but let's not
   call it ``luck'' and let's focus on the task and representations,
-  not the ML methods, which are probably not the heart of the difference}
+  not the ML methods, which are probably not the heart of the difference}}
+  \roy{Modified this to be more concrete. Did end up hinting that they should have done a better job at analyzing their data before publishing. Feel free to tone down.}
 
@@
 gender \cite{Argamon:2003,Schler:2006,bamman2014gender}, and native language
-\cite{Koppel:2005}.  \nascomment{cite generously here, it costs us nothing}
+\cite{Koppel:2005,Tsur:2007,Bergsma:2012}.   \resolved{\nascomment{cite generously here, it costs us nothing}}
 At the extreme case, each individual author adopts a unique writing
@@
 \paragraph{Machine reading.}
-The cloze story task, which is the focus of this paper, is part of a wide set of machine reading works published in the last few years.
+The  story cloze task, which is the focus of this paper, is part of a wide set of machine reading works published in the last few years.
 These include datasets like bAbI \cite{Weston:2015}, SNLI \cite{bowman2015large}, CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad}, and LAMBADA \cite{Paperno:2016}.
@@
 it is often the case that these datasets suffer from methodological
-problems, such as inherent ambiguity caused by applying automatic
-tools \nascomment{this is not clear to me, what does it mean?} when generating the datasets \cite{Chen:2016}. 
+problems caused by applying noisy automatic tools to generate the data\resolved{ \nascomment{this is not clear to me, what does it mean?} when generating the datasets} \roy{better?}\cite{Chen:2016}. 
 In this paper we have pointed to another methodological challenge in
@@
 %, as well as create a discrepancy between the training and the test data.
-\nascomment{dropped the train/test discrepancy here}
+ \resolved{\nascomment{dropped the train/test discrepancy here}}
 
@@
 The research question that guided this work is the extent to which different writing tasks result in different writing styles.
-We experimented with the Story Cloze task, which introduces two interesting comparison points: %setups for our purposes:
+We experimented with the story cloze task, which introduces two interesting comparison points: %setups for our purposes:
 %a setup where the same author writes both a {\it right} and an {\it wrong} ending to a story, 
@@
 They also provide valuable lessons for designing new NLP datasets.
-\nascomment{drop the last sentence, it makes this paper seem less
-  complete} Future work will include testing whether other similar writing tasks, such as fake news, also impose their own unique and identifiable style on their authors.
+ \resolved{\nascomment{drop the last sentence, it makes this paper seem less
+  complete} Future work will include testing whether other similar writing tasks, such as fake news, also impose their own unique and identifiable style on their authors.}
 

### 2017-01-31 docs/shared_task_paper.tex
another pass at the entire shared task paper

@@
 This paper describes the University of Washington's submitted system.
-We use stylistic and text comprehension features to determine which of two endings best fits a short story.
-We achieve $75.1\%$ accuracy.
+We use stylistic and text comprehension features to determine which of two endings best completes a short story.
+We achieve $75.2\%$ accuracy.
 \end{abstract}
@@
 \section{Introduction}
-% Describe the overall landscape of the problem
-%  - Commonsense knowledge
-%  - Script Learning
-%  -
+\ms{note: I don't know if we're emphasizing ``story understanding'' too much, given that we're really not doing that?}
 
@@
 Specifically designed for the purpose of facilitating the learning of commonsense knowledge, the task consist of finding the \textit{corrent} ending to four sentence short stories, out of two possible endings.
-With the two-ending stories, Mostafazadeh, et al.
+% Along with the two-ending stories, Mostafazadeh, et al.
 ~(2016)\nocite{Mostafazadeh:2016} also released nearly $100$k five-sentence short stories (ROC Stories), to facilitate learning of commonsense narratives.
@@
 In this paper, we describe the system submission from the University of Washington NLP group (UW NLP).
-We implement a simple classifier that uses surface features as well as language model features. Using the Shared Task test set, we achieve $75.1\%$ accuracy.
+We implement a simple classifier that uses surface features as well as language model features. Using the Shared Task test set, we achieve $75.2\%$ accuracy.
 
@@
 % this section helps clarify some of the nomenclature?
-\ms{note: I don't know if we're emphasizing ``story understanding'' too much, given that we're really not doing that?}
+
 The \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, selected as the 2017 LSD Sem Shared Task, aims to test commonsense story understanding.
 Towards that goal, two waves of short story collection were done.
+
 \ms{Below is mostly copy-pasted from the paper, with a little of editing to remove our langConstraint angle.}
@@
 A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
-Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}.
+Workers were asked to write a pair of new story endings for each story context: a {\it right} one and a {\it wrong} one.
 Both endings are required to complete the story using one of the characters in the story context. 
@@
 
-Mostafazadeh, et al. ~(2016)\nocite{Mostafazadeh:2016} split the Story Cloze stories into a development and a test set, each containing $1,871$ stories.
-
 \subsection{Data}
+For the Shared task, Mostafazadeh, et al. ~(2016)\nocite{Mostafazadeh:2016} split the Story Cloze stories into a development and a test set, each containing $1,871$ stories.
 While the ROC Stories provide data to do unsupervised learning of how stories should end, our goal is to be able to determine whether an ending is the \textit{right} one or the \textit{wrong} one.
@@
 In our system, we implement a simple linear classifier to determine whether and ending is the \textit{correct} one or the \textit{incorrect} one.
-Specifically, we use the logistic regression implementation by Scikit-Learn \cite{sklearn}, regularizing using an L2 loss.
+Specifically, we use the logistic regression implementation by Scikit-Learn \cite{scikit-learn}, regularizing using an L2 loss.
 We grid search the regularization parameter on our development set. 
@@
 %% take the RLM paragraph from the paper
-In addition to stylistic features, we experiment with state-of-the-art text comprehension models, specifically a recurrent language model (RLM, Mikolov, et al. (2010)\nocite{mikolov2010recurrent}).
-We train the RLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension $h=512$.
-We use the ROC Stories for training, setting aside $10\%$ for validation of the language model. 
-We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of $|V|=21,582$.
+In addition to stylistic features, we experiment with state-of-the-art text comprehension models, specifically a recurrent neural network language model (RNNLM; Mikolov, et al.
+(2010)\nocite{mikolov2010recurrent}).
+We train the RNNLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension 512.
+We use the ROC Stories for training, setting aside 10\% for validation of the language model. 
+We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of 21,582.
 Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
-Using AdamOptimizer \cite{kingma2014adam} and a learning rate of $\eta=.001$, we train with backpropagation on cross-entropy. % minibatches of $50$ stories.
+Using AdamOptimizer \cite{kingma2014adam} and a learning rate of
+$\eta=.001$, we train to minimize cross-entropy.
+
+In our classifier, we include three different scores given by the language model:
+$p_\theta(\textrm{ending})$, $
+p_\theta(\textrm{ending} \mid \textrm{story})$, $
+\frac{p_\theta(\textrm{ending} \mid \textrm{story})}{p_\theta(\textrm{ending})}$.
+
+The intuition is that a \emph{right} ending should be unsurprising (to the model)given the four preceding sentences of the story (the numerator), controlling for the inherent surprisingness of the words in that ending (the denominator).
+\ms{@roy, did we try a classifier trained on all three features only?}
+
 \section{Results \& Discussion}
+
+\begin{table}%[!t]
+\begin{center}
+%\small
+\begin{tabular}{|l|r|} \hline
+{\bf Model} & {\bf Accuracy} \\ \hline
+{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
+{LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
+%{Niko (shared task)}	& 0.700\\ 
+%{tbmihaylov (shared task)} & 0.711\\ \hline\hline
+{RNNLM}		& 0.677 \\ 
+{Stylistic features} & {0.724} \\ 
+{\bf Combined (Style + RNNLM)} & {\bf 0.752} \\ \hline\hline
+Human judgment & 1.000 \\ \hline
+\end{tabular}
+\end{center}
+\caption{\label{cloze_results}
+Results on the test set of the  story cloze task. 
+The first block are published results, the second block
+as-yet-unpublished results from the LSDSem 2017 leaderboard, the third
+block ours.
+LexVec results are taken from \cite{Speer:2016}.
+RNN is our implementation. 
+Human judgement scores are taken from \cite{Mostafazadeh:2016}. 
+}
+\end{table}
+
 % Show results
+The performance of our system is described in Table \ref{cloze_results}.
+With $75.2\%$ accuracy, our system achieved $15.3\%$ better than the published state of the art by Salle et al.
+(2016) \nocite{Salle:2016}.
+\ms{At the time of submission, we beat everyone or we're ranked XX in the leaderboard.}
+Ablation analysis shows that stylistic features have the most predictive power.
+This suggests that while this task is about story understanding, there is some information contained in stylistic features, which are slightly less sensitive to content.
+As expected, RNNLM features complement the stylistic ones, boosting performance by $2.8\%$.
+This suggests that while the stylistic feaures provide useful signal, content-oriented models also contribute information.
+\ms{Perhaps, an even more complex story understanding model would provide an even greater boost.}
+
+\subsection{Further analysis}
+
+\begin{table}[h]
+\begin{center}
+%\small
+\begin{tabular}{|c|c|} \hline
+\textit{\textbf{Right}} & \textit{\textbf{Wrong}}\\ \hline
+`ally' & ` hate'\\ \hline
+`VBD the' & ` hat'\\ \hline
+`START RB' & `START NNP'\\ \hline
+`ved ' & `ated'\\ \hline
+` tim' & `NN .'\\ \hline
+
+\end{tabular}
+\end{center}
+\caption{\label{exp1_features}}
+The top 5 most discriminative features for predicting {\it right} vs.~{\it wrong} endings.\end{table}
+
+\ms{Don't know if this steps onto our other paper's toes.}
+We analyze which features are most predictive of a \textit{wrong} or \textit{right} ending.
+Table \ref{exp1_features} shows the highest weighted features using the logistic regression coefficients. 
+The table shows a few interesting trends. 
+First, authors tend to structure their sentences differently when writing {coherent}  vs. {incoherent} endings.
+For instance, {coherent} endings are more likely to start with an adverb (e.g., ``then'', ``so'', ``eventually''), while {incoherent} ones tend to start with a proper noun.
+In addition, we find that {incoherent} endings are more likely to
+finish the sentence with a common noun.  %\nascomment{note to self to come backto this after we agree on methodology.}
+
+More interestingly, the different writing tasks seem to impose a specific sentiment on the writer. 
+Three of the top four most salient features for detecting {\it wrong} endings are variants of the verb ``hate''.
+This indicates that when authors are asked to write {\it wrong} text, they tend to use negative language.
+
+An alternative explanation to this hypothesis might be that the first four sentences of the stories in the ROC story corpus tend to be positive, and thus in order to make an ending {\it wrong}, authors adopted a negative approach.
+A similar idea was suggested in the original story cloze paper, where two sentiment-based baselines were evaluated. 
+These baselines measured the relative sentiment between the ending and the previous sentences.
+The performance of both these baselines was roughly chance-level, which seems to suggest that this is not entirely the case.
 
@@
 \section{Conclusion}
-
+This paper described the UW NLP's submission to the 2017 LSD Sem Shared Task. 
 % Our system makes use of knowledge brought to us by the constrained writing literature (?)
 % talk about how we use state-of-the-art language modelling tools.
-% We achieve $75.1\%$ which is ranked XXth in the ongoing codalab competition.
+Our system leveraged stylistic features and text comprehension features, achieving $75.2\%$ accuracy on the classification task.
+We used standard NLP features to capture the style of short story endings, and state of the art language model tools for content-sensitive features.
+% We achieve $75.2\%$ which is ranked XXth in the ongoing codalab competition?
+% Say something like:
+While we achieved \ms{(near?)} state of the art performance, we still only achieved 75\% accuracy.
+This means the task is far from being solved.
+We need better tools to understand the common sense knowledge embedded in these stories.
 

### 2017-02-01 docs/shared_task_paper.tex
Shared Task: Maarten+Roy V1

@@
 \usepackage{latexsym,xcolor}
+\usepackage{multirow}
 
@@
 
-\title{Story Cloze task -- UW System}
+\newcommand{\tabref}[1]{Table~\ref{#1}}
+\newcommand{\com}[1]{}
+\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
+
+\title{Story Cloze task -- XXX System}
 
@@
 \begin{abstract} % This is my real quick try at this lol
-As an effort to further commonsense short story understanding, Mostafazadeh, et al.
-~(2016)\nocite{Mostafazadeh:2016} developed the \textit{Story Cloze Task}, now the 2017 LSD Sem shared task.
-This paper describes the University of Washington's submitted system.
-We use stylistic and text comprehension features to determine which of two endings best completes a short story.
-We achieve $75.2\%$ accuracy.
+This paper describes our system for the Linking Models of Lexical, Sentential and Discourse-level Semantics (LSDSem 2017) shared task -- the \textit{Story Cloze Task}.
+%
+Our system feeds a linear classifier with a variety of features, including both the output of a neural language model and style features. %determine which of two endings best completes a short story.
+We report  $75.2\%$ accuracy on the task.
 \end{abstract}
@@
 \section{Introduction}
-\ms{note: I don't know if we're emphasizing ``story understanding'' too much, given that we're really not doing that?}
+%\ms{note: I don't know if we're emphasizing ``story understanding'' too much, given that we're really not doing that?}
+As an effort to advance commonsense  understanding, \newcite{Mostafazadeh:2016} developed the \textit{story cloze task}, which is the focus of the LSDSem 2017 shared task. 
+In this task, systems are given two short, self-contained stories, which differ only in their last sentence: 
+one has a {\it right} (coherent) ending, and the other has a {\it wrong} (incoherent) ending.
+The task is to tell which is the {\it right} story.
+In addition to the task, the authors also introduced the {\it ROC story corpus} --  a training corpus of five-sentence (coherent) stories. 
+%The goal of the task is to determine which of the endings is the correct one.
+%The goal of this dataset is to serve as a commonsense challenge for NLP and AI research. 
+\tabref{ROC-example} shows an example of a {\it coherent} story and an {\it incoherent} story from the story cloze task.
 
+\com{
 Learning of commonsense knowledge is one of AI's biggest challenges, since it is not usually found in knowledge bases.
@@
 ~(2016)\nocite{Mostafazadeh:2016} also released nearly $100$k five-sentence short stories (ROC Stories), to facilitate learning of commonsense narratives.
+}
 
 % Last paragraph should be a quick description of our system.
-In this paper, we describe the system submission from the University of Washington NLP group (UW NLP).
-We implement a simple classifier that uses surface features as well as language model features. Using the Shared Task test set, we achieve $75.2\%$ accuracy.
+In this paper, we describe the system we submitted for the shared task.
+Our system explores several types of features for the task.
+First, we train a neural language model \cite{mikolov2010recurrent} on the ROC story corpus. 
+We use the probabilities assigned by the model to each of the endings ({\it right} and {\it wrong}) as classification features.
 
+Second, we attempt to distinguish between {\it right} and {\it wrong} endings using style features, such as sentence length, character n-grams and word n-grams. 
+Our intuition is that the {\it right} endings use a different style compared to the {\it wrong} endings.
+The features we use are motivated by previous works on tasks such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, 
+and authorship profiling \cite{Stamatatos:2009}, for which similar style features are known to be very effective.
+
+We feed our features to  a logistic regression classifier, and evaluate our system on the shared task.
+Our system obtains $75.2\%$ accuracy on the test set.
+
+\begin{table}[!t]
+%\small
+\begin{tabular}{|p{3.5cm}|p{3.5cm}|} \hline
+{\bf Story Prefix} & {\bf Ending} \\ \hline
+\multirow{2}{*}{\parbox[b][7.5em][c]{3.5cm}{Kathy went shopping.
+She found a pair of great shoes.
+The shoes were \$300.
+She bought the shoes.}}	&{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \cline{2-2}
+& {\color{red}{Kathy hated buying shoes.}} \\ \hline
+\end{tabular}
+\caption{\label{ROC-example}
+Examples of stories from the story cloze task \cite{Mostafazadeh:2016}. 
+The left column shows that first four sentences of a story. 
+The right column shows two contrastive endings for the story:
+ %of the same story: 
+ a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.
+}
+%\end{center}
+\end{table}
+\com{
 \section{Task summary}
@@
 
-\ms{Below is mostly copy-pasted from the paper, with a little of editing to remove our langConstraint angle.}
+%\ms{Below is mostly copy-pasted from the paper, with a little of editing to remove our langConstraint angle.}
 \paragraph{ROC Stories.}
@@
 Instead of classifying pairs of endings, one which is {\it right} and another which is {\it wrong}, we take the set of  {\it right} endings as positive samples and the set of {\it wrong} endings as our negative examples.
+}
 
@@
 %% Maybe mention here that we're doing training on validation set ?
-In our system, we implement a simple linear classifier to determine whether and ending is the \textit{correct} one or the \textit{incorrect} one.
-Specifically, we use the logistic regression implementation by Scikit-Learn \cite{scikit-learn}, regularizing using an L2 loss.
-We grid search the regularization parameter on our development set. 
-\ms{We should maybe add one of two more sentences?}
+We design a system that predicts, given a pair of story endings, which is the  \textit{right} one and which is the \textit{wrong} one.
+Our system applies a linear classifier guided by several types of features to solve the task.
+We describe the system in detail below.
+
+\subsection{Model}
+We train a binary logistic regression classifier to distinguish between {\it right} and {\it wrong} stories. 
+We use the set of {\it right} stories as positive samples and the set of {\it wrong} stories as negative samples.
+At test time, for a given pair, we consider the classification results of both candidates. 
+If our classifier assigns different labels to each candidate, we keep them.  
+If not, the label whose posterior probability is lower is reversed.
+We describe the classification features below.
 
 \subsection{Features}
-We use two types of features (described below), designed to capture different dimensions of the problem.
-We use \textit{stylistic} features to capture differences in writing between ``coherent'' endings and ``incoherent'' ones.
-We opt for \textit{language model} features to leverage corpus level word distributions, specifically longer term sequence probabilities.
-Our end system makes use of $XX$ distinct features. \ms{Would be nice to add that number?}
-\paragraph{Stylistic Features}
-%% take stuff from the paper
-In our classification task, we add the following features to capture style differences between the two endings:
+We use two types of features, designed to capture different aspects of the problem. 
+We use \textit{neural language model} features to leverage corpus level word distributions, specifically longer term sequence probabilities.
+We use \textit{stylistic} features to capture differences in writing between ``coherent'' story endings and ``incoherent'' ones.
+
+\paragraph{Language Model Features.}
+%% take the RLM paragraph from the paper
+We experiment with state-of-the-art text comprehension models, specifically an LSTM \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \newcite{mikolov2010recurrent}).
+Our RNNLM is used to generate two different probabilities:
+$p_\theta(\textrm{ending})$, which is the language model probability of the fifth sentence alone and $p_\theta(\textrm{ending} \mid \textrm{story})$, which is the RNNLM probability of the fifth sentence given the first four sentences.
+We use both of these probabilities as classification features.
+
+In addition, we also apply a third feature:
+\begin{equation}
+\frac{p_\theta(\textrm{ending} \mid
+  \textrm{story})}{p_\theta(\textrm{ending})} \label{eq:ratio}
+\end{equation}
+
+The intuition is that a \emph{correct} ending should be unsurprising (to the model) given the four preceding sentences of the story (the numerator), controlling for the inherent surprise of the words in that ending (the denominator).
+We use these three probabilities as classification features.
+
+\paragraph{Stylistic Features.}
+We hypothesize that {\it right} and {\it wrong} endings might be distinguishable using style features.
+We adopt features that have been shown useful in the past in tasks such as detection of age \cite{Schler:2006,Rosenthal:2011,nguyen:2011:latech}, gender  \cite{Argamon:2003,Schler:2006,bamman2014gender}, and native language
+\cite{Koppel:2005,Tsur:2007,Bergsma:2012}.
+
+We add the following features to capture style differences between the two endings. 
+These features are computed on the story endings alone, and do not consider the first four (shared) sentences of each story.
 \begin{itemize}
@@
 Specifically, we replace content words, which are often low frequency, with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
-\item\textit{\textbf{Character n-grams.}} Character n-grams are useful features in author style \cite{Stamatatos:2009} or language identification \cite{lui2011cross}.
+\item\textit{\textbf{Character n-grams.}} Character n-grams are useful features in the detection of author style \cite{Stamatatos:2009} or language identification \cite{lui2011cross}.
 We use character 4-grams.
 \end{itemize}
-For computing our features, we keep n-gram (character or word) features that occur at least five times in the training set.
-All stylistic feature values are normalized to [0-1].
-For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
 
-\paragraph{Language Model Features}
-%% take the RLM paragraph from the paper
-In addition to stylistic features, we experiment with state-of-the-art text comprehension models, specifically a recurrent neural network language model (RNNLM; Mikolov, et al.
-(2010)\nocite{mikolov2010recurrent}).
-We train the RNNLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension 512.
+\subsection{Experimental Setup}
+We use  Python's sklearn logistic regression implementation with $L_2$
+regularization, performing grid search on the development set to
+tune a single hyperparameter -- the regularization parameter.
+
+We train the RNNLM using a single-layer LSTM of hidden dimension 512.
 We use the ROC Stories for training, setting aside 10\% for validation of the language model. 
@@
 
-In our classifier, we include three different scores given by the language model:
-$p_\theta(\textrm{ending})$, $
-p_\theta(\textrm{ending} \mid \textrm{story})$, $
-\frac{p_\theta(\textrm{ending} \mid \textrm{story})}{p_\theta(\textrm{ending})}$.
+For computing the style features, we keep n-gram (character or word) features that occur at least five times in the training set.
+All stylistic feature values are normalized to [0-1].
+For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
+Our end system makes use of 7,651 distinct features.
 
-The intuition is that a \emph{right} ending should be unsurprising (to the model)given the four preceding sentences of the story (the numerator), controlling for the inherent surprisingness of the words in that ending (the denominator).
-\ms{@roy, did we try a classifier trained on all three features only?}
-
-\section{Results \& Discussion}
+\section{Results}
 
@@
 %{tbmihaylov (shared task)} & 0.711\\ \hline\hline
-{RNNLM}		& 0.677 \\ 
+{RNNLM Features}		& 0.677 \\ 
 {Stylistic features} & {0.724} \\ 
@@
 Results on the test set of the  story cloze task. 
-The first block are published results, the second block
-as-yet-unpublished results from the LSDSem 2017 leaderboard, the third
-block ours.
+The first block are published results, the second block are our results.
 LexVec results are taken from \cite{Speer:2016}.
-RNN is our implementation. 
 Human judgement scores are taken from \cite{Mostafazadeh:2016}. 
@@
 The performance of our system is described in Table \ref{cloze_results}. 
-With $75.2\%$ accuracy, our system achieved $15.3\%$ better than the published state of the art by Salle et al.
-(2016) \nocite{Salle:2016}.
-\ms{At the time of submission, we beat everyone or we're ranked XX in the leaderboard.}
-Ablation analysis shows that stylistic features have the most predictive power.
-This suggests that while this task is about story understanding, there is some information contained in stylistic features, which are slightly less sensitive to content.
-As expected, RNNLM features complement the stylistic ones, boosting performance by $2.8\%$.
-This suggests that while the stylistic feaures provide useful signal, content-oriented models also contribute information.
-\ms{Perhaps, an even more complex story understanding model would provide an even greater boost.}
+With $75.2\%$ accuracy, our system achieves $15.3\%$ better than the published state of the art \cite{Salle:2016}. 
+%\ms{At the time of submission, we beat everyone or we're ranked XX in the leaderboard.}
+The table also shows an analysis of the different features types used by our system.
+While our RNNLM features alone reach 67.7\%, the style features perform better -- 72.4\%. 
+This suggests that while this task is about story understanding, 
+there is some information contained in stylistic features, which are slightly less sensitive to content.
+As expected, the RNNLM features complement the stylistic ones, boosting performance by 7.5\% (over the RNNLM) and 2.8\% (over the style features). 
+%This suggests that while the stylistic features provide useful signal, content-oriented models also contribute information. 
+%\ms{Perhaps, an even more complex story understanding model would provide an even greater boost.}
 
+\com{
 \subsection{Further analysis}
@@
 The performance of both these baselines was roughly chance-level, which seems to suggest that this is not entirely the case.
+}
 
@@
 \section{Conclusion}
-This paper described the UW NLP's submission to the 2017 LSD Sem Shared Task. 
-% Our system makes use of knowledge brought to us by the constrained writing literature (?)
-% talk about how we use state-of-the-art language modelling tools.
-Our system leveraged stylistic features and text comprehension features, achieving $75.2\%$ accuracy on the classification task.
-We used standard NLP features to capture the style of short story endings, and state of the art language model tools for content-sensitive features.
+This paper described our submission to the LSDSem 2017 Shared Task. 
+Our system leveraged both neural language model features and  stylistic features, achieving $75.2\%$ accuracy on the classification task. 
 % We achieve $75.2\%$ which is ranked XXth in the ongoing codalab competition?
 % Say something like:
-While we achieved \ms{(near?)} state of the art performance, we still only achieved 75\% accuracy.
+\com{While we achieved state of the art performance, we still only achieved 75\% accuracy. 
 This means the task is far from being solved. 
-We need better tools to understand the common sense knowledge embedded in these stories.
+We need better tools to understand the common sense knowledge embedded in these stories.}
 

### 2017-02-01 gen_pattern_features.PL

@@ -13,9 +13,11 @@ sub main(@) {
 	my $of;
 	my $use_len;
 	my $char_ngrams=4;
+	my $dont_normalize;
 	
 	MyUtils::usage({
 		"if=s" => \$if,
+		"dont_normalize+"				=> \$dont_normalize,
 		"patt_file=s" 					=> \$patt_file,
 		"of=s"							=> \$of,
 		"max_patt_len=i" 				=> \$max_patt_len,
@@ -57,7 +59,7 @@ sub main(@) {
 				$max_len = @w;
 			}
 
-			my $patts = get_patts(\@w, $max_patt_len, $char_ngrams);
+			my $patts = get_patts(\@w, $max_patt_len, $char_ngrams,$dont_normalize);
 
 			foreach my $patt (keys %$patts) {
 				unless (exists $patts{$patt}) {
@@ -111,12 +113,19 @@ sub main(@) {
 		
 		foreach my $patt (keys %$patts) {
 			if (exists $saved{$patt}) {
-				$ts{$saved{$patt}->[0]} = ($patts->{$patt})/($saved{$patt}->[1]);	
+				$ts{$saved{$patt}->[0]} = $patts->{$patt};
+				unless (defined $dont_normalize) {
+					$ts{$saved{$patt}->[0]} /= ($saved{$patt}->[1]);
+				}	
 			}
 		}
 		
 		if ($use_len) {
-			$ts{$n_feats-1} = scalar(@w)/$max_len;
+			$ts{$n_feats-1} = scalar(@w);
+			
+			unless (defined $dont_normalize) {
+				$ts{$n_feats-1} /= $max_len;
+			}
 		}
 		
 		$ofh->print("$label\t$text\t");		
@@ -131,11 +140,12 @@ sub main(@) {
 	return 0;
 }
 
-sub get_patts($$$) {
+sub get_patts($$$$) {
 	my $w = shift;
 	unshift(@$w, "START_UNK");
 	my $max_patt_len = shift;
 	my $char_ngrams = shift;
+	my $dont_normalize = shift;
 	
 	my %patts;
 	

### 2017-02-01 docs/language_constraint.tex
added one citation

@@
 %\renewcommand{\ms}[1]{}
-\renewcommand{\roy}[1]{}
+%\renewcommand{\roy}[1]{}
 %\renewcommand{\nascomment}[1]{}
@@
 the nature of the writing task the writer was asked to perform, since
-different tasks likely engage different cognitive processes.\clinic{Add citation}
+different tasks likely engage different cognitive processes \cite{Banerjee2014KeystrokePA}.
+%\clinic{Add citation}
 %that would involve different cognitive processes.

### 2017-02-03 docs/language_constraint.tex
a little more editing

@@
 slightly longer than {\it wrong} ones (8.47 words).
-\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
+This is inline with findings by \citet{yanchevaautomatic,qin2004exploratory}, which found that sentence length was indicative of whether a text was deceptive.
+Furthermore, \citet{buller1996interpersonal} suggests lying increases one's cognitive load, which in turn could affect sentence length.
+%\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
 Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
@@
 \yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}
-
+% The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.
 Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
 The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
+\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, is there anything there?}.
 Furthermore, {\it original} and {\it right} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates'').
-\yc{Again, any cogsci literature on this?} \nascomment{feels
-  Pennebaker-ish, that might be a good place to look.}
+This is in line with previous findings that dececptively written text expresses more negative emotion compared to truthful text \cite{Newman:2003}.
+%\yc{Again, any cogsci literature on this?} \nascomment{feels
+%  Pennebaker-ish, that might be a good place to look.}
 Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.

### 2017-02-03 docs/language_constraint.tex
psycho references updated (Section 3)

@@
 \yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}
-% The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.
+\ms{The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.}
 Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
 The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
-\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, is there anything there?}.
+\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, did we find that in our experiments?}.
 Furthermore, {\it original} and {\it right} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates'').

### 2017-02-03 docs/language_constraint.tex
psycho references updated (Section 3) (2)

@@
 slightly longer than {\it wrong} ones (8.47 words).
-This is inline with findings by \citet{yanchevaautomatic,qin2004exploratory}, which found that sentence length was indicative of whether a text was deceptive.
+This is inline with findings by \citet{yancheva2013automatic,qin2004exploratory}, which found that sentence length was indicative of whether a text was deceptive.
 Furthermore, \citet{buller1996interpersonal} suggests lying increases one's cognitive load, which in turn could affect sentence length.

### 2017-02-03 docs/language_constraint.tex
Roy V3 (not final)

--- 2017-02-03 docs/language_constraint.tex
@@
 %\renewcommand{\ms}[1]{}
-%\renewcommand{\roy}[1]{}
+\renewcommand{\roy}[1]{}
 %\renewcommand{\nascomment}[1]{}
@@
 A writer's style depends not just on personal traits but also on her
-intent and cognitive state.
+intent and mental state.
 %In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
-In this paper, we show how writing tasks involving different cognitive processes can lead to measurable differences in writing style. % of the same authors.  
+In this paper, we show how writing tasks involving different mental processes can lead to measurable differences in writing style. % of the same authors.  
 %As a case study, we experiment with a recently published machine reading task: 
@@
 %In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
-where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story on their own vs.~adding only a story ending for a given story context and (2) writing a story ending that makes the overall story coherent or incoherent.\clinic{Many felt these 2 contraints looks like 3 constraints.
-clarify}
+where annotators were assigned similar writing tasks with different constraints: 
+(1) writing an entire story on their own (2) adding only a story ending for a given story context, and (3) writing an incoherent ending to a story.\resolved{\clinic{Many felt these 2 contraints looks like 3 constraints.
+clarify}}
 %We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
-We show that a simple linear classifier informed with stylistic features obtains 
-state-of-the-art results on the story cloze challenge,
-substantially higher than  deep learning models,
+We show that a simple linear classifier informed with stylistic features is able to successfully distinguish between the three cases.
+Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}
+In addition, our style-based classifier obtains state-of-the-art results on the story cloze challange, substantially higher than  deep learning models,
 even without looking at the story context. 
 %Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors.
-Our results demonstrate that different task framings can dramatically affect the way people write.\clinic{Similarly to previous comment: which results does this comment address?} 
+
 \resolved{They also provide important lessons for designing new NLP
@@
 \section{Introduction}
-Writing style is 
-%defined as the the author's choice of words, spelling, grammar and punctuation.\footnote{\url{https://en.wikipedia.org/wiki/Writing_style}}
-expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
-%It is often affected by inter-writer 
-It is influenced by both 
-personal 
-factors such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, 
-%or mere 
-and personality \cite{Stamatatos:2009}, 
-%but also by other parameters 
-as well as the cognitive states\clinic{Avoid using ``cognitive"?} of the authors such as 
-%such as the sentiment of the text \cite{Davidov:2010}, its level of sarcasm \cite{Tsur:2010} and whether it's deceptive \cite{Feng:2012}.
-sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
-In this paper, we study 
-%to what extent is 
-the extent to which 
-writing style is affected by 
-the nature of the writing task the writer was asked to perform, since
-different tasks likely engage different cognitive processes \cite{Banerjee2014KeystrokePA}.
-%\clinic{Add citation}
-%that would involve different cognitive processes.
+Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
+It is influenced by both personal factors such as age \cite{Schler:2006} and gender \cite{Argamon:2003}, 
+by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
+as well as mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
+In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
+different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.
 
@@
 Examples of stories from the story cloze task \cite{Mostafazadeh:2016}. The first row shows an {\color{blue}{Original}} story written by one author. 
-The second and third row show revised stories with two contrastive endings:
+The second and third rows show revised stories with two contrastive endings:
  %of the same story: 
- a {\color{forestgreen}{Coherent}} ending and a {\color{red}{Incoherent}} one.\clinic{They said it would be great to have three endings to the same story.
+ a {\color{forestgreen}{Coherent}} ending and a {\color{red}{Incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story.
 Unfortunately Nasrin et al.
 didn't publish the original endings for the dev/test data.
-We could ask her, but not sure if this is worth it}
+We could ask her, but not sure if this is worth it}}
  \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
@@
 
+We show that different framings of similar writing tasks can lead to measurable differences in people's writing style.
+We explore three  writing tasks, showing that they are distinguishable from one another using a linear classifier informed with stylistic features only. 
+Our results hint that different writing tasks impose different cognitive constraints on the writer, which lead to the substantial style differences.
+
 %As a testbed, we experiment with
@@
 the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
-In this task, crowdsourced authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
+In this task, \com{crowdsourced }authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
 %Following, 
@@
 and asked to write contrastive story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
-%The goal of the task is to determine which of the endings is the correct one.
-Framed as a story cloze task, the goal of this dataset was to serve as
-a commonsense challenge for NLP and AI research. 
-\tabref{ROC-example} shows an example of an {\it original} story, a {\it coherent} story, and an {\it incoherent} story.
+Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP and AI research. 
+\tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.
 
-While originally designed to be 
-%a machine reading task, 
-a story understanding challenge, 
-%the compilation of this task 
-the annotation process  
-%raises several research questions
-triggers interesting questions 
-%which seem to differ from the original intent of the designers.
+\com{While originally designed to be a story understanding challenge, the annotation process triggers interesting questions 
 that may go beyond the original intent of the designers.
-First, do 
-%authors use different
-people maintain the same writing 
-style when asked to write  
-%a {\it right} ending, compared to a {\it wrong} ending?
-both coherent and incoherent story endings? Second, do people  
-%use different style when composing the final sentence as part of their own five sentence story, compared to reading four sentences, and then writing a standalone ({\it right}) ending?
-maintain the same writing style\clinic{What is style? (Luke)} when writing the entire story on their own compared to 
-writing only the final sentence for a given story context written by someone else?
+First, do people maintain the same writing 
+style when asked to write both coherent and incoherent story endings? 
+Second, do people maintain the same writing style when writing the entire story on their own compared to 
+writing only the final sentence for a given story context written by someone else? }
 
+\com{
 %Our analysis indicates that the answer to both questions is positive. 
@@
 (Luke)}
+}
+
+\com{We show that a linear classifier informed with stylistic features can distinguish between {\it original}, {\it right} and {\it wrong}  endings to a large degree, even without looking at the story context.
+Our results allow us to make a few key observations.
+First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
+Second,  people change their writing style when writing the entire story on their own compared to 
+writing only the final sentence for a given story context written by someone else.}
+
+%Our binary classification results range between 64.5\%--75.6\%, where chance performance is 50\%.
 
@@
 
-In order to further estimate the quality of our results, we 
-%turn back to the story cloze task.
-also directly tackle the story cloze challenge. 
-Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase 
-%compared to the published state-of-the-art results 
-over the previously reported state of the art 
-\cite{Salle:2016}.\clinic{Too many numbers in these paragraphs}
-%When analyzing the results of our classifier, we see that sentiment plays a significant role in its success, which suggests that constraining authors to ``wrong'' sentences results in negative text.
-We analyze the results of our classifier, and show that when distinguishing between {\it right} and {\it wrong} endings,  \resolved{\nascomment{feels like a leap here, maybe
-  change wording a bit -- will come back to this.  note after reading
-  all the way to the end:  need to be careful about conclusions drawn
-  from weights alone }} sentiment plays a significant role: authors writing the wrong endings often engage negative sentiment.\roy{Better wording?
-we keep it depending on whether we keep our methodology}\clinic{more details required?}
+While originally designed to be a story understanding challenge, 
+ the annotation process introduced three variants of the same writing task: {\it original}, {\it right} and {\it wrong} endings. 
+We show that a linear classifier informed with stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5\%--75.6\% binary classification results).
+Our results allow us to make a few key observations.
+First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
+Second,  people change their writing style when writing the entire story on their own compared to 
+writing only the final sentence for a given story context written by someone else.
 
-Finally, we show that the style differences captured by our model can be combined with 
-%a state-of-the-art machine reading tool, for which this task was designed, in order to obtain increased performance on the story cloze task.  
-neural language models to make a better use of the story context. 
-%We train a neural language model on the {\it original} five sentence training corpus, and then compute the language probability of each of the candidate endings. 
-%We add the resulting probabilities as features in our linear classifier, and get 
+In order to further estimate the quality of our results, we also directly tackle the story cloze challenge. 
+ Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase over the previously reported state of the art  \cite{Salle:2016}.
+We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
 Our final model that combines context with stylistic features achieves
 75.2\%---an additional 2.8\% gain, 15.3\% better than the best
-published result.\resolved{\footnote{
-%Recently, a shared task for the story cloze
-%  task has been conducted (\url{https://competitions.codalab.org/competitions/15333}). At the time of submission, the leading results was 71.1\%,
-%%, which is  closer to our results, although still inferior.
-%%No details about the validity of this result or the methods used to generate it are available.
-%but no details are available for their results. 
-I commented out this footnote, because we mention this later.  We
-should only mention it once and not in the intro.
-}}
-%For instance, one of the key features for distinguishing between correct and wrong sentences is the over-representation of the word ``hate" in the latter.
+published result.
 
@@
 %Our results may have a wide impact on a range of fields. 
-The contributions of our study are threefold. 
+The contributions of our study are twofold. 
 First, findings from our study can potentially shed light on 
@@
 %as they suggest that these might have different style compared to real news.
-Second, our results provide valuable insights for designing new NLP tasks,\clinic{unclear}
-both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
+%Second, our results provide valuable insights for designing new NLP tasks,\clinic{unclear}
+%both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
 %Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
@@
 %We show that these details are actually very significant. 
-Third, we establish a new state-of-the-art result on the commonsense story cloze challenge.
+Second, we establish a new state-of-the-art result on the commonsense story cloze challenge.
 
+\com{
 The remainder of this paper is organized as follows. In \secref{ROC_Story} we describe the story cloze task.
 We then present our model, experiments and results in Sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
-Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present a further analysis of our results  and a discussion, followed by related work and conclusions.\clinic{Omit this paragraph?}
+Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present a further analysis of our results  and a discussion, followed by related work and conclusions.\clinic{Omit this paragraph?}}
 
@@
 While this task was developed to facilitate representation and learning of commonsense story understanding,
-it introduces a few interesting properties\clinic{which properties?} which make it ideal for our study. 
+its design included a few key choices which  make it ideal for our study. 
 We describe the task below.
@@
 
-\paragraph{ROC Stories.}
+\paragraph{ROC stories.}
 
@@
 
-\paragraph{Story Cloze Task.}
+\paragraph{Story cloze task.}
 After compiling the story corpus, the {\it story cloze task}---a task based on the corpus---was introduced.
@@
 %The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
-The official training data contains only the original stories (without alternative endings), while development and test data consist only of the revised stories with alternative endings (for a different set of original stories that are included in the training set).
+The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are included in the training set).
 The task was suggested as an extensive evaluation framework:
@@
 
-\paragraph{A Hard Task.}\roy{Was ``State-of-the-art results". Luke mentioned that this puts the focus on our results rather than on the nature of the task, as we intended}
+\resolved{\paragraph{A Hard Task.}}\roy{Was a paragraph titled  ``State-of-the-art results".
+Luke mentioned that this puts the focus on our results rather than on the nature of the task, as we intended, so I merged it into the previous paragraph}
 Interestingly, at the time of this submission, 10 months after the
@@
   unpublished along with the underlying methodology.}
-This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad} and SNLI \cite{bowman2015large}, for which results improved dramatically over a similar or shorter period of time.
+This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad} for which results improved dramatically over a similar or shorter period of time.
 This suggests that this task is challenging and that high performance is hard to achieve.
@@
 
-\paragraph{Different Writing Tasks in the Story Cloze Task.}
-\citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
+In addition, \citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
 First, each pair of endings was written by the same author, which ensured that author style differences could not be used to solve the task. 
@@
 
-Several key design decisions make this task an interesting testbed for our purpose.\clinic{Which purpose?}
+\paragraph{Different writing tasks in the story cloze Task.}
+Several key design decisions make this task an interesting testbed for the purpose of this paper.\resolved{\clinic{Which purpose?}}
 First, the training set for the task (ROC Stories corpus) is not a
 training sample in the usual sense,\footnote{I.e., the training
-  instances are drawn from a population similar to the one that future
-  testing instances will be drawn from.}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
+  instances are not drawn from a population similar to the one that future
+  testing instances will be drawn from.\roy{I added \textbf{not} here, as otherwise it is confusing}}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
  \resolved{\yc{As far as I understand, this was intentional --- they didn't want
@@
 and then asking her to generate a fifth {\it right} ending. 
-This raises the question of whether these different writing setups impose different writing styles. 
+%This raises the question of whether these different writing setups impose different writing styles. 
 % We show that this is indeed the case.
@@
 
-\isection{Surface Analysis.}{Surface}
+\isection{Surface Analysis of the Story Cloze Task}{Surface}
 We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
@@
 slightly longer than {\it wrong} ones (8.47 words). 
-This is inline with findings by \citet{yanchevaautomatic,qin2004exploratory}, which found that sentence length was indicative of whether a text was deceptive.
-Furthermore, \citet{buller1996interpersonal} suggests lying increases one's cognitive load, which in turn could affect sentence length.
-%\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
+\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
 Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
@@
 \yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}
-% The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.
+
 Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
 The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
-\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, is there anything there?}.
-Furthermore, {\it original} and {\it right} endings seem to prefer positive words (e.g., ``better''), while {\it wrong} endings prefer negative ones (``hates'').
-This is in line with previous findings that dececptively written text expresses more negative emotion compared to truthful text \cite{Newman:2003}.
-%\yc{Again, any cogsci literature on this?} \nascomment{feels
-%  Pennebaker-ish, that might be a good place to look.}
+Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings prefer negative ones (``hates''). 
+\yc{Again, any cogsci literature on this?} \nascomment{feels
+  Pennebaker-ish, that might be a good place to look.}
 Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.
@@
         \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it original}, 3.4) ({\it right}, 3.9) ({\it wrong}, 4)};
+            coordinates {({\it original}, 3) ({\it right}, 3.3) ({\it wrong}, 3.5)};
 
         \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it original}, 2.8) ({\it right}, 2) ({\it wrong}, 1.5)};
+            coordinates {({\it original}, 2.5) ({\it right}, 1.8) ({\it wrong}, 1.3)};
 
         \addplot[style={ggreen,fill=ggreen,mark=none}]
-            coordinates {({\it original}, 1.1) ({\it right}, 1.4) ({\it wrong}, 1.6)};
+            coordinates {({\it original}, 1) ({\it right}, 1.2) ({\it wrong}, 1.4)};
 
         \addplot[style={brown,fill=brown,mark=none}]
-            coordinates {({\it original}, 0) ({\it right}, 0) ({\it wrong}, 0.7)};
+            coordinates {({\it original}, 0) ({\it right}, 0) ({\it wrong}, 0.6)};
 
         \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it original}, 0.1) ({\it right}, 0.2) ({\it wrong}, 0)};
+            coordinates {({\it original}, 0.9) ({\it right}, 0.2) ({\it wrong}, 0.1)};
 
-        \legend{to, and, I, hates, better}
+        \legend{to, and, I, hates, !}
     \end{axis}
@@
 
-One goal of this paper is to determine the extent to which 
+Our goal of this paper is to determine the extent to which 
 %does constraining authors in their writing assignments lead to them adopting different writing styles. 
@@
 \paragraph{Experiment 1: right/wrong endings.}
-The goal of this experiment is to measure to what extent  style features capture differences between the {\it right} and {\it wrong} endings.
+The goal of this experiment is to measure the extent to which  style features capture differences between the {\it right} and {\it wrong} endings.
 As the story cloze task doesn't have a training corpus for the {\it
@@
 we are able to decrease the impact of author-specific style differences,
-and focus on the difference between the styles accompanied with {\it right} and {\it wrong} writing.
+and focus on the difference between the styles accompanied with {\it right} and {\it wrong} writings.
 \resolved{we
@@
 regularization, performing grid search on the development set to
-tune a single hyperparameter -- the regularization parameter.   \resolved{\nascomment{any other hyperparameters?  if
+tune a single hyperparameter---the regularization parameter.   \resolved{\nascomment{any other hyperparameters?  if
   not, say this is the only one.  else explain what they are.}}
@@
 
-\paragraph{Story Cloze Task.}
+\paragraph{Story cloze task.}
 The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
@@
 This classification task is more constrained than Experiment 1, as two
-endings are given and question is which is \emph{right} and which is
+endings are given and the question is which is \emph{right} and which is
 \emph{wrong}.
@@
 set. Our classifier obtains 72.4\% accuracy, 12.5\% higher than the
-published state-of-the-art result on the task \cite{Salle:2016} \resolved{\nascomment{cite that here}}.
+published state-of-the-art result on the task \cite{Salle:2016}\resolved{\nascomment{cite that here}}.
 Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
@@
 {\bf Model} & {\bf Accuracy} \\ \hline
-{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
-{LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
-{Niko (shared task)}	& 0.700\\ 
-{tbmihaylov (shared task)} & 0.711\\ \hline\hline
-{RNN}		& 0.677 \\ 
+$\dagger${DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
+$\dagger${LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
+%{Niko (shared task)}	& 0.700\\ 
+%{tbmihaylov (shared task)} & 0.711\\ \hline\hline
+$\dagger${RNN}		& 0.677 \\ 
 {\bf Ours} & {\bf 0.724} \\ 
-{\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
-Human judgment & 1.000 \\ \hline
+$\dagger${\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
+$\dagger$Human judgment & 1.000 \\ \hline
 \end{tabular}
@@
 Results on the test set of the  story cloze task. 
-The first block are published results, the second block
-as-yet-unpublished results from the LSDSem 2017 leaderboard, the third
-block ours.
+The first block are published results, 
+the second block is our results.
 LexVec results are taken from \cite{Speer:2016}.
-RNN is our implementation. 
-Human judgement scores are taken from \cite{Mostafazadeh:2016}. \resolved{\nascomment{I added 0s to ``Niko'' result
+%RNN is our implementation. 
+Human judgement scores are taken from \cite{Mostafazadeh:2016}.
+Methods marked with ($\dagger$) use the story context in order to make a predicition. 
+ \resolved{\nascomment{I added 0s to ``Niko'' result
   and ``human''
@@
 human judgments come from?  those are not mentioned in our text anywhere!}
-}\clinic{Add a symbol for ``uses story context?''}}
+}}
 \end{table}
@@
 We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed. 
-Specifically, we experiment with a recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
+Specifically, we experiment with an LSTM-based \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
 %and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
-Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the story cloze task designers, and harnesses their ROC Stories training set, which consists of single-ending stories.
-We show that the adding our features to this powerful language model
+Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the story cloze task designers, and harnesses their ROC Stories training set, which consists of single-ending stories,
+as well as the story context for each pair of endings. 
+We show that adding our features to this powerful language model
 gives improvements over our classifier as well as the language
@@
 
-We train the RNNLM using a single-layer LSTM \cite{hochreiter1997long} of hidden dimension 512.
-We use the ROC Stories for training, setting aside 10\% for validation of the language model. 
-We replace all words occurring less than 3 times by a special
+We train the RNNLM using a single-layer LSTM of hidden dimension 512.
+We use the ROC stories for training,\footnote{We use the extended, 100K stories corpus (see \secref{ROC_Story}).} setting aside 10\% for validation of the language model. 
+We replace all words occurring less than 3 times with a special
 out-of-vocabulary character, yielding a vocabulary size of  21,582.
 Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
-Using AdamOptimizer \cite{kingma2014adam} and a learning rate of
+Using the Adam optimizer \cite{kingma2014adam} and a learning rate of
 $\eta=.001$, we train to minimize cross-entropy. % minibatches of $50$ stories.
@@
 
-\nascomment{please check the paragraph above.  we need to say how we
+\resolved{\nascomment{please check the paragraph above.  we need to say how we
   use the LM before we evaluate it!  also, has anyone tried an approach like this
   before?  even if we aren't exactly replicating another paper, if
-  someone else used RNNs for this task, we should credit them.}
+  someone else used RNNs for this task, we should credit them.}}
+  \roy{Ours is the first work to publish LSTM results on this dataset.}
 
@@
 On its own, our neural language model performs moderately well on the story cloze test. 
-This is not surprising, as \citet{Mostafazadeh:2016} hinted  that
-simple language models are insufficient.
-Indeed, using our neural language model and selecting endings based on
-$p_\theta(\textrm{ending} \mid \textrm{story})$ (i.e., the numerator of
+%This is not surprising, as \citet{Mostafazadeh:2016} hinted  that
+%simple language models are insufficient.
+Selecting endings based on $p_\theta(\textrm{ending} \mid \textrm{story})$ (i.e., the numerator of
 Equation~\ref{eq:ratio}), we obtained only 55\% accuracy.   The ratio
@@
 absolute, reaching 75.2\% (15.3\% better than the published state of
-the art and 4.1\% better than the best unpublished result).
+the art\com{ and 4.1\% better than the best unpublished} result).\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}
 These results indicate that context-ignorant style features can be used to obtain high
@@
 
-\paragraph{Most discriminative feature types.}
+\subsection{Most Discriminative Feature Types}
 A natural question that follows this study is which style features are most
-helpful in detecting the underlying task an ending's author was asked
+helpful in detecting the underlying task an author was asked
 to perform. 
@@
 \tabref{subgroups} shows our results.
-Results show that  character $n$-grams are the most effective style predictors, reaching within  0.6\% of the full model, but that word $n$-grams also capture much of the signal, yielding 61.2\%.
+Results show that  character $n$-grams are the most effective style predictors, reaching within  0.6\% of the full model, but that word $n$-grams also capture much of the signal, yielding 61.2\%, which is 3.3\% worse than the full model.
 These findings are in line with previous work that used character $n$-grams along with other types of features to predict writing  style \cite{Schwartz:2013}.
@@
 
-\paragraph{Most salient features---experiment 1.}
-%In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
-%This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.724).  
-\tabref{exp1_features} shows the five features with the highest positive and negative coefficients in the logistic regression classifier for Experiment 1. 
+\subsection{Most Salient Features}
+A followup question is which individual features contribute most to the classification process,
+as these could shed light on the stylistic differences imposed by each of the writing tasks.
+
+In order to answer this question, we consider the highest absolute positive and negative coefficients in the logistic regression classifier in both Experiments 1 and 2, an  approach widely used  as a method of extracting the most salient features \cite{Nguyen:2013,Burke:2013,Brooks:2013}.\footnote{Although it is worth noting that its reliability is not entirely clear \cite{Yano:2012}.}
+We consider only features appearing in at least 5\% of the endings in our training set.
+
+\paragraph{Experiment 1.}
+\tabref{exp1_features} shows the five features with the highest positive and negative coefficients in the logistic regression classifier for Experiment 1,
+along with their corpus frequency. 
 These correspond to the 5 most salient features for {\it right}
 (coherent) and {\it wrong} (incoherent) endings,
-respectively. \nascomment{have to be very careful here.  see
-  \href{http://homes.cs.washington.edu/~nasmith/papers/yano+smith+wilkerson.naacl12.pdf}{Yano/Smith/Wilkerson}
-  \S 4.3 where we propose an alternative to inspecting
-  feature coefficients!}
+respectively.
 
 The table shows a few interesting trends. 
-First, authors tend to structure their sentences differently when writing {coherent}  vs. {incoherent} endings.
-For instance, {coherent} endings are more likely to start with an adverb (e.g., ``then'', ``so'', ``eventually''), while {incoherent} ones tend to start with a proper noun.
-In addition, we find that {incoherent} endings are more likely to
-finish the sentence with a common noun.  \nascomment{note to self to come back
+First, authors tend to structure their sentences differently when writing {coherent}  vs.~{incoherent} endings.
+For instance, {incoherent} endings are more likely to start with a proper noun and end with a common noun, 
+while coherent endings have a greater tendency to end with a past tense verb.
+Second, {\it right} endings will make wider use of coordination structures, as well as adjectives.
+The latter might indicate that writing coherent stories imposes the authors to write more descriptive text compared to incoherent ones.
+Finally, we notice a few syntactic differences: {\it right} endings will more often use infinite verb structure, while {\it wrong} endings will prefer gerunds (VBG). 
+\nascomment{note to self to come back
   to this after we agree on methodology.}
 
-More interestingly, the different writing tasks seem to impose a specific sentiment on the writer. 
+\com{More interestingly, the different writing tasks seem to impose a specific sentiment on the writer. 
 Three of the top four most salient features for detecting {\it wrong} endings are variants of the verb ``hate''.
@@
 \resolved{\yc{Is it really because there's no statistical tendency in the original stories to have happy endings, as opposed to the alternative possibility --- the sentiment classifier used by Monstafazadeh 2016 didn't quite nail down the optimal feature encodings?}} \roy{this is definitely an option, and that's partly why I used hedging (``seems to suggest'').
-Tones it down a bit more.}
+Tones it down a bit more.}}
 
@@
 %\small
-\begin{tabular}{|c|c|} \hline
-\textit{\textbf{Right}} & \textit{\textbf{Wrong}}\\ \hline
-`ally' & ` hate'\\ \hline
-`VBD the' & ` hat'\\ \hline
-`START RB' & `START NNP'\\ \hline
-`ved ' & `ated'\\ \hline
-` tim' & `NN .'\\ \hline
+\begin{tabular}{|c|c||c|c|} \hline
+\textit{\textbf{Right}} & Freq. & \textit{\textbf{Wrong}}& Freq. \\ \hline
+`ed .' & {\color{white}{0}}6.5\%& START NNP & 54.8\%\\ \hline
+`and ' & 13.6\%& NN . & 47.5\% \\ \hline
+JJ & 45.8\% & NN NN . & {\color{white}{0}}5.1\%\\ \hline
+to VB & 20.1\%& VBG & 10.1\%\\ \hline
+`d th' & 10.9\%& START NNP VBD & 41.9\%\\ \hline
+%`ally' & 3.3\% & `hate' & {\color{white}{0}}1.9\% \\ \hline
+%VBD the NN .& 2.2\% & ` hat' & {\color{white}{0}}2.0\% \\ \hline
+%START RB & 3.1\% & START NNP & 54.8\% \\ \hline
+%`ved ' &4.1\%&  `ated' & {\color{white}{0}}3.0\%\\ \hline
+%` tim' &2.6\%&  NN . & 47.5\%\\ \hline
 
@@
 \caption{\label{exp1_features}}
-The top 5 most discriminative features for predicting {\it right} vs.~{\it wrong} endings.\end{table}
+The top 5 most discriminative features for predicting {\it right} vs.~{\it wrong} endings,
+along with their frequency in our story cloze training set.\end{table}
 
-\paragraph{Most salient features---experiment 2.}
+\paragraph{Experiment 2.}
 %In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
@@
 \tabref{exp2_features} shows the same analysis for Experiment 2.
-Interestingly, here the most salient features are quite different. 
 As noted in \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
-Another clear style difference is the use of punctuation: {\it original} endings often end with exclamation marks, while {\it new} endings end almost exclusively with periods. 
-Finally, syntactic difference appear to play an important role in stylistic differences between the two tasks. 
-Specifically, {\it original} endings contain more common nouns (NN), adverbs (RB) and gerunds (VBG), while {\it new} endings seem to contain more past tense verbs (VBD), especially as the second word in the sentence.
+This is inline with similar findings in the deception detection literature \cite{qin2004exploratory}.
+An interesting observation is that exclamation marks are a strong indication for  {\it original} ending. 
+This indicates that authors are more likely to show enthusiasm when writing their own text compared to ending an existing task.
 
+Finally, when comparing the two groups of salient features from both experiments, we find an interesting trend.
+Several features, such as ``START NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict {\it new} (i.e., {\it correct}) endings in Experiment 2. 
+This indicates that, for instance, incoherent endings have a stronger tendency to begin with a proper noun compared to coherent endings, 
+which in turn are more likely to do so than original endings. 
+This partially explains why distinguishing between {\it original} and {\it wrong} endings is an easier task compared to the other pairs (\secref{Results}).
+
+\setlength\tabcolsep{.15cm}
 \begin{table}[!t]
@@
 %\small
-\begin{tabular}{|c|c|} \hline
-\textit{\textbf{Original}} & \textit{\textbf{New}}\\ \hline
-{\it length} & `.'\\ \hline
-`!' & `START NNP'\\ \hline
-`NN' & `START NNP VBD'\\ \hline
-`RB' & `START I VBD'\\ \hline
-`VBG' & `NNS .'\\ \hline
+\begin{tabular}{|p{1.25cm}|c||p{2.9cm}|c|} \hline
+\textit{\textbf{Original}} & Freq. & \textit{\textbf{New}}& Freq. \\ \hline
+{\it length} & {\color{white}{.}}100.0\% & `.' & 93.0\%\\ \hline
+`!' & {\color{white}{00}}6.1\%& START NNP  & 39.2\% \\ \hline
+NN & {\color{white}{00}}78.9\% & START NNP VBD &29.0\% \\ \hline
+RB & {\color{white}{0}}44.7\%& NN . & 42.3\% \\ \hline
+`,' & {\color{white}{0}}12.7\%&  the NN . & 10.6\% \\ \hline
 
@@
 
-In this paper we have shown that giving a writer a different writing
-task affects writing style in easily detected ways.
+\paragraph{Writing tasks as stimulating mental states.}
+In this paper we have shown that giving a writer different writing tasks affects writing style in easily detected ways.
 Our results indicate that when authors are asked to write the last
@@
 also shown that writing the ending as part of one's own five-sentence story is very different than reading four sentences and then writing the fifth.
-
 Our findings hint that the nature of the writing task imposes a
@@
 are often implicit, but can be observed using extremely simple automatic tools.
-This is in line with previous cognitive findings. 
-For instance, previous studies have shown that when answering questions, people  tend to adopt the writing style of the question \cite{Ireland:2010}.
-\nascomment{there must be closer examples?}
 
-Other studies have shown that writing tasks can even have a long term effect.
-A range of works have shown that writing emotional texts can benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
-Some of these works showed that these health benefits  \resolved{\nascomment{what are
-  ``these changes''?}} are also accompanied by changes in writing style
-\cite{Campbell:2003}.\clinic{Which kind of changes? related to our by any chance?} The current study suggests that even subtle
-changes to a writing prompt can affect these processes.\clinic{Belongs to introduction?}
-%The results of the current study can shed more light on the processes that people undergo when presented with different writing tasks.
+Previous work have shown that  writing task could affect mental states.
+For instance, several works demonstrated that writing deceptive text leads to a significant cognitive burden \cite{Newman:2003,Banerjee:2014}.
+These works have also shown that this cognitive burden is accompanied by different writing style compared to truthful text.
+Other studies have shown that writing tasks can even have a long term effect,
+by showing that writing emotional texts can benefit both physical and mental health \cite{Lepore:2002,Campbell:2003,Frattaroli:2006}. 
+\citet{Campbell:2003} also showed that the health benefits of writing emotional text are accompanied by changes in writing style, mostly in the use of pronouns.
 
-This paper also reveals several important lessons for the future
-design of NLP tasks. 
+Another line of works has shown that different mental states affect writing.
+First, the author's personality traits (e.g., depression, neuroticism, narcissism) affect her writing style \cite{schwartz2013personality,Ireland:2014b}.
+Second, temporary changes, such as a romantic relationship \cite{Ireland:2011,Bowen:2016}, work collaboration \cite{Tausczik:2009,Gonzales:2009} or negotiation \cite{Ireland:2014} may also affect writing style.
+Finally, writing style can also change from one sentence to another, for instance between positive and negative text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}.
+
+This large body of works indicates a tight connection between writing tasks, mental states and different writing styles.
+This connection hints that the link discovered in this paper, between the different writing tasks and the resulting difference in writing style, also goes through a change in mental state. 
+Nonetheless, further investigation is required in order to further validate this hypothesis.
+
+\paragraph{The story cloze task.}
+This paper also provides several insights for the future design of NLP tasks. 
 The story cloze task was very carefully designed. Many factors, such as the topic diversity, as well as  temporal and causal relation diversity,  were controlled for \cite{Mostafazadeh:2016}. 
@@
 A different approach is to use naturally occurring text, as used in recent machine reading tasks (see \secref{Related}). 
-However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
+%However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
+A way to avoid the inherent biases people have when writing is to rather than ask them to write text, have them rate sentences for naturally occurring text by parameters of coherence (or very differently -- the level of surprise).
 
+\com{
 Another lesson from this paper relates to baseline methods. 
@@
   \roy{Modified this to be more concrete. Did end up hinting that they should have done a better job at analyzing their data before publishing. Feel free to tone down.}
-
+}
+\roy{Commented out the lessons about the importance of running baselines.}
 \isection{Related Work}{Related}
@@
 style \cite{mosteller1963inference,pennebaker1999linguistic,Schwartz:2013}. 
-Interestingly, previous work has shown that individual style can be affected from coarse-grained factors such as those just described, but also from other less apparent factors such as mental state, or even living in a high-elevation location \cite{schwartz2013personality}.
+\com{Interestingly, previous work has shown that individual style can be affected from coarse-grained factors such as those just described, but also from other less apparent factors such as mental state, or even living in a high-elevation location \cite{schwartz2013personality}.
 
@@
 can adopt a different style used when writing positive vs.~negative
-text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}. In this work, we have shown that the same author can adopt a different style when facing different writing tasks.
+text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}. In this work, we have shown that the same author can adopt a different style when facing different writing tasks.}
 
@@
 Some works even showed that writing style applied when lying is different across genders \cite{Perez:2014a,Perez:2014b}.
-In this work, we have shown that an even more subtle writing task---writing {\it coherent} and {\it incoherent} story endings---imposes different styles on the author.
+In this work, we have shown that an even more subtle writing task---writing {coherent} and {coherent} story endings---imposes different styles on the author.
 
@@
 they motivate further research on the exact effect that a writing
-prompt has on an author's response.
+prompt has on an author's mental state, and also her response.
 They also provide valuable lessons for designing new NLP datasets.

### 2017-02-03 docs/shared_task_paper.tex
Roy V3 (not final)

@@
 This paper describes our system for the Linking Models of Lexical, Sentential and Discourse-level Semantics (LSDSem 2017) shared task -- the \textit{Story Cloze Task}.
-%
-Our system feeds a linear classifier with a variety of features, including both the output of a neural language model and style features. %determine which of two endings best completes a short story.
+Our system feeds a linear classifier with a variety of features, including both the output of a neural language model and style features.
 We report  $75.2\%$ accuracy on the task.
@@
 We use \textit{neural language model} features to leverage corpus level word distributions, specifically longer term sequence probabilities.
-We use \textit{stylistic} features to capture differences in writing between ``coherent'' story endings and ``incoherent'' ones.
+We use \textit{stylistic} features to capture differences in writing between {\it coherent} story endings and {\it incoherent} ones.
 
@@
 The intuition is that a \emph{correct} ending should be unsurprising (to the model) given the four preceding sentences of the story (the numerator), controlling for the inherent surprise of the words in that ending (the denominator).
-We use these three probabilities as classification features.
+%We use these three probabilities as classification features.
 
@@
 We train the RNNLM using a single-layer LSTM of hidden dimension 512.
-We use the ROC Stories for training, setting aside 10\% for validation of the language model. 
+We use the ROC Stories for training, setting aside 10\% for validation of the language model.\footnote{We train on both the Spring 2016 and the Winter 2017 datasets, a total of roughly 100K stories}
 We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of 21,582.
@@
 For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
-Our end system makes use of 7,651 distinct features.
+The total number of features used by our system is 7,651.
 

### 2017-02-03 ROC_SVM.py

@@ -20,6 +20,7 @@ def read_features(ifile, n_feats):
         
             # print d,line
             labels.append(d[0])
+            # print d[0],d[1]
         
             fs = d[2].split(" ")
         
@@ -40,8 +41,14 @@ def read_features(ifile, n_feats):
     
     return [features, labels]
     
-def evaluate(test,labels,confidence = []):
+def evaluate(test,labels,confidence = [], ids = None, gold = None, ofile = None):
     n_correct = 0
+    
+    if (ofile != None):
+        ofh = FileTools.openWriteFile(ofile)
+        ofh.write("InputStoryid,AnswerRightEnding\n")
+        
+    
     for i in range(len(labels)):
         # print labels[i],test[i]
         n_correct += (labels[i]==test[i])
@@ -51,7 +58,7 @@ def evaluate(test,labels,confidence = []):
 
     if (len(confidence)):    
         n_pairs_correct = 0
-    
+
         replace = {'2':'1', '1':'2'}
         for i in range(len(labels)/2):
             if (test[2*i] == test[2*i+1]):
@@ -60,13 +67,28 @@ def evaluate(test,labels,confidence = []):
                 else:
                     test[2*i] = replace[test[2*i]]
             
+            is_correct = (labels[2*i]==test[2*i])
+            
+            if ((is_correct and not (labels[2*i+1]==test[2*i+1])) or (not is_correct and (labels[2*i+1]==test[2*i+1]))):
+                print "Big problem!!!"
+                
             # print labels[i],test[i]
-            n_pairs_correct += (labels[2*i]==test[2*i])
+            n_pairs_correct += is_correct
             n_pairs_correct += (labels[2*i+1]==test[2*i+1])
     #        print labels[i],test[i],confidence[i]
+
+            if (ofile != None):
+                v = gold[i]
+                if (not is_correct):
+                    v = 3-v
+                    
+                ofh.write(ids[i]+","+str(v)+"\n")
     
         print n_pairs_correct,"/",len(labels),"=",n_pairs_correct*1./len(labels)
 
+    if (ofile != None):
+        ofh.write("\n")
+        ofh.close()
 
 def gen_ranking(features, labels):
     features2 = []
@@ -84,5 +106,5 @@ def gen_ranking(features, labels):
         features2.append(diff.tolist())
         labels2.append(label)
 
-    print len(features2),len(labels2)
+    #print len(features2),len(labels2)
     return [features2, labels2]

### 2017-02-03 test_SVM.py

@@ -3,6 +3,7 @@
 import sys
 sys.path.insert(0, '/Users/roysch/aristo/entailment/scripts/')
 import ROC_SVM
+import FileTools
 from scipy.sparse import *
 from scipy import *
 from sklearn import svm
@@ -11,14 +12,22 @@ import pickle
 
 def main():
     do_rank = 0
-    if (len(sys.argv) < 4):
-        print "Usage:",sys.argv[0],"<if> <n_feats> <model if> <is ranking>" 
+    ids=None
+    gold=None
+    out_file = None
+    if (len(sys.argv) < 3):
+        print "Usage:",sys.argv[0],"<if> <model if> <is ranking> <mapping file> <out file>" 
         return -1
-    elif (len(sys.argv) > 4):
-        do_rank = bool(sys.argv[4])
+    elif (len(sys.argv) > 3):
+        do_rank = int(sys.argv[3])
+        if (len(sys.argv) > 4):
+            mapping_file = sys.argv[4]
+            ids,gold = read_mapping_file(mapping_file)
+            if (len(sys.argv) > 5):
+                out_file = sys.argv[5]
 
-    n_feats = int(sys.argv[2])
-    clf = pickle.load(open(sys.argv[3], 'r'))
+    clf = pickle.load(open(sys.argv[2], 'r'))
+    n_feats = len(clf.coef_[0])
     
     features = []
     labels = []
@@ -37,7 +46,25 @@ def main():
         confidence = clf.decision_function(features)
     
     
-    ROC_SVM.evaluate(test,labels,confidence)
+    ROC_SVM.evaluate(test,labels,confidence,ids,gold, out_file)
     
+
+def read_mapping_file(ifile):
+    ids = []
+    gold = []
+    with FileTools.openReadFile(ifile) as ifh:
+        # Ignore first lione
+        ifh.readline()
+
+        for line in ifh:
+            e = line.rstrip().split("\t");
+            id = e[0]
+            ids.append(id)
+            gold.append(int(e[-1]))
+	
+        ifh.close()
+
+	return ids,gold
+
 
 sys.exit(main())

### 2017-02-03 docs/language_constraint.tex

@@
 We present a case study based on 
-the  {\it story cloze task} \cite{Mostafazadeh:2016}, %.
-%In this task, annotators were asked to generate two sentences: one which makes sense given a previous paragraph and another which doesn't.
-where annotators were assigned similar writing tasks with different constraints: 
-(1) writing an entire story on their own (2) adding only a story ending for a given story context, and (3) writing an incoherent ending to a story.\resolved{\clinic{Many felt these 2 contraints looks like 3 constraints.
+the  {\it story cloze task} \cite{Mostafazadeh:2016},
+where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 contraints looks like 3 constraints.
 clarify}}
@@
 We show that a simple linear classifier informed with stylistic features is able to successfully distinguish between the three cases.
+In addition, our style-based classifier obtains state-of-the-art results on the story cloze challange, substantially higher than  deep learning models, without even looking at the story context. 
 Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}
-In addition, our style-based classifier obtains state-of-the-art results on the story cloze challange, substantially higher than  deep learning models,
-even without looking at the story context. 
-%Importantly, our model doesn't even look at the previous paragraph, just the two candidate sentences, which, out of context, differ only in the writing task presented to the authors.
 
@@
 by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
-as well as mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
+as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
 In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
@@
 
-While originally designed to be a story understanding challenge, 
- the annotation process introduced three variants of the same writing task: {\it original}, {\it right} and {\it wrong} endings. 
+While the story cloze task was originally designed to be a story understanding challenge, 
+its annotation process introduced three variants of the same writing task---the {\it original}, {\it right} and {\it wrong} endings. 
 We show that a linear classifier informed with stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5\%--75.6\% binary classification results).
@@
 In order to further estimate the quality of our results, we also directly tackle the story cloze challenge. 
- Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase over the previously reported state of the art  \cite{Salle:2016}.
+ Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}.
 We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
@@
 
-The ROC Story Corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
+The ROC story corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
 Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
@@
 %The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
-The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are included in the training set).
+The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are not included in the training set).\roy{added {\it not} here}
 The task was suggested as an extensive evaluation framework:
@@
 
-\resolved{\paragraph{A Hard Task.}}\roy{Was a paragraph titled  ``State-of-the-art results".
-Luke mentioned that this puts the focus on our results rather than on the nature of the task, as we intended, so I merged it into the previous paragraph}
 Interestingly, at the time of this submission, 10 months after the
@@
 still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
-  task website (\url{https://competitions.codalab.org/competitions/15333}) does report higher results (71.1\%), which are still
-  unpublished along with the underlying methodology.}
-This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad} for which results improved dramatically over a similar or shorter period of time.
+  task website (\url{https://competitions.codalab.org/competitions/15333}) does report higher results (71.1\%)\roy{Tricky.
+Which number should we report here?
+leave empty?}, which are still unpublished along with the underlying methodology.}
+This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or shorter period of time.
 This suggests that this task is challenging and that high performance is hard to achieve.
@@
 \isection{Surface Analysis of the Story Cloze Task}{Surface}
-We computed several characteristics of the three types of endings: {\it original} endings (from the ROC Story Corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
+We computed several characteristics of the three types of endings: {\it original} endings (from the ROC story corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
 Our analysis  reveals several style differences between different groups. 
@@
 slightly longer than {\it wrong} ones (8.47 words). 
-\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
+Previous work have shown that sentence length is also indicative of whether a text was deceptive \cite{yancheva2013automatic,qin2004exploratory}. 
+Although writing {\it wrong} sentences is not the same as lying, it is not entirely surprising to observe similar trends in both tasks.
+%Furthermore, \citet{Buller:1996} suggests lying increases one's cognitive load, which in turn could affect sentence length.
+%\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
+
 Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
-The figure shows that both {\it original} and {\it right} endings use pronouns more frequently than {\it wrong} endings,
-which in turn prefer proper nouns, especially compared to {\it original} endings.
+The figure shows that both {\it original} and {\it right} endings use pronouns more frequently than {\it wrong} endings.
+Once again, deceptive text is also characterized by fewer pronouns compared to truthful text \cite{Newman:2003}.
+In contrast, {\it wrong} and {\it right} endings favor proper nouns compared to {\it original} endings. 
 \yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}
+\ms{The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.}\roy{Good point!
+This is tricky.
+On the one hand, it hurts our story by saying that the difference is not really the general task by itself, but also the constraints put by  Nasrin et al.
+It also forces us to bash them some more.
+Or we can just ignore it...}
 
@@
 The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
-Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings prefer negative ones (``hates''). 
-\yc{Again, any cogsci literature on this?} \nascomment{feels
-  Pennebaker-ish, that might be a good place to look.}
+%\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, did we find that in our experiments?}.
+Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings tend to use more negative language (``hates''), as is deceptive text \cite{Newman:2003}.
+%\yc{Again, any cogsci literature on this?} \nascomment{feels
+%  Pennebaker-ish, that might be a good place to look.}
 Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.
@@
 Sentence Length (\#words) & 11.02 & 8.75 & 8.47\\ \hline
-Most Frequent POS tags (\%)  & NN:15.3\%, VBD:13.4\%, PRP:10.1, DT:9.1\%, IN:8.7\% & VBD:15.8\%, NN:15.7\%, DT:9.7\%, PRP:8.8\%, NNP:8.3\%  & NN:16.3\%, VBD:15.1\%,  NNP:9.5\%, DT:9.4, IN:7.9\%\\ \hline
+Most Frequent POS tags (\%)  & NN:15.3\%, VBD:13.4\%, PRP:10.1, CC:3.3\%, IN:8.7\% & VBD:15.8\%, NN:15.7\%, CC:2\%, PRP:8.8\%, NNP:8.3\%  & NN:16.3\%, VBD:15.1\%,  NNP:9.5\%, DT:1.4, IN:7.9\%\\ \hline
 Most Frequent Words  (\%) & the:4.5\%, to:3.3\%, and:2.7\%, was:2.6\%, a:2.2\% & the:4.8\%, to:3.9\%, was:3.5\%, a:2.5\%, and:2.1\%   & the:5\%, to:4\%, was:3\%, a:2\%, I:1.6\%\\ \hline
@@
 each of the tasks \nascomment{I'm not sure I follow this sentence; can
-we be more clear?}.}\roy{Better now?}
+we be more clear?}.}
 
@@
 \isectionb{Results}
-\figref{results} shows our results.
+\tabref{results} shows our results.
 In Experiment 1, our model obtains 64.5\%
@@
 \emph{right} ones.  The result is that the effects are somewhat
-additive:  this third classifier achieves 75.2\%.
+additive:  this third classifier achieves 75.6\%.
 % That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
@@
 
-\resolved{\nascomment{please check the paragraph above.  we need to say how we
+\nascomment{please check the paragraph above.  we need to say how we
   use the LM before we evaluate it!  also, has anyone tried an approach like this
   before?  even if we aren't exactly replicating another paper, if
-  someone else used RNNs for this task, we should credit them.}}
+  someone else used RNNs for this task, we should credit them.}
   \roy{Ours is the first work to publish LSTM results on this dataset.}
@@
 We retrain our linear  model with the new feature set, and gain 2.8\%
-absolute, reaching 75.2\% (15.3\% better than the published state of
-the art\com{ and 4.1\% better than the best unpublished} result).\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}
+absolute, reaching 75.2\% (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result).\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}
 These results indicate that context-ignorant style features can be used to obtain high
@@
 \tabref{subgroups} shows our results.
-Results show that  character $n$-grams are the most effective style predictors, reaching within  0.6\% of the full model, but that word $n$-grams also capture much of the signal, yielding 61.2\%, which is 3.3\% worse than the full model.
+Results show that  character $n$-grams are the most effective style predictors, reaching within  0.6\% of the full model, but that word $n$-grams also capture much of the signal, yielding 61.2\%, which is only 3.3\% worse than the full model.
 These findings are in line with previous work that used character $n$-grams along with other types of features to predict writing  style \cite{Schwartz:2013}.
@@
 \paragraph{Experiment 1.}
-\tabref{exp1_features} shows the five features with the highest positive and negative coefficients in the logistic regression classifier for Experiment 1,
+\tabref{exp1_features} shows the most salient features for {\it right} (coherent) and {\it wrong} (incoherent) endings in Experiment 1,
 along with their corpus frequency. 
-These correspond to the 5 most salient features for {\it right}
-(coherent) and {\it wrong} (incoherent) endings,
-respectively.
-
 The table shows a few interesting trends. 
@@
 while coherent endings have a greater tendency to end with a past tense verb.
+
 Second, {\it right} endings will make wider use of coordination structures, as well as adjectives.
-The latter might indicate that writing coherent stories imposes the authors to write more descriptive text compared to incoherent ones.
+The latter might indicate that writing coherent stories imposes the authors to write more descriptive text compared to incoherent ones, 
+as is the case in truthful vs.~deceptive text \cite{ott2011finding}.
 Finally, we notice a few syntactic differences: {\it right} endings will more often use infinite verb structure, while {\it wrong} endings will prefer gerunds (VBG). 
@@
 
-\paragraph{Writing tasks as stimulating mental states.}
+\paragraph{The effect of writing tasks on mental states.}
 In this paper we have shown that giving a writer different writing tasks affects writing style in easily detected ways.
@@
 For instance, several works demonstrated that writing deceptive text leads to a significant cognitive burden \cite{Newman:2003,Banerjee:2014}.
-These works have also shown that this cognitive burden is accompanied by different writing style compared to truthful text.
+These works have also shown that this burden is accompanied by different writing style compared to truthful text.
 Other studies have shown that writing tasks can even have a long term effect,
-by showing that writing emotional texts can benefit both physical and mental health \cite{Lepore:2002,Campbell:2003,Frattaroli:2006}. 
+by showing that writing emotional texts can benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
 \citet{Campbell:2003} also showed that the health benefits of writing emotional text are accompanied by changes in writing style, mostly in the use of pronouns.
 
-Another line of works has shown that different mental states affect writing.
+Another line of works has shown that writing style is affected by the mental state.
 First, the author's personality traits (e.g., depression, neuroticism, narcissism) affect her writing style \cite{schwartz2013personality,Ireland:2014b}.
@@
 \paragraph{The story cloze task.}
-This paper also provides several insights for the future design of NLP tasks. 
+This paper also provides important insights for the future design of NLP tasks. 
 The story cloze task was very carefully designed. Many factors, such as the topic diversity, as well as  temporal and causal relation diversity,  were controlled for \cite{Mostafazadeh:2016}. 
@@
 %However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
-A way to avoid the inherent biases people have when writing is to rather than ask them to write text, have them rate sentences for naturally occurring text by parameters of coherence (or very differently -- the level of surprise).
+A way to avoid the inherent biases people have when writing is to rather than ask them to write text, have them rate sentences for naturally occurring text by parameters such as coherence (or very differently -- the level of surprise).
 
@@
 Some works even showed that writing style applied when lying is different across genders \cite{Perez:2014a,Perez:2014b}.
-In this work, we have shown that an even more subtle writing task---writing {coherent} and {coherent} story endings---imposes different styles on the author.
+In this work, we have shown that an even more subtle writing task---writing {coherent} and {incoherent} story endings---imposes different styles on the author.
 
@@
 it is often the case that these datasets suffer from methodological
-problems caused by applying noisy automatic tools to generate the data\resolved{ \nascomment{this is not clear to me, what does it mean?} when generating the datasets} \roy{better?}\cite{Chen:2016}. 
+problems caused by applying noisy automatic tools to generate them\nascomment{this is not clear to me, what does it mean?} \roy{better?}\cite{Chen:2016}. 
 In this paper we have pointed to another methodological challenge in
@@
 they motivate further research on the exact effect that a writing
-prompt has on an author's mental state, and also her response.
+prompt has on an author's mental state, and also her concrete response.
 They also provide valuable lessons for designing new NLP datasets.

### 2017-02-04 docs/language_constraint.tex
Roy V3.5

@@
 % authors. 
-A writer's style depends not just on personal traits but also on her
-intent and mental state.
+A writer's style depends not just on personal traits but also on her intent and mental state.
 %In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
-In this paper, we show how writing tasks involving different mental processes can lead to measurable differences in writing style. % of the same authors.  
-%As a case study, we experiment with a recently published machine reading task: 
+In this paper, we show how variants of the same writing task can lead to measurable differences in writing style. % of the same authors.  
 We present a case study based on 
 the  {\it story cloze task} \cite{Mostafazadeh:2016},
-where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 contraints looks like 3 constraints.
+where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 constraints looks like 3 constraints.
 clarify}}
 %We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
-We show that a simple linear classifier informed with stylistic features is able to successfully distinguish between the three cases.
-In addition, our style-based classifier obtains state-of-the-art results on the story cloze challange, substantially higher than  deep learning models, without even looking at the story context. 
+We show that a simple linear classifier informed with stylistic features is able to successfully distinguish between the three cases, without even looking at the story context.
+In addition, our style-based classifier obtains state-of-the-art results on the story cloze challenge, substantially higher than  deep learning models. 
+%Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
 Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}
@@
 
-We show that different framings of similar writing tasks can lead to measurable differences in people's writing style.
-We explore three  writing tasks, showing that they are distinguishable from one another using a linear classifier informed with stylistic features only. 
-Our results hint that different writing tasks impose different cognitive constraints on the writer, which lead to the substantial style differences.
-
-%As a testbed, we experiment with
+We show that similar writing tasks with different constraints on the author can lead to measurable differences in people's writing style.
+%We explore three  writing tasks, showing that they are distinguishable from one another using a linear classifier informed with stylistic features only. 
+%Our results hint that different writing tasks impose different cognitive load on the writer, which lead to the substantial style differences.
 As a case study, we present experiments   based on 
@@
 While the story cloze task was originally designed to be a story understanding challenge, 
-its annotation process introduced three variants of the same writing task---the {\it original}, {\it right} and {\it wrong} endings. 
-We show that a linear classifier informed with stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5\%--75.6\% binary classification results).
+its annotation process introduced three variants of the same writing task: writing an {\it original}, {\it right} or {\it wrong} ending to a short story.
+In this paper, we show that a linear classifier informed with stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5\%--75.6\% binary classification results).
+
 Our results allow us to make a few key observations.
@@
 
-%Our results may have a wide impact on a range of fields. 
-The contributions of our study are twofold. 
+The contributions of our study are threefold. 
 First, findings from our study can potentially shed light on 
-%cognitive processes that take place in the brain during writing.
 how different kinds of cognitive load influence the style of written language. 
-%Second, our results might have a more practical value in an era when fake news are becoming prominent,
-%as they suggest that these might have different style compared to real news.
-%Second, our results provide valuable insights for designing new NLP tasks,\clinic{unclear}
+Second, our results indicate that when designing new NLP tasks, special attention needs to be payed to the instructions given to authors.
 %both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
-%Although \cite{Mostafazadeh:2016} seem to have put a lot of effort into designing the task, 
-%addressing many potential methodological flaws (see \secref{ROC_Story}), the importance of a few allegedly minor details were underestimated. 
-%We show that these details are actually very significant. 
-Second, we establish a new state-of-the-art result on the commonsense story cloze challenge.
+Third, we establish a new state-of-the-art result on the commonsense story cloze challenge.
 
@@
 Human judgement scores are taken from \cite{Mostafazadeh:2016}.
-Methods marked with ($\dagger$) use the story context in order to make a predicition. 
+Methods marked with ($\dagger$) use the story context in order to make a prediction. 
  \resolved{\nascomment{I added 0s to ``Niko'' result

### 2017-02-04 docs/language_constraint.tex
Friday edits
small edits through out

@@
 We show that a simple linear classifier informed with stylistic features is able to successfully distinguish between the three cases, without even looking at the story context.
-In addition, our style-based classifier obtains state-of-the-art results on the story cloze challenge, substantially higher than  deep learning models. 
+In addition, our style-based classifier establishes a new state-of-the-art result on the story cloze challenge, substantially higher than previous results based on deep learning models. 
 %Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
@@
 \caption{\label{ROC-example}
-Examples of stories from the story cloze task \cite{Mostafazadeh:2016}. The first row shows an {\color{blue}{Original}} story written by one author. 
+Examples of stories from the story cloze task \cite{Mostafazadeh:2016}. The first row shows an {\color{blue}{original}} story written by one author. 
 The second and third rows show revised stories with two contrastive endings:
  %of the same story: 
- a {\color{forestgreen}{Coherent}} ending and a {\color{red}{Incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story.
+ a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story.
 Unfortunately Nasrin et al.
@@
 Once again, deceptive text is also characterized by fewer pronouns compared to truthful text \cite{Newman:2003}.
-In contrast, {\it wrong} and {\it right} endings favor proper nouns compared to {\it original} endings. 
-\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}
-\ms{The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.}\roy{Good point!
+%In contrast, {\it wrong} and {\it right} endings favor proper nouns compared to {\it original} endings. 
+ \resolved{\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}}
+ \resolved{\ms{The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.}}
+  \resolved{\roy{Good point!
 This is tricky.
@@
 It also forces us to bash them some more.
-Or we can just ignore it...}
+Or we can just ignore it...} }
+  \resolved{\yc{Ok!
+I resolved all comments above and also commented out the comment on how wrong/right endings use more proper nouns compared to the original endings.
+I think it's the best not to talk about this.}}
 
@@
 %\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, did we find that in our experiments?}.
-Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings tend to use more negative language (``hates''), as is deceptive text \cite{Newman:2003}.
+Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings tend to use more negative language (``hates''), similarly as deceptive text \cite{Newman:2003}.
 %\yc{Again, any cogsci literature on this?} \nascomment{feels
@@
 \begin{figure*}[t!]
-\begin{subfigure}{.5\textwidth}
+\begin{subfigure}{.5\textwidth}\center
 \begin{tikzpicture}
@@
 \end{subfigure}
-\begin{subfigure}{.5\textwidth}
+\begin{subfigure}{.5\textwidth}\center
 \begin{tikzpicture}
@@
 
-Our goal of this paper is to determine the extent to which 
+The goal of this paper is to determine the extent to which 
 %does constraining authors in their writing assignments lead to them adopting different writing styles. 
@@
 In Experiment 1, our model obtains 64.5\%
-classification accuracy, well above a (50\%-accurate) random baseline.\clinic{How good is this?}
+classification accuracy, well above a (50\%-accurate) random baseline.
+\clinic{How good is this?}
+\yc{how about addressing above comment from the clinic by adding a commentary such as following: This result is surprising given that our model makes the prediction based only on the last sentence without looking at the story context, thus does not have sufficient information to judge the story coherency.}
 For Experiment 2, our model is even stronger, at 68.5\%.
@@
 {\bf Experiment} & {\bf Accuracy} \\ \hline
-{\it Right/Wrong} & 64.5\% \\ \hline
-{\it Original/Right} & 68.5\% \\ \hline
-{\it Original/Wrong} & 75.6\% \\ \hline
+{\sl right vs. wrong} & 64.5\% \\ \hline
+{\sl original vs. right} & 68.5\% \\ \hline
+{\sl original vs. wrong} & 75.6\% \\ \hline
 \end{tabular}
 \end{center}
-\caption{\label{results} Results of  experiments 1 ({\it Right/Wrong}) and 2 ({\it Original/Right}). 
-Bottom row shows an additional experiment which classifies {\it  original} endings vs \textit{\textbf{wrong}} endings.
+\caption{\label{results} Results of  experiments 1 ({\it right vs. wrong}) and 2 ({\it original vs. right}). 
+Bottom row shows an additional experiment which classifies {\it  original} endings vs \textit{{wrong}} endings.
 In all cases, our setup implies a 50\% random baseline.}
@@
 \begin{tabular}{|l|r|} \hline
-{\bf Model} & {\bf Accuracy} \\ \hline
+{\bf Model} & {\bf Accu} \\ \hline
 $\dagger${DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
@@
 \caption{\label{cloze_results}
+\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}
 Results on the test set of the  story cloze task. 
@@
 \end{center}
-\caption{\label{exp1_features}}
+\caption{\label{exp1_features}
 The top 5 most discriminative features for predicting {\it right} vs.~{\it wrong} endings,
-along with their frequency in our story cloze training set.\end{table}
+along with their frequency in our story cloze training set.
+}
+\end{table}
 
@@
 \end{center}
-\caption{\label{exp2_features}}
-The top 5 most discriminative features for predicting {\it original} vs.~{\it new} ({\it right}) endings.\end{table}
+\caption{\label{exp2_features}
+The top 5 most discriminative features for predicting {\it original} vs.~{\it new} ({\it right}) endings.
+}
+\end{table}
 

### 2017-02-05 docs/language_constraint.tex
Noah

@@
 Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
-It is influenced by both personal factors such as age \cite{Schler:2006} and gender \cite{Argamon:2003}, 
+It is influenced by personal factors such as age \cite{Schler:2006} and gender \cite{Argamon:2003}, 
 by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
@@
 
-We show that similar writing tasks with different constraints on the author can lead to measurable differences in people's writing style.
+We show that similar writing tasks with different constraints on the
+author can lead to measurable differences in her writing style.
 %We explore three  writing tasks, showing that they are distinguishable from one another using a linear classifier informed with stylistic features only. 
@@
 who was shown only the first four sentences as a story context, 
-and asked to write contrastive story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
+and asked to write two contrasting story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
 Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP and AI research. 
@@
 
-\com{We show that a linear classifier informed with stylistic features can distinguish between {\it original}, {\it right} and {\it wrong}  endings to a large degree, even without looking at the story context.
+\com{We show that a linear classifier informed with stylistic features can distinguish among {\it original}, {\it right}, and {\it wrong}  endings to a large degree, even without looking at the story context.
 Our results allow us to make a few key observations.
@@
 While the story cloze task was originally designed to be a story understanding challenge, 
-its annotation process introduced three variants of the same writing task: writing an {\it original}, {\it right} or {\it wrong} ending to a short story.
-In this paper, we show that a linear classifier informed with stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5\%--75.6\% binary classification results).
+its annotation process introduced three variants of the same writing task: writing an {\it original}, {\it right}, or {\it wrong} ending to a short story.
+In this paper, we show that a linear classifier informed by stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5--75.6\% binary classification results).
 
@@
 
-In order to further estimate the quality of our results, we also directly tackle the story cloze challenge. 
- Adapting our classifier to the task, we obtain 72.4\% accuracy, a 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}.
+In order to further validate our method, we also directly tackle the
+story cloze challenge \nascomment{cite the challenge?  a reader may
+  not realize that there is a shared task on this}. 
+ Adapting our classifier to the task, we obtain 72.4\% accuracy, a
+ 12.5\% increase over the previously reported state of the art  \cite{Salle:2016}.
 We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
@@
 
-The ROC story corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
+The ROC story corpus consists of 49,255 five-sentence commonsense
+stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently,
+  an additional 53K stories were released, which results in roughly
+  100K stories.}
 Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
@@
 still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
-  task website (\url{https://competitions.codalab.org/competitions/15333}) does report higher results (71.1\%)\roy{Tricky.
-Which number should we report here?
-leave empty?}, which are still unpublished along with the underlying methodology.}
+  task website
+  (\url{https://competitions.codalab.org/competitions/15333}) does
+  report higher results% (71.1\%)
+\roy{Tricky. Which number should we report here? leave empty?}
+\nascomment{leave empty for now}, which
+are still unpublished along with the underlying methodology.} 
 This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or shorter period of time.
@@
 In addition, \citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
-First, each pair of endings was written by the same author, which ensured that author style differences could not be used to solve the task. 
-Furthermore, the authors implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
-These results indicate that real understanding of text is required in order to solve the task.
-
-\paragraph{Different writing tasks in the story cloze Task.}
-Several key design decisions make this task an interesting testbed for the purpose of this paper.\resolved{\clinic{Which purpose?}}
+First, each pair of endings was written by the same author, which
+ensured that style differences between authors could not be used to solve the task. 
+Furthermore, Mostafazadeh et al.~implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
+These results suggest that real understanding of text is required in order to solve the task.
+
+\paragraph{Different writing tasks in the story cloze task.}
+Several key design decisions make the task an interesting testbed for the purpose of this study.\resolved{\clinic{Which purpose?}}
 First, the training set for the task (ROC Stories corpus) is not a
@@
   instances are not drawn from a population similar to the one that future
-  testing instances will be drawn from.\roy{I added \textbf{not} here, as otherwise it is confusing}}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
+  testing instances will be drawn from.%\roy{I added \textbf{not}
+                                %here, as otherwise it is confusing}
+}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
  \resolved{\yc{As far as I understand, this was intentional --- they didn't want
@@
 slightly longer than {\it wrong} ones (8.47 words). 
-Previous work have shown that sentence length is also indicative of whether a text was deceptive \cite{yancheva2013automatic,qin2004exploratory}. 
+Previous work has shown that sentence length is also indicative of whether a text was deceptive \cite{yancheva2013automatic,qin2004exploratory}. 
 Although writing {\it wrong} sentences is not the same as lying, it is not entirely surprising to observe similar trends in both tasks.
@@
 %  Pennebaker-ish, that might be a good place to look.}
-Next we show that these style differences are not anecdotal, but can be used to distinguish between the different groups of text.
+Next we show that these style differences are not anecdotal, but can
+be used to distinguish between the different types of story endings.
 
@@
 
-We train a logistic regression classifier to distinguish between different endings. 
+We train a logistic regression classifier to categorize an ending,
+either as right vs.~wrong or as original vs.~new.
 Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
@@
 \item\textit{\textbf{Length}.} The number of words in the sentence.
-\item\textit{\textbf{Word n-grams.}} We use sequences of 1-5
+\item\textit{\textbf{Word $n$-grams.}} We use sequences of 1-5
   words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
@@
 \isectionb{Results}
-\tabref{results} shows our results.
-In Experiment 1, our model obtains 64.5\%
-classification accuracy, well above a (50\%-accurate) random baseline.
-\clinic{How good is this?}
-\yc{how about addressing above comment from the clinic by adding a commentary such as following: This result is surprising given that our model makes the prediction based only on the last sentence without looking at the story context, thus does not have sufficient information to judge the story coherency.}
-For Experiment 2, our model is even stronger, at 68.5\%.
-These results indicate that an author's style is affected in an
-easily-detected way when she is prompted to write (1) a \emph{wrong} story ending vs.~a
-\emph{right} one, or (2) finishing her own short story vs.~someone else's.
-%These numbers indicate that these different writing tasks clearly impose different writing styles on authors.
-
-We further measured whether these style effects are additive, by
-classifying \emph{original} vs.~\emph{wrong} endings.  The setup is
-exactly as in Experiment 2, but using \emph{wrong} endings instead of
-\emph{right} ones.  The result is that the effects are somewhat
-additive:  this third classifier achieves 75.6\%.
-% That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
-% We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
-% Our hypothesis is that differences would be even clearer. 
-% Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.
+\tabref{results} shows our results.  In both experiments,
+our model achieves performance well above what would be expected under
+chance (50\% by design).  Noting again that our model ignores the
+story context (the preceding four sentences), our model is unable to
+capture any notion of coherence.   This finding provides
+strong evidence that the authors' style was affected by the writing task they
+were given to perform.  We further applied the model to a third task,
+\emph{original} vs.~\emph{wrong (new)} endings, and even stronger
+differences were apparent to the model, allowing over 75\% accuracy.
+
+\nascomment{I rewrote this section.  old version commented out in
+  latex source}
+% In Experiment 1, our model obtains 64.5\%
+% classification accuracy, well above a (50\%-accurate) random baseline.
+% \clinic{How good is this?}
+% \yc{how about addressing above comment from the clinic by adding a
+%   commentary such as following: This result is surprising given that
+%   our model makes the prediction based only on the last sentence
+%   without looking at the story context, thus does not have sufficient
+%   information to judge the story coherency.} 
+% For Experiment 2, our model is even stronger, at 68.5\%.
+% These results indicate that an author's style is affected in an
+% easily-detected way when she is prompted to write (1) a \emph{wrong} story ending vs.~a
+% \emph{right} one, or (2) finishing her own short story vs.~someone else's.
+% %These numbers indicate that these different writing tasks clearly impose different writing styles on authors.
+
+% We further measured whether these style effects are additive, by
+% classifying \emph{original} vs.~\emph{wrong} endings.  The setup is
+% exactly as in Experiment 2, but using \emph{wrong} endings instead of
+% \emph{right} ones.  The result is that the effects are somewhat
+% additive:  this third classifier achieves 75.6\%.
+% % That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
+% % We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
+% % Our hypothesis is that differences would be even clearer. 
+% % Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.
 
@@
 %\small
-\begin{tabular}{|c|c|} \hline
+\begin{tabular}{|l|r|} \hline
 {\bf Experiment} & {\bf Accuracy} \\ \hline
-{\sl right vs. wrong} & 64.5\% \\ \hline
-{\sl original vs. right} & 68.5\% \\ \hline
-{\sl original vs. wrong} & 75.6\% \\ \hline
+{\sl right vs. wrong} & 0.645 \\ \hline
+{\sl original vs. right} & 0.685 \\ \hline
+{\sl original vs. wrong} & 0.756 \\ \hline
 \end{tabular}
 \end{center}
-\caption{\label{results} Results of  experiments 1 ({\it right vs. wrong}) and 2 ({\it original vs. right}). 
-Bottom row shows an additional experiment which classifies {\it  original} endings vs \textit{{wrong}} endings.
+\caption{\label{results} Results of  experiments 1 ({\it right
+    vs.~wrong}) and 2 ({\it original vs.~right (new)}). 
+The bottom row shows an additional experiment which classifies {\it
+  original vs.~wrong (new)} endings.
 In all cases, our setup implies a 50\% random baseline.}
@@
 \tabref{cloze_results} shows our results on the story cloze test
-set. Our classifier obtains 72.4\% accuracy, 12.5\% higher than the
+set. Our classifier obtains 72.4\% accuracy, 12.5\% (absolute) higher than the
 published state-of-the-art result on the task \cite{Salle:2016}\resolved{\nascomment{cite that here}}.
@@
 \begin{tabular}{|l|r|} \hline
-{\bf Model} & {\bf Accu} \\ \hline
+{\bf Model} & {\bf Acc.} \\ \hline
 $\dagger${DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
@@
 
-\nascomment{please check the paragraph above.  we need to say how we
+\resolved{\nascomment{please check the paragraph above.  we need to say how we
   use the LM before we evaluate it!  also, has anyone tried an approach like this
@@
   someone else used RNNs for this task, we should credit them.}
-  \roy{Ours is the first work to publish LSTM results on this dataset.}
+  \roy{Ours is the first work to publish LSTM results on this dataset.}}
 
@@
 in Equation~\ref{eq:ratio} achieves 67.7\%  (see
-\tabref{cloze_results}).\footnote{Further analysis of this large
-  difference is out of the scope of this paper, but suggests careful
-  study of suitable probabilistic inference methods for such tasks.}
+\tabref{cloze_results}).\footnote{Note that taking the logarithm of
+  the expression in Equation~\ref{eq:ratio} gives the pointwise mutual
+information between the story and the ending, under the language
+model. \nascomment{added this to replace the hedging that was here before}}
 
@@
 \subsection{Most Salient Features}
-A followup question is which individual features contribute most to the classification process,
+A follow-up question is which individual features contribute most to the classification process,
 as these could shed light on the stylistic differences imposed by each of the writing tasks.
 
-In order to answer this question, we consider the highest absolute positive and negative coefficients in the logistic regression classifier in both Experiments 1 and 2, an  approach widely used  as a method of extracting the most salient features \cite{Nguyen:2013,Burke:2013,Brooks:2013}.\footnote{Although it is worth noting that its reliability is not entirely clear \cite{Yano:2012}.}
-We consider only features appearing in at least 5\% of the endings in our training set.
+In order to answer this question, we consider the highest absolute
+positive and negative coefficients in the logistic regression
+classifier in both Experiments 1 and 2, an  approach widely used  as a
+method of extracting the most salient features
+\cite{Nguyen:2013,Burke:2013,Brooks:2013}. It is worth noting
+  that its reliability is not entirely clear, since linear models like
+  logistic regression can assign large coefficients to rare features \cite{Yano:2012}.
+To mitigate this concern, we consider only features appearing in at least 5\% of the endings in our training set.
 
@@
 Second, {\it right} endings will make wider use of coordination structures, as well as adjectives.
-The latter might indicate that writing coherent stories imposes the authors to write more descriptive text compared to incoherent ones, 
+The latter might indicate that writing coherent stories inspires the authors to write more descriptive text compared to incoherent ones, 
 as is the case in truthful vs.~deceptive text \cite{ott2011finding}.
-Finally, we notice a few syntactic differences: {\it right} endings will more often use infinite verb structure, while {\it wrong} endings will prefer gerunds (VBG). 
-\nascomment{note to self to come back
-  to this after we agree on methodology.}
+Finally, we notice a few syntactic differences: {\it right} endings will more often use infinite verb structure, while {\it wrong} endings prefer gerunds (VBG).
 
@@
 \textit{\textbf{Right}} & Freq. & \textit{\textbf{Wrong}}& Freq. \\ \hline
-`ed .' & {\color{white}{0}}6.5\%& START NNP & 54.8\%\\ \hline
+`ed .' & {\color{white}{0}}6.5\%& \textsc{start} NNP & 54.8\%\\ \hline
 `and ' & 13.6\%& NN . & 47.5\% \\ \hline
@@
 to VB & 20.1\%& VBG & 10.1\%\\ \hline
-`d th' & 10.9\%& START NNP VBD & 41.9\%\\ \hline
+`d th' & 10.9\%& \textsc{start} NNP VBD & 41.9\%\\ \hline
 %`ally' & 3.3\% & `hate' & {\color{white}{0}}1.9\% \\ \hline
 %VBD the NN .& 2.2\% & ` hat' & {\color{white}{0}}2.0\% \\ \hline
-%START RB & 3.1\% & START NNP & 54.8\% \\ \hline
+%\textsc{start} RB & 3.1\% & \textsc{start} NNP & 54.8\% \\ \hline
 %`ved ' &4.1\%&  `ated' & {\color{white}{0}}3.0\%\\ \hline
@@
 \caption{\label{exp1_features}
-The top 5 most discriminative features for predicting {\it right} vs.~{\it wrong} endings,
+The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
 along with their frequency in our story cloze training set.
@@
 As noted in \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
-This is inline with similar findings in the deception detection literature \cite{qin2004exploratory}.
-An interesting observation is that exclamation marks are a strong indication for  {\it original} ending. 
-This indicates that authors are more likely to show enthusiasm when writing their own text compared to ending an existing task.
+This is in line with similar findings in the deception detection literature \cite{qin2004exploratory}.
+An interesting observation is that exclamation marks are a strong
+indication for an  {\it original} ending. 
+This suggests that authors are more likely to show or evoke enthusiasm when writing their own text compared to ending an existing task.
 
 Finally, when comparing the two groups of salient features from both experiments, we find an interesting trend.
-Several features, such as ``START NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict {\it new} (i.e., {\it correct}) endings in Experiment 2. 
+Several features, such as ``\textsc{start} NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict {\it new} (i.e., {\it correct}) endings in Experiment 2. 
 This indicates that, for instance, incoherent endings have a stronger tendency to begin with a proper noun compared to coherent endings, 
@@
 {\it length} & {\color{white}{.}}100.0\% & `.' & 93.0\%\\ \hline
-`!' & {\color{white}{00}}6.1\%& START NNP  & 39.2\% \\ \hline
-NN & {\color{white}{00}}78.9\% & START NNP VBD &29.0\% \\ \hline
+`!' & {\color{white}{00}}6.1\%& \textsc{start} NNP  & 39.2\% \\ \hline
+NN & {\color{white}{00}}78.9\% & \textsc{start} NNP VBD &29.0\% \\ \hline
 RB & {\color{white}{0}}44.7\%& NN . & 42.3\% \\ \hline
@@
 \caption{\label{exp2_features}
-The top 5 most discriminative features for predicting {\it original} vs.~{\it new} ({\it right}) endings.
+The top 5 most heavily weighted features for predicting {\it original} vs.~{\it new} ({\it right}) endings.
 }
@@
 Our results indicate that when authors are asked to write the last
-sentence of a five sentence story, they will use different style to
+sentence of a five-sentence story, they will use different style to
 write a {\it right} ending compared to a {\it wrong} ending. We have
@@
 Our findings hint that the nature of the writing task imposes a
-different mental state on the author, which is expressed in ways which
-are often implicit, but can be observed using extremely simple automatic tools.
-
-Previous work have shown that  writing task could affect mental states.
-For instance, several works demonstrated that writing deceptive text leads to a significant cognitive burden \cite{Newman:2003,Banerjee:2014}.
-These works have also shown that this burden is accompanied by different writing style compared to truthful text.
-Other studies have shown that writing tasks can even have a long term effect,
-by showing that writing emotional texts can benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
+different mental state on the author, which is expressed in ways that can be observed using extremely simple automatic tools.
+
+Previous work has shown that a writing task can affect mental state.
+For instance, writing deceptive text leads to a significant cognitive
+burden accompanied by a writing style that is different from truthful
+text \cite{Newman:2003,Banerjee:2014}.
+Writing tasks can even have a long-term effect,
+as writing emotional texts was observed to benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
 \citet{Campbell:2003} also showed that the health benefits of writing emotional text are accompanied by changes in writing style, mostly in the use of pronouns.
 
-Another line of works has shown that writing style is affected by the mental state.
-First, the author's personality traits (e.g., depression, neuroticism, narcissism) affect her writing style \cite{schwartz2013personality,Ireland:2014b}.
-Second, temporary changes, such as a romantic relationship \cite{Ireland:2011,Bowen:2016}, work collaboration \cite{Tausczik:2009,Gonzales:2009} or negotiation \cite{Ireland:2014} may also affect writing style.
+Another line of work has shown that writing style is affected by mental state.
+First, an author's personality traits (e.g., depression, neuroticism, narcissism) affect her writing style \cite{schwartz2013personality,Ireland:2014b}.
+Second, temporary changes, such as a romantic relationship \cite{Ireland:2011,Bowen:2016}, work collaboration \cite{Tausczik:2009,Gonzales:2009}, or negotiation \cite{Ireland:2014} may also affect writing style.
 Finally, writing style can also change from one sentence to another, for instance between positive and negative text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}.
 
-This large body of works indicates a tight connection between writing tasks, mental states and different writing styles.
-This connection hints that the link discovered in this paper, between the different writing tasks and the resulting difference in writing style, also goes through a change in mental state. 
-Nonetheless, further investigation is required in order to further validate this hypothesis.
+This large body of work indicates a tight connection between writing
+tasks, mental states, and variation in writing style.
+This connection hints that the link discovered in this paper, between
+different writing tasks and resulting variation in writing style,
+involves differences in mental state. 
+Further investigation is required in order to further validate this hypothesis.
 
 \paragraph{The story cloze task.}
-This paper also provides important insights for the future design of NLP tasks. 
-The story cloze task was very carefully designed. Many factors, such as the topic diversity, as well as  temporal and causal relation diversity,  were controlled for \cite{Mostafazadeh:2016}. 
-The authors also made sure each pair of endings was written by the same author, partly in order to avoid author specific style effects.
- Nonetheless, this paper shows that despite these efforts, several significant style differences are found between the training and the test set, as well as between the positive and negative labels.
-
-The findings in this paper suggest that careful attention must be paid to instructions given to authors, especially in unnatural tasks such as writing a {\it wrong} ending. 
+Our study also provides important insights for the future design of NLP tasks. 
+The story cloze task was very carefully designed. Many factors, such
+as topic diversity and temporal and causal relation diversity,  were controlled for \cite{Mostafazadeh:2016}. 
+The authors also made sure each pair of endings was written by the
+same author, partly in order to avoid author-specific style effects.
+ Nonetheless, despite these efforts, several significant style
+ differences can be found between the training and the test set, as well as between the positive and negative labels.
+
+Our findings suggest that careful attention must be paid to instructions given to authors, especially in unnatural tasks such as writing a {\it wrong} ending. 
 One way to avoid such problems is by using shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
@@
 %However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
-A way to avoid the inherent biases people have when writing is to rather than ask them to write text, have them rate sentences for naturally occurring text by parameters such as coherence (or very differently -- the level of surprise).
+One way to avoid the inherent biases people have when writing is to 
+have them rate sentences from naturally occurring text by parameters
+such as coherence (or, very differently, the level of surprise),
+rather than asking them to generate new text.
 
@@
 }
-\roy{Commented out the lessons about the importance of running baselines.}
+\roy{Commented out the lessons about the importance of running
+  baselines.} 
+\nascomment{that seems like the right choice}
+
 \isection{Related Work}{Related}
@@
 \cite{Newman:2003,hancock2007lying,ott2011finding,Feng:2012}.
-Some works even showed that writing style applied when lying is different across genders \cite{Perez:2014a,Perez:2014b}.
+Some works even showed that gender affects a person's  writing style when lying \cite{Perez:2014a,Perez:2014b}.
 In this work, we have shown that an even more subtle writing task---writing {coherent} and {incoherent} story endings---imposes different styles on the author.
@@
 \paragraph{Machine reading.}
-The  story cloze task, which is the focus of this paper, is part of a wide set of machine reading works published in the last few years.
+The  story cloze task, which is the focus of this paper, is part of a wide set of machine reading/comprehension challenges published in the last few years.
 These include datasets like bAbI \cite{Weston:2015}, SNLI \cite{bowman2015large}, CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad}, and LAMBADA \cite{Paperno:2016}. 
-
-While these works have presented valuable resources for researchers, 
+While these works have presented resources for researchers, 
 it is often the case that these datasets suffer from methodological
-problems caused by applying noisy automatic tools to generate them\nascomment{this is not clear to me, what does it mean?} \roy{better?}\cite{Chen:2016}. 
-In this paper we have pointed to another methodological challenge in
-designing machine reading tasks, namely that different writing tasks
-used to generated the data affect the writing style of the positive
-and negative samples, confounding the classification problem.
+problems caused by applying noisy automatic tools to generate them \cite{Chen:2016}. 
+In this paper, we have pointed to another methodological challenge in
+designing machine reading tasks:  different writing tasks
+used to generated the data affect writing style, confounding classification problems.
 %, as well as create a discrepancy between the training and the test data.
@@
 
-The research question that guided this work is the extent to which different writing tasks result in different writing styles.
+Different writing tasks assigned to an author result in different
+writing styles for that author.
 We experimented with the story cloze task, which introduces two interesting comparison points: %setups for our purposes:
@@
 The findings presented in this paper have  cognitive implications, as
-they motivate further research on the exact effect that a writing
+they motivate further research on the effects that a writing
 prompt has on an author's mental state, and also her concrete response.

### 2017-02-05 docs/language_constraint.tex
Roy V4

@@
 In order to further validate our method, we also directly tackle the
-story cloze challenge \nascomment{cite the challenge?  a reader may
-  not realize that there is a shared task on this}. 
+story cloze task \nascomment{cite the challenge?  a reader may
+  not realize that there is a shared task on this}\roy{Maybe ``challenge'' was not the right term here.
+We basically mean the story cloze task.
+The shared task was the original task w/o any modification, so I am not referring to it specifically here}.
  Adapting our classifier to the task, we obtain 72.4\% accuracy, a
@@
 %The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
-The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are not included in the training set).\roy{added {\it not} here}
+The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are not included in the training set).\resolved{\roy{added {\it not} here}}
 The task was suggested as an extensive evaluation framework:
@@
   report higher results% (71.1\%)
-\roy{Tricky. Which number should we report here? leave empty?}
-\nascomment{leave empty for now}, which
+\resolved{\roy{Tricky. Which number should we report here? leave empty?}
+\nascomment{leave empty for now}}, which
 are still unpublished along with the underlying methodology.} 
@@
 
-\nascomment{I rewrote this section.  old version commented out in
-  latex source}
+\resolved{\nascomment{I rewrote this section.  old version commented out in
+  latex source}}
 % In Experiment 1, our model obtains 64.5\%
@@
 \end{center}
-\caption{\label{cloze_results}
-\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}
+\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}
 Results on the test set of the  story cloze task. 
@@
 information between the story and the ending, under the language
-model. \nascomment{added this to replace the hedging that was here before}}
+model.\nascomment{added this to replace the hedging that was here before}\roy{We actually also use the RNNLM features in log space. Add that in the next paragraph.}}
 
@@
 our classifier: the numerator, denominator, and ratio in
-Equation~\ref{eq:ratio}. % $p_\theta(ending|story),p_\theta(ending)$ and $\frac{p_\theta(ending|story)}{p_\theta(ending)}$.
+Equation~\ref{eq:ratio}, all in log space. % $p_\theta(ending|story),p_\theta(ending)$ and $\frac{p_\theta(ending|story)}{p_\theta(ending)}$.
 We retrain our linear  model with the new feature set, and gain 2.8\%
-absolute, reaching 75.2\% (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result).\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}
+absolute, reaching 75.2\% (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result).\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
 These results indicate that context-ignorant style features can be used to obtain high
@@
 }
-\roy{Commented out the lessons about the importance of running
+\resolved{\roy{Commented out the lessons about the importance of running
   baselines.} 
-\nascomment{that seems like the right choice}
+\nascomment{that seems like the right choice}}
 

### 2017-02-06 docs/language_constraint.tex
Roy V4.5

@@
 We train a logistic regression classifier to categorize an ending,
-either as right vs.~wrong or as original vs.~new.
+either as {\it right} vs.~{\it wrong} or as {\it original} vs.~new ({\it right}).
 Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
@@
 \end{tikzpicture}
-\caption{\label{results} Results of  experiments 1 and 2 (left two charts). 
+\caption{\label{results}Results of  experiments 1 and 2 (left two charts). 
 Rightmost graph shows a control experiment which classifies {\it
@@
 \end{center}
-\caption{\label{results} Results of  experiments 1 ({\it right
+\caption{\label{results}Results of  experiments 1 ({\it right
     vs.~wrong}) and 2 ({\it original vs.~right (new)}). 
@@
 \end{center}
-\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}
-Results on the test set of the  story cloze task. 
+\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}Results on the test set of the  story cloze task. 
 The first block are published results, 
@@
 Finally, when comparing the two groups of salient features from both experiments, we find an interesting trend.
-Several features, such as ``\textsc{start} NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict {\it new} (i.e., {\it correct}) endings in Experiment 2. 
+Several features, such as ``\textsc{start} NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict new (i.e., {\it right}) endings in Experiment 2. 
 This indicates that, for instance, incoherent endings have a stronger tendency to begin with a proper noun compared to coherent endings, 
@@
 \caption{\label{exp2_features}
-The top 5 most heavily weighted features for predicting {\it original} vs.~{\it new} ({\it right}) endings.
+The top 5 most heavily weighted features for predicting {\it original} vs.~new ({\it right}) endings.
+{\it length} is the sentence length feature (see \secref{Model}).
 }
@@
 \paragraph{The effect of writing tasks on mental states.}
-In this paper we have shown that giving a writer different writing tasks affects writing style in easily detected ways.
+In this paper we have shown that giving a writer different writing tasks affects her writing style in easily detected ways.
 Our results indicate that when authors are asked to write the last
@@
 
-\paragraph{The story cloze task.}
+\paragraph{Design of NLP tasks.}
 Our study also provides important insights for the future design of NLP tasks. 
@@
 The  story cloze task, which is the focus of this paper, is part of a wide set of machine reading/comprehension challenges published in the last few years.
-These include datasets like bAbI \cite{Weston:2015}, SNLI \cite{bowman2015large}, CNN/DailyMail \cite{hermann2015teaching}, SQuAD \cite{rajpurkar2016squad}, and LAMBADA \cite{Paperno:2016}. 
+These include datasets like bAbI \cite{Weston:2015}, SNLI \cite{bowman2015large}, CNN/DailyMail \cite{hermann2015teaching}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}. 
 While these works have presented resources for researchers, 

### 2017-02-06 docs/language_constraint.tex
Roy fix bib issues

@@
 \definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
-
 % Define bar chart colors
@@
 
-%\renewcommand{\ms}[1]{}
-%\renewcommand{\roy}[1]{}
-%\renewcommand{\nascomment}[1]{}
-%\renewcommand{\yc}[1]{}
+\renewcommand{\ms}[1]{}
+\renewcommand{\roy}[1]{}
+\renewcommand{\nascomment}[1]{}
+\renewcommand{\yc}[1]{}
 %\renewcommand{\royb}[1]{}
@@
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\
+\author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
+  $^1$Computer Science \& Engineering, University of Washington, WA 98195, USA \\
+  $^2$Allen Institute for Artificial Intelligence, WA 98103, USA \\
+    {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
+    \And \hspace{-2cm}Leila Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A. Smith$^1$ \\
   }
@@
 \begin{abstract}
-%People's writing style is affected by many factors, including topics, sentiment, and individual personality. 
-% People's writing style depends not just on the authors' personal
-% traits but also on the intent and the cognitive states of the
-% authors. 
 A writer's style depends not just on personal traits but also on her intent and mental state.
-%In this paper we show that engaging authors in different  writing tasks results in them adopting different writing styles.
-In this paper, we show how variants of the same writing task can lead to measurable differences in writing style. % of the same authors.  
+In this paper, we show how variants of the same writing task can lead to measurable differences in writing style.
 We present a case study based on 
@@
 \begin{table}[!t]
-%\small
 \begin{tabular}{|p{1.6cm}|p{5.3cm}|} \hline
@@
 \begin{center}
-%\small
 \begin{tabular}{|p{2.5cm}|p{4cm}|p{4cm}|p{4cm}|} \hline
@@
 \begin{figure*}[t!]
+\begin{small}
 \begin{subfigure}{.5\textwidth}\center
 \begin{tikzpicture}
-\small
     \begin{axis}[
@@
 \begin{tikzpicture}
-\small
     \begin{axis}[
@@
 \end{subfigure}
+\end{small}
 \caption{The distribution of five frequent POS tags
@@
 For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{http://spacy.io/}}
-We use  Python's sklearn logistic regression implementation with $L_2$
+We use  Python's sklearn logistic regression implementation \cite{scikit-learn} with $L_2$
 regularization, performing grid search on the development set to
@@
 \begin{center}
-%\small
 \begin{tabular}{|l|r|} \hline
@@
 \begin{center}
-%\small
 \begin{tabular}{|c|c|} \hline
@@
 \begin{center}
-%\small
 \begin{tabular}{|c|c||c|c|} \hline
@@
 \begin{center}
-%\small
 \begin{tabular}{|p{1.25cm}|c||p{2.9cm}|c|} \hline

### 2017-02-07 docs/language_constraint.tex
Final version

@@
 %We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
-We show that a simple linear classifier informed with stylistic features is able to successfully distinguish between the three cases, without even looking at the story context.
+We show that a simple linear classifier informed with stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
 In addition, our style-based classifier establishes a new state-of-the-art result on the story cloze challenge, substantially higher than previous results based on deep learning models. 
@@
 Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
-It is influenced by personal factors such as age \cite{Schler:2006} and gender \cite{Argamon:2003}, 
+It is influenced by personal factors such as age and gender \cite{Schler:2006}, 
 by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
@@
 its annotation process introduced three variants of the same writing task: writing an {\it original}, {\it right}, or {\it wrong} ending to a short story.
-In this paper, we show that a linear classifier informed by stylistic features can distinguish between the different endings to a large degree, even without looking at the story context (64.5--75.6\% binary classification results).
+In this paper, we show that a linear classifier informed by stylistic features can distinguish among the different endings to a large degree, even without looking at the story context (64.5--75.6\% binary classification results).
 
@@
 In order to further validate our method, we also directly tackle the
-story cloze task \nascomment{cite the challenge?  a reader may
+story cloze task\nascomment{cite the challenge?  a reader may
   not realize that there is a shared task on this}\roy{Maybe ``challenge'' was not the right term here.
@@
  Adapting our classifier to the task, we obtain 72.4\% accuracy, a
- 12.5\% increase over the previously reported state of the art  \cite{Salle:2016}.
+ 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}.
 We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
@@
 
-The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness by additional AMT workers. \resolved{\nascomment{by
--  additional AMT workers? or someone else?}} 
+The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness by additional AMT workers.
 Only stories rated as simultaneously coherent with a {\it right} ending and neutral with a {\it wrong} ending were selected for the task. 
@@
 \isection{Surface Analysis of the Story Cloze Task}{Surface}
-We computed several characteristics of the three types of endings: {\it original} endings (from the ROC story corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
+We begin by computing several characteristics of the three types of endings: {\it original} endings (from the ROC story corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
 Our analysis  reveals several style differences between different groups. 
@@
 Next we show that these style differences are not anecdotal, but can
-be used to distinguish between the different types of story endings.
+be used to distinguish among the different types of story endings.
 
@@
 if it assigns different labels to the two given endings, we keep
-them.  If not, the label whose posterior probability is lower is reversed.
+them.  Otherwise, the label whose posterior probability is lower is reversed.
 
@@
 \caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}Results on the test set of the  story cloze task. 
-The first block are published results, 
-the second block is our results.
+The upper block shows published results, 
+the middle block are our results.
 LexVec results are taken from \cite{Speer:2016}.
@@
 As noted in \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
-This is in line with similar findings in the deception detection literature \cite{qin2004exploratory}.
+%This is in line with similar findings in the deception detection literature \cite{qin2004exploratory}.
 An interesting observation is that exclamation marks are a strong
@@
 gender \cite{Argamon:2003,Schler:2006,bamman2014gender}, and native language
-\cite{Koppel:2005,Tsur:2007,Bergsma:2012}.   \resolved{\nascomment{cite generously here, it costs us nothing}}
+\cite{Koppel:2005,Tsur:2007,Bergsma:2012}.
 At the extreme case, each individual author adopts a unique writing
@@
 \cite{Newman:2003,hancock2007lying,ott2011finding,Feng:2012}.
-Some works even showed that gender affects a person's  writing style when lying \cite{Perez:2014a,Perez:2014b}.
+Some works even showed that gender affects a person's  writing style when lying \cite{Perez:2014b,Perez:2014a}.
 In this work, we have shown that an even more subtle writing task---writing {coherent} and {incoherent} story endings---imposes different styles on the author.

### 2017-02-15 docs/shared_task_paper_camera_ready.tex
Shared task camera ready V1

--- 2017-02-03 docs/shared_task_paper.tex
@@
 
-% \eaclfinalcopy % Uncomment this line for the final submission
+\eaclfinalcopy % Uncomment this line for the final submission
 %\def\eaclpaperid{***} %  Enter the acl Paper ID here
@@
 
-\title{Story Cloze task -- XXX System}
+\title{Story Cloze Task --- UW System}
 
-\author{Roy Schwartz\\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And	
-  Maarten Sap \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
+\author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
+  $^1$Computer Science \& Engineering, University of Washington, WA 98195, USA \\
+  $^2$Allen Institute for Artificial Intelligence, WA 98103, USA \\
+    {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
+    \And \hspace{-2cm}Leila Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A. Smith$^1$ \\
+  }
 
@@
 \begin{abstract} % This is my real quick try at this lol
-This paper describes our system for the Linking Models of Lexical, Sentential and Discourse-level Semantics (LSDSem 2017) shared task -- the \textit{Story Cloze Task}.
+This paper describes the university of Washington NLP group submission for the Linking Models of Lexical, Sentential and Discourse-level Semantics (LSDSem 2017) shared task---the \textit{Story Cloze Task}.
 Our system feeds a linear classifier with a variety of features, including both the output of a neural language model and style features.
 We report  $75.2\%$ accuracy on the task. 
+A further discussion of our results can be found in \cite{Schwartz:2017}.
 \end{abstract}
@@
 The task is to tell which is the {\it right} story.
-In addition to the task, the authors also introduced the {\it ROC story corpus} --  a training corpus of five-sentence (coherent) stories. 
+In addition to the task, the authors also introduced the {\it ROC story corpus}---a training corpus of five-sentence (coherent) stories. 
 %The goal of the task is to determine which of the endings is the correct one.
@@
 
-\com{
-Learning of commonsense knowledge is one of AI's biggest challenges, since it is not usually found in knowledge bases.
-Coming up with the right types of data to analyze has been hard, and models are also not working well.
-
-One particular type of commonsense knowledge that has gotten attention is story understanding \cite{??}. 
-Stories have narratives that require understanding of how events typically flow and of what events are coherent after others.
-Related to understanding event sequences is script learning, which focuses on stereotypical chains of events.
-
-% Mention the specific purpose of the shared task (i.e. from the website)
-The 2017 LSD Sem Shared Task provide a testbed to further commonsense story understanding: the \textit{Story Cloze} task \cite{Mostafazadeh:2016}.
-Specifically designed for the purpose of facilitating the learning of commonsense knowledge, the task consist of finding the \textit{corrent} ending to four sentence short stories, out of two possible endings.
-% Along with the two-ending stories, Mostafazadeh, et al.
-~(2016)\nocite{Mostafazadeh:2016} also released nearly $100$k five-sentence short stories (ROC Stories), to facilitate learning of commonsense narratives.
-}
-
 % Last paragraph should be a quick description of our system.
-In this paper, we describe the system we submitted for the shared task.
+In this paper, we describe the university of Washington NLP group submission for the shared task.
 Our system explores several types of features for the task.
@@
 Our intuition is that the {\it right} endings use a different style compared to the {\it wrong} endings.
-The features we use are motivated by previous works on tasks such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, 
-and authorship profiling \cite{Stamatatos:2009}, for which similar style features are known to be very effective.
+The features we use were shown useful for style detection in tasks such as age \cite{Schler:2006}, gender \cite{Argamon:2003}, 
+and authorship profiling \cite{Stamatatos:2009}.
 
@@
 Our system obtains $75.2\%$ accuracy on the test set.
+Our findings hint that the different writing tasks used to create the story cloze task---writing {\it right} and {\it wrong} endings---impose different writing styles on authors. 
+This is further discussed in \cite{Schwartz:2017}.
 
@@
  %of the same story: 
- a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.
+ a {\color{forestgreen}{coherent}} ending (upper row) and a {\color{red}{incoherent}} one (bottom row).
 }
@@
 
-The intuition is that a \emph{correct} ending should be unsurprising (to the model) given the four preceding sentences of the story (the numerator), controlling for the inherent surprise of the words in that ending (the denominator).
+The intuition is that a \emph{correct} ending should be unsurprising (to the model) given the four preceding sentences of the story (the numerator), controlling for the inherent surprise of the words in that ending (the denominator).\footnote{Note that taking the logarithm of
+the expression in Equation~\ref{eq:ratio} gives the pointwise mutual information between the story and the ending, under the language model.}
 %We use these three probabilities as classification features.
@@
 
-We add the following features to capture style differences between the two endings. 
-These features are computed on the story endings alone, and do not consider the first four (shared) sentences of each story.
+We add the following classification features to capture style differences between the two endings. 
+These features are computed on the story endings alone ({\it right} or {\it wrong}), and do not consider, neither at train nor at test time, the first four (shared) sentences of each story.
 \begin{itemize}
@@
 regularization, performing grid search on the development set to
-tune a single hyperparameter -- the regularization parameter.
+tune a single hyperparameter---the regularization parameter.
 
-We train the RNNLM using a single-layer LSTM of hidden dimension 512.
+We start by tokenizing the text using the nltk tokenizer.\footnote{\url{www.nltk.org/api/nltk.tokenize.html}} 
+We then use TensorFlow\footnote{\url{www.tensorflow.org}} to train the RNNLM using a single-layer LSTM of hidden dimension 512.
 We use the ROC Stories for training, setting aside 10\% for validation of the language model.\footnote{We train on both the Spring 2016 and the Winter 2017 datasets, a total of roughly 100K stories}
@@
 Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
-Using AdamOptimizer \cite{kingma2014adam} and a learning rate of
+Using Adam optimizer \cite{kingma2014adam} and a learning rate of
 $\eta=.001$, we train to minimize cross-entropy.
 
-For computing the style features, we keep n-gram (character or word) features that occur at least five times in the training set.
+For computing the style features, we add a \textsc{start} symbol at the beginning
+of each sentence.\footnote{Virtually all sentences end with a period
+  or an exclamation mark, so we do not add a \textsc{stop} symbol.} 
+ We keep n-gram (character or word) features that occur at least five times in the training set.
 All stylistic feature values are normalized to [0-1].
@@
 \begin{tabular}{|l|r|} \hline
-{\bf Model} & {\bf Accuracy} \\ \hline
+{\bf Model} & {\bf Acc.} \\ \hline
 {DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
@@
 With $75.2\%$ accuracy, our system achieves $15.3\%$ better than the published state of the art \cite{Salle:2016}. 
-%\ms{At the time of submission, we beat everyone or we're ranked XX in the leaderboard.}
 The table also shows an analysis of the different features types used by our system.
-While our RNNLM features alone reach 67.7\%, the style features perform better -- 72.4\%. 
+While our RNNLM features alone reach 67.7\%, the style features perform better---72.4\%. 
 This suggests that while this task is about story understanding, 
@@
 As expected, the RNNLM features complement the stylistic ones, boosting performance by 7.5\% (over the RNNLM) and 2.8\% (over the style features).
-%This suggests that while the stylistic features provide useful signal, content-oriented models also contribute information. 
-%\ms{Perhaps, an even more complex story understanding model would provide an even greater boost.}
 
-\com{
-\subsection{Further analysis}
-
-\begin{table}[h]
-\begin{center}
-%\small
-\begin{tabular}{|c|c|} \hline
-\textit{\textbf{Right}} & \textit{\textbf{Wrong}}\\ \hline
-`ally' & ` hate'\\ \hline
-`VBD the' & ` hat'\\ \hline
-`START RB' & `START NNP'\\ \hline
-`ved ' & `ated'\\ \hline
-` tim' & `NN .'\\ \hline
-
-\end{tabular}
-\end{center}
-\caption{\label{exp1_features}}
-The top 5 most discriminative features for predicting {\it right} vs.~{\it wrong} endings.\end{table}
-
-\ms{Don't know if this steps onto our other paper's toes.}
-We analyze which features are most predictive of a \textit{wrong} or \textit{right} ending.
-Table \ref{exp1_features} shows the highest weighted features using the logistic regression coefficients. 
-The table shows a few interesting trends. 
-First, authors tend to structure their sentences differently when writing {coherent}  vs. {incoherent} endings.
-For instance, {coherent} endings are more likely to start with an adverb (e.g., ``then'', ``so'', ``eventually''), while {incoherent} ones tend to start with a proper noun.
-In addition, we find that {incoherent} endings are more likely to
-finish the sentence with a common noun.  %\nascomment{note to self to come backto this after we agree on methodology.}
-
-More interestingly, the different writing tasks seem to impose a specific sentiment on the writer. 
-Three of the top four most salient features for detecting {\it wrong} endings are variants of the verb ``hate''.
-This indicates that when authors are asked to write {\it wrong} text, they tend to use negative language.
-
-An alternative explanation to this hypothesis might be that the first four sentences of the stories in the ROC story corpus tend to be positive, and thus in order to make an ending {\it wrong}, authors adopted a negative approach.
-A similar idea was suggested in the original story cloze paper, where two sentiment-based baselines were evaluated. 
-These baselines measured the relative sentiment between the ending and the previous sentences.
-The performance of both these baselines was roughly chance-level, which seems to suggest that this is not entirely the case.
-}
-
-% ablation study? Table 2 from the paper sort of?
+In an attempt to provide explanation to the strong performance of the stylistic feature, 
+we hypothesize that the different writing tasks---writing a {\it right} and a {\it wrong} ending---impose a different style on the authors, which is expressed in the different style adopted in each of the cases.
+The reader is referred to \cite{Schwartz:2017} for more details and discussion.
 
 \section{Conclusion}
-This paper described our submission to the LSDSem 2017 Shared Task. 
+This paper described the university of Washington NLP group submission to the LSDSem 2017 Shared Task. 
 Our system leveraged both neural language model features and  stylistic features, achieving $75.2\%$ accuracy on the classification task.
-% We achieve $75.2\%$ which is ranked XXth in the ongoing codalab competition?
-% Say something like:
-\com{While we achieved state of the art performance, we still only achieved 75\% accuracy. 
-This means the task is far from being solved. 
-We need better tools to understand the common sense knowledge embedded in these stories.}
 

### 2017-02-16 docs/shared_task_paper_camera_ready.tex
A few minor comments

@@
 
-For computing the style features, we add a \textsc{start} symbol at the beginning
+For computing the style features, the story cloze task doesn't have a training corpus for the {\it right} and {\it wrong} endings.
+Therefore, we use the development set as our training set, holding out 10\% for development
+(3,366 training endings, 374 for development). We keep the story cloze test set as is (3,742 endings).
+We add a \textsc{start} symbol at the beginning
 of each sentence.\footnote{Virtually all sentences end with a period

### 2017-02-16 docs/shared_task_paper_camera_ready.tex
Noah, polishing

@@
 \newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
-
+\newcommand{\nascomment}[1]{\textcolor{blue}{[\textsc{#1 --nas}]}}
 \newcommand{\tabref}[1]{Table~\ref{#1}}
@@
 
-\title{Story Cloze Task --- UW System}
+\title{Story Cloze Task: UW NLP System}
 
 \author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
-  $^1$Computer Science \& Engineering, University of Washington, WA 98195, USA \\
-  $^2$Allen Institute for Artificial Intelligence, WA 98103, USA \\
+  $^1$Computer Science \& Engineering, University of Washington,
+  Seattle, WA 98195, USA \\
+  $^2$Allen Institute for Artificial Intelligence, Seattle, WA 98103, USA \\
     {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
-    \And \hspace{-2cm}Leila Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A. Smith$^1$ \\
+    \And \hspace{-2cm}Leila Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A.~Smith$^1$ \\
   }
@@
 \begin{abstract} % This is my real quick try at this lol
-This paper describes the university of Washington NLP group submission for the Linking Models of Lexical, Sentential and Discourse-level Semantics (LSDSem 2017) shared task---the \textit{Story Cloze Task}.
-Our system feeds a linear classifier with a variety of features, including both the output of a neural language model and style features.
+This paper describes University of Washington NLP's submission for the Linking Models of Lexical, Sentential and Discourse-level Semantics (LSDSem 2017) shared task---the \textit{Story Cloze Task}.
+Our system is a linear classifier with a variety of features, including both the scores of a neural language model and style features.
 We report  $75.2\%$ accuracy on the task. 
-A further discussion of our results can be found in \cite{Schwartz:2017}.
+A further discussion of our results can be found in \newcite{Schwartz:2017}.
 \end{abstract}
@@
 % Last paragraph should be a quick description of our system.
-In this paper, we describe the university of Washington NLP group submission for the shared task.
+In this paper, we describe University of Washington NLP's submission for the shared task.
 Our system explores several types of features for the task.
@@
 
-Second, we attempt to distinguish between {\it right} and {\it wrong} endings using style features, such as sentence length, character n-grams and word n-grams. 
+Second, we attempt to distinguish between {\it right} and {\it wrong} endings using style features, such as sentence length, character $n$-grams and word $n$-grams. 
 Our intuition is that the {\it right} endings use a different style compared to the {\it wrong} endings.
@@
 Our findings hint that the different writing tasks used to create the story cloze task---writing {\it right} and {\it wrong} endings---impose different writing styles on authors. 
-This is further discussed in \cite{Schwartz:2017}.
+This is further discussed in \newcite{Schwartz:2017}.
 
@@
 The shoes were \$300.
-She bought the shoes.}}	&{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \cline{2-2}
+She bought the shoes.}}	&{\color{blue}{She felt buyer's remorse after the purchase.}} \\ \cline{2-2}
 & {\color{red}{Kathy hated buying shoes.}} \\ \hline
@@
  %of the same story: 
- a {\color{forestgreen}{coherent}} ending (upper row) and a {\color{red}{incoherent}} one (bottom row).
+ a {\color{blue}{coherent}} ending (upper row) and a {\color{red}{incoherent}} one (bottom row).
 }
@@
 
-\paragraph{Language Model Features.}
+\paragraph{Language model features.}
 %% take the RLM paragraph from the paper
-We experiment with state-of-the-art text comprehension models, specifically an LSTM \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \newcite{mikolov2010recurrent}).
+We experiment with state-of-the-art text comprehension models,
+specifically an LSTM \cite{hochreiter1997long} recurrent neural
+network language model (RNNLM; \nocite{mikolov2010recurrent}Mikolov et
+al., 2010).
 Our RNNLM is used to generate two different probabilities:
@@
 
-\paragraph{Stylistic Features.}
+\paragraph{Stylistic features.}
 We hypothesize that {\it right} and {\it wrong} endings might be distinguishable using style features.
@@
 We add the following classification features to capture style differences between the two endings. 
-These features are computed on the story endings alone ({\it right} or {\it wrong}), and do not consider, neither at train nor at test time, the first four (shared) sentences of each story.
+These features are computed on the story endings alone ({\it right} or {\it wrong}), and do not consider, either at train nor at test time, the first four (shared) sentences of each story.
 \begin{itemize}
 \item\textit{\textbf{Length}.} The number of words in the sentence.
-\item\textit{\textbf{Word n-grams.}} We use sequences of 1-5 words. Following \cite{Tsur:2010,Schwartz:2013}, we distinguish between high frequency and low frequency words. 
-Specifically, we replace content words, which are often low frequency, with their part-of-speech tags (Nouns, Verbs, Adjectives and Adverbs).
-\item\textit{\textbf{Character n-grams.}} Character n-grams are useful features in the detection of author style \cite{Stamatatos:2009} or language identification \cite{lui2011cross}.
+\item\textit{\textbf{Word $n$-grams.}} We use sequences of 1--5
+  words. Following \newcite{Tsur:2010} and \newcite{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
+Specifically, we replace content words, which are often low frequency, with their part-of-speech tags (Nouns, Verbs, Adjectives, and Adverbs).
+\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are useful features in the detection of author style \cite{Stamatatos:2009} or language identification \cite{lui2011cross}.
 We use character 4-grams.
@@
 We then use TensorFlow\footnote{\url{www.tensorflow.org}} to train the RNNLM using a single-layer LSTM of hidden dimension 512.
-We use the ROC Stories for training, setting aside 10\% for validation of the language model.\footnote{We train on both the Spring 2016 and the Winter 2017 datasets, a total of roughly 100K stories}
+We use the ROC Stories for training, setting aside 10\% for validation of the language model.\footnote{We train on both the Spring 2016 and the Winter 2017 datasets, a total of roughly 100K stories.}
 We replace all words occurring less than 3 times by a special out-of-vocabulary character, yielding a vocabulary size of 21,582.
@@
   or an exclamation mark, so we do not add a \textsc{stop} symbol.} 
- We keep n-gram (character or word) features that occur at least five times in the training set.
-All stylistic feature values are normalized to [0-1].
-For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
+ We keep $n$-gram (character or word) features that occur at least five times in the training set.
+All stylistic feature values are normalized to [0, 1] \nascomment{the
+  range [0, 1] or the two values \{0, 1\}?}
+For the part-of-speech features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
 The total number of features used by our system is 7,651.
@@
 %{tbmihaylov (shared task)} & 0.711\\ \hline\hline
-{RNNLM Features}		& 0.677 \\ 
+{RNNLM features}		& 0.677 \\ 
 {Stylistic features} & {0.724} \\ 
@@
 we hypothesize that the different writing tasks---writing a {\it right} and a {\it wrong} ending---impose a different style on the authors, which is expressed in the different style adopted in each of the cases.
-The reader is referred to \cite{Schwartz:2017} for more details and discussion.
+The reader is referred to \newcite{Schwartz:2017} for more details and discussion.
 
 \section{Conclusion}
-This paper described the university of Washington NLP group submission to the LSDSem 2017 Shared Task. 
+This paper described University of Washington NLP's submission to the LSDSem 2017 Shared Task. 
 Our system leveraged both neural language model features and  stylistic features, achieving $75.2\%$ accuracy on the classification task.
+
+\section*{Acknowledgments}
+The authors thank the shared task organizers and anonymous reviewers
+for feedback.  \nascomment{anyone else} This research was supported in
+part by the Allen Institute for Artificial Intelligence and in part by
+DARPA under the Communicating with Computers program.
 

### 2017-02-16 docs/shared_task_paper_camera_ready.tex
Camera ready style changes

@@
 \documentclass[11pt]{article}
-\usepackage{eacl2017}
+\usepackage{authblk}
 \usepackage{times}
@@
 \usepackage{multirow}
+\usepackage{eacl2017}
 
@@
 \newcommand{\com}[1]{}
+\newcommand{\resolved}[1]{}
 \definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
@@
 
+\com{
 \author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
@@
   }
+  }
 
+\author[1,2]{\bf Roy Schwartz}
+\author[1]{\bf Maarten Sap}
+\author[1]{\bf Ioannis Konstas}
+\author[1]{\bf Leila Zilles}
+\author[1]{\bf Yejin Choi}
+\author[1]{\bf Noah A.~Smith}
+\affil[1]{Computer Science \& Engineering, University of Washington, Seattle, WA 98195, USA}
+\affil[2]{Allen Institute for Artificial Intelligence, Seattle, WA 98103, USA}
+\affil[  ]{\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}
 \date{}
@@
 We add the following classification features to capture style differences between the two endings. 
-These features are computed on the story endings alone ({\it right} or {\it wrong}), and do not consider, either at train nor at test time, the first four (shared) sentences of each story.
+These features are computed on the story endings alone ({\it right} or {\it wrong}), and do not consider, either at train or at test time, the first four (shared) sentences of each story.
 \begin{itemize}
@@
  We keep $n$-gram (character or word) features that occur at least five times in the training set.
-All stylistic feature values are normalized to [0, 1] \nascomment{the
-  range [0, 1] or the two values \{0, 1\}?}
+All stylistic feature values are normalized to the range [0, 1] \resolved{\nascomment{the
+  range [0, 1] or the two values \{0, 1\}?}}
 For the part-of-speech features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
@@
 
-\bibliography{acl2017}
+\bibliography{eacl2017}
 \bibliographystyle{eacl2017}

### 2017-02-16 docs/shared_task_paper_camera_ready.tex
Camera ready style changes 2

@@
 The authors thank the shared task organizers and anonymous reviewers
-for feedback.  \nascomment{anyone else} This research was supported in
+for feedback.\resolved{\nascomment{ anyone else}} This research was supported in
 part by the Allen Institute for Artificial Intelligence and in part by

### 2017-03-13 docs/acl_rebuttal.txt
acl_rebuttal.txt

We thank all reviewers for their insightful comments.

R1 - 
a. this paper was originally submitted to a different track, but has probably found its way to discourse and pragmatics. Although the stylometry (which we build on here) and discourse literature vary substantially, running discourse analysis seems very relevant here. We will definitely consider it for future work.

b. We believe the target readers for this paper should be anyone interested in stylometry, in cognition and NLP, as well as also anyone designing novel NLP tasks, or working on existing machine reading tasks.

R2 - Thank you for your comments. See general discussion.

R3 - the numbers below relate to the question numbers in R3's review.

(1) We did not sub-sample the ROC story corpus, but took the dataset as is, as well as the terminology from the original paper. Specifically, (a) From Mostafazadeh et al. (2016): 282 authors generated the story cloze task, with an 47.8 endings per author. (b) the "coherent" and "neutral" selection criteria referred to by R3 were done in the original paper, and (c) yes, we assume that the "original" and "right" endings were written by different authors (this was hinted at in the Mostafazadeh et al. paper).

(2) Figure 1 is meant to give the reader a flavor of the characteristics of the data, so we hand picked a few of the interesting words and POS tags which are frequent, but not necessarily the most frequent ones. See additional discussion on style in the general response.

(3) We believe the issues we point out to in this paper with respect to the ROC story corpus are general and should be taken into consideration when designing new NLP tasks or datasets. If accepted, we will clarify section 8.

(4) Lines 209-217 discuss previous efforts that applied state-of-the-art models on the task and got very low results. This could hint that qualitatively better methods are required to successfully solve the task (lines 217-219). One of the key findings of this paper is that our simple model yields much better results on the task, which sheds important light on this dataset.

GENERAL RESPONSE TO COMMENTS

-- We realize the term "style" might be a bit vague. We generally treat style as choice of words that do not necessarily reflect content. These include the choice of function words, punctuation and language patterns, all well-known style markers in areas such as authorship, age and gender detection.

-- The features reported in the paper are the only ones we experimented with. The choice of character 4-grams comes from their prominence in fields such as authorship attribution. We did try experimenting with character 5-grams as well, but didn't see any gain on our development set.

### 2017-03-14 docs/acl_rebuttal.txt
Noah

@@
 
-R1 - 
-a.
-this paper was originally submitted to a different track, but has probably found its way to discourse and pragmatics.
-Although the stylometry (which we build on here) and discourse literature vary substantially, running discourse analysis seems very relevant here.
-We will definitely consider it for future work.
+R1 - We agree that running discourse analysis would be an interesting direction for future work!
+We were drawn to features from computational styolmetry because they are cheap and don't rely on tools like discourse parsers, which might not work well outside the domains of the RST and Penn Discourse treebanks.
+(We actually aren't sure exactly how our paper found its way to the discourse and pragmatics track; please keep this in mind.)
 
-b.
-We believe the target readers for this paper should be anyone interested in stylometry, in cognition and NLP, as well as also anyone designing novel NLP tasks, or working on existing machine reading tasks.
+R1 - The paper targets designers of NLP tasks as well as those working on machine reading tasks.
+In addition, we think the findings will interest researchers of style/stylometry methods and at the junction of cognition and NLP.
 
-R2 - Thank you for your comments. See general discussion.
+R2 - Thanks for the feedback; please see general discussion.
 
-R3 - the numbers below relate to the question numbers in R3's review.
-
-(1) We did not sub-sample the ROC story corpus, but took the dataset as is, as well as the terminology from the original paper.
+R3 - We did not sub-sample the ROC story corpus, but took the dataset as is, as well as the terminology from the original paper .
 Specifically, (a) From Mostafazadeh et al.
 (2016): 282 authors generated the story cloze task, with an 47.8 endings per author.
-(b) the "coherent" and "neutral" selection criteria referred to by R3 were done in the original paper, and (c) yes, we assume that the "original" and "right" endings were written by different authors (this was hinted at in the Mostafazadeh et al.
+(b) The "coherent" and "neutral" selection criteria referred to by R3 were done in the original paper.
+(c) Yes, we assume that the "original" and "right" endings were written by different authors (this was hinted at in the Mostafazadeh et al.
 paper).
 
-(2) Figure 1 is meant to give the reader a flavor of the characteristics of the data, so we hand picked a few of the interesting words and POS tags which are frequent, but not necessarily the most frequent ones.
+(2) Figure 1 is meant to give the reader a flavor of the characteristics of the data, so we handpicked a few of the interesting words and POS tags which are frequent, but not necessarily the most frequent ones.
 See additional discussion on style in the general response.
@@
 
--- We realize the term "style" might be a bit vague.
-We generally treat style as choice of words that do not necessarily reflect content.
-These include the choice of function words, punctuation and language patterns, all well-known style markers in areas such as authorship, age and gender detection.
+- We agree that the term "style" is vague.
+Following work in authorship and age/gender detection, we generally treat style as word choices that do not necessarily reflect content, though this can be hard to disentangle.
+Well-known choices conventionally include the choice of function words, punctuation, and language patterns.
 
--- The features reported in the paper are the only ones we experimented with.
-The choice of character 4-grams comes from their prominence in fields such as authorship attribution.
-We did try experimenting with character 5-grams as well, but didn't see any gain on our development set.
+-- The features reported in the paper are the only ones we experimented with, with the exception of character 5-grams, which didn't show a gain on development data and were discarded.
+The choice of character 4-grams comes from their use in authorship attribution and similar problems.

### 2017-03-14 docs/acl_rebuttal.txt
Noah

@@
 
-(2) Figure 1 is meant to give the reader a flavor of the characteristics of the data, so we handpicked a few of the interesting words and POS tags which are frequent, but not necessarily the most frequent ones.
+R3 - Figure 1 is meant to give the reader a flavor of the characteristics of the data, so we handpicked a few of the interesting words and POS tags which are frequent, but not necessarily the most frequent ones.
 See additional discussion on style in the general response.
 
-(3) We believe the issues we point out to in this paper with respect to the ROC story corpus are general and should be taken into consideration when designing new NLP tasks or datasets.
+R3 - We believe the issues we point out to in this paper with respect to the ROC story corpus are general and should be taken into consideration when designing new NLP tasks or datasets.
 If accepted, we will clarify section 8.
 
-(4) Lines 209-217 discuss previous efforts that applied state-of-the-art models on the task and got very low results.
+R3 - Lines 209-217 discuss previous efforts that applied state-of-the-art models on the task and got very low results.
 This could hint that qualitatively better methods are required to successfully solve the task (lines 217-219).
@@
 - We agree that the term "style" is vague.
-Following work in authorship and age/gender detection, we generally treat style as word choices that do not necessarily reflect content, though this can be hard to disentangle.
+Following work in authorship and age/gender detection, we generally treat style as word choices that do not necessarily reflect content, though this can admittedly be hard to disentangle.
 Well-known choices conventionally include the choice of function words, punctuation, and language patterns.
 
--- The features reported in the paper are the only ones we experimented with, with the exception of character 5-grams, which didn't show a gain on development data and were discarded.
+- The features reported in the paper are the only ones we experimented with, with the exception of character 5-grams, which didn't show a gain on development data and were discarded.
 The choice of character 4-grams comes from their use in authorship attribution and similar problems.

### 2017-03-14 docs/acl_rebuttal.txt
Noah
rebuttal v3 roy

@@
 
-R3 - We did not sub-sample the ROC story corpus, but took the dataset as is, as well as the terminology from the original paper .
+R3 - We did not sub-sample the ROC story corpus, but took the dataset as is, as well as the terminology from the original paper.
 Specifically, (a) From Mostafazadeh et al.
-(2016): 282 authors generated the story cloze task, with an 47.8 endings per author.
+(2016): 282 authors generated the story cloze task, with 47.8 endings per author on average.
 (b) The "coherent" and "neutral" selection criteria referred to by R3 were done in the original paper.
@@
 The choice of character 4-grams comes from their use in authorship attribution and similar problems.
+
+- Thanks for the clarification suggestions; we will use the additional page to address them.

### 2017-03-15 docs/acl_rebuttal.txt
rebuttal final version (Roy)

@@
 R1 - We agree that running discourse analysis would be an interesting direction for future work!
-We were drawn to features from computational styolmetry because they are cheap and don't rely on tools like discourse parsers, which might not work well outside the domains of the RST and Penn Discourse treebanks.
+We were drawn to features from computational stylometry because they are cheap and don't rely on tools like discourse parsers, which might not work well outside the domains of the RST and Penn Discourse treebanks.
 (We actually aren't sure exactly how our paper found its way to the discourse and pragmatics track; please keep this in mind.)
@@
 (2016): 282 authors generated the story cloze task, with 47.8 endings per author on average.
-(b) The "coherent" and "neutral" selection criteria referred to by R3 were done in the original paper.
+(b) The "coherent" and "neutral" selection criteria referred to by R3 were introduced in the original paper.
 (c) Yes, we assume that the "original" and "right" endings were written by different authors (this was hinted at in the Mostafazadeh et al.
@@
 R3 - Figure 1 is meant to give the reader a flavor of the characteristics of the data, so we handpicked a few of the interesting words and POS tags which are frequent, but not necessarily the most frequent ones.
-See additional discussion on style in the general response.
+See additional discussion on style features in the general response.
 

### 2017-04-02 docs/language_constraint_conll.tex
V1 of CoNLL + EMNLP versions

--- 2017-02-07 docs/language_constraint.tex
@@
 \usepackage{times}
+\usepackage{multirow}
 \usepackage{latexsym}
@@
 \usepackage{tikz}
+
+\pgfplotsset{compat=1.11,
+    /pgfplots/ybar legend/.style={
+    /pgfplots/legend image code/.code={%
+       \draw[##1,/tikz/.cd,yshift=-0.25em]
+        (0cm,0cm) rectangle (3pt,0.8em);},
+   },
+}
 
@@
 
-\renewcommand{\ms}[1]{}
-\renewcommand{\roy}[1]{}
+\renewcommand{\roy}[1]{{\color{orange}[#1 --rs]}}
+
+%\renewcommand{\ms}[1]{}
+%\renewcommand{\roy}[1]{#1}
+%\renewcommand{\roy}[1]{}
 \renewcommand{\nascomment}[1]{}
@@
 We show that a simple linear classifier informed with stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
-In addition, our style-based classifier establishes a new state-of-the-art result on the story cloze challenge, substantially higher than previous results based on deep learning models. 
+%\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
+\roy{In addition, our style-based classifier's performance on the story cloze challenge is comparable to state-of-the-art results.} 
 %Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
@@
 \begin{table}[!t]
-\begin{tabular}{|p{1.6cm}|p{5.3cm}|} \hline
-{\bf Type} & {\bf Example} \\ \hline
-{\color{blue}{Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
-{\color{forestgreen}{Coherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
-{\color{red}{Incoherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
+%\begin{tabular}{|p{4.8cm}|p{2.1cm}|} \hline
+\begin{tabular}{|p{4.5cm}|p{2.4cm}|} \hline
+{\bf Story Prefix} & {\bf Ending} \\ \hline
+My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	& {\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
+\multirow{2}{4.5cm}{Joe went to college for art.
+He graduated with a degree in painting.
+He couldn't find a job.
+He then responded to an ad in the paper.} & 	{\color{forestgreen}{Then he got hired.}} \\ \cline{2-2}
+& {\color{red}{Joe hated pizza.}} \\ \hline
 \end{tabular}
@@
 story cloze task\nascomment{cite the challenge?  a reader may
-  not realize that there is a shared task on this}\roy{Maybe ``challenge'' was not the right term here.
+  not realize that there is a shared task on this}\resolved{\roy{Maybe ``challenge'' was not the right term here.
 We basically mean the story cloze task.
-The shared task was the original task w/o any modification, so I am not referring to it specifically here}.
- Adapting our classifier to the task, we obtain 72.4\% accuracy, a
- 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}.
+The shared task was the original task w/o any modification, so I am not referring to it specifically here}}.
+ Adapting our classifier to the task, we obtain 72.4\% accuracy, \com{a
+ 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}}\roy{only 2\% below state-of-the-art results}.
 We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
-Our final model that combines context with stylistic features achieves
-75.2\%---an additional 2.8\% gain, 15.3\% better than the best
-published result.
+Our final model that combines context with stylistic features achieves \roy{new state-of-the-art results---}
+75.2\%---an additional 2.8\% gain\com{, 15.3\% better than the best
+published result}.
 
@@
 Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}.
-Both endings are required to complete the story using one of the characters in the story context. 
+Both endings were required to complete the story using one of the characters in the story context. 
 Additionally,  the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
@@
 %as a machine reading task, 
-as a commonsense story understanding task, 
-as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
-
-Interestingly, at the time of this submission, 10 months after the
-task was first introduced, the published benchmark on this task is
-still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
+as a commonsense story understanding task\com{, 
+as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017),} and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
+
+Interestingly, \roy{until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%}\com{at the time of this submission, 10 months after the
+task was first introduced, the published benchmark on this task is still below 60\% \cite{Salle:2016}}.\footnote{The LSDSem 2017 shared
   task website
@@
 are still unpublished along with the underlying methodology.}
-This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or shorter period of time.
+This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or much shorter periods of time.
 This suggests that this task is challenging and that high performance is hard to achieve.
+\roy{In this paper, we show that this is not necessarily the case, by demonstrating that a simple linear classifier informed with style features reaches near state-of-the-art results on the task---72.4\%.}
  \resolved{\yc{SQuAD was officially published in Nov 2016.
@@
 First, the training set for the task (ROC Stories corpus) is not a
-training sample in the usual sense,\footnote{I.e., the training
+training set in the usual sense,\footnote{I.e., the training
   instances are not drawn from a population similar to the one that future
@@
 \item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
-We use character 4-grams.
+We use character $4$-grams.\footnote{\roy{Experiments with $5$-grams on our development set reached similar performance.}}
 \end{itemize}
@@
 As there are far more {\it original} instances than {\it new}
-instances, we randomly select the same number of \emph{original}
+instances, we randomly select five  {\it original} sets, each with the same number of
 instances  \resolved{\nascomment{(give the number in parentheses, for train/dev/test)} }as we have
 \emph{new} instances (3,366 training endings, 374 development endings, and 3,742 test endings).
-We randomly sample 5 {\it original} sets and repeat the classification experiments.
+%We randomly sample 5 {\it original} sets and repeat the classification experiments.
 We report the average classification result.
 
+\roy{\paragraph{Experiment 3: original/wrong endings.}
+For completeness, we measure the extent to which our classifier can discriminate between {\it original} and {\it wrong} endings.
+We replicate Experiment 2, this time replacing {\it right} endings with {\it wrong} ones.}
+
 \paragraph{Experimental setup.}
-In both experiments, we add a \textsc{start} symbol at the beginning
-of each sentence.\footnote{Virtually all sentences end with a period
+In all experiments, we add a \textsc{start} symbol at the beginning
+of each sentence.\footnote{99\% of all sentences end with a period
   or an exclamation mark, so we do not add a \textsc{stop} symbol.}
@@
 
-\isectionb{Results}
-\tabref{results} shows our results.  In both experiments,
+\paragraph{Results.}
+\tabref{results} shows our results.  In all experiments,
 our model achieves performance well above what would be expected under
@@
 strong evidence that the authors' style was affected by the writing task they
-were given to perform.  We further applied the model to a third task,
-\emph{original} vs.~\emph{wrong (new)} endings, and even stronger
-differences were apparent to the model, allowing over 75\% accuracy.
+were given to perform.\com{ On our third task, which compared 
+\emph{original} vs.~\emph{wrong (new)} endings, even stronger
+differences were apparent to the model, allowing over 75\% accuracy.}
 
@@
 \end{center}
-\caption{\label{results}Results of  experiments 1 ({\it right
-    vs.~wrong}) and 2 ({\it original vs.~right (new)}). 
-The bottom row shows an additional experiment which classifies {\it
-  original vs.~wrong (new)} endings.
+\caption{\label{results}Results of  experiments 1 ({\it right vs.~wrong}), 2 ({\it original vs.~right (new)}) and 3 ({\it
+  original vs.~wrong (new)} endings).
 In all cases, our setup implies a 50\% random baseline.}
@@
 
-\paragraph{Story cloze task.}
+\subsection{Story cloze task.}
 The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
@@
 \tabref{cloze_results} shows our results on the story cloze test
-set. Our classifier obtains 72.4\% accuracy, 12.5\% (absolute) higher than the
-published state-of-the-art result on the task \cite{Salle:2016}\resolved{\nascomment{cite that here}}.
+set. Our classifier obtains 72.4\% accuracy, \roy{only 2\% lower than state-of-the-art results, and equal or higher to all other published results}\com{12.5\% (absolute) higher than the
+published state-of-the-art result on the task \cite{Salle:2016}}\resolved{\nascomment{cite that here}}.
 Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
@@
 % No other information other than the name of the groups and their results is available.
-
+\com{
 \begin{table}[!t]
@@
 \end{table}
+}
+
+\begin{table}[!t]
+\begin{center}
+\begin{tabular}{|l|r|} \hline
+{\bf Model} & {\bf Acc.} \\ \hline
+{DSSM} \cite{Mostafazadeh:2016} & 0.595 \\ 
+{ukp} \cite{Mihaylov:2017} & 0.711\\ 
+{tbmihaylov} \cite{Mihaylov:2017} & 0.724\\ 
+{cogcomp}  & 0.744 \\ \hline\hline
+{RNN}		& 0.677 \\ 
+$\dagger${Ours} & {0.724} \\ 
+{\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
+Human judgment & 1.000 \\ \hline
+\end{tabular}
+\end{center}
+\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}Results on the test set of the  story cloze task.\com{
+The upper block shows published results, }
+The middle block are our results.
+{\it cogcomp} results and human judgement scores are taken from \cite{Mostafazadeh:2017}.
+%RNN is our implementation. 
+Methods marked with ($\dagger$) do not use the story context in order to make a prediction. 
+ \resolved{\nascomment{I added 0s to ``Niko'' result
+  and ``human''
+  so sig. digits would line up.  if we don't have sig digits for some
+  of them, make the zeros white so the numbers line up.  where did the
+human judgments come from?  those are not mentioned in our text anywhere!}
+}}
+\end{table}
 
@@
 information between the story and the ending, under the language
-model.\nascomment{added this to replace the hedging that was here before}\roy{We actually also use the RNNLM features in log space. Add that in the next paragraph.}}
+model.\nascomment{added this to replace the hedging that was here before}\resolved{\roy{We actually also use the RNNLM features in log space. Add that in the next paragraph.}}}
 
@@
 We retrain our linear  model with the new feature set, and gain 2.8\%
-absolute, reaching 75.2\% (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result).\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
+absolute, reaching 75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}\roy, a new-state-of-the-art result for the task.\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
 These results indicate that context-ignorant style features can be used to obtain high
@@
 positive and negative coefficients in the logistic regression
-classifier in both Experiments 1 and 2, an  approach widely used  as a
+classifier in Experiments 1 and 2, an approach widely used  as a
 method of extracting the most salient features
@@
 indication for an  {\it original} ending. 
-This suggests that authors are more likely to show or evoke enthusiasm when writing their own text compared to ending an existing task.
+This suggests that authors are more likely to show or evoke enthusiasm when writing their own text compared to ending an existing text.
 
@@
 Our findings suggest that careful attention must be paid to instructions given to authors, especially in unnatural tasks such as writing a {\it wrong} ending. 
-One way to avoid such problems is by using shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
+One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
 A different approach is to use naturally occurring text, as used in recent machine reading tasks (see \secref{Related}). 

### 2017-04-02 docs/language_constraint_emnlp.tex
V1 of CoNLL + EMNLP versions

--- 2017-04-02 docs/language_constraint_conll.tex
@@
 \documentclass[11pt,a4paper]{article}
-\usepackage[hyperref]{acl2017}
+\usepackage[hyperref]{emnlp2017}
 \usepackage{times}
@@
 \newcommand{\isectionb}[1]{\section{#1}\label{ssec:#1}}
+\newcommand{\isubsection}[2]{\subsection{#1}\label{ssec:#2}}
+\newcommand{\isubsectionb}[1]{\subsection{#1}\label{ssec:#1}}
 \newcommand{\com}[1]{}
 \newcommand{\resolved}[1]{}
+\newcommand{\shortv}[1]{}
+
 % Editing macros
@@
 %\renewcommand{\ms}[1]{}
-%\renewcommand{\roy}[1]{#1}
+\renewcommand{\roy}[1]{#1}
 %\renewcommand{\roy}[1]{}
@@
 %We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
-We show that a simple linear classifier informed with stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
+We show that a  linear classifier informed with stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
 %\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
-\roy{In addition, our style-based classifier's performance on the story cloze challenge is comparable to state-of-the-art results.} 
+\roy{In addition, our style-based classifier also performs on a par with state-of-the-art models on the story cloze task.} 
 %Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
@@
 by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
-as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
-In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
+as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} like sentiment \cite{Davidov:2010}\shortv{, sarcasm \cite{Tsur:2010},} and deception \cite{Feng:2012}.  
+In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, as
 different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.
 
+\shortv{
 \begin{table}[!t]
@@
 %\end{center}
-\end{table}
+\end{table}}
 
@@
 As a case study, we present experiments based on 
-the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
-In this task, \com{crowdsourced }authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
+the \shortv{recently introduced ROC }story cloze task \cite{Mostafazadeh:2016}. 
+\roy{In this task, whose goal is to serve as a commonsense challenge for NLP \shortv{and AI }research, a system is presented with two short stories that differ only in their last sentence: one ending makes the entire story {\it coherent} while the other makes it {\it incoherent}.
+The system then decides which is the coherent one.}
+\shortv{In this task, \com{crowdsourced }authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
 %Following, 
@@
 and asked to write two contrasting story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
-Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP and AI research. 
-\tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.
+Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP \shortv{and AI }research. }
+\shortv{\tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.}
 
@@
 
-While the story cloze task was originally designed to be a story understanding challenge, 
-its annotation process introduced three variants of the same writing task: writing an {\it original}, {\it right}, or {\it wrong} ending to a short story.
-In this paper, we show that a linear classifier informed by stylistic features can distinguish among the different endings to a large degree, even without looking at the story context (64.5--75.6\% binary classification results).
+\shortv{While the story cloze task was originally designed to be a story understanding challenge, }
+Interestingly, the story cloze task annotation process introduced three variants of the same writing task: writing an ending to a short story (see \secref{ROC_Story}).
+In this paper, we show that a linear classifier informed by stylistic features can distinguish among the different variants to a large degree, even without looking at the story context\shortv{ (64.5--68.5\% binary classification results)}.
 
@@
 
-In order to further validate our method, we also directly tackle the
+In order to further validate our method, we directly tackle the
 story cloze task\nascomment{cite the challenge?  a reader may
@@
 We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
-Our final model that combines context with stylistic features achieves \roy{new state-of-the-art results---}
-75.2\%---an additional 2.8\% gain\com{, 15.3\% better than the best
-published result}.
+Our final model that combines context with stylistic features achieves an additional 2.8\% gain--75.2\%,  a new state-of-the-art result.\com{, 15.3\% better than the best
+published result}
 
@@
 %both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
-Third, we establish a new state-of-the-art result on the commonsense story cloze challenge.
+Third, we establish a new state-of-the-art result on the \shortv{commonsense }story cloze task.
 
@@
 
-\isection{Background: The Story Cloze Task}{ROC_Story}
+\isubsection{Background: The Story Cloze Task}{ROC_Story}
 To understand how different writing tasks affect writing style, 
@@
 The ROC story corpus consists of 49,255 five-sentence commonsense
-stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently,
+stories, collected on Amazon Mechanical Turk (AMT).\shortv{\footnote{Recently,
   an additional 53K stories were released, which results in roughly
-  100K stories.}
+  100K stories.}}
 Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
-To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
+\shortv{To collect a broad spectrum of commonsense knowledge,  n}No subject was imposed for the stories,
 which resulted in a wide range of different topics.
@@
 A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
-Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}.
+Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}\shortv{.
 Both endings were required to complete the story using one of the characters in the story context.
-Additionally,  the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
-
-The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness by additional AMT workers.
+Additionally,  }.
+Importantly, both endings were required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
+
+\shortv{The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness by additional AMT workers.
 Only stories rated as simultaneously coherent with a {\it right} ending and neutral with a {\it wrong} ending were selected for the task. 
-It is worth noting that workers rated the stories as a whole, not only the endings.
-
-Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it story cloze task}. 
-The task is simple:  given a pair of stories that differ only in their endings, the system decides which ending is {\it right} and which is {\it wrong}. 
+It is worth noting that workers rated the stories as a whole, not only the endings.}
+
+Based on the new stories, \shortv{\citet{Mostafazadeh:2016} proposed }the {\it story cloze task} was proposed\shortv{. 
+The task is simple}:  given a pair of stories that differ only in their endings, the system decides which ending is {\it right} and which is {\it wrong}. 
 %The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
-The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are not included in the training set).\resolved{\roy{added {\it not} here}}
-The task was suggested as an extensive evaluation framework:
+The \shortv{official }training data contains  the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a \shortv{different }set of original stories not included in the training set).\resolved{\roy{added {\it not} here}}
+The task was suggested as \shortv{an extensive evaluation framework:
 %as a machine reading task, 
-as a commonsense story understanding task\com{, 
+as }a commonsense story understanding task\com{, 
 as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017),} and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
 
-Interestingly, \roy{until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%}\com{at the time of this submission, 10 months after the
-task was first introduced, the published benchmark on this task is still below 60\% \cite{Salle:2016}}.\footnote{The LSDSem 2017 shared
+Interestingly, \roy{until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%.}\com{at the time of this submission, 10 months after the
+task was first introduced, the published benchmark on this task is still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
   task website
@@
 \nascomment{leave empty for now}}, which
-are still unpublished along with the underlying methodology.}
-This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or much shorter periods of time.
+are still unpublished along with the underlying methodology.}} This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}\shortv{, LAMBADA \cite{Paperno:2016}} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over much shorter periods of time.
 This suggests that this task is challenging and that high performance is hard to achieve.
-\roy{In this paper, we show that this is not necessarily the case, by demonstrating that a simple linear classifier informed with style features reaches near state-of-the-art results on the task---72.4\%.}
+\roy{In this paper, we show that this is not necessarily the case, by demostrating that a simple linear classifier informed with style features reaches near state-of-the-art results for the task---72.4\%.}
  \resolved{\yc{SQuAD was officially published in Nov 2016.
@@
 or that we should change ``similar period of time'' to ``similar or shorter period of time''?}}
-
+\shortv{
 In addition, \citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
@@
 Furthermore, Mostafazadeh et al.~implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
-These results suggest that real understanding of text is required in order to solve the task.
+These results suggest that real understanding of text is required in order to solve the task.}
 
 \paragraph{Different writing tasks in the story cloze task.}
-Several key design decisions make the task an interesting testbed for the purpose of this study.\resolved{\clinic{Which purpose?}}
+Several \shortv{key }design decisions make the task an interesting testbed for the purpose of this study.\resolved{\clinic{Which purpose?}}
 First, the training set for the task (ROC Stories corpus) is not a
 training set in the usual sense,\footnote{I.e., the training
-  instances are not drawn from a population similar to the one that future
+  instances are drawn from a different population than the one
   testing instances will be drawn from.%\roy{I added \textbf{not}
                                 %here, as otherwise it is confusing}
-}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
- \resolved{\yc{As far as I understand, this was intentional --- they didn't want
+}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones.\resolved{\yc{As far as I understand, this was intentional --- they didn't want
   people to pick up on random superfluous cues that can inevidently
@@
 facts here and just describe what they did without judgment.}}
-
 On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} samples, which serve as the positive samples in the development and test sets.
@@
 
-Finally, although the {\it right} and {\it wrong} sentences were generated by the same author, 
-the tasks for generating them were quite different: in one case, the author was asked to write a {\it right} ending, which would create a coherent five-sentence story along with the other four sentences.
-In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story.
+Finally,\shortv{ although the {\it right} and {\it wrong} sentences were generated by the same author,} 
+the tasks for generating the pairs of endings were quite different from each other: in one case, the author was asked to write a {\it right} ending, which would create a coherent five-sentence story along with the other four sentences.
+In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent \shortv{five-sentence }story.
  \resolved{In this work, we show that these differences are significant and
@@
 
+\shortv{
 \isection{Surface Analysis of the Story Cloze Task}{Surface}
@@
 %Then you can add the benchmark text below, and conclude that this indicates that this task is well designed and hard and the one hand, but might also point to potential disagreements between the train and the test data, which we highlight in this paper.}
+}
 
@@
 different writing constraints lead the authors to adopt different writing styles. 
-In order to answer these questions, we use simple methods that have been shown to be very effective for recognizing style (see \secref{Related}).
+In order to answer these questions, we use simple methods that have been shown to be very effective for recognizing style\shortv{ (see \secref{Related})}.
 We describe our model below.
@@
 Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
-We use the following style features.
-
-\begin{itemize}
-\item\textit{\textbf{Length}.} The number of words in the sentence.
-\item\textit{\textbf{Word $n$-grams.}} We use sequences of 1-5
-  words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
-Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their part-of-speech tags.
-\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
-We use character $4$-grams.\footnote{\roy{Experiments with $5$-grams on our development set reached similar performance.}}
-\end{itemize}
+We use the following style features: (a) \textit{\textbf{Length}.} The number of words in the sentence, 
+(b) \textit{\textbf{Word $n$-grams.}} Sequences of 1-5
+  words,\footnote{Following and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
+Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their POS tags.}
+and (c) \textit{\textbf{Character $n$-grams.}} \shortv{Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
+We use character $4$-grams}\roy{Sequences of 4 characters}.\footnote{\roy{Character $4$-grams are very common features in style detection \cite{Stamatatos:2009}.}}
 
@@
 the second  between {\it original} endings and new ({\it right}) endings.
-We describe both experiments below.
+\shortv{We describe both experiments below.}
 
 \paragraph{Experiment 1: right/wrong endings.}
-The goal of this experiment is to measure the extent to which  style features capture differences between the {\it right} and {\it wrong} endings.
+We measure the extent to which  style features capture differences between the {\it right} and {\it wrong} endings.
 As the story cloze task doesn't have a training corpus for the {\it
@@
 It is worth noting that our classification task is slightly different from the story cloze task. 
-Instead of classifying pairs of endings, one which is {\it right} and
-another which is {\it wrong}, our classifier decides about each ending
+Instead of classifying pairs of endings, \shortv{one which is {\it right} and
+another which is {\it wrong}, }our classifier decides about each ending
 individually, whether it is \emph{right} (positive instance) or
@@
 By ignoring the coupling between {\it right} and {\it wrong} pairs, 
-we are able to decrease the impact of author-specific style differences,
+we \shortv{are able to }decrease the impact of author-specific style differences,
 and focus on the difference between the styles accompanied with {\it right} and {\it wrong} writings.
@@
 
-Here the goal is to measure whether writing the ending as part of a
+Here we measure whether writing the ending as part of a
 story imposes different style compared to writing a new ({\it right}) ending to an existing story.
@@
 
+\shortv{
 \roy{\paragraph{Experiment 3: original/wrong endings.}
 For completeness, we measure the extent to which our classifier can discriminate between {\it original} and {\it wrong} endings.
-We replicate Experiment 2, this time replacing {\it right} endings with {\it wrong} ones.}
+We replicate Experiment 2, this time replacing {\it right} endings with {\it wrong} ones.}}
 
 \paragraph{Experimental setup.}
-In all experiments, we add a \textsc{start} symbol at the beginning
+\shortv{In both experiments, we add a \textsc{start} symbol at the beginning
 of each sentence.\footnote{99\% of all sentences end with a period
-  or an exclamation mark, so we do not add a \textsc{stop} symbol.}
+  or an exclamation mark, so we do not add a \textsc{stop} symbol.}}
 For computing our features, we keep $n$-gram (character or word) features that occur at least five times in the training set.
-All feature values are normalized to $[0, 1]$.
-For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{http://spacy.io/}}
-We use  Python's sklearn logistic regression implementation \cite{scikit-learn} with $L_2$
+All feature values are normalized to $[0, 1]$.\shortv{
+For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{http://spacy.io/}}}
+We use  Python's sklearn logistic regression implementation \shortv{\cite{scikit-learn} }with $L_2$
 regularization, performing grid search on the development set to
@@
 \paragraph{Results.}
-\tabref{results} shows our results.  In all experiments,
+\shortv{\tabref{results} shows our results.  }In both experiments,
 our model achieves performance well above what would be expected under
-chance (50\% by design).  Noting again that our model ignores the
+chance (50\% by design)\roy{: 64.5\% accuracy for Experiment 1, and 68.5\% for Experiment 2.}
+Noting again that our model ignores the
 story context (the preceding four sentences), our model is unable to
@@
 \end{tikzpicture}
-\caption{\label{results}Results of  experiments 1 and 2 (left two charts). 
-Rightmost graph shows a control experiment which classifies {\it
-  original} endings vs \textit{\textbf{wrong}}
+\caption{\label{results}Results of  experiments 1, 2 and 3. 
+\com{Rightmost graph shows a control experiment which classifies {\it
+  original} endings vs \textit{\textbf{wrong}}}
 endings. \nascomment{this is overkill.  I suggest replacing it with a
@@
 
+\shortv{
 \begin{table}[!t]
@@
 {\sl original vs. right} & 0.685 \\ \hline
-{\sl original vs. wrong} & 0.756 \\ \hline
+\shortv{{\sl original vs. wrong} & 0.756 \\ \hline}
 \end{tabular}
 \end{center}
-\caption{\label{results}Results of  experiments 1 ({\it right vs.~wrong}), 2 ({\it original vs.~right (new)}) and 3 ({\it
-  original vs.~wrong (new)} endings).
-In all cases, our setup implies a 50\% random baseline.}
+\caption{\label{results}Results of  experiments 1 ({\it right vs.~wrong}) and 2 ({\it original vs.~right (new)})\shortv{ and 3 ({\it
+  original vs.~wrong (new)} endings)}.
+In both cases, our setup implies a 50\% random baseline.}
 \end{table}
-
-\subsection{Story cloze task.}
+}
+\paragraph{Story cloze task.}
 The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
-In order to further estimate the quality of our classification results, we tackle the story cloze task using our classifier.
+In order to further estimate the quality of our \shortv{classification }results, we tackle the story cloze task\shortv{ using our classifier}.
 This classification task is more constrained than Experiment 1, as two
@@
 published state-of-the-art result on the task \cite{Salle:2016}}\resolved{\nascomment{cite that here}}.
-Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
+Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and \shortv{in fact }doesn't even consider the \shortv{first four sentences of the }story context in question.
 These numbers further support the claim that the styles of {\it right} and {\it wrong} endings are indeed very different.
@@
 % No other information other than the name of the groups and their results is available.
-\com{
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{|l|r|} \hline
-{\bf Model} & {\bf Acc.} \\ \hline
-$\dagger${DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
-$\dagger${LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
-%{Niko (shared task)}	& 0.700\\ 
-%{tbmihaylov (shared task)} & 0.711\\ \hline\hline
-$\dagger${RNN}		& 0.677 \\ 
-{\bf Ours} & {\bf 0.724} \\ 
-$\dagger${\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
-$\dagger$Human judgment & 1.000 \\ \hline
-\end{tabular}
-\end{center}
-\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}Results on the test set of the  story cloze task. 
-The upper block shows published results, 
-the middle block are our results.
-LexVec results are taken from \cite{Speer:2016}.
-%RNN is our implementation. 
-Human judgement scores are taken from \cite{Mostafazadeh:2016}.
-Methods marked with ($\dagger$) use the story context in order to make a prediction. 
- \resolved{\nascomment{I added 0s to ``Niko'' result
-  and ``human''
-  so sig. digits would line up.  if we don't have sig digits for some
-  of them, make the zeros white so the numbers line up.  where did the
-human judgments come from?  those are not mentioned in our text anywhere!}
-}}
-\end{table}
-}
 
@@
 {DSSM} \cite{Mostafazadeh:2016} & 0.595 \\ 
-{ukp} \cite{Mihaylov:2017} & 0.711\\ 
+{ukp} \cite{Bugert:2017} & 0.717\\ 
 {tbmihaylov} \cite{Mihaylov:2017} & 0.724\\ 
@@
 \end{center}
-\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}Results on the test set of the  story cloze task.\com{
+\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}Results on the \shortv{test set of the }story cloze task.\com{
 The upper block shows published results, }
 The middle block are our results.
-{\it cogcomp} results and human judgement scores are taken from \cite{Mostafazadeh:2017}.
+{\it cogcomp} results and human \shortv{judgement }scores are taken from \cite{Mostafazadeh:2017}.
 %RNN is our implementation. 
-Methods marked with ($\dagger$) do not use the story context in order to make a prediction. 
+Methods marked with ($\dagger$) do not use the story context\shortv{ in order} to make a prediction. 
  \resolved{\nascomment{I added 0s to ``Niko'' result
@@
 \paragraph{Combination with a neural language model.}
-We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed. 
-Specifically, we experiment with an LSTM-based \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
+We investigate whether our model can benefit from state-of-the-art text comprehension models\shortv{, for which this task was designed}. 
+We experiment with an LSTM\shortv{-based} \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
 %and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
-Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the story cloze task designers, and harnesses their ROC Stories training set, which consists of single-ending stories,
+Unlike the model in this paper\shortv{, which only considers the story endings}, this LM \shortv{follows the protocol suggested by the story cloze task designers, and }harnesses the \shortv{ROC Stories }story cloze training set, which consists of single-ending stories,
 as well as the story context for each pair of endings. 
-We show that adding our features to this powerful language model
-gives improvements over our classifier as well as the language
-model.  \resolved{\nascomment{reworded.  more important that our features help
+We show that adding our features to this powerful \shortv{language model}LM
+gives improvements over our classifier as well as the \shortv{language
+model}LM.  \resolved{\nascomment{reworded.  more important that our features help
   the language model, than the other way around!}}
 
-We train the RNNLM using a single-layer LSTM of hidden dimension 512.
-We use the ROC stories for training,\footnote{We use the extended, 100K stories corpus (see \secref{ROC_Story}).} setting aside 10\% for validation of the language model. 
-We replace all words occurring less than 3 times with a special
+\shortv{We train the RNNLM using a single-layer LSTM of hidden dimension 512.}
+\shortv{We use the ROC stories for training,\footnote{We use the extended, 100K stories corpus (see \secref{ROC_Story}).} setting aside 10\% for validation of the language model.}\shortv{We replace all words occurring less than 3 times with a special
 out-of-vocabulary character, yielding a vocabulary size of  21,582.
-Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
-Using the Adam optimizer \cite{kingma2014adam} and a learning rate of
-$\eta=.001$, we train to minimize cross-entropy. % minibatches of $50$ stories.
+Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. }
+We train the RNNLM using the Adam optimizer \cite{kingma2014adam} and a learning rate of
+$\eta=.001$, while \shortv{train to }minimizing cross-entropy. % minibatches of $50$ stories.
 % h=512, dropout rate of 60%, V=21582, 10% validation set
-
-To apply the language model to the classification problem, we select
-as \emph{right} the ending with the higher value of
+To apply \shortv{the RNNLM}it to the classification problem, we select
+as \emph{right} the ending with the higher value of\footnote{The intuition is that a \emph{right} ending should be unsurprising (to
+the model)
+given the four preceding sentences of the story (the numerator), controlling for the
+inherent surprisingness of the words in that ending (the denominator).}
 \begin{equation}
@@
 \end{equation}
-The intuition is that a \emph{right} ending should be unsurprising (to
-the model)
-given the four preceding sentences of the story (the numerator), controlling for the
-inherent surprisingness of the words in that ending (the denominator).
+\roy{Selecting endings based on the ratio in Equation~\ref{eq:ratio} achieves 67.7\% on the story cloze task\shortv{ (see
+\tabref{cloze_results})}.}
 
@@
 % Eval
-On its own, our neural language model performs moderately well on the story cloze test. 
+\shortv{On its own, our neural language model performs moderately well on the story cloze test. 
 %This is not surprising, as \citet{Mostafazadeh:2016} hinted  that
@@
 information between the story and the ending, under the language
-model.\nascomment{added this to replace the hedging that was here before}\resolved{\roy{We actually also use the RNNLM features in log space. Add that in the next paragraph.}}}
+model.\nascomment{added this to replace the hedging that was here before}\resolved{\roy{We actually also use the RNNLM features in log space. Add that in the next paragraph.}}}}
 
@@
 We retrain our linear  model with the new feature set, and gain 2.8\%
-absolute, reaching 75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}\roy, a new-state-of-the-art result for the task.\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
+absolute, reaching 75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}\roy, a new-state-of-the-art result\shortv{  for the task}.\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
 These results indicate that context-ignorant style features can be used to obtain high
@@
 
+\shortv{
 \isection{Further Analysis}{Ablation}
@@
 \end{table}
+}
 
@@
 \paragraph{The effect of writing tasks on mental states.}
-In this paper we have shown that giving a writer different writing tasks affects her writing style in easily detected ways.
+\shortv{In this paper we have shown that giving a writer different writing tasks affects her writing style in easily detected ways.
 Our results indicate that when authors are asked to write the last
-sentence of a five-sentence story, they will use different style to
+sentence of a short story, they will use different style to
 write a {\it right} ending compared to a {\it wrong} ending. We have
-also shown that writing the ending as part of one's own five-sentence story is very different than reading four sentences and then writing the fifth.
-Our findings hint that the nature of the writing task imposes a
-different mental state on the author, which is expressed in ways that can be observed using extremely simple automatic tools.
+also shown that writing the ending as part of one's own story is very different than reading a story prefix and then writing the ending.
+\shortv{Our findings hint that the nature of the writing task imposes a
+different mental state on the author, which is expressed in ways that can be observed using extremely simple automatic tools. }}
 
@@
 as writing emotional texts was observed to benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
-\citet{Campbell:2003} also showed that the health benefits of writing emotional text are accompanied by changes in writing style, mostly in the use of pronouns.
+\citet{Campbell:2003} also showed that the health benefits of writing emotional text are accompanied by changes in writing style\shortv{, mostly in the use of pronouns}.
 
@@
 Second, temporary changes, such as a romantic relationship \cite{Ireland:2011,Bowen:2016}, work collaboration \cite{Tausczik:2009,Gonzales:2009}, or negotiation \cite{Ireland:2014} may also affect writing style.
-Finally, writing style can also change from one sentence to another, for instance between positive and negative text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}.
+\shortv{Finally, writing style can also change from one sentence to another, for instance between positive and negative text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}.}
 
 This large body of work indicates a tight connection between writing
-tasks, mental states, and variation in writing style.
+tasks, mental states, and \shortv{variation in }writing style.
 This connection hints that the link discovered in this paper, between
@@
 involves differences in mental state. 
-Further investigation is required in order to further validate this hypothesis.
+Further investigation is required \shortv{in order to further}to validate this hypothesis.
 
 \paragraph{Design of NLP tasks.}
-Our study also provides important insights for the future design of NLP tasks. 
-The story cloze task was very carefully designed. Many factors, such
-as topic diversity and temporal and causal relation diversity,  were controlled for \cite{Mostafazadeh:2016}. 
-The authors also made sure each pair of endings was written by the
-same author, partly in order to avoid author-specific style effects.
- Nonetheless, despite these efforts, several significant style
+Our study  provides important insights for the future design of NLP tasks. 
+The story cloze task was very carefully designed, controlling for factors such
+as topic diversity and temporal and causal relation diversity.\com{,  were controlled for \cite{Mostafazadeh:2016}. }\shortv{The authors also made sure each pair of endings was written by the
+same author, partly in order to avoid author-specific style effects.}
+ Nonetheless\shortv{, despite these efforts}, several significant style
  differences can be found between the training and the test set, as well as between the positive and negative labels.
@@
 One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
-A different approach is to use naturally occurring text, as used in recent machine reading tasks (see \secref{Related}). 
+A different approach is to use naturally occurring text, as used in recent machine reading tasks \cite{hermann2015teaching}\shortv{ (see \secref{Related})}. 
 %However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
-One way to avoid the inherent biases people have when writing is to 
-have them rate sentences from naturally occurring text by parameters
+One way to avoid inherent writing biases is to 
+have annotators rate sentences from naturally occurring text by parameters
 such as coherence (or, very differently, the level of surprise),
-rather than asking them to generate new text.
+rather than asking them to generate  text.
 
@@
 
+\shortv{
 \isection{Related Work}{Related}
@@
  \resolved{\nascomment{dropped the train/test discrepancy here}}
-
+}
 \isectionb{Conclusion}
@@
  and the difference between writing a coherent and an incoherent story ending.
-In both cases, a simple linear model reveals measurable differences in writing styles, %that different styles are imposed.
+In both cases, a simple \shortv{linear }model reveals measurable differences in writing styles, %that different styles are imposed.
 %The different styles allow our style detection 
@@
 \bibliography{acl2017}
-\bibliographystyle{acl_natbib}
+\bibliographystyle{emnlp_natbib}
 

### 2017-04-09 docs/language_constraint_emnlp.tex
V2 of CoNLL + EMNLP versions (Roy)

@@
 \newcommand{\shortv}[1]{}
+\newcommand{\supl}[1]{}
 
@@
 %\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
-\roy{In addition, our style-based classifier also performs on a par with state-of-the-art models on the story cloze task.} 
+\roy{In addition, our style-based classifier performs on a par with state-of-the-art models on the story cloze task.} 
 %Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
@@
 In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, as
-different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.
+different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purpose of this paper, \emph{style} is defined as content-agnostic writing characteristics, e.g., sentence length.}}
 
@@
 \begin{table}[!t]
+\small
 %\begin{tabular}{|p{4.8cm}|p{2.1cm}|} \hline
-\begin{tabular}{|p{4.5cm}|p{2.4cm}|} \hline
+\begin{tabular}{|p{4.6cm}|p{2.3cm}|} \hline
 {\bf Story Prefix} & {\bf Ending} \\ \hline
-My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	& {\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
-\multirow{2}{4.5cm}{Joe went to college for art.
+John went for a walk.	He walked to the park.	There was a guy mowing the lawn.	He waved at John.		& {\color{blue}{John waved back.}} \\ \hline
+\multirow{2}{4.6cm}{Joe went to college for art.
 He graduated with a degree in painting.
@@
 %Our results hint that different writing tasks impose different cognitive load on the writer, which lead to the substantial style differences.
-As a case study, we present experiments based on 
-the \shortv{recently introduced ROC }story cloze task \cite{Mostafazadeh:2016}. 
-\roy{In this task, whose goal is to serve as a commonsense challenge for NLP \shortv{and AI }research, a system is presented with two short stories that differ only in their last sentence: one ending makes the entire story {\it coherent} while the other makes it {\it incoherent}.
-The system then decides which is the coherent one.}
+As a case study, we present experiments based on the recently introduced commonsense challenge---the \shortv{ROC }story cloze task \cite{Mostafazadeh:2016}. 
+In this task, a system is presented with two short stories that differ only in their last sentence: one ending makes the entire story {\it coherent} while the other makes it {\it incoherent}. 
+The system then decides which is the coherent one.
 \shortv{In this task, \com{crowdsourced }authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
@@
 and asked to write two contrasting story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
-Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP \shortv{and AI }research. }
-\shortv{\tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.}
+Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP \shortv{and AI }research. 
+\tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.}
 
@@
 
-\com{We show that a linear classifier informed with stylistic features can distinguish among {\it original}, {\it right}, and {\it wrong}  endings to a large degree, even without looking at the story context.
-Our results allow us to make a few key observations.
-First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
-Second,  people change their writing style when writing the entire story on their own compared to 
-writing only the final sentence for a given story context written by someone else.}
-
 %Our binary classification results range between 64.5\%--75.6\%, where chance performance is 50\%.
@@
 Interestingly, the story cloze task annotation process introduced three variants of the same writing task: writing an ending to a short story (see \secref{ROC_Story}).
-In this paper, we show that a linear classifier informed by stylistic features can distinguish among the different variants to a large degree, even without looking at the story context\shortv{ (64.5--68.5\% binary classification results)}.
+In this paper, we show that a linear classifier informed by stylistic features can distinguish among the different variants to a large degree, even without looking at the rest of the story\shortv{ (64.5--68.5\% binary classification results)}.
 
@@
 Additionally,  }.
-Importantly, both endings were required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
+Importantly, both endings were required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context (see \tabref{ROC-example}).
+
+\begin{table}[!t]
+\small
+%\begin{tabular}{|p{4.8cm}|p{2.1cm}|} \hline
+\begin{tabular}{|c|c|} \hline
+{\bf Story Prefix} & {\bf Ending} \\ \hline
+\multirow{4}{*}{\parbox{4.6cm}{Joe went to college for art.
+He graduated with a degree in painting.
+He couldn't find a job.
+He then responded to an ad in the paper.}} & 	{\color{blue}{???}} \\ \cline{2-2}
+& 	{\color{forestgreen}{Then he got hired.}} \\ \cline{2-2}
+& {\color{red}{Joe hated pizza.}} \\ %\cline{2-2}
+&  \\ \hline
+\end{tabular}
+\caption{\label{ROC-example}
+Examples of stories from the story cloze task\shortv{ \cite{Mostafazadeh:2016}}. The table shows a story prefix with three contrastive endings:
+ %of the same story: 
+The {\color{blue}{original}} ending, a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story.
+Unfortunately Nasrin et al.
+didn't publish the original endings for the dev/test data.
+We could ask her, but not sure if this is worth it}}
+ \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
+let's consider just color-coding these three terms.  It's less distracting.}}
+}
+%\end{center}
+\end{table}
 
@@
 Based on the new stories, \shortv{\citet{Mostafazadeh:2016} proposed }the {\it story cloze task} was proposed\shortv{. 
-The task is simple}:  given a pair of stories that differ only in their endings, the system decides which ending is {\it right} and which is {\it wrong}. 
+The task is simple}:  given a pair of stories that differ only in their endings, the system decides which \shortv{ending }is {\it right} and which is {\it wrong}. 
 %The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
@@
 %as a machine reading task, 
-as }a commonsense story understanding task\com{, 
+as }a commonsense\shortv{ story} understanding task\com{, 
 as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017),} and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
@@
 On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} samples, which serve as the positive samples in the development and test sets.
-While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
-and then asking her to generate a fifth {\it right} ending. 
+While the former are part of a \shortv{single }coherent story written by the same author, the latter were generated by asking an author to read four sentences, 
+and then \shortv{asking her to }generate a fifth {\it right} ending. 
 %This raises the question of whether these different writing setups impose different writing styles. 
@@
 \com{\begin{table*}[!t]
+\small
 \begin{center}
@@
 different writing constraints lead the authors to adopt different writing styles. 
-In order to answer these questions, we use simple methods that have been shown to be very effective for recognizing style\shortv{ (see \secref{Related})}.
-We describe our model below.
+In order to answer these questions, we use simple methods that do not capture content, and have been shown to be\shortv{ very} effective for recognizing style\shortv{ (see \secref{Related})}.
+\shortv{We describe our model below.}
 
@@
 (b) \textit{\textbf{Word $n$-grams.}} Sequences of 1-5
-  words,\footnote{Following and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
-Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their POS tags.}
+  words,\footnote{In order to focus on style, we replace content words (nouns, verbs, adjectives, and adverbs) with their POS tags.}
 and (c) \textit{\textbf{Character $n$-grams.}} \shortv{Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
@@
 The first is an attempt to distinguish between {\it right} and {\it wrong} endings,
-the second  between {\it original} endings and new ({\it right}) endings.
+the second  between {\it original} endings and new ({\it right}) endings.\roy{\footnote{Experimental details are found in the supplementary file.}}
 \shortv{We describe both experiments below.}
@@
 
+\supl{
 \paragraph{Experimental setup.}
@@
 tune a single hyperparameter---the regularization parameter.   \resolved{\nascomment{any other hyperparameters?  if
-  not, say this is the only one.  else explain what they are.}}
+  not, say this is the only one.  else explain what they are.}}}
 
@@
 \shortv{\tabref{results} shows our results.  }In both experiments,
-our model achieves performance well above what would be expected under
+our model performs well above what would be expected under
 chance (50\% by design)\roy{: 64.5\% accuracy for Experiment 1, and 68.5\% for Experiment 2.}
@@
 strong evidence that the authors' style was affected by the writing task they
-were given to perform.\com{  On our third task, which compared 
+performed.\com{  On our third task, which compared 
 \emph{original} vs.~\emph{wrong (new)} endings, even stronger
@@
 \begin{table}[!t]
+\small
 \begin{center}
@@
 {\bf Model} & {\bf Acc.} \\ \hline
-{DSSM} \cite{Mostafazadeh:2016} & 0.595 \\ 
+{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
 {ukp} \cite{Bugert:2017} & 0.717\\ 
@@
 We investigate whether our model can benefit from state-of-the-art text comprehension models\shortv{, for which this task was designed}. 
-We experiment with an LSTM\shortv{-based} \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
+We experiment with an LSTM\shortv{-based} \cite{hochreiter1997long} recurrent neural network language model (LM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
 %and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
@@
 gives improvements over our classifier as well as the \shortv{language
-model}LM.  \resolved{\nascomment{reworded.  more important that our features help
-  the language model, than the other way around!}}
-
+model}LM.\resolved{\nascomment{reworded.  more important that our features help
+  the language model, than the other way around!}}\footnote{The LM training details are in the supplementary file.}\supl{
 \shortv{We train the RNNLM using a single-layer LSTM of hidden dimension 512.}
@@
 We train the RNNLM using the Adam optimizer \cite{kingma2014adam} and a learning rate of
-$\eta=.001$, while \shortv{train to }minimizing cross-entropy. % minibatches of $50$ stories.
+$\eta=.001$, while \shortv{train to }minimizing cross-entropy.} % minibatches of $50$ stories.
 % h=512, dropout rate of 60%, V=21582, 10% validation set
 To apply \shortv{the RNNLM}it to the classification problem, we select
-as \emph{right} the ending with the higher value of\footnote{The intuition is that a \emph{right} ending should be unsurprising (to
+as \emph{right} the ending with the higher value of\shortv{\footnote{The intuition is that a \emph{right} ending should be unsurprising (to
 the model)
 given the four preceding sentences of the story (the numerator), controlling for the
-inherent surprisingness of the words in that ending (the denominator).}
+inherent surprisingness of the words in that ending (the denominator).}}
 \begin{equation}
@@
 
-We combine our linear model with the RNNLM by adding three features to
+We combine our linear model with the \shortv{RNN}LM by adding three features to
 our classifier: the numerator, denominator, and ratio in
@@
 We retrain our linear  model with the new feature set, and gain 2.8\%
-absolute, reaching 75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}\roy, a new-state-of-the-art result\shortv{  for the task}.\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
-These results indicate that context-ignorant style features can be used to obtain high
+absolute.
+Our final result---75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}---is a new-state-of-the-art\shortv{  for the task}.\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
+This result indicates that context-ignorant style features can be used to obtain high
 accuracy on the task, adding value even when context and a large
@@
 Our findings suggest that careful attention must be paid to instructions given to authors, especially in unnatural tasks such as writing a {\it wrong} ending. 
-One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
+\roy{The COPA dataset \cite{Roemmele:2011} was also designed to test commonsense knowledge, by presenting systems with premises like {\it I put my plate in the sink.} and then letting it decide between two alternatives, e.g.: (a) {\it I finished eating.} and (b) {\it I skipped dinner.}}
+Importantly, in this task,  annotators were asked to be as brief as possible and avoid proper names, as well as  slang.
+
+Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
+While this could be partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), this indicates that simple instructions  can help alleviate the effects of writing style found in this paper.
+\shortv{One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
+
 A different approach is to use naturally occurring text, as used in recent machine reading tasks \cite{hermann2015teaching}\shortv{ (see \secref{Related})}. 
@@
 such as coherence (or, very differently, the level of surprise),
-rather than asking them to generate  text.
+rather than asking them to generate  text.}
 

### 2017-04-09 docs/language_constraint_conll.tex
V2 of CoNLL + EMNLP versions (Roy)

@@
 \newcommand{\isectionb}[1]{\section{#1}\label{ssec:#1}}
+\newcommand{\isubsectionb}[1]{\subsection{#1}\label{ssec:#1}}
 \newcommand{\com}[1]{}
@@
 In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
-different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.
+different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purpose of this paper, \emph{style} is defined as content-agnostic writing characteristics, such as the number of words in a sentence.}}
 
@@
 
-\paragraph{Results.}
+\isubsectionb{Results}
 \tabref{results} shows our results.  In all experiments,
@@
 We retrain our linear  model with the new feature set, and gain 2.8\%
-absolute, reaching 75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}\roy, a new-state-of-the-art result for the task.\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
+absolute, reaching 75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}\roy{, a new-state-of-the-art result for the task.}\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
 These results indicate that context-ignorant style features can be used to obtain high
@@
 Our findings suggest that careful attention must be paid to instructions given to authors, especially in unnatural tasks such as writing a {\it wrong} ending. 
-One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
+\roy{The COPA dataset \cite{Roemmele:2011}, which was also designed to test commonsense knowledge, explicitly addressed potential style differences in their instructions.
+In this task,  systems are presented with premises like {\it I put my plate in the sink.} and then letting it decide between two alternatives, e.g.: (a) {\it I finished eating.} and (b) {\it I skipped dinner.}}
+Importantly, when writing the alternatives,  annotators were asked to be as brief as possible and avoid proper names, as well as  slang.
+
+Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
+While this could be partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), this indicates that simple instructions  can help alleviate the effects of writing style found in this paper.
+
+Another way to avoid such effects is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
 A different approach is to use naturally occurring text, as used in recent machine reading tasks (see \secref{Related}). 
 %However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
-One way to avoid the inherent biases people have when writing is to 
-have them rate sentences from naturally occurring text by parameters
+Finally, a third approach is to have people rate sentences from naturally occurring text by parameters
 such as coherence (or, very differently, the level of surprise),

### 2017-04-09 docs/language_constraint_emnlp.tex
V2 of CoNLL + EMNLP versions (Roy)

@@
 \usepackage{url}
+\usepackage{tabularx}
 \usepackage{caption}
@@
 \newcommand{\shortv}[1]{}
+\newcommand{\shortvb}[1]{}
+%\renewcommand{\shortv}[1]{{\color{magenta}\textsc{[#1 --sv]}}}
+
 \newcommand{\supl}[1]{}
@@
 %Our results hint that different writing tasks impose different cognitive load on the writer, which lead to the substantial style differences.
-As a case study, we present experiments based on the recently introduced commonsense challenge---the \shortv{ROC }story cloze task \cite{Mostafazadeh:2016}. 
+As a case study, we present experiments based on a recently introduced commonsense challenge---the story cloze task \cite{Mostafazadeh:2016}. 
 In this task, a system is presented with two short stories that differ only in their last sentence: one ending makes the entire story {\it coherent} while the other makes it {\it incoherent}. 
@@
 and asked to write two contrasting story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
-Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP \shortv{and AI }research. 
+Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP research. 
 \tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.}
@@
 \shortv{While the story cloze task was originally designed to be a story understanding challenge, }
-Interestingly, the story cloze task annotation process introduced three variants of the same writing task: writing an ending to a short story (see \secref{ROC_Story}).
-In this paper, we show that a linear classifier informed by stylistic features can distinguish among the different variants to a large degree, even without looking at the rest of the story\shortv{ (64.5--68.5\% binary classification results)}.
+Interestingly, the story cloze task annotation process introduced three different variants of the writing task of writing an ending to a short story (\secref{ROC_Story}).
+In this paper, we show that a linear classifier informed with stylistic features can distinguish among these endings to a large degree, even without looking at the rest of the story\shortv{ (64.5--68.5\% binary classification results)}.
 
@@
 We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
-Our final model that combines context with stylistic features achieves an additional 2.8\% gain--75.2\%,  a new state-of-the-art result.\com{, 15.3\% better than the best
+Our final model that combines context with stylistic features achieves an additional 2.8\% gain---75.2\%---a new state-of-the-art result.\com{, 15.3\% better than the best
 published result}
@@
 %both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
-Third, we establish a new state-of-the-art result on the \shortv{commonsense }story cloze task.
+Third, we establish a new state-of-the-art result on the story cloze task.
 
@@
 A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
-Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}\shortv{.
+Workers were asked to write a pair of new story endings for each story context: one {\it right}, making the entire story coherent, and one {\it wrong}, making it incoherent\shortv{.
 Both endings were required to complete the story using one of the characters in the story context.
@@
 %\begin{tabular}{|p{4.8cm}|p{2.1cm}|} \hline
-\begin{tabular}{|c|c|} \hline
+%\begin{tabular}{|p{4.8cm}|p{1.9cm}|} \hline
+\begin{tabularx}{\linewidth}%
+{l>{\setlength\hsize{0.67\hsize}}X%
+>{\setlength\hsize{1.33\hsize}}X}
 {\bf Story Prefix} & {\bf Ending} \\ \hline
-\multirow{4}{*}{\parbox{4.6cm}{Joe went to college for art.
-He graduated with a degree in painting.
-He couldn't find a job.
-He then responded to an ad in the paper.}} & 	{\color{blue}{???}} \\ \cline{2-2}
-& 	{\color{forestgreen}{Then he got hired.}} \\ \cline{2-2}
-& {\color{red}{Joe hated pizza.}} \\ %\cline{2-2}
-&  \\ \hline
-\end{tabular}
+\multirow{4}{*}{\parbox{4.75cm}{%Joe went to college for art. He graduated with a degree in painting. He couldn't find a job. He then responded to an ad in the paper.
+\vspace{.1cm}Betsy comes home late one night and wants to eat something simple.	She notices that she has spaghetti and sauce in the house.	She quickly cooks and eats a pot of spaghetti.	After eating, she falls asleep on the couch.}} & \vspace{-0.3cm}	{\color{blue}{{\it \tiny $<$waiting for examples from  Nasrin$>$}}} \\ \cline{2-2}
+& 	{\color{forestgreen}{\vspace{-0.1cm}She was full and happy.     %Then he got hired.
+}} \\ \cline{2-2}
+& {\color{red}{%Joe hated pizza.
+\vspace{-0.1cm}Betsy likes{\color{white}{0}}{\color{white}{0}}{\color{white}{0}}{\color{white}{0}} cheeseburgers.}} \\\hline %\cline{2-2}
+%&  \\ \hline
+\end{tabularx}
 \caption{\label{ROC-example}
-Examples of stories from the story cloze task\shortv{ \cite{Mostafazadeh:2016}}. The table shows a story prefix with three contrastive endings:
+Examples of stories from the story cloze task. The table shows a story prefix with three contrastive endings:
  %of the same story: 
@@
 
-Based on the new stories, \shortv{\citet{Mostafazadeh:2016} proposed }the {\it story cloze task} was proposed\shortv{. 
-The task is simple}:  given a pair of stories that differ only in their endings, the system decides which \shortv{ending }is {\it right} and which is {\it wrong}. 
+Based on the new stories, the {\it story cloze task} was proposed\shortv{. 
+The task is simple}:  given a pair of stories that differ only in their endings, the system decides which is {\it right} and which is {\it wrong}. 
 %The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
-The \shortv{official }training data contains  the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a \shortv{different }set of original stories not included in the training set).\resolved{\roy{added {\it not} here}}
+The training data contains  the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a set of original stories not included in the training set).\resolved{\roy{added {\it not} here}}
 The task was suggested as \shortv{an extensive evaluation framework:
 %as a machine reading task, 
-as }a commonsense\shortv{ story} understanding task\com{, 
+as }a commonsense understanding task\com{, 
 as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017),} and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
@@
 \paragraph{Different writing tasks in the story cloze task.}
-Several \shortv{key }design decisions make the task an interesting testbed for the purpose of this study.\resolved{\clinic{Which purpose?}}
+Several design decisions make the task an interesting testbed for the purpose of this study.\resolved{\clinic{Which purpose?}}
 First, the training set for the task (ROC Stories corpus) is not a
@@
 On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} samples, which serve as the positive samples in the development and test sets.
-While the former are part of a \shortv{single }coherent story written by the same author, the latter were generated by asking an author to read four sentences, 
-and then \shortv{asking her to }generate a fifth {\it right} ending. 
+While the former are part of a coherent story written by the same author, the latter were generated by asking an author to read four sentences, 
+and then generate a fifth {\it right} ending. 
 %This raises the question of whether these different writing setups impose different writing styles. 
@@
 the tasks for generating the pairs of endings were quite different from each other: in one case, the author was asked to write a {\it right} ending, which would create a coherent five-sentence story along with the other four sentences.
-In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent \shortv{five-sentence }story.
+In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent story.
  \resolved{In this work, we show that these differences are significant and
@@
 
-\shortv{
+\shortvb{
 \isection{Surface Analysis of the Story Cloze Task}{Surface}
@@
 different writing constraints lead the authors to adopt different writing styles. 
-In order to answer these questions, we use simple methods that do not capture content, and have been shown to be\shortv{ very} effective for recognizing style\shortv{ (see \secref{Related})}.
+In order to answer these questions, we use simple methods that do not capture content, and have been shown to be effective for recognizing style\shortv{ (see \secref{Related})}.
 \shortv{We describe our model below.}
@@
   words,\footnote{In order to focus on style, we replace content words (nouns, verbs, adjectives, and adverbs) with their POS tags.}
-and (c) \textit{\textbf{Character $n$-grams.}} \shortv{Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
-We use character $4$-grams}\roy{Sequences of 4 characters}.\footnote{\roy{Character $4$-grams are very common features in style detection \cite{Stamatatos:2009}.}}
+and (c) \textit{\textbf{Character $n$-grams.}} \roy{Sequences of 4 characters}.\footnote{\roy{Character $4$-grams are very common features in style detection \cite{Stamatatos:2009}.}}
 
@@
 
-\paragraph{Experiment 1: right/wrong endings.}
+\paragraph{Exp.~1: right/wrong endings.}
 We measure the extent to which  style features capture differences between the {\it right} and {\it wrong} endings.
-As the story cloze task doesn't have a training corpus for the {\it
+\supl{As the story cloze task doesn't have a training corpus for the {\it
   right} and {\it wrong} endings (see \secref{ROC_Story}), we use the
@@
 
-It is worth noting that our classification task is slightly different from the story cloze task. 
+}Our classification task is slightly different from the story cloze task. 
 Instead of classifying pairs of endings, \shortv{one which is {\it right} and
@@
 By ignoring the coupling between {\it right} and {\it wrong} pairs, 
-we \shortv{are able to }decrease the impact of author-specific style differences,
+we decrease the impact of author-specific style differences,
 and focus on the difference between the styles accompanied with {\it right} and {\it wrong} writings.
@@
 
-\paragraph{Experiment 2: original/new endings.}
-
-Here we measure whether writing the ending as part of a
+\paragraph{Exp.~2: original/new endings.}
+
+We measure whether writing the ending as part of a
 story imposes different style compared to writing a new ({\it right}) ending to an existing story.
-We use the endings of the ROC stories as our {\it original} samples and {\it right} endings from the story cloze task   \resolved{\nascomment{if you're using the test examples as
-  training data, what are you using for test? and development?  I would have thought
-  you'd follow the same pattern as above ... }}as {\it new} samples.
-As there are far more {\it original} instances than {\it new}
+We use endings of the ROC stories ({\it original} samples) and {\it right} endings from the story cloze task  ({\it new} samples).
+\supl{As there are far more {\it original} instances than {\it new}
 instances, we randomly select five  {\it original} sets, each with the same number of
@@
 %We randomly sample 5 {\it original} sets and repeat the classification experiments.
-We report the average classification result.
+We report the average classification result.}
 
@@
 For computing our features, we keep $n$-gram (character or word) features that occur at least five times in the training set.
-All feature values are normalized to $[0, 1]$.\shortv{
-For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{http://spacy.io/}}}
-We use  Python's sklearn logistic regression implementation \shortv{\cite{scikit-learn} }with $L_2$
+All feature values are normalized to $[0, 1]$. 
+For the POS features, we tag all endings with the Spacy POS tagger.\footnote{\url{http://spacy.io/}}
+We use  Python's sklearn logistic regression implementation \cite{scikit-learn} with $L_2$
 regularization, performing grid search on the development set to
@@
 our model performs well above what would be expected under
-chance (50\% by design)\roy{: 64.5\% accuracy for Experiment 1, and 68.5\% for Experiment 2.}
+chance (50\% by design)\roy{: 64.5\% accuracy for Exp.~1, and 68.5\% for Exp.~2.}
 Noting again that our model ignores the
@@
 
-\shortv{
+\shortvb{
 \begin{table}[!t]
@@
 }
+
+\paragraph{Further Analysis.}
+
+\tabref{exp1_features} shows the most salient features for {\it right} and {\it wrong} endings in Exp.~1. 
+{\it Right} endings tend to end with past tense verbs, while {\it wrong} endings with common nouns.
+Further, {\it right} endings make wider use of  adjectives,
+which might indicate that incoherent writing  inspires authors to write less descriptive text, 
+as is the case in deceptive text \cite{ott2011finding}.
+
+\begin{table}[!t]
+\small
+\begin{center}
+\begin{tabular}{|c|c|c||c|c|c|} \hline
+\textit{\textbf{Right}} & Wt. & Freq. &   \textit{\textbf{Wrong}}& Wt. & Freq.  \\ \hline
+`ed .' & 0.17 & {\color{white}{0}}6.5\%&  \textsc{start} NNP & 0.21& 54.8\%  \\ \hline
+`and ' &  0.15 & 13.6\%  & NN . & 0.17 & 47.5\%  \\ \hline
+JJ & 0.14 & 45.8\%  & NN NN . & 0.15 &  {\color{white}{0}}5.1\%  \\ \hline
+%to VB & 20.1\%& VBG & 10.1\%\\ \hline
+%`d th' & 10.9\%& \textsc{start} NNP VBD & 41.9\%\\ \hline
+%`ally' & 3.3\% & `hate' & {\color{white}{0}}1.9\% \\ \hline
+%VBD the NN .& 2.2\% & ` hat' & {\color{white}{0}}2.0\% \\ \hline
+%\textsc{start} RB & 3.1\% & \textsc{start} NNP & 54.8\% \\ \hline
+%`ved ' &4.1\%&  `ated' & {\color{white}{0}}3.0\%\\ \hline
+%` tim' &2.6\%&  NN . & 47.5\%\\ \hline
+
+\end{tabular}
+\end{center}
+\caption{\label{exp1_features}
+The top 3 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
+along with their feature weight (Wt.)~and their frequency in our story cloze training set (Freq.).
+}
+\end{table}
+
 \paragraph{Story cloze task.}
-The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
-In order to further estimate the quality of our \shortv{classification }results, we tackle the story cloze task\shortv{ using our classifier}.
-This classification task is more constrained than Experiment 1, as two
+\shortv{The results of Exp.~1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.}
+To further estimate the quality of our results, we tackle the story cloze task.
+We apply the classifier from Exp.~1 as follows:
+if it assigns different labels to the two given endings, we keep
+them.  Otherwise, the label whose posterior probability is lower is reversed.
+This task is easier than Exp.~1, as two 
 endings are given and the question is which is \emph{right} and which is
 \emph{wrong}.
-We apply the classifier from Experiment 1 as follows:
-if it assigns different labels to the two given endings, we keep
-them.  Otherwise, the label whose posterior probability is lower is reversed.
 
@@
 published state-of-the-art result on the task \cite{Salle:2016}}\resolved{\nascomment{cite that here}}.
-Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and \shortv{in fact }doesn't even consider the \shortv{first four sentences of the }story context in question.
+Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and doesn't even consider the \shortv{first four sentences of the }story context in question.
 These numbers further support the claim that the styles of {\it right} and {\it wrong} endings are indeed very different.
@@
 The middle block are our results.
-{\it cogcomp} results and human \shortv{judgement }scores are taken from \cite{Mostafazadeh:2017}.
+{\it cogcomp} results and human scores are taken from \cite{Mostafazadeh:2017}.
 %RNN is our implementation. 
-Methods marked with ($\dagger$) do not use the story context\shortv{ in order} to make a prediction. 
+Methods marked with ($\dagger$) do not use the story context to make a prediction. 
  \resolved{\nascomment{I added 0s to ``Niko'' result
@@
 We investigate whether our model can benefit from state-of-the-art text comprehension models\shortv{, for which this task was designed}. 
-We experiment with an LSTM\shortv{-based} \cite{hochreiter1997long} recurrent neural network language model (LM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
+We experiment with an LSTM \cite{hochreiter1997long} recurrent neural network language model (LM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
 %and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
-Unlike the model in this paper\shortv{, which only considers the story endings}, this LM \shortv{follows the protocol suggested by the story cloze task designers, and }harnesses the \shortv{ROC Stories }story cloze training set, which consists of single-ending stories,
-as well as the story context for each pair of endings. 
-We show that adding our features to this powerful \shortv{language model}LM
-gives improvements over our classifier as well as the \shortv{language
-model}LM.\resolved{\nascomment{reworded.  more important that our features help
-  the language model, than the other way around!}}\footnote{The LM training details are in the supplementary file.}\supl{
+Unlike the model in this paper\shortv{, which only considers the story endings}, this LM \shortv{follows the protocol suggested by the story cloze task designers, and }harnesses the story cloze training set, which consists of single-ending stories,
+as well as the story context for each pair of endings.\footnote{The LM training details are in the supplementary file.} 
+We show that adding our features to this powerful LM
+gives improvements over our classifier as well as the LM.\resolved{\nascomment{reworded.  more important that our features help
+  the language model, than the other way around!}}\supl{
 \shortv{We train the RNNLM using a single-layer LSTM of hidden dimension 512.}
@@
 We train the RNNLM using the Adam optimizer \cite{kingma2014adam} and a learning rate of
-$\eta=.001$, while \shortv{train to }minimizing cross-entropy.} % minibatches of $50$ stories.
+$\eta=.001$, while minimizing cross-entropy.} % minibatches of $50$ stories.
 % h=512, dropout rate of 60%, V=21582, 10% validation set
-To apply \shortv{the RNNLM}it to the classification problem, we select
+To apply it to the classification problem, we select
 as \emph{right} the ending with the higher value of\shortv{\footnote{The intuition is that a \emph{right} ending should be unsurprising (to
@@
 
-We combine our linear model with the \shortv{RNN}LM by adding three features to
+We combine our model with the LM by adding three features to
 our classifier: the numerator, denominator, and ratio in
 Equation~\ref{eq:ratio}, all in log space. % $p_\theta(ending|story),p_\theta(ending)$ and $\frac{p_\theta(ending|story)}{p_\theta(ending)}$.
-We retrain our linear  model with the new feature set, and gain 2.8\%
+We retrain our  model with the new feature set, and gain 2.8\%
 absolute.
-Our final result---75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}---is a new-state-of-the-art\shortv{  for the task}.\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
+Our final result---75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}---is a new-state-of-the-art.\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
 This result indicates that context-ignorant style features can be used to obtain high
@@
 
-\shortv{
+\shortvb{
 \isection{Further Analysis}{Ablation}
@@
 
-Previous work has shown that a writing task can affect mental state.
-For instance, writing deceptive text leads to a significant cognitive
+\shortv{Previous work has shown that }Writing tasks can affect mental states.
+For instance, writing deceptive text leads to a  cognitive
 burden accompanied by a writing style that is different from truthful
@@
 This large body of work indicates a tight connection between writing
-tasks, mental states, and \shortv{variation in }writing style.
+tasks, mental states, and writing style.
 This connection hints that the link discovered in this paper, between
@@
 involves differences in mental state. 
-Further investigation is required \shortv{in order to further}to validate this hypothesis.
+Further investigation is required to validate this hypothesis.
 
@@
 same author, partly in order to avoid author-specific style effects.}
- Nonetheless\shortv{, despite these efforts}, several significant style
+ Nonetheless, several significant style
  differences can be found between the training and the test set, as well as between the positive and negative labels.
@@
 Our findings suggest that careful attention must be paid to instructions given to authors, especially in unnatural tasks such as writing a {\it wrong} ending. 
-\roy{The COPA dataset \cite{Roemmele:2011} was also designed to test commonsense knowledge, by presenting systems with premises like {\it I put my plate in the sink.} and then letting it decide between two alternatives, e.g.: (a) {\it I finished eating.} and (b) {\it I skipped dinner.}}
-Importantly, in this task,  annotators were asked to be as brief as possible and avoid proper names, as well as  slang.
+\roy{The COPA dataset \cite{Roemmele:2011}, which was also designed to test commonsense knowledge, explicitly addressed potential style differences in its annotation instructions.
+In this task,  systems are presented with premises like {\it I put my plate in the sink}, and then decide between two alternatives, e.g.: (a) {\it I finished eating} and (b) {\it I skipped dinner}}.
+Importantly, when writing the alternatives,  annotators were asked to be as brief as possible and avoid proper names, as well as  slang.
 
 Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
-While this could be partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), this indicates that simple instructions  can help alleviate the effects of writing style found in this paper.
-\shortv{One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
-
-A different approach is to use naturally occurring text, as used in recent machine reading tasks \cite{hermann2015teaching}\shortv{ (see \secref{Related})}. 
+While this is partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), our findings also indicate that simple instructions  can help alleviate the effects of writing style found in this paper.
+\shortv{One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.}
+
+\shortv{A different approach is to use naturally occurring text, as used in recent machine reading tasks \cite{hermann2015teaching}\shortv{ (see \secref{Related})}. 
 %However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
@@
 
-\shortv{
+\shortvb{
 \isection{Related Work}{Related}
@@
  and the difference between writing a coherent and an incoherent story ending.
-In both cases, a simple \shortv{linear }model reveals measurable differences in writing styles, %that different styles are imposed.
+In both cases, a simple model reveals measurable differences in writing styles, %that different styles are imposed.
 %The different styles allow our style detection 
@@
 %\bibliography{acl2017}
-
+\newpage
 \bibliography{acl2017}

### 2017-04-09 docs/language_constraint_emnlp_supplementary.tex
V2 of CoNLL + EMNLP versions (Roy)

--- 2017-02-07 docs/language_constraint.tex
@@
 \documentclass[11pt,a4paper]{article}
-\usepackage[hyperref]{acl2017}
+\usepackage[hyperref]{emnlp2017}
 \usepackage{times}
+\usepackage{multirow}
 \usepackage{latexsym}
@@
 
-\renewcommand{\ms}[1]{}
-\renewcommand{\roy}[1]{}
+\renewcommand{\roy}[1]{{\color{orange}[#1 --rs]}}
+
+%\renewcommand{\ms}[1]{}
+\renewcommand{\roy}[1]{#1}
+%\renewcommand{\roy}[1]{}
 \renewcommand{\nascomment}[1]{}
@@
 
-\title{The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task}
+\title{The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task: Supplementary Material}
 
@@
 \maketitle
-\begin{abstract}
-A writer's style depends not just on personal traits but also on her intent and mental state.
-In this paper, we show how variants of the same writing task can lead to measurable differences in writing style.
-We present a case study based on 
-the  {\it story cloze task} \cite{Mostafazadeh:2016},
-where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 constraints looks like 3 constraints.
-clarify}}
-%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
-We show that a simple linear classifier informed with stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
-In addition, our style-based classifier establishes a new state-of-the-art result on the story cloze challenge, substantially higher than previous results based on deep learning models. 
-%Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
-Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}
 
-\resolved{They also provide important lessons for designing new NLP
-tasks. \nascomment{drop this sentence if we only have a paragraph
-  about this at the end, as we currently do}}
+\section{Experimental setup.}
+This section describes the experimental setup of both Experiments 1 and 2.
 
-\end{abstract}
-
-\section{Introduction}
-Writing style is expressed through a range of linguistic elements such as words, sentence structure, and rhetorical devices.
-It is influenced by personal factors such as age and gender \cite{Schler:2006}, 
-by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
-as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
-In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
-different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.
-
-\begin{table}[!t]
-\begin{tabular}{|p{1.6cm}|p{5.3cm}|} \hline
-{\bf Type} & {\bf Example} \\ \hline
-{\color{blue}{Original}} story & My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	{\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
-{\color{forestgreen}{Coherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{forestgreen}{She felt buyer's remorse after the purchase.}} \\ \hline
-{\color{red}{Incoherent}} story & Kathy went shopping.	She found a pair of great shoes.	The shoes were \$300.	She bought the shoes.	{\color{red}{Kathy hated buying shoes.}} \\ \hline
-\end{tabular}
-\caption{\label{ROC-example}
-Examples of stories from the story cloze task \cite{Mostafazadeh:2016}. The first row shows an {\color{blue}{original}} story written by one author. 
-The second and third rows show revised stories with two contrastive endings:
- %of the same story: 
- a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story.
-Unfortunately Nasrin et al.
-didn't publish the original endings for the dev/test data.
-We could ask her, but not sure if this is worth it}}
- \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
-let's consider just color-coding these three terms.  It's less distracting.}}
-}
-%\end{center}
-\end{table}
-
-We show that similar writing tasks with different constraints on the
-author can lead to measurable differences in her writing style.
-%We explore three  writing tasks, showing that they are distinguishable from one another using a linear classifier informed with stylistic features only. 
-%Our results hint that different writing tasks impose different cognitive load on the writer, which lead to the substantial style differences.
-As a case study, we present experiments   based on 
-the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
-In this task, \com{crowdsourced }authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
-%Following, 
-Then, 
-%the stories were given to other authors, 
-each original story was given to a different author, 
-who was shown only the first four sentences as a story context, 
-and asked to write two contrasting story endings: a {\it right} (coherent) ending, and a {\it wrong} (incoherent) ending. 
-Framed as a story cloze task, the goal of this dataset is to serve as a commonsense challenge for NLP and AI research. 
-\tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.
-
-\com{While originally designed to be a story understanding challenge, the annotation process triggers interesting questions 
-that may go beyond the original intent of the designers.
-First, do people maintain the same writing 
-style when asked to write both coherent and incoherent story endings? 
-Second, do people maintain the same writing style when writing the entire story on their own compared to 
-writing only the final sentence for a given story context written by someone else? }
-
-\com{
-%Our analysis indicates that the answer to both questions is positive. 
-Our analysis indicates that different framings of similar writing tasks 
-can lead to measurable differences in people's writing style.\clinic{This is the main message -- should come earlier}
-%We experiment with a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
-%First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between the {\it right} and {\it wrong} endings in 64.5\% of the cases. 
-Using a simple classifier informed with stylistic features, we show that our classifier can distinguish the {\it right} and {\it wrong} endings with 64.5\% accuracy, even without looking at the story context, where chance performance is 50\%.
-%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
-%Second, when trained to distinguish between the {\it original} endings and the new ({\it right}) endings, the classifier obtains 68.5\% accuracy. 
-Further, our classifier can also distinguish between the {\it original} endings and the new ({\it right}) endings with 68.5\% accuracy, again without looking at the story context.
-\clinic{Why do we care?
-(Luke)}
-}
-
-\com{We show that a linear classifier informed with stylistic features can distinguish among {\it original}, {\it right}, and {\it wrong}  endings to a large degree, even without looking at the story context.
-Our results allow us to make a few key observations.
-First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
-Second,  people change their writing style when writing the entire story on their own compared to 
-writing only the final sentence for a given story context written by someone else.}
-
-%Our binary classification results range between 64.5\%--75.6\%, where chance performance is 50\%.
-
-%Importantly, in both experiments, the classifier uses {\bf only} the 
-%last sentence of each of the stories, and does not consider the first four sentences.
-%final sentence without the story context.
-
-While the story cloze task was originally designed to be a story understanding challenge, 
-its annotation process introduced three variants of the same writing task: writing an {\it original}, {\it right}, or {\it wrong} ending to a short story.
-In this paper, we show that a linear classifier informed by stylistic features can distinguish among the different endings to a large degree, even without looking at the story context (64.5--75.6\% binary classification results).
-
-Our results allow us to make a few key observations.
-First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
-Second,  people change their writing style when writing the entire story on their own compared to 
-writing only the final sentence for a given story context written by someone else.
-
-In order to further validate our method, we also directly tackle the
-story cloze task\nascomment{cite the challenge?  a reader may
-  not realize that there is a shared task on this}\roy{Maybe ``challenge'' was not the right term here.
-We basically mean the story cloze task.
-The shared task was the original task w/o any modification, so I am not referring to it specifically here}.
- Adapting our classifier to the task, we obtain 72.4\% accuracy, a
- 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}.
-We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
-Our final model that combines context with stylistic features achieves
-75.2\%---an additional 2.8\% gain, 15.3\% better than the best
-published result.
-
-\com{Our results suggest that writing style is affected by the the writer's state of mind.
-Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it right}. 
-Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.}
-
-The contributions of our study are threefold. 
-First, findings from our study can potentially shed light on 
-how different kinds of cognitive load influence the style of written language. 
-Second, our results indicate that when designing new NLP tasks, special attention needs to be payed to the instructions given to authors.
-%both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
-Third, we establish a new state-of-the-art result on the commonsense story cloze challenge.
-
-\com{
-The remainder of this paper is organized as follows. In \secref{ROC_Story} we describe the story cloze task.
-We then present our model, experiments and results in Sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
-Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present a further analysis of our results  and a discussion, followed by related work and conclusions.\clinic{Omit this paragraph?}}
-
-\isection{Background: The Story Cloze Task}{ROC_Story}
-To understand how different writing tasks affect writing style, 
-we focus on the \textit{story cloze task} \cite{Mostafazadeh:2016}. 
-While this task was developed to facilitate representation and learning of commonsense story understanding,
-its design included a few key choices which  make it ideal for our study. 
-We describe the task below.
-
-%For that purpose, \citet{Mostafazadeh:2016} crowdsourced the collection of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
-
-\paragraph{ROC stories.}
-
-The ROC story corpus consists of 49,255 five-sentence commonsense
-stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently,
-  an additional 53K stories were released, which results in roughly
-  100K stories.}
-Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
-To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
-which resulted in a wide range of different topics.
-
-\paragraph{Story cloze task.}
-After compiling the story corpus, the {\it story cloze task}---a task based on the corpus---was introduced.
-A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
-Workers were asked to write a pair of new story endings for each story context: one {\it right} and one {\it wrong}.
-Both endings are required to complete the story using one of the characters in the story context. 
-Additionally,  the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
-
-The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness by additional AMT workers.
-Only stories rated as simultaneously coherent with a {\it right} ending and neutral with a {\it wrong} ending were selected for the task. 
-It is worth noting that workers rated the stories as a whole, not only the endings.
-
-Based on the new stories, \citet{Mostafazadeh:2016} proposed the {\it story cloze task}. 
-The task is simple:  given a pair of stories that differ only in their endings, the system decides which ending is {\it right} and which is {\it wrong}. 
-%The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
-The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are not included in the training set).\resolved{\roy{added {\it not} here}}
-The task was suggested as an extensive evaluation framework:
-%as a machine reading task, 
-as a commonsense story understanding task, 
-as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
-
-Interestingly, at the time of this submission, 10 months after the
-task was first introduced, the published benchmark on this task is
-still below 60\% \cite{Salle:2016}.\footnote{The LSDSem 2017 shared
-  task website
-  (\url{https://competitions.codalab.org/competitions/15333}) does
-  report higher results% (71.1\%)
-\resolved{\roy{Tricky. Which number should we report here? leave empty?}
-\nascomment{leave empty for now}}, which
-are still unpublished along with the underlying methodology.} 
-This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or shorter period of time.
-This suggests that this task is challenging and that high performance is hard to achieve.
- \resolved{\yc{SQuAD was officially published in Nov 2016.
-by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper.
-Given that, the statement of this paragraph seems a bit of overkill...?} \nascomment{it sounds like Yejin is saying that on squad, there was an even faster acceleration?
-or that we should change ``similar period of time'' to ``similar or shorter period of time''?}}
-
-In addition, \citet{Mostafazadeh:2016} made substantial efforts to ensure the quality of this dataset. 
-First, each pair of endings was written by the same author, which
-ensured that style differences between authors could not be used to solve the task. 
-Furthermore, Mostafazadeh et al.~implemented nine baselines for the task, using surface level features as well as narrative-informed ones, and showed that each of them reached roughly chance-level.
-These results suggest that real understanding of text is required in order to solve the task.
-
-\paragraph{Different writing tasks in the story cloze task.}
-Several key design decisions make the task an interesting testbed for the purpose of this study.\resolved{\clinic{Which purpose?}}
-First, the training set for the task (ROC Stories corpus) is not a
-training sample in the usual sense,\footnote{I.e., the training
-  instances are not drawn from a population similar to the one that future
-  testing instances will be drawn from.%\roy{I added \textbf{not}
-                                %here, as otherwise it is confusing}
-}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones. 
- \resolved{\yc{As far as I understand, this was intentional --- they didn't want
-  people to pick up on random superfluous cues that can inevidently
-  get into the data creation process, exactly the kind that our work
-  picks up. Given that, stating this can be viewed as
-  misunderstanding, I'm afraid.} \nascomment{We should maybe say that
-  they did this intentionally and concede that our approach goes
-  against the intentions of their task design.  But a task that
-  insists that systems avoid using features that might encode one kind
-of information (like style) is absurd.  Alternately, we could reframe
-this not as ``things weren't controlled for'' but instead stick to the
-facts here and just describe what they did without judgment.}}
-
-On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} samples, which serve as the positive samples in the development and test sets.
-While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
-and then asking her to generate a fifth {\it right} ending. 
-%This raises the question of whether these different writing setups impose different writing styles. 
-% We show that this is indeed the case.
-
-Finally, although the {\it right} and {\it wrong} sentences were generated by the same author, 
-the tasks for generating them were quite different: in one case, the author was asked to write a {\it right} ending, which would create a coherent five-sentence story along with the other four sentences.
-In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story.
- \resolved{In this work, we show that these differences are significant and
-impose different writing styles on authors. \nascomment{this bit feels
-  a little heavy and reptititive.}}
-
-\isection{Surface Analysis of the Story Cloze Task}{Surface}
-We begin by computing several characteristics of the three types of endings: {\it original} endings (from the ROC story corpus training set), {\it right} endings and {\it wrong} endings (both from the story cloze task development set).
-Our analysis  reveals several style differences between different groups. 
-First, {\it original} endings are on average longer (11 words per
-sentence) than {\it right} endings (8.75 words), which are in turn
-slightly longer than {\it wrong} ones (8.47 words). 
-Previous work has shown that sentence length is also indicative of whether a text was deceptive \cite{yancheva2013automatic,qin2004exploratory}. 
-Although writing {\it wrong} sentences is not the same as lying, it is not entirely surprising to observe similar trends in both tasks.
-%Furthermore, \citet{Buller:1996} suggests lying increases one's cognitive load, which in turn could affect sentence length.
-%\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
-
-Second, \figref{roc_pos_distribution} shows the distribution of five frequent POS tags in all three groups. 
-The figure shows that both {\it original} and {\it right} endings use pronouns more frequently than {\it wrong} endings.
-Once again, deceptive text is also characterized by fewer pronouns compared to truthful text \cite{Newman:2003}.
-%In contrast, {\it wrong} and {\it right} endings favor proper nouns compared to {\it original} endings. 
- \resolved{\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}}
- \resolved{\ms{The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.}}
-  \resolved{\roy{Good point!
-This is tricky.
-On the one hand, it hurts our story by saying that the difference is not really the general task by itself, but also the constraints put by  Nasrin et al.
-It also forces us to bash them some more.
-Or we can just ignore it...} }
-  \resolved{\yc{Ok!
-I resolved all comments above and also commented out the comment on how wrong/right endings use more proper nouns compared to the original endings.
-I think it's the best not to talk about this.}}
-
-Finally, \figref{roc_word_distribution} presents the distribution of five frequent words across the different groups. 
-The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones.
-%\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, did we find that in our experiments?}.
-Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings tend to use more negative language (``hates''), similarly as deceptive text \cite{Newman:2003}.
-%\yc{Again, any cogsci literature on this?} \nascomment{feels
-%  Pennebaker-ish, that might be a good place to look.}
-Next we show that these style differences are not anecdotal, but can
-be used to distinguish among the different types of story endings.
-
-\com{\begin{table*}[!t]
-\begin{center}
-\begin{tabular}{|p{2.5cm}|p{4cm}|p{4cm}|p{4cm}|} \hline
- & {\bf Original}& {\bf Right} & {\bf Wrong}\\ \hline
-Sentence Length (\#words) & 11.02 & 8.75 & 8.47\\ \hline
-Most Frequent POS tags (\%)  & NN:15.3\%, VBD:13.4\%, PRP:10.1, CC:3.3\%, IN:8.7\% & VBD:15.8\%, NN:15.7\%, CC:2\%, PRP:8.8\%, NNP:8.3\%  & NN:16.3\%, VBD:15.1\%,  NNP:9.5\%, DT:1.4, IN:7.9\%\\ \hline
-Most Frequent Words  (\%) & the:4.5\%, to:3.3\%, and:2.7\%, was:2.6\%, a:2.2\% & the:4.8\%, to:3.9\%, was:3.5\%, a:2.5\%, and:2.1\%   & the:5\%, to:4\%, was:3\%, a:2\%, I:1.6\%\\ \hline
-\end{tabular}
-\end{center}
-\caption{\label{roc_pos_distribution} 
-\end{table*}
-}}
-
-\begin{figure*}[t!]
-\begin{small}
-\begin{subfigure}{.5\textwidth}\center
-\begin{tikzpicture}
-    \begin{axis}[
-        width  = 0.4*\textwidth,
-        height = 4cm,
-      %  major x tick style = transparent,
-        ybar=\pgflinewidth,
-        x=2.5cm,
-       bar width=5pt,
-        ymajorgrids = true,
-        ylabel = {Frequency in Corpus (\%)},
-        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
-        xtick = data,
-        scaled y ticks = false,
-        %enlarge x limits=0.25,
-        ymin=3,
-        legend cell align=left,
-        legend style={
-        		legend columns=-1,
-                at={(1,1.05)},
-                anchor=south east,
-                column sep=1ex
-        }
-    ]
-        \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it original}, 15.3) ({\it right}, 15.7) ({\it wrong}, 16.3)};
-
-        \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it original}, 13.4) ({\it right}, 15.8) ({\it wrong}, 15.1)};
-
-        \addplot[style={ggreen,fill=ggreen,mark=none}]
-            coordinates {({\it original}, 10.1) ({\it right}, 9.7) ({\it wrong}, 7.4)};
-
-        \addplot[style={brown,fill=brown,mark=none}]
-            coordinates {({\it original}, 9.1) ({\it right}, 9.7) ({\it wrong}, 9.4)};
-
-        \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it original}, 4.7) ({\it right}, 8.3) ({\it wrong}, 9.5)};
-
-        \legend{NN, VBD, PRP, DT, NNP}
-    \end{axis}
-\end{tikzpicture}
-\caption{\label{roc_pos_distribution}POS tags}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}\center
-\begin{tikzpicture}
-    \begin{axis}[
-        width  = 0.4*\textwidth,
-        height = 4cm,
-      %  major x tick style = transparent,
-        ybar=\pgflinewidth,
-        x=2.5cm,
-       bar width=5pt,
-        ymajorgrids = true,
-%        ylabel = {Frequency in Corpus (\%)},
-        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
-        xtick = data,
-        scaled y ticks = false,
-        %enlarge x limits=0.25,
-        ymin=0,
-        legend cell align=left,
-        legend style={
-        		legend columns=-1,
-                at={(1,1.05)},
-                anchor=south east,
-                column sep=1ex
-        }
-    ]
-        \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it original}, 3) ({\it right}, 3.3) ({\it wrong}, 3.5)};
-
-        \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it original}, 2.5) ({\it right}, 1.8) ({\it wrong}, 1.3)};
-
-        \addplot[style={ggreen,fill=ggreen,mark=none}]
-            coordinates {({\it original}, 1) ({\it right}, 1.2) ({\it wrong}, 1.4)};
-
-        \addplot[style={brown,fill=brown,mark=none}]
-            coordinates {({\it original}, 0) ({\it right}, 0) ({\it wrong}, 0.6)};
-
-        \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it original}, 0.9) ({\it right}, 0.2) ({\it wrong}, 0.1)};
-
-        \legend{to, and, I, hates, !}
-    \end{axis}
-\end{tikzpicture}
-\caption{\label{roc_word_distribution}Words}
-\end{subfigure}
-\end{small}
-\caption{The distribution of five frequent POS tags
-  (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})
-  across \emph{original} endings (story cloze training set), and
-  \emph{right} and \emph{wrong} endings (from the story cloze task).}
-
-\end{figure*}
-
-%\roy{Other things to talk about (not necessarily in that order): 
-%1.
-no training corpus for the task.
-That is, the training set (a) does not contain negative example (just positive), and (b) was not generated in the same way as the positive test samples.
-Here you need to explicitly say that we show that we show that the training and test sets use very different styles.
-%2. Maybe talk about the shared task, as well as their RepEval paper, which suggested this task as a vector-space evaluation measure?
-%3.
-Say that the authors did an extensive work in order to  assure that the positive and negative samples are not easily distinguishable: for each pair, both endings were written by the same author (you addressed this earlier, but this seems like a better location), they tried an extensive set of baselines, showing all don't surpass a random baseline by much.
-Maybe now you can briefly mention the benchmarks, saying that several baselines were presented in the papers.
-All benchmarks attempted to learn the connection between the previous paragraph and the ending, and all performed near chance level..
-However, no baseline looked at the endings independently.
-%Then you can add the benchmark text below, and conclude that this indicates that this task is well designed and hard and the one hand, but might also point to potential disagreements between the train and the test data, which we highlight in this paper.}
-
-\isectionb{Model}
-
-The goal of this paper is to determine the extent to which 
-%does constraining authors in their writing assignments lead to them adopting different writing styles. 
-different writing constraints lead the authors to adopt different writing styles. 
-In order to answer these questions, we use simple methods that have been shown to be very effective for recognizing style (see \secref{Related}).
-We describe our model below.
-
-We train a logistic regression classifier to categorize an ending,
-either as {\it right} vs.~{\it wrong} or as {\it original} vs.~new ({\it right}).
-Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
-We use the following style features.
-
-\begin{itemize}
-\item\textit{\textbf{Length}.} The number of words in the sentence.
-\item\textit{\textbf{Word $n$-grams.}} We use sequences of 1-5
-  words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
-Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their part-of-speech tags.
-\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
-We use character 4-grams.
-\end{itemize}
-
-\isectionb{Experiments}
-We design two experiments to answer our research questions. 
-The first is an attempt to distinguish between {\it right} and {\it wrong} endings,
-the second  between {\it original} endings and new ({\it right}) endings.
-We describe both experiments below.
-
-\paragraph{Experiment 1: right/wrong endings.}
-The goal of this experiment is to measure the extent to which  style features capture differences between the {\it right} and {\it wrong} endings.
-As the story cloze task doesn't have a training corpus for the {\it
-  right} and {\it wrong} endings (see \secref{ROC_Story}), we use the
-development set as our training set, holding out 10\% for development
-(3,366 training endings, 374 for development). 
- We keep the story cloze test set as is (3,742 endings).
-
-It is worth noting that our classification task is slightly different from the story cloze task. 
-Instead of classifying pairs of endings, one which is {\it right} and
-another which is {\it wrong}, our classifier decides about each ending
-individually, whether it is \emph{right} (positive instance) or
-\emph{wrong} (negative instance).
-By ignoring the coupling between {\it right} and {\it wrong} pairs, 
-we are able to decrease the impact of author-specific style differences,
-and focus on the difference between the styles accompanied with {\it right} and {\it wrong} writings.
-\resolved{we
-are able make a more general claim about the style used when writing
-each of the tasks \nascomment{I'm not sure I follow this sentence; can
-we be more clear?}.}
-
-\paragraph{Experiment 2: original/new endings.}
-
-Here the goal is to measure whether writing the ending as part of a
-story imposes different style compared to writing a new ({\it right}) ending to an existing story.
-We use the endings of the ROC stories as our {\it original} samples and {\it right} endings from the story cloze task   \resolved{\nascomment{if you're using the test examples as
-  training data, what are you using for test? and development?  I would have thought
-  you'd follow the same pattern as above ... }}as {\it new} samples.
-As there are far more {\it original} instances than {\it new}
-instances, we randomly select the same number of \emph{original}
-instances  \resolved{\nascomment{(give the number in parentheses, for train/dev/test)} }as we have
-\emph{new} instances (3,366 training endings, 374 development endings, and 3,742 test endings).
-We randomly sample 5 {\it original} sets and repeat the classification experiments.
-We report the average classification result.
-
-\paragraph{Experimental setup.}
 In both experiments, we add a \textsc{start} symbol at the beginning
-of each sentence.\footnote{Virtually all sentences end with a period
+of each sentence.\footnote{99\% of all sentences end with a period
   or an exclamation mark, so we do not add a \textsc{stop} symbol.}
@@
 
-\isectionb{Results}
-\tabref{results} shows our results.  In both experiments,
-our model achieves performance well above what would be expected under
-chance (50\% by design).  Noting again that our model ignores the
-story context (the preceding four sentences), our model is unable to
-capture any notion of coherence.   This finding provides
-strong evidence that the authors' style was affected by the writing task they
-were given to perform.  We further applied the model to a third task,
-\emph{original} vs.~\emph{wrong (new)} endings, and even stronger
-differences were apparent to the model, allowing over 75\% accuracy.
+For Exp.~1, as the story cloze task doesn't have a training corpus for the {\it
+  right} and {\it wrong} endings\com{ (see \secref{ROC_Story})}, we use the
+development set as our training set, holding out 10\% for development
+(3,366 training endings, 374 for development). 
+ We keep the story cloze test set as is (3,742 endings).
 
-\resolved{\nascomment{I rewrote this section.  old version commented out in
-  latex source}}
-% In Experiment 1, our model obtains 64.5\%
-% classification accuracy, well above a (50\%-accurate) random baseline.
-% \clinic{How good is this?}
-% \yc{how about addressing above comment from the clinic by adding a
-%   commentary such as following: This result is surprising given that
-%   our model makes the prediction based only on the last sentence
-%   without looking at the story context, thus does not have sufficient
-%   information to judge the story coherency.} 
-% For Experiment 2, our model is even stronger, at 68.5\%.
-% These results indicate that an author's style is affected in an
-% easily-detected way when she is prompted to write (1) a \emph{wrong} story ending vs.~a
-% \emph{right} one, or (2) finishing her own short story vs.~someone else's.
-% %These numbers indicate that these different writing tasks clearly impose different writing styles on authors.
+For Exp.~2, as there are far more {\it original} instances than {\it new}
+instances, we randomly select five  {\it original} sets, each with the same number of
+instances  \resolved{\nascomment{(give the number in parentheses, for train/dev/test)} }as we have
+\emph{new} instances (3,366 training endings, 374 development endings, and 3,742 test endings).
+%We randomly sample 5 {\it original} sets and repeat the classification experiments.
+We report the average classification result.
 
-% We further measured whether these style effects are additive, by
-% classifying \emph{original} vs.~\emph{wrong} endings.  The setup is
-% exactly as in Experiment 2, but using \emph{wrong} endings instead of
-% \emph{right} ones.  The result is that the effects are somewhat
-% additive:  this third classifier achieves 75.6\%.
-% % That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
-% % We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
-% % Our hypothesis is that differences would be even clearer. 
-% % Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.
+\section{Neural Language Model Training}
+This section describes the training details of our neural language model.
 
- \resolved{
-\begin{figure}
-\begin{tikzpicture}
-\small
-    \begin{axis}[
-        width  = 0.45*\textwidth,
-        height = 4cm,
-      %  major x tick style = transparent,
-        ybar=2*\pgflinewidth,
-       % bar width=14pt,
-        ymajorgrids = true,
-        ylabel = {Classification Performance},
-        symbolic x coords={{\it Correct/Wrong}, {\it Original/New}, {\it Original/Wrong}},
-        xtick = data,
-        scaled y ticks = false,
-        %enlarge x limits=0.25,
-        ymin=0.4,
-        legend cell align=left,
-        legend style={
-                at={(1,1.05)},
-                anchor=south east,
-                column sep=1ex
-        }
-    ]
-        \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it Correct/Wrong}, 0.5) ({\it Original/New}, 0.5) ({\it Original/Wrong},.5)};
-
-        \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it Correct/Wrong}, 0.645) ({\it Original/New}, 0.685) ({\it Original/Wrong},0.756)};
-
-        \legend{Random Baseline, Our Model}
-    \end{axis}
-\end{tikzpicture}
-\caption{\label{results}Results of  experiments 1 and 2 (left two charts). 
-Rightmost graph shows a control experiment which classifies {\it
-  original} endings vs \textit{\textbf{wrong}}
-endings. \nascomment{this is overkill.  I suggest replacing it with a
-  table that just shows our model, no baseline, and reiterate in the
-  caption that our setup implies a 50\%-accurate random baseline.
-  Also, I like including the third comparison, but I don't
-  see how it's a ``control.'' }}
-\end{figure}
-}
-
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{|l|r|} \hline
-{\bf Experiment} & {\bf Accuracy} \\ \hline
-{\sl right vs. wrong} & 0.645 \\ \hline
-{\sl original vs. right} & 0.685 \\ \hline
-{\sl original vs. wrong} & 0.756 \\ \hline
-\end{tabular}
-\end{center}
-\caption{\label{results}Results of  experiments 1 ({\it right
-    vs.~wrong}) and 2 ({\it original vs.~right (new)}). 
-The bottom row shows an additional experiment which classifies {\it
-  original vs.~wrong (new)} endings.
-In all cases, our setup implies a 50\% random baseline.}
-\end{table}
-
-\paragraph{Story cloze task.}
-The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
-In order to further estimate the quality of our classification results, we tackle the story cloze task using our classifier.
-This classification task is more constrained than Experiment 1, as two
-endings are given and the question is which is \emph{right} and which is
-\emph{wrong}.
-We apply the classifier from Experiment 1 as follows:
-if it assigns different labels to the two given endings, we keep
-them.  Otherwise, the label whose posterior probability is lower is reversed.
-
-\tabref{cloze_results} shows our results on the story cloze test
-set. Our classifier obtains 72.4\% accuracy, 12.5\% (absolute) higher than the
-published state-of-the-art result on the task \cite{Salle:2016}\resolved{\nascomment{cite that here}}.
-Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
-These numbers further support the claim that the styles of {\it right} and {\it wrong} endings are indeed very different.
-
- \resolved{\nascomment{I suppressed the sentences about the LSDSem shared task;
-  once, in the earlier footnote, is enough.}}
-% Other than the published works that tackled this task, a few  recent works published their results in the LSDSem shared task website.\footnote{\url{https://competitions.codalab.org/competitions/15333}}
-% At the time of submission, our results are still state-of-the-art (though by a  smaller margin). 
-% No other information other than the name of the groups and their results is available.
-
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{|l|r|} \hline
-{\bf Model} & {\bf Acc.} \\ \hline
-$\dagger${DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
-$\dagger${LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
-%{Niko (shared task)}	& 0.700\\ 
-%{tbmihaylov (shared task)} & 0.711\\ \hline\hline
-$\dagger${RNN}		& 0.677 \\ 
-{\bf Ours} & {\bf 0.724} \\ 
-$\dagger${\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
-$\dagger$Human judgment & 1.000 \\ \hline
-\end{tabular}
-\end{center}
-\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}Results on the test set of the  story cloze task. 
-The upper block shows published results, 
-the middle block are our results.
-LexVec results are taken from \cite{Speer:2016}.
-%RNN is our implementation. 
-Human judgement scores are taken from \cite{Mostafazadeh:2016}.
-Methods marked with ($\dagger$) use the story context in order to make a prediction. 
- \resolved{\nascomment{I added 0s to ``Niko'' result
-  and ``human''
-  so sig. digits would line up.  if we don't have sig digits for some
-  of them, make the zeros white so the numbers line up.  where did the
-human judgments come from?  those are not mentioned in our text anywhere!}
-}}
-\end{table}
-
-\paragraph{Combination with a neural language model.}
-We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed. 
-Specifically, we experiment with an LSTM-based \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
-%and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
-Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the story cloze task designers, and harnesses their ROC Stories training set, which consists of single-ending stories,
-as well as the story context for each pair of endings. 
-We show that adding our features to this powerful language model
-gives improvements over our classifier as well as the language
-model.  \resolved{\nascomment{reworded.  more important that our features help
-  the language model, than the other way around!}}
-
-We train the RNNLM using a single-layer LSTM of hidden dimension 512.
-We use the ROC stories for training,\footnote{We use the extended, 100K stories corpus (see \secref{ROC_Story}).} setting aside 10\% for validation of the language model. 
+We train the LM using a single-layer LSTM of hidden dimension 512.
+We use the ROC stories for training,\footnote{We use the extended, 100K stories corpus, released in winter 2017.} setting aside 10\% for validation of the language model.
 We replace all words occurring less than 3 times with a special
@@
 Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories.
-Using the Adam optimizer \cite{kingma2014adam} and a learning rate of
-$\eta=.001$, we train to minimize cross-entropy. % minibatches of $50$ stories.
-% h=512, dropout rate of 60%, V=21582, 10% validation set
-
-To apply the language model to the classification problem, we select
-as \emph{right} the ending with the higher value of
-\begin{equation}
-\frac{p_\theta(\textrm{ending} \mid
-  \textrm{story})}{p_\theta(\textrm{ending})} \label{eq:ratio}
-\end{equation}
-The intuition is that a \emph{right} ending should be unsurprising (to
-the model)
-given the four preceding sentences of the story (the numerator), controlling for the
-inherent surprisingness of the words in that ending (the denominator).
-
-\resolved{\nascomment{please check the paragraph above.  we need to say how we
-  use the LM before we evaluate it!  also, has anyone tried an approach like this
-  before?  even if we aren't exactly replicating another paper, if
-  someone else used RNNs for this task, we should credit them.}
-  \roy{Ours is the first work to publish LSTM results on this dataset.}}
-
-% Eval
-On its own, our neural language model performs moderately well on the story cloze test. 
-%This is not surprising, as \citet{Mostafazadeh:2016} hinted  that
-%simple language models are insufficient.
-Selecting endings based on $p_\theta(\textrm{ending} \mid \textrm{story})$ (i.e., the numerator of
-Equation~\ref{eq:ratio}), we obtained only 55\% accuracy.   The ratio
-in Equation~\ref{eq:ratio} achieves 67.7\%  (see
-\tabref{cloze_results}).\footnote{Note that taking the logarithm of
-  the expression in Equation~\ref{eq:ratio} gives the pointwise mutual
-information between the story and the ending, under the language
-model.\nascomment{added this to replace the hedging that was here before}\roy{We actually also use the RNNLM features in log space. Add that in the next paragraph.}}
-
-We combine our linear model with the RNNLM by adding three features to
-our classifier: the numerator, denominator, and ratio in
-Equation~\ref{eq:ratio}, all in log space. % $p_\theta(ending|story),p_\theta(ending)$ and $\frac{p_\theta(ending|story)}{p_\theta(ending)}$.
-We retrain our linear  model with the new feature set, and gain 2.8\%
-absolute, reaching 75.2\% (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result).\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
-These results indicate that context-ignorant style features can be used to obtain high
-accuracy on the task, adding value even when context and a large
-training dataset are used.  \resolved{\nascomment{check reframing here}}
-
-\isection{Further Analysis}{Ablation}
-
- \resolved{\nascomment{these aren't just ablations, so I retitled}}
-
-\subsection{Most Discriminative Feature Types}
-A natural question that follows this study is which style features are most
-helpful in detecting the underlying task an author was asked
-to perform. 
-To answer this question, we re-ran Experiment 1 with different sub-groups of features. 
-\tabref{subgroups} shows our results.
-Results show that  character $n$-grams are the most effective style predictors, reaching within  0.6\% of the full model, but that word $n$-grams also capture much of the signal, yielding 61.2\%, which is only 3.3\% worse than the full model.
-These findings are in line with previous work that used character $n$-grams along with other types of features to predict writing  style \cite{Schwartz:2013}.
-
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{|c|c|} \hline
-{\bf Feature Type} & {\bf Accuracy}\\ \hline
-Word $n$-grams & 0.612 \\ \hline
-Character $n$-grams & 0.639 \\ \hline
-Full model & 0.645 \\ \hline
-
-\end{tabular}
-\end{center}
-\caption{\label{subgroups}
-Results on Experiment 1 with different subsets of features.
-}
-\end{table}
-
-\subsection{Most Salient Features}
-A follow-up question is which individual features contribute most to the classification process,
-as these could shed light on the stylistic differences imposed by each of the writing tasks.
-
-In order to answer this question, we consider the highest absolute
-positive and negative coefficients in the logistic regression
-classifier in both Experiments 1 and 2, an  approach widely used  as a
-method of extracting the most salient features
-\cite{Nguyen:2013,Burke:2013,Brooks:2013}. It is worth noting
-  that its reliability is not entirely clear, since linear models like
-  logistic regression can assign large coefficients to rare features \cite{Yano:2012}.
-To mitigate this concern, we consider only features appearing in at least 5\% of the endings in our training set.
-
-\paragraph{Experiment 1.}
-\tabref{exp1_features} shows the most salient features for {\it right} (coherent) and {\it wrong} (incoherent) endings in Experiment 1,
-along with their corpus frequency. 
-The table shows a few interesting trends. 
-First, authors tend to structure their sentences differently when writing {coherent}  vs.~{incoherent} endings.
-For instance, {incoherent} endings are more likely to start with a proper noun and end with a common noun, 
-while coherent endings have a greater tendency to end with a past tense verb.
-
-Second, {\it right} endings will make wider use of coordination structures, as well as adjectives.
-The latter might indicate that writing coherent stories inspires the authors to write more descriptive text compared to incoherent ones, 
-as is the case in truthful vs.~deceptive text \cite{ott2011finding}.
-Finally, we notice a few syntactic differences: {\it right} endings will more often use infinite verb structure, while {\it wrong} endings prefer gerunds (VBG).
-
-\com{More interestingly, the different writing tasks seem to impose a specific sentiment on the writer. 
-Three of the top four most salient features for detecting {\it wrong} endings are variants of the verb ``hate''.
-This indicates that when authors are asked to write {\it wrong} text, they tend to use negative language.
-
-An alternative explanation to this hypothesis might be that the first four sentences of the stories in the ROC story corpus tend to be positive, and thus in order to make an ending {\it wrong}, authors adopted a negative approach.
-A similar idea was suggested in the original story cloze paper, where two sentiment-based baselines were evaluated. 
-These baselines measured the relative sentiment between the ending and the previous sentences.
-The performance of both these baselines was roughly chance-level, which seems to suggest that this is not entirely the case.
-\resolved{\yc{Is it really because there's no statistical tendency in the original stories to have happy endings, as opposed to the alternative possibility --- the sentiment classifier used by Monstafazadeh 2016 didn't quite nail down the optimal feature encodings?}} \roy{this is definitely an option, and that's partly why I used hedging (``seems to suggest'').
-Tones it down a bit more.}}
-
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{|c|c||c|c|} \hline
-\textit{\textbf{Right}} & Freq. & \textit{\textbf{Wrong}}& Freq. \\ \hline
-`ed .' & {\color{white}{0}}6.5\%& \textsc{start} NNP & 54.8\%\\ \hline
-`and ' & 13.6\%& NN . & 47.5\% \\ \hline
-JJ & 45.8\% & NN NN . & {\color{white}{0}}5.1\%\\ \hline
-to VB & 20.1\%& VBG & 10.1\%\\ \hline
-`d th' & 10.9\%& \textsc{start} NNP VBD & 41.9\%\\ \hline
-%`ally' & 3.3\% & `hate' & {\color{white}{0}}1.9\% \\ \hline
-%VBD the NN .& 2.2\% & ` hat' & {\color{white}{0}}2.0\% \\ \hline
-%\textsc{start} RB & 3.1\% & \textsc{start} NNP & 54.8\% \\ \hline
-%`ved ' &4.1\%&  `ated' & {\color{white}{0}}3.0\%\\ \hline
-%` tim' &2.6\%&  NN . & 47.5\%\\ \hline
-
-\end{tabular}
-\end{center}
-\caption{\label{exp1_features}
-The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
-along with their frequency in our story cloze training set.
-}
-\end{table}
-
-\paragraph{Experiment 2.}
-%In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
-%This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.724).  
-\tabref{exp2_features} shows the same analysis for Experiment 2.
-As noted in \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
-%This is in line with similar findings in the deception detection literature \cite{qin2004exploratory}.
-An interesting observation is that exclamation marks are a strong
-indication for an  {\it original} ending. 
-This suggests that authors are more likely to show or evoke enthusiasm when writing their own text compared to ending an existing task.
-
-Finally, when comparing the two groups of salient features from both experiments, we find an interesting trend.
-Several features, such as ``\textsc{start} NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict new (i.e., {\it right}) endings in Experiment 2. 
-This indicates that, for instance, incoherent endings have a stronger tendency to begin with a proper noun compared to coherent endings, 
-which in turn are more likely to do so than original endings. 
-This partially explains why distinguishing between {\it original} and {\it wrong} endings is an easier task compared to the other pairs (\secref{Results}).
-
-\setlength\tabcolsep{.15cm}
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{|p{1.25cm}|c||p{2.9cm}|c|} \hline
-\textit{\textbf{Original}} & Freq. & \textit{\textbf{New}}& Freq. \\ \hline
-{\it length} & {\color{white}{.}}100.0\% & `.' & 93.0\%\\ \hline
-`!' & {\color{white}{00}}6.1\%& \textsc{start} NNP  & 39.2\% \\ \hline
-NN & {\color{white}{00}}78.9\% & \textsc{start} NNP VBD &29.0\% \\ \hline
-RB & {\color{white}{0}}44.7\%& NN . & 42.3\% \\ \hline
-`,' & {\color{white}{0}}12.7\%&  the NN . & 10.6\% \\ \hline
-
-\end{tabular}
-\end{center}
-\caption{\label{exp2_features}
-The top 5 most heavily weighted features for predicting {\it original} vs.~new ({\it right}) endings.
-{\it length} is the sentence length feature (see \secref{Model}).
-}
-\end{table}
-
-\isectionb{Discussion}
-
-\paragraph{The effect of writing tasks on mental states.}
-In this paper we have shown that giving a writer different writing tasks affects her writing style in easily detected ways.
-Our results indicate that when authors are asked to write the last
-sentence of a five-sentence story, they will use different style to
-write a {\it right} ending compared to a {\it wrong} ending. We have
-also shown that writing the ending as part of one's own five-sentence story is very different than reading four sentences and then writing the fifth.
-Our findings hint that the nature of the writing task imposes a
-different mental state on the author, which is expressed in ways that can be observed using extremely simple automatic tools.
-
-Previous work has shown that a writing task can affect mental state.
-For instance, writing deceptive text leads to a significant cognitive
-burden accompanied by a writing style that is different from truthful
-text \cite{Newman:2003,Banerjee:2014}.
-Writing tasks can even have a long-term effect,
-as writing emotional texts was observed to benefit both physical and mental health \cite{Lepore:2002,Frattaroli:2006}. 
-\citet{Campbell:2003} also showed that the health benefits of writing emotional text are accompanied by changes in writing style, mostly in the use of pronouns.
-
-Another line of work has shown that writing style is affected by mental state.
-First, an author's personality traits (e.g., depression, neuroticism, narcissism) affect her writing style \cite{schwartz2013personality,Ireland:2014b}.
-Second, temporary changes, such as a romantic relationship \cite{Ireland:2011,Bowen:2016}, work collaboration \cite{Tausczik:2009,Gonzales:2009}, or negotiation \cite{Ireland:2014} may also affect writing style.
-Finally, writing style can also change from one sentence to another, for instance between positive and negative text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}.
-
-This large body of work indicates a tight connection between writing
-tasks, mental states, and variation in writing style.
-This connection hints that the link discovered in this paper, between
-different writing tasks and resulting variation in writing style,
-involves differences in mental state. 
-Further investigation is required in order to further validate this hypothesis.
-
-\paragraph{Design of NLP tasks.}
-Our study also provides important insights for the future design of NLP tasks. 
-The story cloze task was very carefully designed. Many factors, such
-as topic diversity and temporal and causal relation diversity,  were controlled for \cite{Mostafazadeh:2016}. 
-The authors also made sure each pair of endings was written by the
-same author, partly in order to avoid author-specific style effects.
- Nonetheless, despite these efforts, several significant style
- differences can be found between the training and the test set, as well as between the positive and negative labels.
-
-Our findings suggest that careful attention must be paid to instructions given to authors, especially in unnatural tasks such as writing a {\it wrong} ending. 
-One way to avoid such problems is by using shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
-A different approach is to use naturally occurring text, as used in recent machine reading tasks (see \secref{Related}). 
-%However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
-One way to avoid the inherent biases people have when writing is to 
-have them rate sentences from naturally occurring text by parameters
-such as coherence (or, very differently, the level of surprise),
-rather than asking them to generate new text.
-
-\com{
-Another lesson from this paper relates to baseline methods. 
-The authors of the story cloze task experimented with a wide and diverse set of baselines, including n-gram baselines, word embeddings baselines, sentiment baselines, and narrative chain baselines. 
-Nonetheless, running preliminary tests on the data, such as average length or  POS and word distribution,  could have revealed potentially unwanted phenomena in the data.
-\resolved{\nascomment{this paragraph needs extra care.  the authors of the ROC
-  paper did try to control for a lot of things and they did run
-  baselines.  we ought to be generous and reiterate that here.  what,
-  precisely, did they miss?  the lesson isn't just ``run more controls
-  and baselines'' is it?}
-First, it stresses the need to carefully control for even seemingly minor details. 
-Second, it emphasizes the importance of running baseline models.
-While recent advances in NLP  suggest that many classic NLP methods are out-of-date, 
-this is not necessarily the case, especially for small
-datasets. \nascomment{ this bit about simple models feels like a red herring}}
-This is particularly important in order to ensure that  new technological improvements are capturing a qualitatively different signal.
-The substantial improvement we get when combining our model
-with the RNN language model (\secref{Experiments}) suggests that
-despite the high results obtained by the simple model, 
-methods that exploit the wider context  capture a different aspect of the
-task. \resolved{\nascomment{I like ending on this happier note, but let's not
-  call it ``luck'' and let's focus on the task and representations,
-  not the ML methods, which are probably not the heart of the difference}}
-  \roy{Modified this to be more concrete. Did end up hinting that they should have done a better job at analyzing their data before publishing. Feel free to tone down.}
-}
-\resolved{\roy{Commented out the lessons about the importance of running
-  baselines.} 
-\nascomment{that seems like the right choice}}
-
-\isection{Related Work}{Related}
-
-\paragraph{Writing style.}
-Writing style has been an active topic of research for decades. 
-The models used to characterize style are often linear classifiers with style features such as character and word $n$-grams \cite{Stamatatos:2009,Koppel:2009}.
-Previous work has shown that different authors can be grouped by their
-writing style, according to factors such as age
-\cite{Pennebaker:2003,Argamon:2003,Schler:2006,Rosenthal:2011,nguyen:2011:latech},
-gender \cite{Argamon:2003,Schler:2006,bamman2014gender}, and native language
-\cite{Koppel:2005,Tsur:2007,Bergsma:2012}.
-At the extreme case, each individual author adopts a unique writing
-style \cite{mosteller1963inference,pennebaker1999linguistic,Schwartz:2013}. 
-\com{Interestingly, previous work has shown that individual style can be affected from coarse-grained factors such as those just described, but also from other less apparent factors such as mental state, or even living in a high-elevation location \cite{schwartz2013personality}.
-
-Unlike the works just described which compare the writing style
-between different authors, some works have shown that the same author
-can adopt a different style used when writing positive vs.~negative
-text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}. In this work, we have shown that the same author can adopt a different style when facing different writing tasks.}
-
-The line of work that most resembles our work is the detection of deceptive text. 
-Several researchers have used stylometric features to  predict deception 
-\cite{Newman:2003,hancock2007lying,ott2011finding,Feng:2012}.
-Some works even showed that gender affects a person's  writing style when lying \cite{Perez:2014b,Perez:2014a}.
-In this work, we have shown that an even more subtle writing task---writing {coherent} and {incoherent} story endings---imposes different styles on the author.
-
-\paragraph{Machine reading.}
-The  story cloze task, which is the focus of this paper, is part of a wide set of machine reading/comprehension challenges published in the last few years.
-These include datasets like bAbI \cite{Weston:2015}, SNLI \cite{bowman2015large}, CNN/DailyMail \cite{hermann2015teaching}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}. 
-While these works have presented resources for researchers, 
-it is often the case that these datasets suffer from methodological
-problems caused by applying noisy automatic tools to generate them \cite{Chen:2016}. 
-In this paper, we have pointed to another methodological challenge in
-designing machine reading tasks:  different writing tasks
-used to generated the data affect writing style, confounding classification problems.
-%, as well as create a discrepancy between the training and the test data.
- \resolved{\nascomment{dropped the train/test discrepancy here}}
-
-\isectionb{Conclusion}
-
-Different writing tasks assigned to an author result in different
-writing styles for that author.
-We experimented with the story cloze task, which introduces two interesting comparison points: %setups for our purposes:
-%a setup where the same author writes both a {\it right} and an {\it wrong} ending to a story, 
-%and one which compares an ending written as part of a story to a standalone ending added to a story written by someone else.
- the difference between writing a story on one's own and continuing someone else's story,
- and the difference between writing a coherent and an incoherent story ending.
-In both cases, a simple linear model reveals measurable differences in writing styles, %that different styles are imposed.
-%The different styles allow our style detection 
-which in turn allows our final 
-model to achieve state-of-the-art results on the story cloze task.
-
-The findings presented in this paper have  cognitive implications, as
-they motivate further research on the effects that a writing
-prompt has on an author's mental state, and also her concrete response.
-They also provide valuable lessons for designing new NLP datasets.
- \resolved{\nascomment{drop the last sentence, it makes this paper seem less
-  complete} Future work will include testing whether other similar writing tasks, such as fake news, also impose their own unique and identifiable style on their authors.}
-
-% include your own bib file like this:
-%\bibliographystyle{acl}
-%\bibliography{acl2017}
+We train the LM using the Adam optimizer \cite{kingma2014adam} and a learning rate of
+$\eta=.001$, while minimizing cross-entropy.
 
 \bibliography{acl2017}
-\bibliographystyle{acl_natbib}
+\bibliographystyle{emnlp_natbib}
 

### 2017-04-09 docs/language_constraint_conll.tex
Noah

@@
 %We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
-We show that a simple linear classifier informed with stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
+We show that a simple linear classifier informed by stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
 %\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
@@
 In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
-different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purpose of this paper, \emph{style} is defined as content-agnostic writing characteristics, such as the number of words in a sentence.}}
+different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purposes of this paper, \emph{style} is defined as content-agnostic writing characteristics, such as the number of words in a sentence.}}
 
@@
 
-The ROC story corpus consists of 49,255 five-sentence commonsense
+The ROC story corpus consists of 49,255 five-sentence 
 stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently,
@@
 
-The goal of this paper is to determine the extent to which 
+To what extent do
  %does constraining authors in their writing assignments lead to them adopting different writing styles. 
-different writing constraints lead the authors to adopt different writing styles. 
-In order to answer these questions, we use simple methods that have been shown to be very effective for recognizing style (see \secref{Related}).
+different writing constraints lead authors to adopt different writing styles?
+In order to answer this question, we first use simple methods that have been shown to be very effective for recognizing style (see \secref{Related}).
 We describe our model below.
@@
 \begin{itemize}
-\item\textit{\textbf{Length}.} The number of words in the sentence.
-\item\textit{\textbf{Word $n$-grams.}} We use sequences of 1-5
+\item\textit{\textbf{Length}:} the number of words in the sentence.
+\item\textit{\textbf{Word $n$-grams:}} we use sequences of 1-5
   words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
 Specifically, we replace content words (nouns, verbs, adjectives, and adverbs), which are often low frequency, with their part-of-speech tags.
-\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
+\item\textit{\textbf{Character $n$-grams:}} character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
 We use character $4$-grams.\footnote{\roy{Experiments with $5$-grams on our development set reached similar performance.}}
@@
 The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
-along with their frequency in our story cloze training set.
+along with their frequencies in our story cloze training set.
 }
@@
 Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
-While this could be partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), this indicates that simple instructions  can help alleviate the effects of writing style found in this paper.
+While this could be partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), this indicates that simple instructions may help alleviate the effects of writing style found in this paper.
 

### 2017-04-09 docs/language_constraint_emnlp.tex
Noah

@@
 %We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
-We show that a  linear classifier informed with stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
+We show that a  linear classifier informed by stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
 %\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
@@
 In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, as
-different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purpose of this paper, \emph{style} is defined as content-agnostic writing characteristics, e.g., sentence length.}}
+different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purposes of this paper, \emph{style} is defined as content-agnostic writing characteristics, e.g., sentence length.}}
 
@@
 \shortv{While the story cloze task was originally designed to be a story understanding challenge, }
-Interestingly, the story cloze task annotation process introduced three different variants of the writing task of writing an ending to a short story (\secref{ROC_Story}).
+Interestingly, the story cloze task annotation process introduced three different variants of the task of writing an ending to a short story (\secref{ROC_Story}).
 In this paper, we show that a linear classifier informed with stylistic features can distinguish among these endings to a large degree, even without looking at the rest of the story\shortv{ (64.5--68.5\% binary classification results)}.
@@
 
-\isubsection{Background: The Story Cloze Task}{ROC_Story}
+\isection{Background: The Story Cloze Task}{ROC_Story}
 To understand how different writing tasks affect writing style, 
@@
 
-The ROC story corpus consists of 49,255 five-sentence commonsense
+The ROC story corpus consists of 49,255 five-sentence 
 stories, collected on Amazon Mechanical Turk (AMT).\shortv{\footnote{Recently,
@@
 
-The goal of this paper is to determine the extent to which 
+To what extent do
 %does constraining authors in their writing assignments lead to them adopting different writing styles. 
-different writing constraints lead the authors to adopt different writing styles. 
-In order to answer these questions, we use simple methods that do not capture content, and have been shown to be effective for recognizing style\shortv{ (see \secref{Related})}.
+different writing constraints lead authors to adopt different writing styles?
+In order to answer this question, we first use simple methods that do not capture content, and have been shown to be effective for recognizing style\shortv{ (see \secref{Related})}.
 \shortv{We describe our model below.}
@@
 Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
-We use the following style features: (a) \textit{\textbf{Length}.} The number of words in the sentence, 
-(b) \textit{\textbf{Word $n$-grams.}} Sequences of 1-5
-  words,\footnote{In order to focus on style, we replace content words (nouns, verbs, adjectives, and adverbs) with their POS tags.}
-and (c) \textit{\textbf{Character $n$-grams.}} \roy{Sequences of 4 characters}.\footnote{\roy{Character $4$-grams are very common features in style detection \cite{Stamatatos:2009}.}}
+We use the following style features: (a) \textit{\textbf{Length}:} the number of words in the sentence;
+(b) \textit{\textbf{Word $n$-grams:}} sequences of 1-5
+  words;\footnote{In order to focus on style, we replace content words (nouns, verbs, adjectives, and adverbs) with their POS tags.}
+and (c) \textit{\textbf{Character $n$-grams:}} \roy{sequences of 4 characters}.\footnote{\roy{Character $4$-grams are very common features in style detection \cite{Stamatatos:2009}.}}
 
@@
 The top 3 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
-along with their feature weight (Wt.)~and their frequency in our story cloze training set (Freq.).
+along with their weights (Wt.)~and their frequencies in our story cloze training set (Freq.).
 }
@@
 Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
-While this is partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), our findings also indicate that simple instructions  can help alleviate the effects of writing style found in this paper.
+While this is partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), our findings also indicate that simple instructions  may help alleviate the effects of writing style found in this paper.
 \shortv{One way to avoid such problems is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.}

### 2017-04-12 docs/language_constraint_emnlp.tex
EMNLP submitted version

@@
 {\bf Story Prefix} & {\bf Ending} \\ \hline
-\multirow{4}{*}{\parbox{4.75cm}{%Joe went to college for art. He graduated with a degree in painting. He couldn't find a job. He then responded to an ad in the paper.
-\vspace{.1cm}Betsy comes home late one night and wants to eat something simple.	She notices that she has spaghetti and sauce in the house.	She quickly cooks and eats a pot of spaghetti.	After eating, she falls asleep on the couch.}} & \vspace{-0.3cm}	{\color{blue}{{\it \tiny $<$waiting for examples from  Nasrin$>$}}} \\ \cline{2-2}
-& 	{\color{forestgreen}{\vspace{-0.1cm}She was full and happy.     %Then he got hired.
+\multirow{4}{*}{\parbox{3.05cm}{\vspace{.05cm}John liked a girl at his work.	He tried to get her attention by acting silly.	She told him to grow up.
+John confesses he was trying to make her like him more.}} & \vspace{-0.2cm}	{\color{blue}{{She feels flattered and asks John on a date.}}} 	 \\\cline{2-2}
+
+%Travis needed some fast cash.	He thought about it and decided that selling his car was a good idea.	Travis listed his car for sale in the local paper.	After only a couple weeks he found somebody very interested.}}& \vspace{-0.2cm}	{\color{blue}{{\it This person came and test drove the car and bought it on the spot.}}} \\\cline{2-2}
+%Joe went to college for art. He graduated with a degree in painting. He couldn't find a job. He then responded to an ad in the paper.
+%\vspace{.3cm}Betsy comes home late one night and wants to eat something simple.	She notices that she has spaghetti and sauce in the house.	She quickly cooks and eats a pot of spaghetti.	After eating, she falls asleep on the couch.}} & \vspace{-0.3cm}	{\color{blue}{{\it $<$waiting for examples from  Nasrin$>$}}} \\ \cline{2-2}
+& 	{\color{forestgreen}{\vspace{-0.1cm}The girl found this charming, and gave him a second chance.% He sold the car and solved his money problems.%She was full and happy.     %Then he got hired.
 }} \\ \cline{2-2}
-& {\color{red}{%Joe hated pizza.
-\vspace{-0.1cm}Betsy likes{\color{white}{0}}{\color{white}{0}}{\color{white}{0}}{\color{white}{0}} cheeseburgers.}} \\\hline %\cline{2-2}
+& {\color{red}{%Joe hated pizza.\vspace{-0.1cm}Betsy likes{\color{white}{0}}{\color{white}{0}}{\color{white}{0}}{\color{white}{0}} cheeseburgers.
+\vspace{-0.1cm}John was happy about being rejected.%Travis gave it to the man for free.
+}} \\\hline %\cline{2-2}
 %&  \\ \hline
@@
 % h=512, dropout rate of 60%, V=21582, 10% validation set
-To apply it to the classification problem, we select
+To apply this LM to the classification problem, we select
 as \emph{right} the ending with the higher value of\shortv{\footnote{The intuition is that a \emph{right} ending should be unsurprising (to

### 2017-04-14 docs/language_constraint_conll.tex
Submitted EMNLP version

@@
 \usepackage{xcolor}
+\usepackage{tabularx}
 \usepackage[normalem]{ulem}
@@
 
+\com{
 \begin{table}[!t]
@@
  a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story.
+Unfortunately Nasrin et al.
+didn't publish the original endings for the dev/test data.
+We could ask her, but not sure if this is worth it}}
+ \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
+let's consider just color-coding these three terms.  It's less distracting.}}
+}
+%\end{center}
+\end{table}}
+
+\begin{table}[!t]
+%\small
+%\begin{tabular}{|p{4.8cm}|p{2.1cm}|} \hline
+%\begin{tabular}{|p{4.8cm}|p{1.9cm}|} \hline
+\begin{tabularx}{\linewidth}%
+{l>{\setlength\hsize{0.67\hsize}}X%
+>{\setlength\hsize{1.33\hsize}}X}
+{\bf Story Prefix} & {\bf Ending} \\ \hline
+\multirow{4}{*}{\parbox{3.5cm}{\vspace{.1cm}John liked a girl at his work.	He tried to get her attention by acting silly.	She told him to grow up.
+John confesses he was trying to make her like him more.}} & \vspace{-0.2cm}	{\color{blue}{{She feels flattered and asks John on a date.}}} 	 \\\cline{2-2}
+
+%Travis needed some fast cash.	He thought about it and decided that selling his car was a good idea.	Travis listed his car for sale in the local paper.	After only a couple weeks he found somebody very interested.}}& \vspace{-0.2cm}	{\color{blue}{{\it This person came and test drove the car and bought it on the spot.}}} \\\cline{2-2}
+%Joe went to college for art. He graduated with a degree in painting. He couldn't find a job. He then responded to an ad in the paper.
+%\vspace{.3cm}Betsy comes home late one night and wants to eat something simple.	She notices that she has spaghetti and sauce in the house.	She quickly cooks and eats a pot of spaghetti.	After eating, she falls asleep on the couch.}} & \vspace{-0.3cm}	{\color{blue}{{\it $<$waiting for examples from  Nasrin$>$}}} \\ \cline{2-2}
+& 	{\color{forestgreen}{\vspace{-0.1cm}The girl found this charming, and gave him a second chance.% He sold the car and solved his money problems.%She was full and happy.     %Then he got hired.
+}} \\ \cline{2-2}
+& {\color{red}{%Joe hated pizza.\vspace{-0.1cm}Betsy likes{\color{white}{0}}{\color{white}{0}}{\color{white}{0}}{\color{white}{0}} cheeseburgers.
+\vspace{-0.1cm}John was happy about being rejected.%Travis gave it to the man for free.
+}} \\\hline %\cline{2-2}
+%&  \\ \hline
+\end{tabularx}
+\caption{\label{ROC-example}
+Examples of stories from the story cloze task. The table shows a story prefix with three contrastive endings:
+ %of the same story: 
+The {\color{blue}{original}} ending, a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story.
 Unfortunately Nasrin et al.

### 2017-04-14 docs/language_constraint_emnlp.tex
Submitted EMNLP version

@@
 %\aclfinalcopy % Uncomment this line for the final submission
-%\def\aclpaperid{***} %  Enter the acl Paper ID here
+\def\aclpaperid{818} %  Enter the acl Paper ID here
 
@@
 the  {\it story cloze task} \cite{Mostafazadeh:2016},
-where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 constraints looks like 3 constraints.
-clarify}}
-%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
+where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.
 We show that a  linear classifier informed by stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
-%\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
-\roy{In addition, our style-based classifier performs on a par with state-of-the-art models on the story cloze task.} 
-%Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
-Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}
+In addition, our style-based classifier performs on a par with state-of-the-art models on the story cloze task.
+Our results demonstrate that different task framings can dramatically affect the way people write.
 

### 2017-04-15 docs/language_constraint_conll.tex
EMNLP submitted

@@
 \usepackage{caption}
-\usepackage{subcaption}
+%\usepackage{subcaption}
 \usepackage{pgfplots}
 \usepackage{tikz}
+\usepackage{subfig}% http://ctan.org/pkg/subfig
 
@@
     {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
-    \And \hspace{-2cm}Leila Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A. Smith$^1$ \\
+    \And \hspace{-2cm}Li Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A. Smith$^1$ \\
   }
@@
 Both endings were required to complete the story using one of the characters in the story context. 
-Additionally,  the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
+Additionally,  the endings were required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
 
@@
 
-Interestingly, \roy{until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%}\com{at the time of this submission, 10 months after the
-task was first introduced, the published benchmark on this task is still below 60\% \cite{Salle:2016}}.\footnote{The LSDSem 2017 shared
-  task website
-  (\url{https://competitions.codalab.org/competitions/15333}) does
-  report higher results% (71.1\%)
-\resolved{\roy{Tricky. Which number should we report here? leave empty?}
-\nascomment{leave empty for now}}, which
-are still unpublished along with the underlying methodology.}
+Interestingly, \roy{until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%}.
 This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or much shorter periods of time.
 This suggests that this task is challenging and that high performance is hard to achieve.
-\roy{In this paper, we show that this is not necessarily the case, by demonstrating that a simple linear classifier informed with style features reaches near state-of-the-art results on the task---72.4\%.}
- \resolved{\yc{SQuAD was officially published in Nov 2016.
-by the time the official EMNLP talk was presented, the leaderboard performance (still unpublished) was  30\% beyond the best results in the paper.
-Given that, the statement of this paragraph seems a bit of overkill...?} \nascomment{it sounds like Yejin is saying that on squad, there was an even faster acceleration?
-or that we should change ``similar period of time'' to ``similar or shorter period of time''?}}
 
@@
 These results suggest that real understanding of text is required in order to solve the task.
+\roy{In this paper, we show that this is not necessarily the case, by demonstrating that a simple linear classifier informed with style features reaches near state-of-the-art results on the task---72.4\%.}
 
@@
 \begin{small}
-\begin{subfigure}{.5\textwidth}\center
+\subfloat[POS tags]{
+%\begin{subfigure}{.5\textwidth}\center
 \begin{tikzpicture}
@@
         ybar=\pgflinewidth,
-        x=2.5cm,
+        x=1.25cm,
        bar width=5pt,
@@
         ylabel = {Frequency in Corpus (\%)},
-        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
+%        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
+        symbolic x coords={NN, VBD, PRP, DT, NNP},
         xtick = data,
@@
     ]
-        \addplot[style={bblue,fill=bblue,mark=none}]
+    \addplot[style={blue,fill=blue,mark=none}]
+            coordinates {(NN, 15.3) (VBD, 13.4) (PRP, 10.1) (DT, 9.1) (NNP, 4.7)};
+
+        \addplot[style={forestgreen,fill=forestgreen,mark=none}]
+            coordinates {(NN, 15.7) (VBD, 15.8) (PRP, 9.7) (DT, 9.7) (NNP, 8.3)};
+
+        \addplot[style={red,fill=red,mark=none}]
+            coordinates {(NN, 16.3) (VBD, 15.1) (PRP, 7.4) (DT, 9.4) (NNP, 9.5)};
+\com{        \addplot[style={bblue,fill=bblue,mark=none}]
             coordinates {({\it original}, 15.3) ({\it right}, 15.7) ({\it wrong}, 16.3)};
@@
         \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it original}, 4.7) ({\it right}, 8.3) ({\it wrong}, 9.5)};
-
-        \legend{NN, VBD, PRP, DT, NNP}
+            coordinates {({\it original}, 4.7) ({\it right}, 8.3) ({\it wrong}, 9.5)};}
+
+%        \legend{NN, VBD, PRP, DT, NNP}
+	\legend{{\it original}, {\it right}, {\it wrong}}
     \end{axis}
 \end{tikzpicture}
-\caption{\label{roc_pos_distribution}POS tags}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}\center
+%\caption{
+\label{roc_pos_distribution}
+%}
+%\end{subfigure}
+}
+\qquad\qquad\qquad
+\subfloat[Words]{%\begin{subfigure}{.5\textwidth}\center
 \begin{tikzpicture}
@@
 %        ylabel = {Frequency in Corpus (\%)},
-        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
+    %    symbolic x coords={{\it original}, {\it right}, {\it wrong}},
+    symbolic x coords={to, and, I, hates, !},
         xtick = data,
@@
     ]
+
+   \addplot[style={blue,fill=blue,mark=none}]
+            coordinates {(to, 3) (and, 2.5) (I, 1) (hates, 0) (!, 0.9)};
+
+        \addplot[style={forestgreen,fill=forestgreen,mark=none}]
+            coordinates {(to, 3.3) (and, 1.8) (I, 1.2) (hates, 0) (!, 0.2)};
+
+        \addplot[style={red,fill=red,mark=none}]
+            coordinates {(to, 3.5) (and, 1.3) (I, 1.4) (hates, 0.6) (!, 0.1)};
+
+    \com{
         \addplot[style={bblue,fill=bblue,mark=none}]
@@
             coordinates {({\it original}, 0.9) ({\it right}, 0.2) ({\it wrong}, 0.1)};
-
-        \legend{to, and, I, hates, !}
+}
+%        \legend{to, and, I, hates, !}
+        	\legend{{\it original}, {\it right}, {\it wrong}}
+
     \end{axis}
 \end{tikzpicture}
-\caption{\label{roc_word_distribution}Words}
-\end{subfigure}
+%\caption{
+\label{roc_word_distribution}
+%Words}
+%\end{subfigure}
+}
 \end{small}
@@
 the second  between {\it original} endings and new ({\it right}) endings.
-We describe both experiments below.
+For completeness, we also run a third experiment, which compares between {\it original} and {\it wrong} endings. 
+We describe all experiments below.
 
@@
 Here the goal is to measure whether writing the ending as part of a
-story imposes different style compared to writing a new ({\it right}) ending to an existing story.
+story imposes different style compared to writing a {\it new} ({\it right}) ending to an existing story.
 We use the endings of the ROC stories as our {\it original} samples and {\it right} endings from the story cloze task   \resolved{\nascomment{if you're using the test examples as
@@
 %We randomly sample 5 {\it original} sets and repeat the classification experiments.
-We report the average classification result.
+We train five classifiers with each of the {\it original} training sets, and report the average classification result.
 
@@
 
-\subsection{Story cloze task.}
+\subsection{Story cloze task}
 The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
@@
 {\bf Model} & {\bf Acc.} \\ \hline
-{DSSM} \cite{Mostafazadeh:2016} & 0.595 \\ 
+{DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
 {ukp} \cite{Mihaylov:2017} & 0.711\\ 
@@
 We use the ROC stories for training,\footnote{We use the extended, 100K stories corpus (see \secref{ROC_Story}).} setting aside 10\% for validation of the language model. 
-We replace all words occurring less than 3 times with a special
-out-of-vocabulary character, yielding a vocabulary size of  21,582.
+We replace all words occurring less than 3 times with an 
+out-of-vocabulary token, yielding a vocabulary size of  21,582.
 Only during training, we apply a dropout rate of 60\% while running the LSTM over all 5 sentences of the stories. 
@@
 
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{|c|c||c|c|} \hline
-\textit{\textbf{Right}} & Freq. & \textit{\textbf{Wrong}}& Freq. \\ \hline
-`ed .' & {\color{white}{0}}6.5\%& \textsc{start} NNP & 54.8\%\\ \hline
-`and ' & 13.6\%& NN . & 47.5\% \\ \hline
-JJ & 45.8\% & NN NN . & {\color{white}{0}}5.1\%\\ \hline
-to VB & 20.1\%& VBG & 10.1\%\\ \hline
-`d th' & 10.9\%& \textsc{start} NNP VBD & 41.9\%\\ \hline
-%`ally' & 3.3\% & `hate' & {\color{white}{0}}1.9\% \\ \hline
-%VBD the NN .& 2.2\% & ` hat' & {\color{white}{0}}2.0\% \\ \hline
-%\textsc{start} RB & 3.1\% & \textsc{start} NNP & 54.8\% \\ \hline
-%`ved ' &4.1\%&  `ated' & {\color{white}{0}}3.0\%\\ \hline
-%` tim' &2.6\%&  NN . & 47.5\%\\ \hline
-
+\begin{figure*}
+%\small
+\centering
+\subfloat[Experiment 1]{
+\begin{tabular}{|c|c|c||c|c|c|} \hline
+\textit{\textbf{Right}} & Weight & Freq. &   \textit{\textbf{Wrong}}& Weight & Freq.  \\ \hline
+`ed .' & 0.17 & {\color{white}{0}}6.5\%&  \textsc{start} NNP & 0.21& 54.8\%  \\ \hline
+`and ' &  0.15 & 13.6\%  & NN . & 0.17 & 47.5\%  \\ \hline
+JJ & 0.14 & 45.8\%  & NN NN . & 0.15 &  {\color{white}{0}}5.1\%  \\ \hline
+to VB & 0.13 & 20.1\%& VBG & 0.11 & 10.1\%\\ \hline
+`d th' & 0.12 & 10.9\%& \textsc{start} NNP VBD & 0.11 & 41.9\%\\ \hline
 \end{tabular}
-\end{center}
-\caption{\label{exp1_features}
-The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings,
-along with their frequencies in our story cloze training set.
-}
-\end{table}
+\label{exp1_features}
+}
+\quad
+\subfloat[Experiment 2]{
+\begin{tabular}{|c|c|c||c|c|c|} \hline
+\textit{\textbf{Right}} & Weight & Freq. &   \textit{\textbf{Wrong}}& Weight & Freq.  \\ \hline
+{\it length} & 0.81&  {\color{white}{.}}100.0\% & `.' & 0.74&93.0\%\\ \hline
+`!' & 0.46&{\color{white}{00}}6.1\%& \textsc{start} NNP  & 0.40&39.2\% \\ \hline
+NN & 0.35&{\color{white}{0}}78.9\% & \textsc{start} NNP VBD &0.23&29.0\% \\ \hline
+RB & 0.34&{\color{white}{0}}44.7\%& NN . & 0.20&42.3\% \\ \hline
+`,' & 0.32&{\color{white}{0}}12.7\%&  the NN . & 0.20&10.6\% \\ \hline
+
+\end{tabular}
+\label{exp2_features}
+}
+\caption{
+The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings (\ref{exp1_features}) and  {\it original} vs.~new ({\it right}) endings (\ref{exp2_features}). 
+{\it length} is the sentence length feature (see \secref{Model}).
+}
+%\end{table}
+
+%\end{subfigure}
+\end{figure*}
 
@@
 
-\setlength\tabcolsep{.15cm}
-\begin{table}[!t]
-\begin{center}
-\begin{tabular}{|p{1.25cm}|c||p{2.9cm}|c|} \hline
-\textit{\textbf{Original}} & Freq. & \textit{\textbf{New}}& Freq. \\ \hline
-{\it length} & {\color{white}{.}}100.0\% & `.' & 93.0\%\\ \hline
-`!' & {\color{white}{00}}6.1\%& \textsc{start} NNP  & 39.2\% \\ \hline
-NN & {\color{white}{00}}78.9\% & \textsc{start} NNP VBD &29.0\% \\ \hline
-RB & {\color{white}{0}}44.7\%& NN . & 42.3\% \\ \hline
-`,' & {\color{white}{0}}12.7\%&  the NN . & 10.6\% \\ \hline
-
-\end{tabular}
-\end{center}
-\caption{\label{exp2_features}
-The top 5 most heavily weighted features for predicting {\it original} vs.~new ({\it right}) endings.
-{\it length} is the sentence length feature (see \secref{Model}).
-}
-\end{table}
-
 \isectionb{Discussion}
@@
 \paragraph{The effect of writing tasks on mental states.}
-In this paper we have shown that giving a writer different writing tasks affects her writing style in easily detected ways.
+In this paper we have shown that different writing tasks affect a writer's writing style in easily detected ways.
 Our results indicate that when authors are asked to write the last
@@
 involves differences in mental state. 
-Further investigation is required in order to further validate this hypothesis.
+Additional investigation is required in order to further validate this hypothesis.
 
@@
  Nonetheless, despite these efforts, several significant style
- differences can be found between the training and the test set, as well as between the positive and negative labels.
+ differences can be found between the story cloze training and test set, as well as between the positive and negative labels.
 
@@
 \roy{The COPA dataset \cite{Roemmele:2011}, which was also designed to test commonsense knowledge, explicitly addressed potential style differences in their instructions.
-In this task,  systems are presented with premises like {\it I put my plate in the sink.} and then letting it decide between two alternatives, e.g.: (a) {\it I finished eating.} and (b) {\it I skipped dinner.}}
+In this task,  systems are presented with premises like {\it I put my plate in the sink}, and then decide between two alternatives, e.g.: (a) {\it I finished eating.} and (b) {\it I skipped dinner.}}
 Importantly, when writing the alternatives,  annotators were asked to be as brief as possible and avoid proper names, as well as  slang.
@@
 
-Another way to avoid such effects is by instructing authors to write shorter text spans, such as the ones used in the Winograd schema \cite{Levesque:2011}.
-A different approach is to use naturally occurring text, as used in recent machine reading tasks (see \secref{Related}). 
+Another way to avoid such effects is to use naturally occurring text, as used in recent machine reading tasks (see \secref{Related}). 
 %However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
-Finally, a third approach is to have people rate sentences from naturally occurring text by parameters
+Finally, a different approach is to have people rate sentences from naturally occurring text by parameters
 such as coherence (or, very differently, the level of surprise),

### 2017-04-18 docs/language_constraint_conll.tex
CoNLL V2 (Roy)

@@
 In order to further validate our method, we also directly tackle the
-story cloze task\nascomment{cite the challenge?  a reader may
-  not realize that there is a shared task on this}\resolved{\roy{Maybe ``challenge'' was not the right term here.
-We basically mean the story cloze task.
-The shared task was the original task w/o any modification, so I am not referring to it specifically here}}.
+story cloze task. 
 Adapting our classifier to the task, we obtain 72.4\% accuracy, \com{a
@@
 stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently,
-  an additional 53K stories were released, which results in roughly
+  additional 53K stories were released, which results in roughly
   100K stories.}
@@
 slightly longer than {\it wrong} ones (8.47 words). 
-Previous work has shown that sentence length is also indicative of whether a text was deceptive \cite{yancheva2013automatic,qin2004exploratory}. 
+The latter finding is consistent with previous work, which has shown that sentence length is also indicative of whether a text was deceptive \cite{yancheva2013automatic,qin2004exploratory}. 
 Although writing {\it wrong} sentences is not the same as lying, it is not entirely surprising to observe similar trends in both tasks.
@@
         ymin=3,
-        legend cell align=left,
-        legend style={
-        		legend columns=-1,
-                at={(1,1.05)},
-                anchor=south east,
-                column sep=1ex
-        }
+%        legend cell align=left,
+%        legend style={
+%        		legend columns=-1,
+%                at={(1,1.05)},
+%                anchor=south east,
+%                column sep=1ex
+%        }
     ]
@@
 %        \legend{NN, VBD, PRP, DT, NNP}
-	\legend{{\it original}, {\it right}, {\it wrong}}
+%	\legend{{\it original}, {\it right}, {\it wrong}}
     \end{axis}
@@
         ymin=0,
-        legend cell align=left,
-        legend style={
-        		legend columns=-1,
-                at={(1,1.05)},
-                anchor=south east,
-                column sep=1ex
-        }
+%        legend cell align=left,
+%        legend style={
+%        		legend columns=-1,
+%                at={(1,1.05)},
+%                anchor=south east,
+%                column sep=1ex
+%        }
     ]
@@
 %        \legend{to, and, I, hates, !}
-        	\legend{{\it original}, {\it right}, {\it wrong}}
+%        	\legend{{\it original}, {\it right}, {\it wrong}}
 
@@
   (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})
-  across \emph{original} endings (story cloze training set), and
-  \emph{right} and \emph{wrong} endings (from the story cloze task).}
+  across {\color{blue}{\emph{original}}} endings (story cloze training set), and
+  {\color{forestgreen}{\emph{right}}} and {\color{red}{\emph{wrong}}} endings (from the story cloze task).}
 
@@
 We train a logistic regression classifier to categorize an ending,
-either as {\it right} vs.~{\it wrong} or as {\it original} vs.~new ({\it right}).
+either as {\it right} vs.~{\it wrong} or as {\it original} vs.~{\it new} ({\it right}).
 Each feature vector is computed using the words in one ending, without considering earlier parts of the story. 
@@
 The first is an attempt to distinguish between {\it right} and {\it wrong} endings,
-the second  between {\it original} endings and new ({\it right}) endings.
+the second  between {\it original} endings and {\it new} ({\it right}) endings.
 For completeness, we also run a third experiment, which compares between {\it original} and {\it wrong} endings. 
@@
 %We randomly sample 5 {\it original} sets and repeat the classification experiments.
-We train five classifiers with each of the {\it original} training sets, and report the average classification result.
+We train five classifiers, one with each of the {\it original} training sets, and report the average classification result.
 
@@
         ymin=0.4,
-        legend cell align=left,
-        legend style={
-                at={(1,1.05)},
-                anchor=south east,
-                column sep=1ex
-        }
+%        legend cell align=left,
+%        legend style={
+%                at={(1,1.05)},
+%                anchor=south east,
+%                column sep=1ex
+%        }
     ]
@@
 \begin{center}
-\begin{tabular}{|l|r|} \hline
+\begin{tabular}{|l|c|} \hline
 {\bf Experiment} & {\bf Accuracy} \\ \hline
@@
 \begin{center}
-\begin{tabular}{|c|c|} \hline
+\begin{tabular}{|l|c|} \hline
 {\bf Feature Type} & {\bf Accuracy}\\ \hline
@@
 
-Second, {\it right} endings will make wider use of coordination structures, as well as adjectives.
+Second, {\it right} endings make wider use of coordination structures, as well as adjectives.
 The latter might indicate that writing coherent stories inspires the authors to write more descriptive text compared to incoherent ones, 
 as is the case in truthful vs.~deceptive text \cite{ott2011finding}.
-Finally, we notice a few syntactic differences: {\it right} endings will more often use infinite verb structure, while {\it wrong} endings prefer gerunds (VBG).
+Finally, we notice a few syntactic differences: {\it right} endings more often use infinite verb structure, while {\it wrong} endings prefer gerunds (VBG).
 
@@
 \caption{
-The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings (\ref{exp1_features}) and  {\it original} vs.~new ({\it right}) endings (\ref{exp2_features}). 
+The top 5 most heavily weighted features for predicting {\it right} vs.~{\it wrong} endings (\ref{exp1_features}) and  {\it original} vs.~{\it new} ({\it right}) endings (\ref{exp2_features}). 
 {\it length} is the sentence length feature (see \secref{Model}).
@@
 Finally, when comparing the two groups of salient features from both experiments, we find an interesting trend.
-Several features, such as ``\textsc{start} NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict new (i.e., {\it right}) endings in Experiment 2. 
+Several features, such as ``\textsc{start} NNP'' and  ``NN .'', which indicate {\it wrong} sentences in Experiment 1, are used to predict {\it new} (i.e., {\it right}) endings in Experiment 2. 
 This indicates that, for instance, incoherent endings have a stronger tendency to begin with a proper noun compared to coherent endings, 
@@
 While this could be partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), this indicates that simple instructions may help alleviate the effects of writing style found in this paper.
-
-Another way to avoid such effects is to use naturally occurring text, as used in recent machine reading tasks (see \secref{Related}). 
-%However,  these approaches have their shortcomings, and do not capture the same signal as intended by the author of the story cloze task.
-Finally, a different approach is to have people rate sentences from naturally occurring text by parameters
-such as coherence (or, very differently, the level of surprise),
+Another way to avoid such effects is to have people rate naturally occurring sentences  by parameters
+such as coherence (or, conversely, the level of surprise),
 rather than asking them to generate new text.

### 2017-04-18 docs/language_constraint_conll.tex
Noah

@@
 %\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
-\roy{In addition, our style-based classifier's performance on the story cloze challenge is comparable to state-of-the-art results.} 
+\roy{In addition, our style-based classifier's performance on the
+  story cloze challenge is comparable to the state of the art.}
 %Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
@@
 We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
-Our final model that combines context with stylistic features achieves \roy{new state-of-the-art results---}
-75.2\%---an additional 2.8\% gain\com{, 15.3\% better than the best
+Our final model that combines context with stylistic features achieves
+\roy{a new state of the art---}75.2\%---an additional 2.8\% gain\com{, 15.3\% better than the best
 published result}.
@@
 
-On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} samples, which serve as the positive samples in the development and test sets.
+On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} endings, which serve as the positive samples in the development and test sets.
 While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
@@
 \item\textit{\textbf{Length}:} the number of words in the sentence.
-\item\textit{\textbf{Word $n$-grams:}} we use sequences of 1-5
+\item\textit{\textbf{Word $n$-grams:}} we use sequences of 1--5
   words. Following \citet{Tsur:2010} and \citet{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
@@
 For completeness, we also run a third experiment, which compares between {\it original} and {\it wrong} endings.
-We describe all experiments below.
 
@@
 
-\subsection{Story cloze task}
+\subsection{Story Cloze Task}
 The results of Experiment 1 indicate that {\it right} and {\it wrong} endings are characterized by different styles.
@@
 Using the Adam optimizer \cite{kingma2014adam} and a learning rate of
-$\eta=.001$, we train to minimize cross-entropy. % minibatches of $50$ stories.
+$\eta=0.001$, we train to minimize cross-entropy. % minibatches of $50$ stories.
 % h=512, dropout rate of 60%, V=21582, 10% validation set

### 2017-04-19 docs/language_constraint_conll.tex
CoNLL V3 (Roy)

@@
 \usepackage{tikz}
+\usetikzlibrary{patterns}
 \usepackage{subfig}% http://ctan.org/pkg/subfig
@@
 Adapting our classifier to the task, we obtain 72.4\% accuracy, \com{a
- 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}}\roy{only 2\% below state-of-the-art results}.
+ 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}}\roy{only 2\% below state of the art results}.
 We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
@@
 %both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
-Third, we establish a new state-of-the-art result on the commonsense story cloze challenge.
+Third, we establish a new state of the art result on the commonsense story cloze challenge.
 
@@
 These results suggest that real understanding of text is required in order to solve the task.
-\roy{In this paper, we show that this is not necessarily the case, by demonstrating that a simple linear classifier informed with style features reaches near state-of-the-art results on the task---72.4\%.}
+\roy{In this paper, we show that this is not necessarily the case, by demonstrating that a simple linear classifier informed with style features reaches near state of the art results on the task---72.4\%.}
 
@@
     ]
-    \addplot[style={blue,fill=blue,mark=none}]
+    \addplot[style={blue,fill=blue,pattern=horizontal lines, pattern color=blue,mark=none}]
             coordinates {(NN, 15.3) (VBD, 13.4) (PRP, 10.1) (DT, 9.1) (NNP, 4.7)};
 
-        \addplot[style={forestgreen,fill=forestgreen,mark=none}]
+        \addplot[style={forestgreen,fill=forestgreen,pattern=north west lines, pattern color=forestgreen,mark=none}]
             coordinates {(NN, 15.7) (VBD, 15.8) (PRP, 9.7) (DT, 9.7) (NNP, 8.3)};
@@
 
-        \addplot[style={rred,fill=rred,mark=none}]
+        \addplot[pattern=dots,style={rred,fill=rred,mark=none}]
             coordinates {({\it original}, 13.4) ({\it right}, 15.8) ({\it wrong}, 15.1)};
@@
 
-   \addplot[style={blue,fill=blue,mark=none}]
+   \addplot[style={blue,fill=blue,pattern=horizontal lines, pattern color=blue,mark=none}]
             coordinates {(to, 3) (and, 2.5) (I, 1) (hates, 0) (!, 0.9)};
 
-        \addplot[style={forestgreen,fill=forestgreen,mark=none}]
+        \addplot[style={forestgreen,fill=forestgreen,pattern=north west lines, pattern color=forestgreen,mark=none}]
             coordinates {(to, 3.3) (and, 1.8) (I, 1.2) (hates, 0) (!, 0.2)};
@@
   (\ref{roc_pos_distribution}) and words (\ref{roc_word_distribution})
-  across {\color{blue}{\emph{original}}} endings (story cloze training set), and
-  {\color{forestgreen}{\emph{right}}} and {\color{red}{\emph{wrong}}} endings (from the story cloze task).}
+  across {\color{blue}{\emph{original}}} endings (horizontal lines) from the story cloze training set, and
+  {\color{forestgreen}{\emph{right}}} (diagonal lines) and {\color{red}{\emph{wrong}}} (solid lines) endings, both from the story cloze task.}
 
@@
 \tabref{cloze_results} shows our results on the story cloze test
-set. Our classifier obtains 72.4\% accuracy, \roy{only 2\% lower than state-of-the-art results, and equal or higher to all other published results}\com{12.5\% (absolute) higher than the
+set. Our classifier obtains 72.4\% accuracy, \roy{only 2\% lower than state of the art results, and equal or higher to all other published results}\com{12.5\% (absolute) higher than the
 published state-of-the-art result on the task \cite{Salle:2016}}\resolved{\nascomment{cite that here}}.
@@
 \paragraph{Combination with a neural language model.}
-We investigate whether our model can benefit from state-of-the-art text comprehension models, for which this task was designed. 
+We investigate whether our model can benefit from state of the art text comprehension models, for which this task was designed. 
 Specifically, we experiment with an LSTM-based \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
@@
 We retrain our linear  model with the new feature set, and gain 2.8\%
-absolute, reaching 75.2\%\com{ (15.3\% better than the published state-of-the-art\com{ and 4.1\% better than the best unpublished} result)}\roy{, a new-state-of-the-art result for the task.}\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
+absolute, reaching 75.2\%\com{ (15.3\% better than the published state of the art\com{ and 4.1\% better than the best unpublished} result)}\roy{, a new state of the art result for the task.}\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
 These results indicate that context-ignorant style features can be used to obtain high
@@
 which in turn allows our final 
-model to achieve state-of-the-art results on the story cloze task.
+model to achieve state of the art results on the story cloze task.
 

### 2017-06-08 docs/language_constraint_conll_camera_ready.tex
CoNLL camera ready

--- 2017-04-19 docs/language_constraint_conll.tex
@@
 \usepackage{caption}
-%\usepackage{subcaption}
 \usepackage{pgfplots}
@@
 
-%\aclfinalcopy % Uncomment this line for the final submission
+\aclfinalcopy % Uncomment this line for the final submission
 %\def\aclpaperid{***} %  Enter the acl Paper ID here
@@
 \newcommand{\isubsectionb}[1]{\subsection{#1}\label{ssec:#1}}
-\newcommand{\com}[1]{}
-\newcommand{\resolved}[1]{}
+
 % Editing macros
@@
 
-\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
-\newcommand{\roy}[1]{{\color{orange}\textsc{[#1 --rs]}}}
-\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
-\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
-\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
-\newcommand{\nascomment}[1]{{\color{blue}\textsc{[#1 --nas]}}}
-\newcommand{\clinic}[1]{{\color{magenta}\textsc{[#1 --CLINIC]}}}
+%\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
+%\newcommand{\roy}[1]{{\color{orange}\textsc{[#1 --rs]}}}
+%\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
+%\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
+%\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
+%\newcommand{\nascomment}[1]{{\color{blue}\textsc{[#1 --nas]}}}
+%\newcommand{\clinic}[1]{{\color{magenta}\textsc{[#1 --CLINIC]}}}
 
-\renewcommand{\roy}[1]{{\color{orange}[#1 --rs]}}
+%\renewcommand{\roy}[1]{{\color{orange}[#1 --rs]}}
 
 %\renewcommand{\ms}[1]{}
-\renewcommand{\roy}[1]{#1}
+%\renewcommand{\roy}[1]{#1}
 %\renewcommand{\roy}[1]{}
-\renewcommand{\nascomment}[1]{}
-\renewcommand{\yc}[1]{}
+%\renewcommand{\nascomment}[1]{}
+%\renewcommand{\yc}[1]{}
 %\renewcommand{\royb}[1]{}
@@
     {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
-    \And \hspace{-2cm}Li Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A. Smith$^1$ \\
+    \And \hspace{-2cm}Li Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A.~Smith$^1$ \\
   }
@@
 the  {\it story cloze task} \cite{Mostafazadeh:2016},
-where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.\resolved{\clinic{Many felt these 2 constraints looks like 3 constraints.
-clarify}}
-%We show that a linear classifier, which applies only simple style features, such as sentence length and character n-grams, 
+where annotators were assigned similar writing tasks with different constraints: (1) writing an entire story, (2) adding a story ending for a given story context, and (3) adding an incoherent ending to a story.
 We show that a simple linear classifier informed by stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
-%\roy{In addition, our style-based classifier reaches only 2\% below state-of-the-art results on the story cloze challenge, equal or higher to other previous results.} 
-\roy{In addition, our style-based classifier's performance on the
-  story cloze challenge is comparable to the state of the art.}
-%Furthermore, combining our model with an LSTM-based language model, which does look at the context, leads to additional gains.
-Our results demonstrate that different task framings can dramatically affect the way people write.\resolved{\clinic{Similarly to previous comment: which results does this comment address?}}
-
-\resolved{They also provide important lessons for designing new NLP
-tasks. \nascomment{drop this sentence if we only have a paragraph
-  about this at the end, as we currently do}}
+In addition, our style-based classifier's performance on the
+  story cloze challenge is comparable to the state of the art.
+Our results demonstrate that different task framings can dramatically affect the way people write.\footnote{This paper extends our LSDSem 2017 shared task submission \cite{Schwartz:2017b}.}
 
@@
 by personality traits such as agreeableness and openness  \cite{Ireland:2014b},
-as well as by mental states\resolved{\clinic{Avoid using ``cognitive"?}} such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
+as well as by mental states such as sentiment \cite{Davidov:2010}, sarcasm \cite{Tsur:2010}, and deception \cite{Feng:2012}.  
 In this paper, we study the extent to which writing style is affected by the nature of the writing task the writer was asked to perform, since
-different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\roy{\footnote{For the purposes of this paper, \emph{style} is defined as content-agnostic writing characteristics, such as the number of words in a sentence.}}
-
-\com{
-\begin{table}[!t]
-%\begin{tabular}{|p{4.8cm}|p{2.1cm}|} \hline
-\begin{tabular}{|p{4.5cm}|p{2.4cm}|} \hline
-{\bf Story Prefix} & {\bf Ending} \\ \hline
-My mother loves clocks that chime.	Her house is full of them.	She sets them each a little different so she can hear them chime.	It sounds like a bell tower during a wedding in her house all day.	& {\color{blue}{When I visit I stop them or I'd never be able to sleep at night.}} \\ \hline
-\multirow{2}{4.5cm}{Joe went to college for art.
-He graduated with a degree in painting.
-He couldn't find a job.
-He then responded to an ad in the paper.} & 	{\color{forestgreen}{Then he got hired.}} \\ \cline{2-2}
-& {\color{red}{Joe hated pizza.}} \\ \hline
-\end{tabular}
-\caption{\label{ROC-example}
-Examples of stories from the story cloze task \cite{Mostafazadeh:2016}. The first row shows an {\color{blue}{original}} story written by one author. 
-The second and third rows show revised stories with two contrastive endings:
- %of the same story: 
- a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story.
-Unfortunately Nasrin et al.
-didn't publish the original endings for the dev/test data.
-We could ask her, but not sure if this is worth it}}
- \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
-let's consider just color-coding these three terms.  It's less distracting.}}
-}
-%\end{center}
-\end{table}}
+different tasks likely engage different cognitive processes \cite{Campbell:2003,Banerjee:2014}.\footnote{For the purposes of this paper, \emph{style} is defined as content-agnostic writing characteristics, such as the number of words in a sentence.}
 
@@
 Examples of stories from the story cloze task. The table shows a story prefix with three contrastive endings:
- %of the same story: 
-The {\color{blue}{original}} ending, a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.\resolved{ \clinic{They said it would be great to have three endings to the same story.
-Unfortunately Nasrin et al.
-didn't publish the original endings for the dev/test data.
-We could ask her, but not sure if this is worth it}}
- \resolved{\nascomment{I like the colors a lot.  Instead of all the italicizing,
-let's consider just color-coding these three terms.  It's less distracting.}}
+The {\color{blue}{original}} ending, a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.
 }
-%\end{center}
 \end{table}
@@
 the recently introduced ROC story cloze task \cite{Mostafazadeh:2016}. 
-In this task, \com{crowdsourced }authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
+In this task, authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
 %Following, 
@@
 \tabref{ROC-example} shows an example of an {original} story, a {coherent} story, and an {incoherent} story.
-
-\com{While originally designed to be a story understanding challenge, the annotation process triggers interesting questions 
-that may go beyond the original intent of the designers.
-First, do people maintain the same writing 
-style when asked to write both coherent and incoherent story endings? 
-Second, do people maintain the same writing style when writing the entire story on their own compared to 
-writing only the final sentence for a given story context written by someone else? }
-
-\com{
-%Our analysis indicates that the answer to both questions is positive. 
-Our analysis indicates that different framings of similar writing tasks 
-can lead to measurable differences in people's writing style.\clinic{This is the main message -- should come earlier}
-%We experiment with a linear classifier, using simple stylistic features, such as sentence length, character n-grams and word n-grams. 
-%First, we show that on a balanced dataset (chance level is 50\%) our classifier distinguishes between the {\it right} and {\it wrong} endings in 64.5\% of the cases. 
-Using a simple classifier informed with stylistic features, we show that our classifier can distinguish the {\it right} and {\it wrong} endings with 64.5\% accuracy, even without looking at the story context, where chance performance is 50\%.
-%It is also trained on a set of positive samples and a set of negative ones, rather than pairs of (positive, negative) pairs, as in the original story cloze task.
-%Second, when trained to distinguish between the {\it original} endings and the new ({\it right}) endings, the classifier obtains 68.5\% accuracy. 
-Further, our classifier can also distinguish between the {\it original} endings and the new ({\it right}) endings with 68.5\% accuracy, again without looking at the story context.
-\clinic{Why do we care?
-(Luke)}
-}
-
-\com{We show that a linear classifier informed with stylistic features can distinguish among {\it original}, {\it right}, and {\it wrong}  endings to a large degree, even without looking at the story context.
-Our results allow us to make a few key observations.
-First, people adopt a different writing style when asked to write coherent vs.~incoherent story endings.
-Second,  people change their writing style when writing the entire story on their own compared to 
-writing only the final sentence for a given story context written by someone else.}
-
-%Our binary classification results range between 64.5\%--75.6\%, where chance performance is 50\%.
-
-%Importantly, in both experiments, the classifier uses {\bf only} the 
-%last sentence of each of the stories, and does not consider the first four sentences.
-%final sentence without the story context.
 
@@
 story cloze task. 
-Adapting our classifier to the task, we obtain 72.4\% accuracy, \com{a
- 12.5\% increase over the previously reported state-of-the-art  \cite{Salle:2016}}\roy{only 2\% below state of the art results}.
+Adapting our classifier to the task, we obtain 72.4\% accuracy, only 2.3\% below state of the art results.
 We also show that the style differences captured by our model can be combined with neural language models to make a better use of the story context. 
 Our final model that combines context with stylistic features achieves
-\roy{a new state of the art---}75.2\%---an additional 2.8\% gain\com{, 15.3\% better than the best
-published result}.
-
-\com{Our results suggest that writing style is affected by the the writer's state of mind.
-Writing a sentence intended to be {\it wrong} turns out quite differently than a sentence intended to be {\it right}. 
-Similarly, writing a sentence as part of the story is different from reading a story, and then writing the final sentence.}
+a new state of the art---75.2\%---an additional 2.8\% gain.
 
@@
 how different kinds of cognitive load influence the style of written language. 
-Second, our results indicate that when designing new NLP tasks, special attention needs to be payed to the instructions given to authors.
+Second, combined with recent similar findings of \cite{Cai:2017}, our results indicate that when designing new NLP tasks, special attention needs to be paid to the instructions given to authors.
 %both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
 Third, we establish a new state of the art result on the commonsense story cloze challenge. 
-
-\com{
-The remainder of this paper is organized as follows. In \secref{ROC_Story} we describe the story cloze task.
-We then present our model, experiments and results in Sections \ref{ssec:Model}, \ref{ssec:Experiments} and \ref{ssec:Results} respectively.
-Sections \ref{ssec:Ablation} and \ref{ssec:Discussion} present a further analysis of our results  and a discussion, followed by related work and conclusions.\clinic{Omit this paragraph?}}
+Our code is available at \url{https://github.com/roys174/writing_style}.
 
@@
 %The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
-The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are not included in the training set).\resolved{\roy{added {\it not} here}}
+The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are not included in the training set).
 The task was suggested as an extensive evaluation framework:
 %as a machine reading task, 
-as a commonsense story understanding task\com{, 
-as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017),} and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
+as a commonsense story understanding task, 
+as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017, \citet{LSDSem:2017}), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
 
-Interestingly, \roy{until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%}.
+Interestingly, until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%.
 This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or much shorter periods of time.
@@
 These results suggest that real understanding of text is required in order to solve the task.
-\roy{In this paper, we show that this is not necessarily the case, by demonstrating that a simple linear classifier informed with style features reaches near state of the art results on the task---72.4\%.}
+In this paper, we show that this is not necessarily the case, by demonstrating that a simple linear classifier informed with style features reaches near state of the art results on the task---72.4\%.
 
 \paragraph{Different writing tasks in the story cloze task.}
-Several key design decisions make the task an interesting testbed for the purpose of this study.\resolved{\clinic{Which purpose?}}
+Several key design decisions make the task an interesting testbed for the purpose of this study.
 First, the training set for the task (ROC Stories corpus) is not a
@@
   instances are not drawn from a population similar to the one that future
-  testing instances will be drawn from.%\roy{I added \textbf{not}
-                                %here, as otherwise it is confusing}
+  testing instances will be drawn from.
 }  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones.
- \resolved{\yc{As far as I understand, this was intentional --- they didn't want
-  people to pick up on random superfluous cues that can inevidently
-  get into the data creation process, exactly the kind that our work
-  picks up. Given that, stating this can be viewed as
-  misunderstanding, I'm afraid.} \nascomment{We should maybe say that
-  they did this intentionally and concede that our approach goes
-  against the intentions of their task design.  But a task that
-  insists that systems avoid using features that might encode one kind
-of information (like style) is absurd.  Alternately, we could reframe
-this not as ``things weren't controlled for'' but instead stick to the
-facts here and just describe what they did without judgment.}}
 
@@
 In the other case, the author was asked to write a {\it wrong} ending, which would result in an incoherent five-sentence story.
- \resolved{In this work, we show that these differences are significant and
-impose different writing styles on authors. \nascomment{this bit feels
-  a little heavy and reptititive.}}
 
@@
 slightly longer than {\it wrong} ones (8.47 words). 
-The latter finding is consistent with previous work, which has shown that sentence length is also indicative of whether a text was deceptive \cite{yancheva2013automatic,qin2004exploratory}. 
-Although writing {\it wrong} sentences is not the same as lying, it is not entirely surprising to observe similar trends in both tasks.
+The latter finding is consistent with previous work, which has shown that sentence length is also indicative of whether a text was deceptive \cite{qin2004exploratory,yancheva2013automatic}. 
+Although writing {\it wrong} sentences is not the same as deceiving, it is not entirely surprising to observe similar trends in both tasks.
 %Furthermore, \citet{Buller:1996} suggests lying increases one's cognitive load, which in turn could affect sentence length.
@@
 %In contrast, {\it wrong} and {\it right} endings favor proper nouns compared to {\it original} endings.
- \resolved{\yc{Is there literature that may have shown that (1) pronouns correlate with coherent text, and/or (2) referencing characters by proper nouns shows a way of cognitive distancing...?}}
- \resolved{\ms{The proper noun thing is prolly related to the task design, which stated that people had to use at least one of the characters; research shows people usually use more other references when lying, but it's not clear whether there's a pronoun/proper noun distinction.}}
-  \resolved{\roy{Good point!
-This is tricky.
-On the one hand, it hurts our story by saying that the difference is not really the general task by itself, but also the constraints put by  Nasrin et al.
-It also forces us to bash them some more.
-Or we can just ignore it...} }
-  \resolved{\yc{Ok!
-I resolved all comments above and also commented out the comment on how wrong/right endings use more proper nouns compared to the original endings.
-I think it's the best not to talk about this.}}
 
@@
 be used to distinguish among the different types of story endings.
-
-\com{\begin{table*}[!t]
-\begin{center}
-\begin{tabular}{|p{2.5cm}|p{4cm}|p{4cm}|p{4cm}|} \hline
- & {\bf Original}& {\bf Right} & {\bf Wrong}\\ \hline
-Sentence Length (\#words) & 11.02 & 8.75 & 8.47\\ \hline
-Most Frequent POS tags (\%)  & NN:15.3\%, VBD:13.4\%, PRP:10.1, CC:3.3\%, IN:8.7\% & VBD:15.8\%, NN:15.7\%, CC:2\%, PRP:8.8\%, NNP:8.3\%  & NN:16.3\%, VBD:15.1\%,  NNP:9.5\%, DT:1.4, IN:7.9\%\\ \hline
-Most Frequent Words  (\%) & the:4.5\%, to:3.3\%, and:2.7\%, was:2.6\%, a:2.2\% & the:4.8\%, to:3.9\%, was:3.5\%, a:2.5\%, and:2.1\%   & the:5\%, to:4\%, was:3\%, a:2\%, I:1.6\%\\ \hline
-\end{tabular}
-\end{center}
-\caption{\label{roc_pos_distribution} 
-\end{table*}
-}}
 
@@
             coordinates {(NN, 16.3) (VBD, 15.1) (PRP, 7.4) (DT, 9.4) (NNP, 9.5)};
-\com{        \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it original}, 15.3) ({\it right}, 15.7) ({\it wrong}, 16.3)};
-
-        \addplot[pattern=dots,style={rred,fill=rred,mark=none}]
-            coordinates {({\it original}, 13.4) ({\it right}, 15.8) ({\it wrong}, 15.1)};
-
-        \addplot[style={ggreen,fill=ggreen,mark=none}]
-            coordinates {({\it original}, 10.1) ({\it right}, 9.7) ({\it wrong}, 7.4)};
-
-        \addplot[style={brown,fill=brown,mark=none}]
-            coordinates {({\it original}, 9.1) ({\it right}, 9.7) ({\it wrong}, 9.4)};
-
-        \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it original}, 4.7) ({\it right}, 8.3) ({\it wrong}, 9.5)};}
-
-%        \legend{NN, VBD, PRP, DT, NNP}
-%	\legend{{\it original}, {\it right}, {\it wrong}}
     \end{axis}
@@
 
-    \com{
-        \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it original}, 3) ({\it right}, 3.3) ({\it wrong}, 3.5)};
-
-        \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it original}, 2.5) ({\it right}, 1.8) ({\it wrong}, 1.3)};
-
-        \addplot[style={ggreen,fill=ggreen,mark=none}]
-            coordinates {({\it original}, 1) ({\it right}, 1.2) ({\it wrong}, 1.4)};
-
-        \addplot[style={brown,fill=brown,mark=none}]
-            coordinates {({\it original}, 0) ({\it right}, 0) ({\it wrong}, 0.6)};
-
-        \addplot[style={gray,fill=gray,mark=none}]
-            coordinates {({\it original}, 0.9) ({\it right}, 0.2) ({\it wrong}, 0.1)};
-}
-%        \legend{to, and, I, hates, !}
-%        	\legend{{\it original}, {\it right}, {\it wrong}}
-
     \end{axis}
@@
   across {\color{blue}{\emph{original}}} endings (horizontal lines) from the story cloze training set, and
-  {\color{forestgreen}{\emph{right}}} (diagonal lines) and {\color{red}{\emph{wrong}}} (solid lines) endings, both from the story cloze task.}
+  {\color{forestgreen}{\emph{right}}} (diagonal lines) and {\color{red}{\emph{wrong}}} (solid lines) endings, both from the story cloze task development set.}
 
 \end{figure*}
-
-%\roy{Other things to talk about (not necessarily in that order): 
-%1.
-no training corpus for the task.
-That is, the training set (a) does not contain negative example (just positive), and (b) was not generated in the same way as the positive test samples.
-Here you need to explicitly say that we show that we show that the training and test sets use very different styles.
-%2. Maybe talk about the shared task, as well as their RepEval paper, which suggested this task as a vector-space evaluation measure?
-%3.
-Say that the authors did an extensive work in order to  assure that the positive and negative samples are not easily distinguishable: for each pair, both endings were written by the same author (you addressed this earlier, but this seems like a better location), they tried an extensive set of baselines, showing all don't surpass a random baseline by much.
-Maybe now you can briefly mention the benchmarks, saying that several baselines were presented in the papers.
-All benchmarks attempted to learn the connection between the previous paragraph and the ending, and all performed near chance level..
-However, no baseline looked at the endings independently.
-%Then you can add the benchmark text below, and conclude that this indicates that this task is well designed and hard and the one hand, but might also point to potential disagreements between the train and the test data, which we highlight in this paper.}
 
@@
 \item\textit{\textbf{Character $n$-grams:}} character $n$-grams are one of the most useful features in identifying author style \cite{Stamatatos:2009}. 
-We use character $4$-grams.\footnote{\roy{Experiments with $5$-grams on our development set reached similar performance.}}
+We use character $4$-grams.\footnote{Experiments with $5$-grams on our development set reached similar performance.}
 \end{itemize}
@@
 and focus on the difference between the styles accompanied with {\it right} and {\it wrong} writings.
-\resolved{we
-are able make a more general claim about the style used when writing
-each of the tasks \nascomment{I'm not sure I follow this sentence; can
-we be more clear?}.}
 
@@
 story imposes different style compared to writing a {\it new} ({\it right}) ending to an existing story.
-We use the endings of the ROC stories as our {\it original} samples and {\it right} endings from the story cloze task   \resolved{\nascomment{if you're using the test examples as
-  training data, what are you using for test? and development?  I would have thought
-  you'd follow the same pattern as above ... }}as {\it new} samples.
+We use the endings of the ROC stories as our {\it original} samples and {\it right} endings from the story cloze task  as {\it new} samples.
 As there are far more {\it original} instances than {\it new}
 instances, we randomly select five  {\it original} sets, each with the same number of
-instances  \resolved{\nascomment{(give the number in parentheses, for train/dev/test)} }as we have
+instances as we have
 \emph{new} instances (3,366 training endings, 374 development endings, and 3,742 test endings).
@@
 
-\roy{\paragraph{Experiment 3: original/wrong endings.}
+\paragraph{Experiment 3: original/wrong endings.}
 For completeness, we measure the extent to which our classifier can discriminate between {\it original} and {\it wrong} endings.
-We replicate Experiment 2, this time replacing {\it right} endings with {\it wrong} ones.}
+We replicate Experiment 2, this time replacing {\it right} endings with {\it wrong} ones.
 
@@
 regularization, performing grid search on the development set to
-tune a single hyperparameter---the regularization parameter.   \resolved{\nascomment{any other hyperparameters?  if
-  not, say this is the only one.  else explain what they are.}}
+tune a single hyperparameter---the regularization parameter.
 
@@
 strong evidence that the authors' style was affected by the writing task they
-were given to perform.\com{ On our third task, which compared 
-\emph{original} vs.~\emph{wrong (new)} endings, even stronger
-differences were apparent to the model, allowing over 75\% accuracy.}
-
-\resolved{\nascomment{I rewrote this section.  old version commented out in
-  latex source}}
-% In Experiment 1, our model obtains 64.5\%
-% classification accuracy, well above a (50\%-accurate) random baseline.
-% \clinic{How good is this?}
-% \yc{how about addressing above comment from the clinic by adding a
-%   commentary such as following: This result is surprising given that
-%   our model makes the prediction based only on the last sentence
-%   without looking at the story context, thus does not have sufficient
-%   information to judge the story coherency.} 
-% For Experiment 2, our model is even stronger, at 68.5\%.
-% These results indicate that an author's style is affected in an
-% easily-detected way when she is prompted to write (1) a \emph{wrong} story ending vs.~a
-% \emph{right} one, or (2) finishing her own short story vs.~someone else's.
-% %These numbers indicate that these different writing tasks clearly impose different writing styles on authors.
-
-% We further measured whether these style effects are additive, by
-% classifying \emph{original} vs.~\emph{wrong} endings.  The setup is
-% exactly as in Experiment 2, but using \emph{wrong} endings instead of
-% \emph{right} ones.  The result is that the effects are somewhat
-% additive:  this third classifier achieves 75.6\%.
-% % That is, whether the style differences between {\it right} endings and {\it wrong} ones are different from the differences between {\it right} and {\it original} endings.
-% % We repeated Experiment 2, this time comparing between {\it original} and {\it wrong} sentences. 
-% % Our hypothesis is that differences would be even clearer. 
-% % Our results (\figref{results}) show that this is indeed the case: the classifier's accuracy jumps to 75.2\%.
-
- \resolved{
-\begin{figure}
-\begin{tikzpicture}
-\small
-    \begin{axis}[
-        width  = 0.45*\textwidth,
-        height = 4cm,
-      %  major x tick style = transparent,
-        ybar=2*\pgflinewidth,
-       % bar width=14pt,
-        ymajorgrids = true,
-        ylabel = {Classification Performance},
-        symbolic x coords={{\it Correct/Wrong}, {\it Original/New}, {\it Original/Wrong}},
-        xtick = data,
-        scaled y ticks = false,
-        %enlarge x limits=0.25,
-        ymin=0.4,
-%        legend cell align=left,
-%        legend style={
-%                at={(1,1.05)},
-%                anchor=south east,
-%                column sep=1ex
-%        }
-    ]
-        \addplot[style={bblue,fill=bblue,mark=none}]
-            coordinates {({\it Correct/Wrong}, 0.5) ({\it Original/New}, 0.5) ({\it Original/Wrong},.5)};
-
-        \addplot[style={rred,fill=rred,mark=none}]
-            coordinates {({\it Correct/Wrong}, 0.645) ({\it Original/New}, 0.685) ({\it Original/Wrong},0.756)};
-
-        \legend{Random Baseline, Our Model}
-    \end{axis}
-\end{tikzpicture}
-\caption{\label{results}Results of  experiments 1 and 2 (left two charts). 
-Rightmost graph shows a control experiment which classifies {\it
-  original} endings vs \textit{\textbf{wrong}}
-endings. \nascomment{this is overkill.  I suggest replacing it with a
-  table that just shows our model, no baseline, and reiterate in the
-  caption that our setup implies a 50\%-accurate random baseline.
-  Also, I like including the third comparison, but I don't
-  see how it's a ``control.'' }}
-\end{figure}
-}
+were given to perform.
 
@@
 \tabref{cloze_results} shows our results on the story cloze test
-set. Our classifier obtains 72.4\% accuracy, \roy{only 2\% lower than state of the art results, and equal or higher to all other published results}\com{12.5\% (absolute) higher than the
-published state-of-the-art result on the task \cite{Salle:2016}}\resolved{\nascomment{cite that here}}.
-Importantly, unlike previous approaches, our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
+set. Our classifier obtains 72.4\% accuracy, only 2.3\% lower than state of the art results.
+Importantly, unlike previous approaches,\footnote{One exception is the  EndingsOnly system \cite{Cai:2017}, which was published in concurrence with this work, and obtains roughly the same results.} our classifier does not require the story corpus training data, and in fact doesn't even consider the first four sentences of the story in question.
 These numbers further support the claim that the styles of {\it right} and {\it wrong} endings are indeed very different.
 
- \resolved{\nascomment{I suppressed the sentences about the LSDSem shared task;
-  once, in the earlier footnote, is enough.}}
-% Other than the published works that tackled this task, a few  recent works published their results in the LSDSem shared task website.\footnote{\url{https://competitions.codalab.org/competitions/15333}}
-% At the time of submission, our results are still state-of-the-art (though by a  smaller margin). 
-% No other information other than the name of the groups and their results is available.
-\com{
 \begin{table}[!t]
-\begin{center}
-\begin{tabular}{|l|r|} \hline
-{\bf Model} & {\bf Acc.} \\ \hline
-$\dagger${DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
-$\dagger${LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
-%{Niko (shared task)}	& 0.700\\ 
-%{tbmihaylov (shared task)} & 0.711\\ \hline\hline
-$\dagger${RNN}		& 0.677 \\ 
-{\bf Ours} & {\bf 0.724} \\ 
-$\dagger${\bf Combined (ours + RNN)} & {\bf 0.752} \\ \hline\hline
-$\dagger$Human judgment & 1.000 \\ \hline
-\end{tabular}
-\end{center}
-\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}Results on the test set of the  story cloze task. 
-The upper block shows published results, 
-the middle block are our results.
-LexVec results are taken from \cite{Speer:2016}.
-%RNN is our implementation. 
-Human judgement scores are taken from \cite{Mostafazadeh:2016}.
-Methods marked with ($\dagger$) use the story context in order to make a prediction. 
- \resolved{\nascomment{I added 0s to ``Niko'' result
-  and ``human''
-  so sig. digits would line up.  if we don't have sig digits for some
-  of them, make the zeros white so the numbers line up.  where did the
-human judgments come from?  those are not mentioned in our text anywhere!}
-}}
-\end{table}
-}
-
-\begin{table}[!t]
+\small
 \begin{center}
@@
 {tbmihaylov} \cite{Mihaylov:2017} & 0.724\\ 
-{cogcomp}  & 0.744 \\ \hline\hline
+$\dagger$EndingsOnly \cite{Cai:2017} & 0.725 \\
+{cogcomp}  & 0.744 \\ 
+{HIER,ENCPLOTEND,ATT} \cite{Cai:2017} & 0.747 \\\hline\hline
 {RNN}		& 0.677 \\ 
@@
 \end{center}
-\caption{\label{cloze_results}\resolved{\yc{we should change accuracy to be in 0-100\% scale to be consistent with Table 2}}Results on the test set of the  story cloze task.\com{
-The upper block shows published results, }
+\caption{\label{cloze_results} Results on the test set of the  story cloze task.
 The middle block are our results.
 {\it cogcomp} results and human judgement scores are taken from \cite{Mostafazadeh:2017}.
-%RNN is our implementation. 
-Methods marked with ($\dagger$) do not use the story context in order to make a prediction. 
- \resolved{\nascomment{I added 0s to ``Niko'' result
-  and ``human''
-  so sig. digits would line up.  if we don't have sig digits for some
-  of them, make the zeros white so the numbers line up.  where did the
-human judgments come from?  those are not mentioned in our text anywhere!}
-}}
+Methods marked with ($\dagger$) do not use the story context in order to make a prediction.}
 \end{table}
@@
 We investigate whether our model can benefit from state of the art text comprehension models, for which this task was designed. 
-Specifically, we experiment with an LSTM-based \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). % on the ROC story corpus training data,
-%and use it to compute the probability of both {\it right} and {\it wrong} endings in the story cloze test set.
+Specifically, we experiment with an LSTM-based \cite{hochreiter1997long} recurrent neural network language model (RNNLM; \citealp{mikolov2010recurrent}). 
 Unlike the model in this paper, which only considers the story endings, this language model follows the protocol suggested by the story cloze task designers, and harnesses their ROC Stories training set, which consists of single-ending stories,
@@
 gives improvements over our classifier as well as the language
-model.  \resolved{\nascomment{reworded.  more important that our features help
-  the language model, than the other way around!}}
+model.
 
@@
 Using the Adam optimizer \cite{kingma2014adam} and a learning rate of
-$\eta=0.001$, we train to minimize cross-entropy. % minibatches of $50$ stories.
-% h=512, dropout rate of 60%, V=21582, 10% validation set
+$\eta=0.001$, we train to minimize cross-entropy.
 
@@
 
-\resolved{\nascomment{please check the paragraph above.  we need to say how we
-  use the LM before we evaluate it!  also, has anyone tried an approach like this
-  before?  even if we aren't exactly replicating another paper, if
-  someone else used RNNs for this task, we should credit them.}
-  \roy{Ours is the first work to publish LSTM results on this dataset.}}
-
 % Eval
 On its own, our neural language model performs moderately well on the story cloze test. 
-%This is not surprising, as \citet{Mostafazadeh:2016} hinted  that
-%simple language models are insufficient.
 Selecting endings based on $p_\theta(\textrm{ending} \mid \textrm{story})$ (i.e., the numerator of
@@
 information between the story and the ending, under the language
-model.\nascomment{added this to replace the hedging that was here before}\resolved{\roy{We actually also use the RNNLM features in log space. Add that in the next paragraph.}}}
+model.}
 
@@
 our classifier: the numerator, denominator, and ratio in
-Equation~\ref{eq:ratio}, all in log space. % $p_\theta(ending|story),p_\theta(ending)$ and $\frac{p_\theta(ending|story)}{p_\theta(ending)}$.
+Equation~\ref{eq:ratio}, all in log space. 
 We retrain our linear  model with the new feature set, and gain 2.8\%
-absolute, reaching 75.2\%\com{ (15.3\% better than the published state of the art\com{ and 4.1\% better than the best unpublished} result)}\roy{, a new state of the art result for the task.}\resolved{\roy{As now the codalab shared task table contains our numbers, I removed the references to these works, and left only the footnote earlier which says that there are higher, unpublished numbers.}}
+absolute, reaching 75.2\%, a new state of the art result for the task.
 These results indicate that context-ignorant style features can be used to obtain high
 accuracy on the task, adding value even when context and a large
-training dataset are used.  \resolved{\nascomment{check reframing here}}
+training dataset are used.
 
 \isection{Further Analysis}{Ablation}
-
- \resolved{\nascomment{these aren't just ablations, so I retitled}}
 
@@
 
-\com{More interestingly, the different writing tasks seem to impose a specific sentiment on the writer. 
-Three of the top four most salient features for detecting {\it wrong} endings are variants of the verb ``hate''.
-This indicates that when authors are asked to write {\it wrong} text, they tend to use negative language.
-
-An alternative explanation to this hypothesis might be that the first four sentences of the stories in the ROC story corpus tend to be positive, and thus in order to make an ending {\it wrong}, authors adopted a negative approach.
-A similar idea was suggested in the original story cloze paper, where two sentiment-based baselines were evaluated. 
-These baselines measured the relative sentiment between the ending and the previous sentences.
-The performance of both these baselines was roughly chance-level, which seems to suggest that this is not entirely the case.
-\resolved{\yc{Is it really because there's no statistical tendency in the original stories to have happy endings, as opposed to the alternative possibility --- the sentiment classifier used by Monstafazadeh 2016 didn't quite nail down the optimal feature encodings?}} \roy{this is definitely an option, and that's partly why I used hedging (``seems to suggest'').
-Tones it down a bit more.}}
-
-\begin{figure*}
-%\small
+\begin{table*}
 \centering
@@
 }
-%\end{table}
-
-%\end{subfigure}
-\end{figure*}
+\end{table*}
 
 \paragraph{Experiment 2.}
-%In order to understand which features were most salient, we repeated Experiment 1, this time running SVM with L1 norm, such that it generates a sparse separating hyperplane. 
-%This came at a minor cost of less than 2\% in performance compared to our L2 results (0.697 compared to 0.724).  
 \tabref{exp2_features} shows the same analysis for Experiment 2.
 As noted in \secref{ROC_Story}, {\it original} endings tend to be much longer, which is indeed the most salient feature for them.
-%This is in line with similar findings in the deception detection literature \cite{qin2004exploratory}.
 An interesting observation is that exclamation marks are a strong
@@
 Our findings suggest that careful attention must be paid to instructions given to authors, especially in unnatural tasks such as writing a {\it wrong} ending. 
-\roy{The COPA dataset \cite{Roemmele:2011}, which was also designed to test commonsense knowledge, explicitly addressed potential style differences in their instructions.
-In this task,  systems are presented with premises like {\it I put my plate in the sink}, and then decide between two alternatives, e.g.: (a) {\it I finished eating.} and (b) {\it I skipped dinner.}}
+The COPA dataset \cite{Roemmele:2011}, which was also designed to test commonsense knowledge, explicitly addressed potential style differences in their instructions.
+In this task,  systems are presented with premises like {\it I put my plate in the sink}, and then decide between two alternatives, e.g.: (a) {\it I finished eating.} and (b) {\it I skipped dinner.}
 Importantly, when writing the alternatives,  annotators were asked to be as brief as possible and avoid proper names, as well as  slang.
@@
 rather than asking them to generate new text.
-
-\com{
-Another lesson from this paper relates to baseline methods. 
-The authors of the story cloze task experimented with a wide and diverse set of baselines, including n-gram baselines, word embeddings baselines, sentiment baselines, and narrative chain baselines. 
-Nonetheless, running preliminary tests on the data, such as average length or  POS and word distribution,  could have revealed potentially unwanted phenomena in the data.
-\resolved{\nascomment{this paragraph needs extra care.  the authors of the ROC
-  paper did try to control for a lot of things and they did run
-  baselines.  we ought to be generous and reiterate that here.  what,
-  precisely, did they miss?  the lesson isn't just ``run more controls
-  and baselines'' is it?}
-First, it stresses the need to carefully control for even seemingly minor details. 
-Second, it emphasizes the importance of running baseline models.
-While recent advances in NLP  suggest that many classic NLP methods are out-of-date, 
-this is not necessarily the case, especially for small
-datasets. \nascomment{ this bit about simple models feels like a red herring}}
-This is particularly important in order to ensure that  new technological improvements are capturing a qualitatively different signal.
-The substantial improvement we get when combining our model
-with the RNN language model (\secref{Experiments}) suggests that
-despite the high results obtained by the simple model, 
-methods that exploit the wider context  capture a different aspect of the
-task. \resolved{\nascomment{I like ending on this happier note, but let's not
-  call it ``luck'' and let's focus on the task and representations,
-  not the ML methods, which are probably not the heart of the difference}}
-  \roy{Modified this to be more concrete. Did end up hinting that they should have done a better job at analyzing their data before publishing. Feel free to tone down.}
-}
-\resolved{\roy{Commented out the lessons about the importance of running
-  baselines.} 
-\nascomment{that seems like the right choice}}
 
@@
 style \cite{mosteller1963inference,pennebaker1999linguistic,Schwartz:2013}.
-\com{Interestingly, previous work has shown that individual style can be affected from coarse-grained factors such as those just described, but also from other less apparent factors such as mental state, or even living in a high-elevation location \cite{schwartz2013personality}.
-
-Unlike the works just described which compare the writing style
-between different authors, some works have shown that the same author
-can adopt a different style used when writing positive vs.~negative
-text \cite{Davidov:2010} or when writing sarcastic text \cite{Tsur:2010}. In this work, we have shown that the same author can adopt a different style when facing different writing tasks.}
 
@@
 it is often the case that these datasets suffer from methodological
-problems caused by applying noisy automatic tools to generate them \cite{Chen:2016}. 
+problems caused by applying noisy automatic tools to generate them \cite{Chen:2016}.\footnote{Similar problems have been shown in visual question answering datasets, where simple models that rely mostly on the question text perform competitively with state of the art models by exploiting language biases \cite{Zhou:2015,Jabri:2016}.}
 In this paper, we have pointed to another methodological challenge in
@@
 used to generated the data affect writing style, confounding classification problems.
-%, as well as create a discrepancy between the training and the test data.
- \resolved{\nascomment{dropped the train/test discrepancy here}}
 
@@
 writing styles for that author.
-We experimented with the story cloze task, which introduces two interesting comparison points: %setups for our purposes:
-%a setup where the same author writes both a {\it right} and an {\it wrong} ending to a story, 
-%and one which compares an ending written as part of a story to a standalone ending added to a story written by someone else.
+We experimented with the story cloze task, which introduces two interesting comparison points: 
  the difference between writing a story on one's own and continuing someone else's story,
  and the difference between writing a coherent and an incoherent story ending.
-In both cases, a simple linear model reveals measurable differences in writing styles, %that different styles are imposed.
-%The different styles allow our style detection 
+In both cases, a simple linear model reveals measurable differences in writing styles, 
 which in turn allows our final 
@@
 They also provide valuable lessons for designing new NLP datasets.
- \resolved{\nascomment{drop the last sentence, it makes this paper seem less
-  complete} Future work will include testing whether other similar writing tasks, such as fake news, also impose their own unique and identifiable style on their authors.}
 
-% include your own bib file like this:
-%\bibliographystyle{acl}
-%\bibliography{acl2017}
+\section{Acknowledgements}
+This research was supported in part by DARPA under the Communicating with Computers program.
 

### 2017-06-08 docs/shared_task_paper_camera_ready.tex

--- 2017-02-16 docs/shared_task_paper_camera_ready.tex
@@
-\documentclass[11pt]{article}
+\documentclass[a4paper,11pt]{article}
 \usepackage{authblk}
@@
 \usepackage{multirow}
-\usepackage{eacl2017}
-
-\eaclfinalcopy % Uncomment this line for the final submission
-%\def\eaclpaperid{***} %  Enter the acl Paper ID here
 
@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
+\renewcommand{\Authands}{ and }
 % Editing macros
@@
 \definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}
+\newcommand{\isubsectionb}[1]{\subsection{#1}\label{ssec:#1}}
+\newcommand{\secref}[1]{Section~\ref{ssec:#1}}
+
+\usepackage{eacl2017}
+\eaclfinalcopy % Uncomment this line for the final submission
+%\def\eaclpaperid{***} %  Enter the acl Paper ID here
 
 \title{Story Cloze Task: UW NLP System}
-
-\com{
-\author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
-  $^1$Computer Science \& Engineering, University of Washington,
-  Seattle, WA 98195, USA \\
-  $^2$Allen Institute for Artificial Intelligence, Seattle, WA 98103, USA \\
-    {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
-    \And \hspace{-2cm}Leila Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A.~Smith$^1$ \\
-  }
-  }
 
@@
 \author[1]{\bf Ioannis Konstas}
-\author[1]{\bf Leila Zilles}
+\author[1]{\\ \bf Leila Zilles}
 \author[1]{\bf Yejin Choi}
@@
 \maketitle
-\begin{abstract} % This is my real quick try at this lol
+\begin{abstract} 
 This paper describes University of Washington NLP's submission for the Linking Models of Lexical, Sentential and Discourse-level Semantics (LSDSem 2017) shared task---the \textit{Story Cloze Task}.
@@
 \section{Introduction}
-%\ms{note: I don't know if we're emphasizing ``story understanding'' too much, given that we're really not doing that?}
 As an effort to advance commonsense  understanding, \newcite{Mostafazadeh:2016} developed the \textit{story cloze task}, which is the focus of the LSDSem 2017 shared task. 
@@
 In addition to the task, the authors also introduced the {\it ROC story corpus}---a training corpus of five-sentence (coherent) stories. 
-%The goal of the task is to determine which of the endings is the correct one.
-%The goal of this dataset is to serve as a commonsense challenge for NLP and AI research. 
 \tabref{ROC-example} shows an example of a {\it coherent} story and an {\it incoherent} story from the story cloze task.
 
-% Last paragraph should be a quick description of our system.
 In this paper, we describe University of Washington NLP's submission for the shared task.
@@
 %\small
-\begin{tabular}{|p{3.5cm}|p{3.5cm}|} \hline
+\begin{tabular}{|p{3.5cm}|p{3.25cm}|} \hline
 {\bf Story Prefix} & {\bf Ending} \\ \hline
@@
 The right column shows two contrastive endings for the story:
- %of the same story: 
   a {\color{blue}{coherent}} ending (upper row) and a {\color{red}{incoherent}} one (bottom row).
@@
 \end{table}
-\com{
-\section{Task summary}
-% this section helps clarify some of the nomenclature?
-
-The \textit{Story Cloze Task} \cite{Mostafazadeh:2016}, selected as the 2017 LSD Sem Shared Task, aims to test commonsense story understanding.
-Towards that goal, two waves of short story collection were done.
-
-%\ms{Below is mostly copy-pasted from the paper, with a little of editing to remove our langConstraint angle.}
-\paragraph{ROC Stories.}
-The ROC Story Corpus consists of 49,255 five-sentence commonsense stories, collected on Amazon Mechanical Turk (AMT).\footnote{Recently, an additional 53K stories were released, which results in roughly 100K stories.}
-Workers were instructed to write a coherent self-contained story, which has a clear beginning and end. 
-To collect a broad spectrum of commonsense knowledge, there was no imposed subject for the stories,
-which resulted in a wide range of different topics.
-\paragraph{Story Cloze Task.}
-After compiling the story corpus, the {\it Story Cloze Task}---a task based on the corpus---was introduced.
-A subset of the stories was selected, and only the first four sentences of each story were presented to AMT workers.
-Workers were asked to write a pair of new story endings for each story context: a {\it right} one and a {\it wrong} one.
-Both endings are required to complete the story using one of the characters in the story context. 
-Additionally, the ending is required to be ``realistic and sensible'' \cite{Mostafazadeh:2016} when read out of context.
-
-The resulting stories, both {\it right} and {\it wrong}, were then individually rated for coherence and meaningfulness. 
-Only stories rated as simultaneously coherent with a {\it right} ending and neutral with a {\it wrong} ending were selected for the task.
-
-Based on these new stories, the task becomes: given a pair of stories that differ only in their endings, how well can the system determine which ending is {\it right} and which is {\it wrong}?
-
-\subsection{Data}
-For the Shared task, Mostafazadeh, et al. ~(2016)\nocite{Mostafazadeh:2016} split the Story Cloze stories into a development and a test set, each containing $1,871$ stories.
-While the ROC Stories provide data to do unsupervised learning of how stories should end, our goal is to be able to determine whether an ending is the \textit{right} one or the \textit{wrong} one.
-To that extent, we use the development set to train a classifier using features of the individual endings.
-We split that development set (90/10) into training and development.
-The final size of our training/development/test sizes are 3,366/374/3,742 endings, respectively.
-
-It is worth nothing that our classification task is a slightly different take on the {\it Story cloze task}. 
-Instead of classifying pairs of endings, one which is {\it right} and another which is {\it wrong}, we take the set of  {\it right} endings as positive samples and the set of {\it wrong} endings as our negative examples.
-}
 
 \section{System Description}
-%% Explain that we have two sets of features, style and language.
-%% Maybe mention here that we're doing training on validation set ?
 We design a system that predicts, given a pair of story endings, which is the  \textit{right} one and which is the \textit{wrong} one.
@@
 
-\subsection{Features}
+\isubsectionb{Features}
 We use two types of features, designed to capture different aspects of the problem. 
@@
 \paragraph{Language model features.}
-%% take the RLM paragraph from the paper
+
 We experiment with state-of-the-art text comprehension models,
@@
 the expression in Equation~\ref{eq:ratio} gives the pointwise mutual information between the story and the ending, under the language model.}
-%We use these three probabilities as classification features.
 
@@
 We hypothesize that {\it right} and {\it wrong} endings might be distinguishable using style features.
-We adopt features that have been shown useful in the past in tasks such as detection of age \cite{Schler:2006,Rosenthal:2011,nguyen:2011:latech}, gender  \cite{Argamon:2003,Schler:2006,bamman2014gender}, and native language
+We adopt style features that have been shown useful in the past in tasks such as detection of age \cite{Schler:2006,Rosenthal:2011,nguyen:2011:latech}, gender  \cite{Argamon:2003,Schler:2006,bamman2014gender}, and native language
 \cite{Koppel:2005,Tsur:2007,Bergsma:2012}.
@@
 \subsection{Experimental Setup}
+The story cloze task doesn't have a training corpus for the {\it right} and {\it wrong} endings.
+Therefore, we use the development set as our training set, holding out 10\% for development
+(3,366 training endings, 374 for development). We keep the story cloze test set as is (3,742 endings).
+
 We use  Python's sklearn logistic regression implementation with $L_2$
@@
 
-We start by tokenizing the text using the nltk tokenizer.\footnote{\url{www.nltk.org/api/nltk.tokenize.html}} 
+For computing the RNN features, we start by tokenizing the text using the nltk tokenizer.\footnote{\url{www.nltk.org/api/nltk.tokenize.html}} 
 We then use TensorFlow\footnote{\url{www.tensorflow.org}} to train the RNNLM using a single-layer LSTM of hidden dimension 512.
@@
 $\eta=.001$, we train to minimize cross-entropy.
+The resulting RNN features (see \secref{Features}) are taken in log space.
 
-For computing the style features, the story cloze task doesn't have a training corpus for the {\it right} and {\it wrong} endings.
-Therefore, we use the development set as our training set, holding out 10\% for development
-(3,366 training endings, 374 for development). We keep the story cloze test set as is (3,742 endings).
-We add a \textsc{start} symbol at the beginning
+For  the style features, we add a \textsc{start} symbol at the beginning
 of each sentence.\footnote{Virtually all sentences end with a period
@@
  We keep $n$-gram (character or word) features that occur at least five times in the training set.
-All stylistic feature values are normalized to the range [0, 1] \resolved{\nascomment{the
-  range [0, 1] or the two values \{0, 1\}?}}
+All stylistic feature values are normalized to the range [0, 1].
 For the part-of-speech features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
@@
 {LexVec} \cite{Salle:2016} & 0.599 \\ \hline\hline
-%{Niko (shared task)}	& 0.700\\ 
-%{tbmihaylov (shared task)} & 0.711\\ \hline\hline
 {RNNLM features}		& 0.677 \\ 
@@
 there is some information contained in stylistic features, which are slightly less sensitive to content.
-As expected, the RNNLM features complement the stylistic ones, boosting performance by 7.5\% (over the RNNLM) and 2.8\% (over the style features).
+As expected, the RNNLM features complement the stylistic ones, boosting performance by 7.5\% (over the RNNLM features) and 2.8\% (over the style features).
 
@@
 The authors thank the shared task organizers and anonymous reviewers
-for feedback.  \nascomment{anyone else} This research was supported in
-part by the Allen Institute for Artificial Intelligence and in part by
-DARPA under the Communicating with Computers program.
+for feedback. This research was supported in
+part by DARPA under the Communicating with Computers program.
 

### 2017-06-08 docs/language_constraint_conll_camera_ready.tex
fixed the affiliation I think

@@
 \author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
-  $^1$Computer Science \& Engineering, University of Washington, WA 98195, USA \\
+  $^1$Paul G. Allen School of Computer Science \& Engineering, WA 98195, USA \\
   $^2$Allen Institute for Artificial Intelligence, WA 98103, USA \\

### 2017-06-08 docs/language_constraint_conll_camera_ready.tex
fixed the affiliation I think (2)

@@
 \author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
-  $^1$Paul G. Allen School of Computer Science \& Engineering, WA 98195, USA \\
-  $^2$Allen Institute for Artificial Intelligence, WA 98103, USA \\
+  $^1$Paul G. Allen School of Computer Science \& Engineering, University of Washington \\
+  $^2$Allen Institute for Artificial Intelligence\\
     {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\

### 2017-06-09 docs/language_constraint_conll_camera_ready.tex
Noah, not done yet

@@
 %\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
-%\newcommand{\nascomment}[1]{{\color{blue}\textsc{[#1 --nas]}}}
+\newcommand{\nascomment}[1]{{\color{blue}\textsc{[#1 --nas]}}}
 %\newcommand{\clinic}[1]{{\color{magenta}\textsc{[#1 --CLINIC]}}}
@@
 \author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
-  $^1$Paul G. Allen School of Computer Science \& Engineering, University of Washington \\
-  $^2$Allen Institute for Artificial Intelligence\\
+  $^1$Paul G. Allen School of Computer Science \& Engineering,
+  University of Washington, Seattle, WA, USA \\
+  $^2$Allen Institute for Artificial Intelligence, Seattle, WA, USA\\
     {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
@@
 In addition, our style-based classifier's performance on the
-  story cloze challenge is comparable to the state of the art.
+  story cloze challenge is comparable \nascomment{why isn't this stronger?} to the state of the art.
 Our results demonstrate that different task framings can dramatically affect the way people write.\footnote{This paper extends our LSDSem 2017 shared task submission \cite{Schwartz:2017b}.}
@@
 how different kinds of cognitive load influence the style of written language. 
-Second, combined with recent similar findings of \cite{Cai:2017}, our results indicate that when designing new NLP tasks, special attention needs to be paid to the instructions given to authors.
+Second, combined with recent similar findings of \citet{Cai:2017}, our results indicate that when designing new NLP tasks, special attention needs to be paid to the instructions given to authors.
 %both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
@@
 as a commonsense story understanding task, 
-as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017, \citet{LSDSem:2017}), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
+as the shared task for the  Linking Models of Lexical, Sentential and Discourse-level Semantics workshop (LSDSem 2017, \citealp{LSDSem:2017}), and as a testbed for vector-space evaluation \cite{mostafazadeh2016story}.
 
-Interestingly, until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%.
+\nascomment{should this be updated given the shared task, and Gimpel's
+  results?} Interestingly, until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%.
 This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or much shorter periods of time.
@@
   testing instances will be drawn from.
-}  as it contains only positive ({\it right}) samples, and not negative ({\it wrong}) ones.
+}  as it contains only positive ({\it right}) examples, and not negative ({\it wrong}) ones.
 
-On top of that, the {\it original} endings, which serve as positive training samples, were generated differently from the {\it right} endings, which serve as the positive samples in the development and test sets.
+On top of that, the {\it original} endings, which serve as positive training examples, were generated differently from the {\it right} endings, which serve as the positive examples in the development and test sets.
 While the former are part of a single coherent story written by the same author, the latter were generated by letting an author read four sentences, 
@@
 %\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, did we find that in our experiments?}.
-Furthermore, {\it original} and {\it right} endings seem to prefer enthusiastic language (e.g., ``!''), while {\it wrong} endings tend to use more negative language (``hates''), similarly as deceptive text \cite{Newman:2003}.
+Furthermore, {\it original} and {\it right} endings seem to prefer
+enthusiastic language (e.g., ``!''), while {\it wrong} endings tend to
+use more negative language (``hates''), similar to deceptive text \cite{Newman:2003}.
 %\yc{Again, any cogsci literature on this?} \nascomment{feels
@@
 story imposes different style compared to writing a {\it new} ({\it right}) ending to an existing story.
-We use the endings of the ROC stories as our {\it original} samples and {\it right} endings from the story cloze task  as {\it new} samples.
+We use the endings of the ROC stories as our {\it original} examples and {\it right} endings from the story cloze task  as {\it new} examples.
 As there are far more {\it original} instances than {\it new}
@@
 The middle block are our results.
-{\it cogcomp} results and human judgement scores are taken from \cite{Mostafazadeh:2017}.
+{\it cogcomp} results and human judgement scores are taken from \citet{Mostafazadeh:2017}.
 Methods marked with ($\dagger$) do not use the story context in order to make a prediction.}
@@
 \subsection{Most Discriminative Feature Types}
-A natural question that follows this study is which style features are most
+A natural question that follows from this study is which style features are most
 helpful in detecting the underlying task an author was asked
@@
 as is the case in truthful vs.~deceptive text \cite{ott2011finding}.
-Finally, we notice a few syntactic differences: {\it right} endings more often use infinite verb structure, while {\it wrong} endings prefer gerunds (VBG).
+Finally, we notice a few syntactic differences: {\it right} endings more often use infinitive verb structure, while {\it wrong} endings prefer gerunds (VBG).
 
@@
 
-Applying our story cloze classifier to this dataset yields 53.2\% classification accuracy---higher than a random baseline, but substantially lower than our story cloze task results. 
-While this could be partially explained by the smaller data size of the COPA dataset (1,000 samples compared to 3,742 in the story cloze task), this indicates that simple instructions may help alleviate the effects of writing style found in this paper.
+Applying our story cloze classifier to this dataset yields 53.2\%
+classification accuracy---\nascomment{is that actually higher
+  (statistically speaking) than random?  maybe say ``close to a random
+  baseline'' and leave it at that?} higher than a random baseline, but substantially lower than our story cloze task results. 
+While this could be partially explained by the smaller data size of the COPA dataset (1,000 examples compared to 3,742 in the story cloze task), this indicates that simple instructions may help alleviate the effects of writing style found in this paper.
 Another way to avoid such effects is to have people rate naturally occurring sentences  by parameters
@@
 it is often the case that these datasets suffer from methodological
-problems caused by applying noisy automatic tools to generate them \cite{Chen:2016}.\footnote{Similar problems have been shown in visual question answering datasets, where simple models that rely mostly on the question text perform competitively with state of the art models by exploiting language biases \cite{Zhou:2015,Jabri:2016}.}
+problems caused by applying noisy automatic tools to generate them
+\cite{Chen:2016}.\footnote{Similar problems have been shown in visual
+  question answering datasets, where simple models that rely mostly on
+  the question text perform competitively with state of the art models
+  by exploiting language biases
+  \cite{Zhou:2015,Jabri:2016}.}
 In this paper, we have pointed to another methodological challenge in
@@
 
-\section{Acknowledgements}
-This research was supported in part by DARPA under the Communicating with Computers program.
+\section{Acknowledgments}
+The authors thank several anonymous reviewers for helpful feedback.
+\nascomment{anyone else?  who read drafts?} This research was supported in part by DARPA under the Communicating with Computers program.
 

### 2017-06-11 docs/language_constraint_conll_camera_ready.tex
CoNLL camera ready 2.0 (Roy)

@@
 We show that a simple linear classifier informed by stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
-In addition, our style-based classifier's performance on the
-  story cloze challenge is comparable \nascomment{why isn't this stronger?} to the state of the art.
+In addition, %our style-based classifier's performance on the story cloze challenge is comparable \nascomment{why isn't this stronger?} to the state of the art.
+combining our stylistic features with language model predictions reaches state of the art performance on the story cloze challenge.
 Our results demonstrate that different task framings can dramatically affect the way people write.\footnote{This paper extends our LSDSem 2017 shared task submission \cite{Schwartz:2017b}.}
@@
 \begin{table}[!t]
-%\small
-%\begin{tabular}{|p{4.8cm}|p{2.1cm}|} \hline
-%\begin{tabular}{|p{4.8cm}|p{1.9cm}|} \hline
-\begin{tabularx}{\linewidth}%
-{l>{\setlength\hsize{0.67\hsize}}X%
+\begin{tabularx}{\linewidth}
+{l>{\setlength\hsize{0.67\hsize}}X
 >{\setlength\hsize{1.33\hsize}}X}
@@
 
-%Travis needed some fast cash.	He thought about it and decided that selling his car was a good idea.	Travis listed his car for sale in the local paper.	After only a couple weeks he found somebody very interested.}}& \vspace{-0.2cm}	{\color{blue}{{\it This person came and test drove the car and bought it on the spot.}}} \\\cline{2-2}
-%Joe went to college for art. He graduated with a degree in painting. He couldn't find a job. He then responded to an ad in the paper.
-%\vspace{.3cm}Betsy comes home late one night and wants to eat something simple.	She notices that she has spaghetti and sauce in the house.	She quickly cooks and eats a pot of spaghetti.	After eating, she falls asleep on the couch.}} & \vspace{-0.3cm}	{\color{blue}{{\it $<$waiting for examples from  Nasrin$>$}}} \\ \cline{2-2}
-& 	{\color{forestgreen}{\vspace{-0.1cm}The girl found this charming, and gave him a second chance.% He sold the car and solved his money problems.%She was full and happy.     %Then he got hired.
+& 	{\color{forestgreen}{\vspace{-0.1cm}The girl found this charming, and gave him a second chance.
 }} \\ \cline{2-2}
-& {\color{red}{%Joe hated pizza.\vspace{-0.1cm}Betsy likes{\color{white}{0}}{\color{white}{0}}{\color{white}{0}}{\color{white}{0}} cheeseburgers.
-\vspace{-0.1cm}John was happy about being rejected.%Travis gave it to the man for free.
-}} \\\hline %\cline{2-2}
-%&  \\ \hline
+& {\color{red}{
+\vspace{-0.1cm}John was happy about being rejected.
+}} \\\hline 
 \end{tabularx}
@@
 author can lead to measurable differences in her writing style.
-%We explore three  writing tasks, showing that they are distinguishable from one another using a linear classifier informed with stylistic features only. 
-%Our results hint that different writing tasks impose different cognitive load on the writer, which lead to the substantial style differences.
 As a case study, we present experiments   based on 
@@
 In this task, authors were asked to write five-sentence self-contained stories, henceforth {\it original} stories.
-%Following, 
 Then, 
-%the stories were given to other authors, 
 each original story was given to a different author, 
@@
 Second, combined with recent similar findings of \citet{Cai:2017}, our results indicate that when designing new NLP tasks, special attention needs to be paid to the instructions given to authors.
-%both in terms of the potential impact of even the smallest details, and the need to carefully run baseline models.
 Third, we establish a new state of the art result on the commonsense story cloze challenge. 
@@
 We describe the task below.
-
-%For that purpose, \citet{Mostafazadeh:2016} crowdsourced the collection of two types of datasets: the \textit{ROC Stories} and the \textit{Story Cloze test sets}.
 
@@
 The task is simple:  given a pair of stories that differ only in their endings, the system decides which ending is {\it right} and which is {\it wrong}. 
-%The authors published the ROC story corpus as the training data, and the task composed of development and test sets for which both {\it right} and {\it wrong} endings are found. 
 The official training data contains only the original stories (without alternative endings), while development and test data consist of the revised stories with alternative endings (for a different set of original stories that are not included in the training set).
 The task was suggested as an extensive evaluation framework:
-%as a machine reading task, 
 as a commonsense story understanding task, 
@@
 
-\nascomment{should this be updated given the shared task, and Gimpel's
-  results?} Interestingly, until very recently, one year after the task was first introduced, the published benchmark on this task was still below 60\%.
-This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over a similar or much shorter periods of time.
+%\nascomment{should this be updated given the shared task, and Gimpel's results?} 
+Interestingly, only very recently, one year after the task was first introduced, the published benchmark on this task surpassed 60\%.
+This comes in contrast to other recent similar machine reading tasks such as CNN/DailyMail \cite{hermann2015teaching}, SNLI \cite{bowman2015large}, LAMBADA \cite{Paperno:2016} and SQuAD \cite{rajpurkar2016squad}, for which results improved dramatically over similar or much shorter periods of time.
 This suggests that this task is challenging and that high performance is hard to achieve.
@@
 and then asking her to generate a fifth {\it right} ending.
-%This raises the question of whether these different writing setups impose different writing styles. 
-% We show that this is indeed the case.
 
@@
 Although writing {\it wrong} sentences is not the same as deceiving, it is not entirely surprising to observe similar trends in both tasks.
-%Furthermore, \citet{Buller:1996} suggests lying increases one's cognitive load, which in turn could affect sentence length.
-%\yc{Is there psycholinguistic literature that we can cite that may have shown that cognitive burden causes writers to write shorter sentences...?}
 
@@
 Once again, deceptive text is also characterized by fewer pronouns compared to truthful text \cite{Newman:2003}.
-%In contrast, {\it wrong} and {\it right} endings favor proper nouns compared to {\it original} endings.
 
@@
 The figure shows that {\it original} endings use coordinations (``and'') more than  {\it right} endings, and substantially more than {\it wrong} ones. 
-%\ms{\cite{Newman:2003} found that liars use less ``contrast'' coordination, did we find that in our experiments?}.
 Furthermore, {\it original} and {\it right} endings seem to prefer
@@
 use more negative language (``hates''), similar to deceptive text \cite{Newman:2003}.
-%\yc{Again, any cogsci literature on this?} \nascomment{feels
-%  Pennebaker-ish, that might be a good place to look.}
 Next we show that these style differences are not anecdotal, but can
@@
 \subfloat[POS tags]{
-%\begin{subfigure}{.5\textwidth}\center
+
 \begin{tikzpicture}
@@
         height = 4cm,
-      %  major x tick style = transparent,
         ybar=\pgflinewidth,
@@
         ylabel = {Frequency in Corpus (\%)},
-%        symbolic x coords={{\it original}, {\it right}, {\it wrong}},
         symbolic x coords={NN, VBD, PRP, DT, NNP},
@@
         scaled y ticks = false,
-        %enlarge x limits=0.25,
         ymin=3,
-%        legend cell align=left,
-%        legend style={
-%        		legend columns=-1,
-%                at={(1,1.05)},
-%                anchor=south east,
-%                column sep=1ex
-%        }
     ]
@@
 \end{tikzpicture}
-%\caption{
 \label{roc_pos_distribution}
-%}
-%\end{subfigure}
 }
 \qquad\qquad\qquad
-\subfloat[Words]{%\begin{subfigure}{.5\textwidth}\center
+\subfloat[Words]{
 \begin{tikzpicture}
@@
         ymajorgrids = true,
-%        ylabel = {Frequency in Corpus (\%)},
-    %    symbolic x coords={{\it original}, {\it right}, {\it wrong}},
     symbolic x coords={to, and, I, hates, !},
@@
         scaled y ticks = false,
-        %enlarge x limits=0.25,
         ymin=0,
-%        legend cell align=left,
-%        legend style={
-%        		legend columns=-1,
-%                at={(1,1.05)},
-%                anchor=south east,
-%                column sep=1ex
-%        }
     ]
@@
 \end{tikzpicture}
-%\caption{
 \label{roc_word_distribution}
-%Words}
-%\end{subfigure}
 }
@@
 
-To what extent do
- %does constraining authors in their writing assignments lead to them adopting different writing styles. 
-different writing constraints lead authors to adopt different writing styles?
+To what extent do different writing constraints lead authors to adopt different writing styles?
 In order to answer this question, we first use simple methods that have been shown to be very effective for recognizing style (see \secref{Related}).
@@
 \emph{new} instances (3,366 training endings, 374 development endings, and 3,742 test endings).
-%We randomly sample 5 {\it original} sets and repeat the classification experiments.
 We train five classifiers, one with each of the {\it original} training sets, and report the average classification result.
@@
 Applying our story cloze classifier to this dataset yields 53.2\%
-classification accuracy---\nascomment{is that actually higher
-  (statistically speaking) than random?  maybe say ``close to a random
-  baseline'' and leave it at that?} higher than a random baseline, but substantially lower than our story cloze task results. 
+classification accuracy---close to a random baseline. 
 While this could be partially explained by the smaller data size of the COPA dataset (1,000 examples compared to 3,742 in the story cloze task), this indicates that simple instructions may help alleviate the effects of writing style found in this paper.
@@
 \section{Acknowledgments}
-The authors thank several anonymous reviewers for helpful feedback.
-\nascomment{anyone else?  who read drafts?} This research was supported in part by DARPA under the Communicating with Computers program.
+The authors thank several anonymous reviewers for helpful feedback. %\nascomment{anyone else?  who read drafts?} 
+This research was supported in part by DARPA under the Communicating with Computers program.
 

### 2017-06-12 docs/language_constraint_conll_camera_ready.tex
CoNLL camera ready 2.0 (Roy)
ack
ack

@@
 \section{Acknowledgments}
-The authors thank several anonymous reviewers for helpful feedback. %\nascomment{anyone else?  who read drafts?} 
-This research was supported in part by DARPA under the Communicating with Computers program.
+The authors thank Chenhao Tan and several anonymous reviewers for helpful feedback. %\nascomment{anyone else?  who read drafts?} 
+This research was supported in part by Darpa CwC program through ARO (W911NF-15-1-0543), Samsung GRO, NSF IIS-1524371, and gifts from Google and Facebook.
 

### 2017-06-12 docs/language_constraint_conll_camera_ready.tex
comment
CoNLL camera ready -- final

--- 2017-06-11 docs/language_constraint_conll_camera_ready.tex
@@
 \documentclass[11pt,a4paper]{article}
+\usepackage{authblk}
 \usepackage[hyperref]{acl2017}
@@
 %\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
-%\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
+\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
 \newcommand{\nascomment}[1]{{\color{blue}\textsc{[#1 --nas]}}}
@@
 \title{The Effect of Different Writing Tasks on Linguistic Style:\\ A Case Study of the ROC Story Cloze Task}
+\author[1,2]{\bf Roy Schwartz}
+\author[1]{\bf Maarten Sap}
+\author[1]{\bf Ioannis Konstas}
+\author[1]{\\ \bf Li Zilles}
+\author[1]{\bf Yejin Choi}
+\author[1]{\bf Noah A.~Smith}
+\affil[1]{Paul G.~Allen School of Computer Science \& Engineering,\protect\\University of Washington, Seattle, WA, USA}
+\affil[2]{Allen Institute for Artificial Intelligence, Seattle, WA, USA}
+\affil[  ]{\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}
+%\date{}
+\renewcommand\Authands{ and }
 
-\author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
-  $^1$Paul G. Allen School of Computer Science \& Engineering,
-  University of Washington, Seattle, WA, USA \\
-  $^2$Allen Institute for Artificial Intelligence, Seattle, WA, USA\\
-    {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
-    \And \hspace{-2cm}Li Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A.~Smith$^1$ \\
-  }
+%\author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.75cm}Maarten Sap$^1$ \And \hspace{3.5cm}Ioannis Konstas$^1$ \And \\
+%  $^1$Paul G. Allen School of Computer Science \& Engineering,
+%  University of Washington, Seattle, WA, USA \\
+%  $^2$Allen Institute for Artificial Intelligence, Seattle, WA, USA\\
+%    {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
+%    \And \hspace{-2.25cm}Li Zilles$^1$ \And \hspace{-3cm}Yejin Choi$^1$ \And \hspace{-3cm}Noah A.~Smith$^1$ \\
+%  }
 
@@
 We show that a simple linear classifier informed by stylistic features is able to successfully distinguish among the three cases, without even looking at the story context.
-In addition, %our style-based classifier's performance on the story cloze challenge is comparable \nascomment{why isn't this stronger?} to the state of the art.
-combining our stylistic features with language model predictions reaches state of the art performance on the story cloze challenge.
+In addition, combining our stylistic features with language model predictions reaches state of the art performance on the story cloze challenge.
 Our results demonstrate that different task framings can dramatically affect the way people write.\footnote{This paper extends our LSDSem 2017 shared task submission \cite{Schwartz:2017b}.}
@@
 \multirow{4}{*}{\parbox{3.5cm}{\vspace{.1cm}John liked a girl at his work.	He tried to get her attention by acting silly.	She told him to grow up.
-John confesses he was trying to make her like him more.}} & \vspace{-0.2cm}	{\color{blue}{{She feels flattered and asks John on a date.}}} 	 \\\cline{2-2}
+John confesses he was trying to make her like him more.}} & \vspace{-0.2cm}	{\color{blue}{{\bf She feels flattered and asks John on a date.}}} 	 \\\cline{2-2}
 
-& 	{\color{forestgreen}{\vspace{-0.1cm}The girl found this charming, and gave him a second chance.
+& 	{\color{forestgreen}{\vspace{-0.3cm} \it The girl found this charming, and gave him a second chance.\vspace{-0.4cm}
 }} \\ \cline{2-2}
 & {\color{red}{
-\vspace{-0.1cm}John was happy about being rejected.
+\vspace{-0.3cm}\uline{John was happy about being rejected.}
 }} \\\hline 
@@
 Examples of stories from the story cloze task. The table shows a story prefix with three contrastive endings:
-The {\color{blue}{original}} ending, a {\color{forestgreen}{coherent}} ending and a {\color{red}{incoherent}} one.
+The {\color{blue}{\bf original}} ending, a {\color{forestgreen}{\it coherent}} ending and a {\color{red}{\uline{incoherent}}} one.
 }
@@
 
-%\nascomment{should this be updated given the shared task, and Gimpel's results?} 
 Interestingly, only very recently, one year after the task was first introduced, the published benchmark on this task surpassed 60\%.
@@
 \section{Acknowledgments}
-The authors thank several anonymous reviewers for helpful feedback. %\nascomment{anyone else?  who read drafts?} 
-This research was supported in part by DARPA under the Communicating with Computers program.
+The authors thank Chenhao Tan, Luke Zettlemoyer, Rik Koncel-Kedziorski, Rowan Zellers, Yangfeng Ji and several anonymous reviewers for helpful feedback.
+This research was supported in part by Darpa CwC program through ARO (W911NF-15-1-0543), Samsung GRO, NSF IIS-1524371, and gifts from Google and Facebook.
 

### 2017-07-13 docs/language_constraint_conll_camera_ready.tex
Fixed a small reference problem Table 3, as well as a link problem at the end of the introduction

@@
 \usepackage{url}
+\usepackage{breakurl}
+%\usepackage[breaklinks]{hyperref}
 \usepackage{caption}
@@
 {DSSM} \cite{Mostafazadeh:2016} & 0.585 \\ 
-{ukp} \cite{Mihaylov:2017} & 0.711\\ 
+{ukp} \cite{Bugert:2017} & 0.717\\ 
 {tbmihaylov} \cite{Mihaylov:2017} & 0.724\\ 
